### 2023-09-09 manuscript/paper.tex
adding manuscript tex file. beast files changed mostly due to back and forth num tests.

\documentclass[a4paper,prb]{revtex4-1}  %,twocolumn
%\documentclass[preprint]{revtex4-1}

\usepackage{graphicx}  % needed for figures
\usepackage{dcolumn}   % needed for some tables
\usepackage{bm}        % for math
\usepackage{amssymb}   % for math
\usepackage{hyperref}

\usepackage{soul,color}

\usepackage{caption} %For two images side by side
\usepackage{subcaption} %For two images side by side

\usepackage{amsfonts}

\usepackage{amsmath}
%\usepackage{kbordermatrix}
\usepackage{blkarray}
\usepackage{braket}
\usepackage{multirow}
\usepackage{mathtools}

% for figure (Cartoon)
\usepackage{tikz}
\usepackage[utf8]{inputenc}

\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type

\newcommand{\y}{\lambda}
\newcommand{\yp}{\lambda^\prime}
\newcommand{\ph}{\Phi}
\newcommand{\ps}{\Psi}
\newcommand{\w}{E}
\newcommand{\cw}{\Omega}
\newcommand{\dl}{\delta}
\newcommand{\x}{\times}
\newcommand{\llra}{\Longleftrightarrow}
\newcommand{\ep}{\varepsilon}
\newcommand{\sig}{\sigma}
\newcommand{\al}{\alpha}
\newcommand{\be}{\beta}

\newcommand{\eps}{\epsilon}
\newcommand{\wrr}{\Omega_R}

\newcommand{\sx}{\mathcal{\hat S}_0}
\newcommand{\sy}{\mathcal{\hat S}_k}

\newcommand{\N}{\mathcal{N}}
\newcommand{\nb}{N}
\newcommand{\nd}{N_D}
\newcommand{\Nd}{\mathcal{N}_D}
\newcommand{\Nb}{\mathcal{N}_B}

\newcommand{\stt}{\hat{\mathcal{S}}}
\newcommand{\stf}{\hat{\tilde{\mathcal{S}}}}

\newcommand{\ws}{{\omega^\prime}}

\newcommand{\ev}{\hat{\Psi}^+(\w)}

\newcommand{\stket}[1]{{\mathcal{S}_{#1}}}

\newcommand{\nex}{\hat{\mathcal{N}}_{ex}}

\newcommand{\h}{\mathcal{\hat H}}
\newcommand{\z}{\mathcal{Z}_{\alpha}}
\newcommand{\hi}{\hat h_{\alpha}}
\newcommand{\hj}{\mathcal{\hat H}_j}

\newcommand{\hd}{\mathcal{\hat H}_{\Delta}}

\newcommand{\com}[1]{}

%\DeclareMathOperator{\Tr}{Tr}
\DeclareMathOperator{\diag}{diag} 
\DeclareMathOperator{\integer}{integer}
%\DeclareMathOperator{\nd}{and}
\DeclareMathOperator{\eV}{eV}
%\everymath{\displaystyle}

\newcommand{\ad}{\hat{a}^\dagger}
\newcommand{\an}{\hat{a}^{}}
\newcommand{\sd}{\hat{\sigma}^{+}_i}
\newcommand{\sn}{\hat{\sigma}^{-}_i}

\newcommand{\ua}{\uparrow}

\newcommand{\fd}{f(\hat{b}^\dagger)}
\newcommand{\fn}{f(\hat{b}^{})}

\newcommand{\mbf}[1]{\mathbf{#1}}
\newcommand{\del}{\hat{\Delta}^{}}

\newcommand{\fref}[1]{Fig.~(\ref{#1})}
\newcommand{\tref}[1]{Table~\ref{#1}}
\newcommand{\eref}[1]{Eq.~(\ref{#1})}

\newcommand{\rev}[1]{{\color{blue}{#1}}}  
\newcommand{\az}[1]{{\color{magenta}{#1}}} %Ahsan Zeb
\newcommand{\ha}[1]{{\color{red}{#1}}} 
\newcommand{\sm}[1]{{\color{brown}{#1}}}

\newcommand{\Tau}{\mathrm{T}}

\DeclareMathOperator\erf{erf}
\DeclareMathOperator\erfi{erfi}
\DeclareMathOperator\ArcTanh{ArcTanh}
\DeclareMathOperator\sgn{sign}

\newcommand{\ylm}[1]{Y_{#1}(\hat r)}

\def\Xint#1{\mathchoice
   {\XXint\displaystyle\textstyle{#1}}%
   {\XXint\textstyle\scriptstyle{#1}}%
   {\XXint\scriptstyle\scriptscriptstyle{#1}}%
   {\XXint\scriptscriptstyle\scriptscriptstyle{#1}}%
   \!\int}
\def\XXint#1#2#3{{\setbox0=\hbox{$#1{#2#3}{\int}$}
     \vcenter{\hbox{$#2#3$}}\kern-.5\wd0}}
\def\ddashint{\Xint=}
\def\dashint{\Xint -} % \sim

\newcommand\scalemath[2]{\scalebox{#1}{\mbox{\ensuremath{\displaystyle #2}}}}

\begin{document}

\title{Cooperative Jahn-Teller effect with rigid octahedral rotations in perovskites}

%\title{Orbital ordering in perovskites transition metal oxides with rigid octahedral rotations}

\author{Rukhshanda Naheed}
\affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}

\author{M. Ahsan Zeb}
\affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}

\date{\today}
\begin{abstract}

Rigid octahedral rotations in a perovskite structure 
deform the crystal field ... from the symmetric octahedral ...

AB ions: cubic and octahedral cages....
O ions: octahedral cage....
Cubic structure: octahedral fields of AB and O are aligned... oriented 
Tilting and rotation of the O octahedra.... change their relative orientation....
and the the combined field is no more octahedral but has a lower symmetry. 
AB lattice: V: -10 to 17 percent of V of O lattice....
So... it is a strong perturbation to the octahedral field... and couples eg and t2g manifolds... and in lifts their degeneracies....

\end{abstract}
\maketitle

\section{Formalism: Crystal field Hamiltonian using multipole expansion of the crystal field potential}

If we have an arrangement of ions with charge $q$ around a given site,
we can express their (crystal field) potential in terms of spherical harmonics~(see \ref{append:multipoles}), 
\begin{align}
V(\vec r) &= \frac{q}{a}\sum_{lm}V_{l,m}~\left(\frac{r}{a}\right)^l \ylm{l,m},
\end{align}
and calculate the crystal field hamiltonian of the central ion/atom.
Assuming we only have d-orbitals ($l=2$) on the central atom,
the matrix elements of the crystal field Hamiltonian of this system 
are given by,
\begin{align}
H_{m',m''} &= -\frac{q}{a}\sum_{l,m} V_{l,m} C_{l}^{m'm''m} D_{l} ,
\end{align}
where 
$C_{l}^{m'm''m}=\braket{Y_{2,m'}| Y_{l,m}| Y_{2,m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the d-orbitals, assumed to be the same for all d-orbitals, i.e., the radial part of all d-orbitals is assumed to the same~\cite{paxton-notes}.

\subsection{Atom/ion in an octahedral field: $t_{2g}$  and $e_g$ manifolds}
\label{sec:egt2g}
Consider six O ions each of charge $-q_o$ making an octahedron of size $a$ (placed at the face centres of a cube of edge length $a$).
The octahedral field at the centre of the octahedron or cube  
is given by~\cite{pavariniChap},
\begin{align}
\label{eq:voct}
V_{oct}(\vec r) = -\frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right].
\end{align}
%where the monopole and $l>4$ components have been dropped
The crystal field Hamiltonian of a transition metal ion B at the centre 
turns out to be diagonal
and splits the energy levels into two manifolds,
$H_{m,m} = -\Delta/3$ for $m\in\{-2,-1,1\}$ ($xy,yz,zx$ orbitals)
called $t_{2g}$,
and 
$H_{m,m} = +2\Delta/3$ for $m\in\{2,0\}$ ($x^2-y^2,z^2$ orbitals)
called $e_g$.
The crystal field splitting between the two manifolds is
${\Delta=\frac{160}{3}\frac{q_o}{a} D_{4}}$.

\com{
$V_{oct}(\vec r)$ causes the d-orbitals to split into two manifolds,
$t_{2g}$  and $e_g$, where $t_{2g}$ contains three degenerate states ($xy,yz,zx$) while $e_g$ has two degenerate states ($x^2-y^2,z^2$).
The crystal field splitting between the two manifolds is
${\Delta=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
\az{We will see how these degeneracies are lifted as we elongate (or compress)
the octahedron along a ....??}
}

\section{Janh-Teller Effect}

The Jahn--Teller effect~\cite{Jahn-Teller} describes the 
geometric and electronic instability of a %non-linear 
molecule, cluster or crystal with
a symmetric structure and orbitally degenerate ground state
%(i.e., except Kramers degeneracy)
against structural distortions that reduce the symmetry, lift the degeneracy, thereby
lowering the energy of the system.

\subsection{Tetragonal distortion of an octahedron}

Let's consider elongation of an octahedron in sec.~\ref{sec:egt2g} 
along one of its O-B-O bond. 
Align the cartesian axes along O-B-O bonds and stretch the two bonds along z-axis equally by an amount $a\delta$.
%where $a$ is the size of the octahedron (the distance between the O-O along any cartesian axes).
The electric potential at the central B-site (JT ion) of this deformed octahedron can be calculated 
and expanded in terms of (real) spherical harmonics as
\begin{align}
V^{JT}(\vec r) &= \frac{-q_o}{a}\sum_{lm}V_{l,m}^{JT}~\left(\frac{r}{a}\right)^l \ylm{l,m}.
\end{align}
%where the charge on O ion is taken as $-q_o$ ($q_o>0$, for brevity and clarity).
Only few multipole components are non-zero due to their strict symmetries.
The components %$V_{l,m}$ 
up to $l=4$, which are relevant for d-orbitals with $l=2$, are given by
~(see \ref{append:multipoles})
\begin{align}
V_{0,0}^{JT}=& \frac{8 \sqrt{\pi } (2 \delta +3)}{\delta +1},\\
V_{2,0}^{JT}=& -\frac{32 \sqrt{\frac{\pi }{5}} \delta  \left(\delta ^2+3 \delta +3\right)}{(\delta +1)^3},\\
V_{4,0}^{JT}=& \frac{32}{3} \sqrt{\pi } \left(\frac{4}{(\delta +1)^5}+3\right),\\
V_{4,4}^{JT}=& \frac{32 \sqrt{35 \pi }}{3}.
\end{align}
%The d-orbitals are not affected by odd-$l$ components either, here we do not have them anyway.
%(it's non-spherical components)
\rev{$V_{0,0}^{JT}$ rigidly shifts the whole spectrum 
[by $\simeq 4 \sqrt{\pi } (3-\delta )q_o/a$, 
favouring elongation ($\delta>0$) over
compression ($\delta<0$).... filling dependent argumetns... , might confuse??
]
and 
can be assumed to be contributing to the anharmonic part of the elastic energy of the system
that tends to prevent the structural distortion. 
We will ignore it and focus on the shifts and splittings that keep the average of the whole spectrum fixed.
}

\com{
At $\delta=0$, keeping only the non-spherical components, 
we obtain the
 octahedral potential for a symmetric octahedron~\cite{pavariniChap},
\begin{align}
\label{eq:voct}
\lim_{\delta\to0}V^{JT}(\vec r) \to V_{oct}(\vec r) = -\frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right],
\end{align}
}

%\subsection{Crystal Field Splittings}

\az{The deformation $\delta$
will not couple these orbitals to each other either but 
modify the eg-t2g splitting as
${\Delta\to(1-\delta/3) \Delta }$,
and lift the degeneracies, as follows.
...
}
The crystal field Hamiltonian of the central B ion/JT ion
${H_{m',m''}^{JT} = (q_o/a)\sum_{l,m} V_{l,m}^{JT} C_{l}^{m'm''m} D_{l}}$
still turns out to be diagonal,
but the degeneracies of the two manifolds is lifted
and their average energies also shifted.
The $t_{2g}$ now splits into two levels,
with energies
\begin{align}
E_{xy} =&
\frac{32}{7} \left[
\left(1-\frac{1}{(\delta +1)^3}\right) D_2
-
\left(1-\frac{1}{(\delta +1)^5}\right) \frac{20}{9}D_4
\right]\frac{q_o}{a},\\
E_{yz} =& E_{zx} = -3/2 E_{xy},
\end{align}
as measured from their average 
%\begin{align}
$E_0^{t_{2g}} = -64q_oD_4 \left(2+(\delta +1)^{-5}\right)/9a$.
%\frac{64}{9} \left(-\frac{1}{(\delta +1)^5}-2\right) \text{D4}
%\end{align}
Similarly, $e_g$ splits up as
\begin{align}
E_{x^2-y^2}=&\frac{32}{7} \left[\left(1-\frac{1}{(\delta +1)^3}\right) \text{D2}+\frac{5}{3}\left(1-\frac{1}{(\delta +1)^5}\right) \text{D4}\right]\frac{q_o}{a},\\
E_{z^2}=&-E_{x^2-y^2},
\end{align}
measured from their average 
%\begin{align}
$E_0^{e_{g}} = 32 q_oD_4 \left(2+(\delta +1)^{-5}\right)/3a$.
%\frac{32}{3} \left(\frac{1}{(\delta +1)^5}+2\right) \text{D4}
%\end{align}
The crystal field splitting becomes
\begin{align}
\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=\frac{160}{9} \left(\frac{1}{(\delta +1)^5}+2\right) D_4.
\end{align}

At small $\delta$, 
we can expand the above expressions
 up to first order in $\delta$.
 $E_0^{t_{2g}}$, $E_0^{e_{g}}$ and $\Delta$ are rescaled by ${1-5\delta/3}$,
 and we can write
\begin{align}
(E_{xy},E_{yz},E_{zx})&= (2, -1, -1)
%\left[\frac{16}{63} (27 \text{D2}-100 \text{D4})\right]
\left[(D_2-\frac{100}{27}  D_4)\right]\Delta_{\delta},\\
(E_{x^2-y^2},E_{z^2})&=(2,-2)
\left[(D_2+\frac{25}{9} D_4)\right]\Delta_{\delta}
\end{align}
where 
${\Delta_{\delta}= \frac{48}{7}\frac{q_o}{a}\frac{\delta}{a}}$.

\com{
The crystal field splitting becomes
\begin{align}
E_0^{t_{2g}},E_0^{e_{g}},\Delta \to (1-\frac{5}{3}\delta)E_0^{t_{2g}}
E_0^{e_{g}} \to (1-\frac{5}{3}\delta) E_0^{e_{g}}
\Delta \to (1-\frac{5}{3}\delta)\Delta
\end{align}
}

\az{update the numbers,,, and quote realistic values of D2 and D4.}
Note the relative strengths of the two terms with $D_{2}$ and $D_{4}$.
\az{[refine argument]}
Typically, ${D_{2}\approx \sqrt{D_{4}}}$. 
Since
$D_{2}$ and $D_{4}$ are scaled with different 
powers of $a$ ($D_l=\braket{r^l}/a^l$),
their ratio depends on
the octahedron's size, i.e., $D_{2}/D_{4}\propto a^2$.
For well localised d-orbitals in a large octahedron,
${D_{2}/D_{4} > 25/9}$ so that elongation of the octahedron raises $xy$ and lowers $yz,xz$ states.
(Similarly, under such a condition, 
${D_{2}/D_{4} > 20/27}$ is automatically met so
it raises $x^2-y^2$ and lowers $z^2$).
However, if the d-orbitals are extended and octahedron is smaller,
a situation might result where ${20/27 < D_{2}/D_{4} < 25/9}$.
If so,
the ordering of the eg will be reversed as if a compression of the octahedron would have happened.
The extreme case of ${D_{2}/D_{4} < 20/27}$ (that seems less realistic)
would reverse both eg and t2g ordering for a given tetragonal distortion.

So far, we have calculated the changes in the single particle energy levels of the B ion. Whether the deformation would be energetically favourable or not will depend on the number of electrons occupying these levels. The magnitude of the deformation will be determined by a competition between the electronic energy gain and elastic energy required.

An example here a degen and a non degen case:....

\subsection{cooperative JT and orbital order}
just a brief description...

\section{Model and calculations of ABO$_3$ Perovskites}%}

cubic ABO3 crystal Structure... 
rigid rotation/tilting: orthorhombic deformation... 
typically associated with the relative sizes of the A, B,O ions.~\cite{goodenoughPRL05}.

\subsection{Contribution of different ion cages in a cubic perovskite}
\label{sec:relativeVoctABO}

cube of A, octa of B, and octa of O.
%Assuming $q_o=-2$ and charge neutrality, $q_A+q_B + 3q_o=0$.

\com{
\begin{align}
%V_{oct}(\vec r) &= \frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right],\\
V(\vec r) &= V_{O}(\vec r) + V_{A}(\vec r) + V_{B}(\vec r),\\
V_{O}(\vec r) &= V_{oct}(\vec r),\\
V_{A}(\vec r) &= \left(\frac{4}{81 \sqrt{3}}q_A \right)V_{oct}(\vec r),\\
V_{B}(\vec r) &= -\left(\frac{q_B}{64}\right)V_{oct}(\vec r).
\end{align}
It is interesting to note that 
$V_{A}(\vec r)$ and $V_{B}(\vec r)$ have opposite signs
and 
their combined effect
depends on their relative charges and vanishes
as
${q_A\to 1458/({256 \sqrt{3}+243})\simeq 2.124}$
where they cancel each other exactly.
}

\begin{align}
%V_{oct}(\vec r) &= \frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right],\\
V(\vec r) &= V_{O}(\vec r) + V_{AB}(\vec r),\\
V_{O}(\vec r) &= V_{oct}(\vec r),\\
V_{AB}(\vec r) &= f_{q_A}V_{oct}(\vec r),\\
f_{q_A} &= \left(\frac{1}{32}+\frac{8}{81 \sqrt{3}}\right)\frac{q_A}{q_o} -\frac{3}{32},
\end{align}
where we have use the charge neutrality $q_B=3q_o-q_A$ in the last equation.
It is interesting to note that 
$V_{A}(\vec r)$ and $V_{B}(\vec r)$ have opposite signs
and 
their combined effect
depends on their relative charges and vanishes
as
${q_A\to 1458/({256 \sqrt{3}+243})\simeq 2.124}$
where they cancel each other exactly.

Including the contribution of these cages to the crystal field splitting $\Delta$, we obtain

\begin{align}
\Delta &= (1+f_{q_A})\Delta_O,
\end{align}
where
${\Delta_O=\frac{160}{3}\frac{q_o}{a} D_{4}}$.

\com{
\begin{align}
\Delta &= \left\{\frac{29}{32} + \left(\frac{8}{81 \sqrt{3}}+\frac{1}{32}\right)
 \left|\frac{q_A}{q_o}\right|  
\right\}\Delta_O,
\end{align}
}

We see that, relative to the O octahedron,
 the contribution of the
 two cation cages towards the total field splitting
 is relatively small at any $q_A$ but
 still large enough to be ignored.
It can be measured as $\Delta_{AB}/\Delta_O=(\Delta-\Delta_O)/\Delta_O$, 
which linearly changes from 
$-\frac{3}{32}\simeq -10\%$ at $q_A=0$
to $\frac{8}{27 \sqrt{3}}\simeq 17\%$ at $q_A=6$. 
Typical values of $q_A$ relevant for real transition metal oxides
can be safely assumed to range between $0$ and $4$;  
$q_A=0$ for systems like tungsten oxide $WO_3$ that do not have any cations at the A sites,
and $q_A=4$ still contributing just above $8\%$. 
% Delta_AB expression... and plot....
\az{Not just this pot, deformation induces $l=2$ V2m that can couple much more strongly.... bcs of larger D222. 
}

\subsection{Rigid octahedral rotations}

\subsection{Deformation of the crystal structure}

Octahedra rotation, and resulting unit cell changes:\\
bases rotation:\\
\az{Rotation matrices $R$ and $\mathcal{R}$ given in appendix.}

Coordinates of the Oxygen atoms transform according to 
the rotation matrix $R$.
While the d-orbitals basis states attached to the octahedron transform according to
$\mathcal{R}$.

Four adjesent octahedra in two layers along z have to rotate/tilt simultaneously in different directions...

\az{figure vesta structure, label octahedra 1-4.}

We consider a
$\sqrt{2}\times\sqrt{2}\times 2$ unit cell of the cubic structure that transforms
to the unit cell of the orthorhombic structure under octahedral rotation and tilting.
Assuming $\vec a_1,\vec a_2,\vec a_3$ to be the lattice vectors,
two A and two B atoms in a layer are situated at
$(\vec a_1 + \vec a_3/2)/2$, $(\vec a_2+ \vec a_3/2)/2$,
and $(0,0,0)$, $(\vec a_1 + \vec a_2)/2$, 
while similar atoms in the second layer are shifted by $\vec a_3/2$ from these.
While the lattice vectors change under the rotation and tilting of the octahedra, 
these relations do not change.
%The B atom at the origin will be considered as the central JT atom.
The O atoms in the cubic structure lie half way between the B atoms and make octahedral cages around them.
Their positions in the deformed structure (see appendix) are not directly required for our calculations and discussion.

We rotate the octahedra by an angle $\beta$ about $\hat z \equiv 001$
and then tilt it by rotating it about new $110$ by an angle $\alpha$.
Four octahedra have to be rotated and tilted clockwise or counter closckwise
consistently. For example, %$\alpha  \{1,-1,-1,1\}$, $\beta  \{1,-1,1,-1\}$.
$(\alpha,\beta)$,
$(-\alpha,-\beta)$,
$(-\alpha,\beta)$,
$(\alpha,-\beta)$
for the atoms labelled $1$ through $4$ in Fig.~\ref{fig:structure}.
The structure transforms from cubic to orthorhombic under these rotation and tilting of the octahedra.
The lattice vectors of the deformed structure and the positions of A and B atoms can be calculated easily by calculating the coordinates of all six oxygen atoms that make the octahedra (by rotating and tilting the octahedra) for all four octahedra and 
comparing them for different octahedra for the shared atoms.
We obtain
% lattice vectors:
\begin{align}
\left(
\begin{array}{c}
\vec a_1 \\
\vec a_2\\
\vec a_3\\
\end{array}
\right)
= a
\left(
\begin{array}{ccc}
 \cos \beta  & \cos \beta  & 0 \\
 -\cos \alpha  \cos \beta  & \cos \alpha  \cos \beta  & 0 \\
 0 & 0 & 2 \cos \alpha  \\
\end{array}
\right)
\end{align}

\subsection{Deformation of the crystal field}

There are two different ways the crystal field $V(\vec r)$
 is deformed from the ideal case, $V_{voct}(\vec r)$.
\begin{enumerate}
\item The relative rotations of the AB and O frames due to
the rigid rotation and tilting of the oxygen octahedra removes the
choice of a set of d-orbitals where the effect of 
AB and O cages is the same. 
We no longer just get eg-t2g in any frame but with splittings induced by the rotation.
This can generate non-octahedral but still $l=4$ field components. 
\item
The rigid rotation and tilting of the octahedra keeps the octahedra symmetric but deforms the unit cell and AB ionic cages with it.
This not only changes the $l=4$ components but also induces 
$l=2$ field components
that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below).
So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see sec.~\ref{sec:relativeVoctABO}).
\end{enumerate}

Since $V_{O}(\vec r)$ is relatively stronger, 
we can take the octahedra's local frames (that are rotated with them)
to describe the effect of $V_{O}(\vec r)$ first 
(leading to eg-t2g manifolds with a splitting of $\Delta_O$) 
and consider the effect of $V_{AB}(\vec r)$ on these later.
$V_{AB}(\vec r)$ will then couple and mix the orbitals in the two manifolds.
Since $\Delta_AB << \Delta_O$,
we can even ignore the coupling between the states belonging to the 
different manifolds.
This also makes it possible to analytically solve the problem in two limiting cases discussed later.

The total crystal field potential at the central B atom that we consider
 is given by
\begin{align}
V(\vec r) &= V_O(\vec r) + V_{AB}(\vec r),
\end{align}
where
$V_{AB}(\vec r)=V_{A}(\vec r)+V_{B}(\vec r)$
is due to A and B ion cages.
\az{repetition.... cubic case has similar expressions.... }

It is worth reminding that
$V(\vec r) $ a scalar quantity in the position space but a vector 
%$V$ is as a vector %of length $(l_{max}+1)^2=25$ for $l_{max}=4$.
in the spherical harmonics basis, so
we can calculate it in one basis as per our convenience and then transform it to another.
%Its components in the new basis.
\begin{align}
V(\vec r) &= \sum_{l,m} V_{lm} r^l Y_{lm}(\hat r)
= \sum_{l,m} \tilde V_{lm} r^l \tilde Y_{lm}(\hat r),\\
\tilde V_{lm} &= \sum_{l',m'}\mathcal{R}_{lm,l'm'}V_{l'm'},
\end{align}
where 
$\mathcal{R}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics that we use. It can be calculated using the method described in Ref.~\cite{evanic}.

The multipole components of $V_O(\vec r)$ in the rotated frame does not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
These can be read off Eq.~\ref{eq:voct}.
Similarly, its easier to obtain the components of $V(\vec r)^{AB}$
in the unrotated frame so we do that first and later transforms them to obtain the rotated frame components.
That is,
\begin{gather}
\tilde V_{lm} = \tilde V_{lm}^O + \sum_{l',m'}\mathcal{R}_{lm,l'm'} V_{l'm'}^{AB},\\
V_{l'm'}^{AB} = \left(\frac{q_A}{a} \right)V_{l'm'}^{A}   
+ \left(\frac{q_B}{a}\right)V_{l'm'}^{B}.
\end{gather}
%where $q_A + q_B = 3q_o$ ensures charge neutrality.

$\tilde V_{lm}^O$ are simply octahedral field components $l=4,m=0,4$ (see Eq.~\ref{eq:voct}).
However, $V_{lm}^{AB}$ contains the effect of the deformation of the crystal structure on two ion cages due to the octahedral rotations
so it now has not only other $l=4$ components but also $l=2$ components; see below.

\com{
\begin{table}[htp]
\caption{default}
\begin{center}
\begin{tabular}{|L|L|}
\hline
V^A_{2,-2}& 64 \sqrt{\frac{3 \pi }{5}} \cos ^2\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}-\frac{\sec ^3\alpha }{(\cos 2 \beta +2)^{5/2}}\right)\\ \hline
V^A_{2,0}& 32 \sqrt{\frac{\pi }{5}} \left(\frac{2 \sec ^3\alpha  \sin ^2\beta }{(\cos 2 \beta +2)^{5/2}}-\frac{32 \sqrt{\frac{\pi }{5}} (\cos 2 \beta -\cos 2 \alpha )}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}\right)\\ \hline
V^A_{4,-2}& \frac{128}{3} \sqrt{5 \pi } \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right)\\ \hline
V^A_{4,0}& -\frac{16}{3} \sqrt{\pi } \left(\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}\right. \\ 
&+\left. \frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}\right) \\ \hline
V^A_{4,4}&\frac{1}{3} (-128) \sqrt{35 \pi } \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right)\\ \hline

\end{tabular}
\end{center}
\label{default}
\end{table}%
}

\rev{$V(r)=q\sum_{i}(\sqrt{ ..... r\cos... })^{-1}$}

\az{full potential of the charges in deformed cage: manually refined}:
\begin{align}
V^A_{2,-2}&= 64 \sqrt{\frac{3 \pi }{5}} \cos ^2\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}-\frac{\sec ^3\alpha }{(\cos 2 \beta +2)^{5/2}}\right),\\
V^A_{2,0}&= 32 \sqrt{\frac{\pi }{5}} \left(\frac{2 \sec ^3\alpha  \sin ^2\beta }{(\cos 2 \beta +2)^{5/2}}-\frac{32 \sqrt{\frac{\pi }{5}} (\cos 2 \beta -\cos 2 \alpha )}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}\right),\\
V^A_{4,-2}&= \frac{128}{3} \sqrt{5 \pi } \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right),\\
V^A_{4,0}&= -\frac{16}{3} \sqrt{\pi } \left(\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}\right. \\
&+\left. \frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}\right),\\
V^A_{4,4}&=\frac{1}{3} (-128) \sqrt{35 \pi } \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right),
\end{align}

\com{
\begin{table}[htp]
\caption{default}
\begin{center}
\begin{tabular}{|L|}
\hline
V^{B}_{2,-2}=  \frac{64 \sqrt{\frac{3 \pi }{5}} \sin ^2\alpha  \sec ^3\beta }{(\cos 2 \alpha +3)^{5/2}}\\ %\hline
V^{B}_{2,0}=  4 \sqrt{\frac{\pi }{5}} \left(\sec ^3\alpha -\frac{8 \sec ^3\beta }{(\cos 2 \alpha +3)^{3/2}}\right)\\ %\hline
 V^{B}_{4,-2}=  -\frac{128 \sqrt{5 \pi } \sin ^2\alpha  \sec ^5\beta }{3 (\cos 2 \alpha +3)^{7/2}}\\ %\hline
V^{B}_{4,0}= \frac{4}{3} \sqrt{\pi } \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right)\\ %\hline
 V^{B}_{4,4}=  -\frac{16 \sqrt{35 \pi } (-20 \cos 2 \alpha +\cos 4 \alpha -13) \sec ^5\beta }{3 (\cos 2 \alpha +3)^{9/2}}\\ \hline
\end{tabular}
\end{center}
\label{default}
\end{table}%
}

\az{full potential of the charges in deformed cage: }:

\begin{align}
V^{B}_{2,-2}&=  \frac{64 \sqrt{\frac{3 \pi }{5}} \sin ^2\alpha  \sec ^3\beta }{(\cos 2 \alpha +3)^{5/2}},
 \\ V^{B}_{2,0}&=  4 \sqrt{\frac{\pi }{5}} \left(\sec ^3\alpha -\frac{8 \sec ^3\beta }{(\cos 2 \alpha +3)^{3/2}}\right),\\
 V^{B}_{4,-2}&=  -\frac{128 \sqrt{5 \pi } \sin ^2\alpha  \sec ^5\beta }{3 (\cos 2 \alpha +3)^{7/2}},\\ 
V^{B}_{4,0}&= \frac{4}{3} \sqrt{\pi } \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right),\\
 V^{B}_{4,4}&=  -\frac{16 \sqrt{35 \pi } (-20 \cos 2 \alpha +\cos 4 \alpha -13) \sec ^5\beta }{3 (\cos 2 \alpha +3)^{9/2}}
 \end{align}

\com{
$V_{l,m}^{A/B}$ are multipole components
of the potentials ${V_{dipoles}^{A/B}(\vec r;\alpha,\beta)}$ due to the deformation of A/B cages.
We need to include only $l=2,4$ components, $l=0$ uniformly shifts the whole spectrum (and can be taken to be part of the elastic energy of the lattice, as in JT case). [refine these arguments...]
}

\subsection{Crystal Field Hamiltonian}

The Hamiltonian of the central ion (JT ion) including 
the crystal field of the AB cages 
in the octahedron's local frame (rotated frame)
are given by,
\begin{align}
\tilde H_{m',m''} &= \sum_{l,m} \tilde V_{l,m} \tilde C_{l}^{m'm''m} D_{l} ,
%C_{l}^{m'm''m} &= \braket{\tilde Y_{2,m'}|\tilde Y_{l,m}|\tilde Y_{2,m''}},
\end{align}
where %$C_{l}^{m'm''m}$ 
$\tilde C_{l}^{m'm''m}=\braket{\tilde Y_{2,m'}|\tilde Y_{l,m}|\tilde Y_{2,m''}}= C_{l}^{m'm''m}$. 
% are again the Gaunt coefficients for the real spherical harmonics.

%\begin{align}
% bcs ham for electron with charge =-e=-1; sign change here
%\tilde H = \tilde H^O -  q_A \tilde H^A + (3q_o+q_A) \tilde H^B,
%\end{align}

\section{Results: Single particle spectrum and JT instability}

\subsection{t2g manifold} %states and energies}

\az{Focus on t2g:}\\
Let's consider three cases separately, only rotation, only tilting, and both rotation and tilting.

\subsubsection{Only rotation: $\alpha=0,\beta\neq 0$}
If we ignore the coupling between the eg and t2g manifolds (between $xy$ and $x^2-y^2$ at $\alpha=0$[see if it's the same at non zero alhpa?]),
their Hamiltonians turn out to be diagonal.

% from HA
\begin{align}
%\tilde H^A_{xy} =& -2 \Delta_{t2g},~
%\tilde H^A_{yz} = \tilde H^A_{zx} =\Delta_{t2g},\\
% \Delta_{t2g}(\alpha=0,\beta)
%\Delta_{t2g} =&\left( \Delta_{2}  D_2 + \Delta_4 D_4\right),\\
(E_{xy},&E_{yz},E_{zx})= (2, -1, -1)
\left[\frac{}{} \Delta_{2}  D_2 + \Delta_4 D_4\right],\\
\Delta_{l} =&  \left(q_A \Delta_{l}^A + q_B\Delta_{l}^B\right)/a,~(l=2,4),\\
\Delta_{2}^A =& 
%from A
\frac{64 \sin ^2\beta }{7 (\cos 2 \beta +2)^{5/2}},\\ % simplifies.... from:
 %\frac{16 (3 \sin \beta+\sin 3\beta)^2}{7 (\cos 2\beta+2)^{9/2}},\\
\Delta_4^A =&
 \frac{160 \sin ^2\beta}{63 (\cos 2\beta+2)^{9/2}} \times \\
&  (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82),\\
% \Delta_4^A =&
% \frac{160 \sin ^2\beta (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82)}{63 (\cos 2\beta+2)^{9/2}},\\
 %from B
\Delta_{2}^B =& \frac{2}{7} \left(1-\sec ^3\beta\right),\\
  \Delta_4^B =&\frac{5}{126} \left((7 \cos 4\beta-3) \sec ^5\beta-4\right),\\
 %\left( \Delta_{2}  D_2 + \Delta_4 D_4\right),\\
 \end{align}
along with an overall shift
\begin{align}
E_{0} =& \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a,\\
E_{0}^A =&
 \frac{8 (92 \cos 2\beta+24 \cos 4\beta+20 \cos 6\beta+5 \cos 8\beta+51)}{9 (\cos 2\beta+2)^{9/2}},\\
E_{0}^B=&
 -\frac{1}{18} \left((5 \cos 4\beta+3) \sec ^5\beta+4\right),\\
 \end{align}

\begin{align}
\end{align}

Ignoring the coupling between t2g and eg states due to their large energetic difference, we still see that the hamiltonian seems to couple yz and zx if written in terms of multipoles compoments.
 it's only when we substitute Vlm in terms of alpha beta, 
 we see that i

  and since in a degenrate manifold any linear combination can be taken as a valid eigenstate set, we we can take yz and zx as degenerate eigenstates.

$D_2/D_4\simeq 14$ at 
$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)

\az{$D_4=<r^4>=12.005$ at $a=7$ gives normalised $D_4=<r^4>/a^4=1/200$ that gives $\Delta=15/4 (q_o/a)$.}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
\caption{$alpha=0$. 
}
\label{fig:evals-beta}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
\caption{$beta=0$ case, $q_A=q_o/2$}
\label{fig:evals-alpha}
\end{center}
\end{figure}

\rev{

$\eta=\left(\frac{a\Delta_{O}}{q_o}\right)=\frac{4}{15}$
at $D_4=1/200$\\

$a=7$ bohr, and $\braket{r^4}=11.5809$ gives $2eV$ crystal field gap: $D_4=11.5809/a^4=0.004823365264473\simeq0.005=1/200=5\times10^{-3}$,
$D_2=\sqrt{D4}=0.0694503$,
$D_2/D_4\simeq 14$.
}

\az{$D_2/D_4$ ranges between $15$-$20$ for typical gaps of $2$-$1$ eV and $a\simeq 7$ bohr (and $q_o=2e$). 
It decreases with increasing gap as $1/\sqrt(gap)$, but is still $10$ at $gap=3.5$eV.}

\subsubsection{Only tilting: $\alpha\neq 0,\beta = 0$}

The Hamiltonian still has a simple structure, 
\begin{align} 
\tilde H = 
\left(
\begin{array}{ccc}
 E_{xy} & g & -g \\
 g & E_{yz} & \lambda  \\
 -g & \lambda  & E_{yz} \\
\end{array}
\right),
\end{align}
where the matrix elements have relatively long expressions and are can be found in the appendix. An approximation at small $\alpha,\beta$ is given later in this section.

$\tilde H$ can be simplified by rotating the basis in $\{\ket{yz},\ket{zx}\}$ space,
as follows.
\begin{align}
\ket{B} &= \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
\ket{D} &=  (\ket{yz} + \ket{zx})/\sqrt{2}.
\end{align}
The state $\ket{D}$ at energy ${E_D= E_{yz}+\lambda}$ decouples 
from the rest and the state $\ket{B}$ at energy ${E_{yz}-\lambda}$ obtains the enhanced collective coupling $\sqrt{2} g$, 
\com{
\begin{align}
\tilde H_{Bright} = 
\left(
\begin{array}{cc}
E_{xy} & \sqrt{2} g \\
\sqrt{2} g & E_{yz}-\lambda
\end{array}
\right).
\end{align}
The Hamiltonian can be solved analytically.
}
and can be solved analytically to
obtain the 
the eigenstates
\begin{gather}
\ket{+} = \cos\gamma \ket{xy} + \sin\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
\ket{-} = \sin\gamma \ket{xy} - \cos\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
\tan2\gamma = \sqrt{8}g/(E_{xy}-E_{yz}+\lambda)
\end{gather}
at 
energies
\begin{gather}
E_{\pm} = \frac{E_{xy}+E_{yz}-\lambda}{2}  \pm \sqrt{(E_{xy}-E_{yz}+\lambda)^2 + 8g^2 }.
%\delta = E_{xy}-e_z+\lambda.
\end{gather}

Since we are only interested in small tilt and rotation,
an expansion of the matrix elements of the Hamiltonian about 
%${\alpha=0=\beta}$
${\alpha,\beta=0}$
%${(\alpha,\beta)=(0,0)}$
to the leading order turns out to be quite good an approximation.
The matrix elements in this case simplify a lot.
Defining ${Q = -\left( q_A D_2, q_A D_4, q_B D_2,q_B D_4  \right)}$,
 we can write them as
\begin{align}
E_{xy}=& Q.
\left(\frac{64 \alpha ^2}{63 \sqrt{3}},\frac{512 \left(15 \alpha ^2+7\right)}{1701 \sqrt{3}},-\frac{3\alpha ^2}{7} ,-\frac{5 \alpha ^2}{7}-\frac{2}{3}\right)\\
E_{yz}=& Q.
\left(-\frac{32 \alpha ^2}{63 \sqrt{3}},-\frac{512 \left(25 \alpha ^2-7\right)}{1701 \sqrt{3}},\frac{3 \alpha ^2}{14},\frac{85 \alpha ^2}{42}-\frac{2}{3}\right)\\
g=& Q.
\left(\frac{80}{63} \sqrt{\frac{2}{3}} \alpha ^3,0,-\frac{15 \alpha ^3}{14 \sqrt{2}},-\frac{5 \alpha ^3}{2 \sqrt{2}}\right)\\
\lambda=& Q.
\left(-\frac{64 \alpha ^2}{63 \sqrt{3}},\frac{2560 \alpha ^2}{1701 \sqrt{3}},\frac{3 \alpha ^2}{7},-\frac{40 \alpha ^2}{21}\right).
%E_0=& Q.\left(-\frac{16 \alpha ^2}{21 \sqrt{3}},\frac{256 \left(15 \alpha ^2-14\right)}{1701 \sqrt{3}},\frac{9 \alpha ^2}{28},\frac{2}{3}-\frac{45 \alpha ^2}{28}\right),
%Q =& \left( q_A D_2, q_A D_4, q_B D_2,q_B D_4     \right).
%E_0(0,0)=& Q.
%\frac{1}{2} \left(\frac{4 \text{D4} \text{qB}}{3}-\frac{1024 \text{D4} \text{qA}}{243 \sqrt{3}}\right)
\end{align}

$E_D$ and $E_{\pm}$ relative to their average ${E_0= \left(E_{xy} + 2 E_{yz}\right)/3}$
are shown in Fig.~\ref{fig:evals-alpha}.
$E_0$ itself shifts 
with the tilting $\alpha$, 
reflecting 
the change in eg-t2g gap $\Delta$.
This shift in $E_0$ is
%from its value 
%$\frac{D_4}{3} \left(\frac{512q}{81 \sqrt{3}}-2 (6-q)\right)$\\
%$\left(\frac{2}{729} \left(256 \sqrt{3}+243\right) q-4\right)D_4 $
%at $\alpha=0=\beta$, 
also included in Fig.~\ref{fig:evals-alpha}.

\com{
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-0-r}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-1-r}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-2-r}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-3-r}
\caption{d224=11.; norm should be eq to 0.00482334; d222=sqrt d224=0.0694503, d222/d224=14.3988 here. Dark state shuld b labelled, as well as pm states.
update to q=1,3 and analytic... d224norm=0.2?? or update theta0 figs to reduce d224 to 0.005?}
\label{default}
\end{center}
\end{figure}
}

\subsubsection{Rotation and tilting: $\alpha,\beta\neq 0$}

The t2g Hamiltonian in the general case cannot be solve analytically
 so there is no longer any advantage of ignoring the coupling between 
 the eg and t2g manifolds.
We can thus keep these couplings and numerically solve 
the full Hamiltonian instead.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
\caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
\label{default}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
\caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
\label{default}
\end{center}
\end{figure}

\com{
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/q-1-4-alpha-14deg-states-wts-vs-beta}
\caption{eigenstates: weights of xy, yz, zx.}
\label{default}
\end{center}
\end{figure}
}

\subsection{eg manifold}

2x2 system so analytical sol always possible...
either theta or phi 0 givens no couplings but just shifts and eg orbitals stays as the eigenstates....

both theta phi couples the two states..... expressions relatively longer, but, can be approximated by simpler expressions obtained by an expansion about zero angles....

simpler expressions of eigenstates and eigenvalues.... in terms of D2 and D4 terms of A and B.

presentation and discussion of eg splitting...
combined plots for the three cases w.r.t  angles... as three  rows
and two q values on the opposite side of the crossover...
so 2x3 panel figure.

\begin{align}
(H_{x^2-y^2},&H_{z^2}) = (1,-1)
\left[\frac{}{} \Omega_{2}  D_2 + \Omega_4 D_4\right],\\
\Omega_{l} =&  \left(q_A \Omega_{l}^A + q_B\Omega_{l}^B\right)/a,~(l=2,4),\\
\Omega_{2}^A =&  -\frac{64 \left(\alpha ^2 \left(7 \beta ^2+3\right)-6 \beta ^2\right)}{189 \sqrt{3}},\\
\Omega_{4}^A =& \frac{640 \left(\alpha ^2 \left(\beta ^2+16\right)-32 \beta ^2\right)}{1701 \sqrt{3}},\\
\Omega_{2}^B =&  \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right),\\
\Omega_{4}^B =& \frac{1}{168} (-5) \left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right)
\end{align}

\begin{align}
E_0 &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a,\\
E_0^A &=
\frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}}\\
E_0^B &=
(-\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1).
\end{align}

% important, dont delete: H_{x^2-y^2,z^2} in terms of \Lambda_{l}^A/B
% where \Lambda_{l}^A/B are approximated upto second order in alpha beta.  
\com{
\begin{align}
H_{x^2-y^2,z^2}&=
\left[\frac{}{} \Lambda_{2}  D_2 + \Lambda_4 D_4\right],\\
\Lambda_{l} =&  \left(q_A \Lambda_{l}^A + q_B\Lambda_{l}^B\right)/a,~(l=2,4),\\
\Lambda_{2}^A =&
\frac{256 \alpha ^2 \beta }{189},\\
\Lambda_{4}^A =&
-\frac{1}{567} \left(5120 \alpha ^2 \beta \right),\\
\Lambda_{2}^B =&\frac{1}{7} (-4) \sqrt{3} \alpha ^2 \beta ,\\
\Lambda_{4}^B =&\frac{10}{7} \sqrt{3} \alpha ^2 \beta
\end{align}
}

\begin{align}
H_{x^2-y^2,z^2}&=
\frac{2\alpha ^2 \beta}{567} 
\left(128 q_A (3 D_2-20 D_4) - 81 \sqrt{3} q_B (2 D_2 -5 D_4)\right)
%&=\frac{2\alpha ^2 \beta}{567} \left(384 ( D_2-\frac{20}{3} D_4)q_A  - 162 \sqrt{3} (D_2 -\frac{5}{2} D_4)q_B \right)
\end{align}

\com{
\begin{align}
\left(
\begin{array}{cc}
 -\frac{64 \left(\alpha ^2 \left(7 \beta ^2+3\right)-6 \beta ^2\right)}{189 \sqrt{3}} & \frac{640 \left(\alpha ^2 \left(\beta ^2+16\right)-32 \beta ^2\right)}{1701 \sqrt{3}} \\
 \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right) & \frac{1}{168} (-5) \left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right) \\
\end{array}
\right)
\end{align}

\begin{align}
mean=
\left(
\begin{array}{cc}
 0 & \frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}} \\
 0 & -\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1 \\
\end{array}
\right)
\end{align}
}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
\caption{$alpha=10^\circ$ case, $q_A=q_o/2,2q_o$}
\label{fig:e-wts-eg}
\end{center}
\end{figure}

\subsection{Effect of the full lattice}

In a crystal, obviously not only the nearest AB ions matter but other ions at longer distances also participate in the effect described in the prev sec.

We can numerically calculate the multipole components of the potential of the full lattice by following the recipe in Ref.~\cite{PaxtonNotes, book?}
and Ewald summation method~\cite{Ewald}.
To do this, 
we borrow relevant routines from the Tight Binding code TBE [confirm the names] in Questaal~\cite{https://www.questaal.org/} that implements these methods.

First,
FL does not preserve the cubic symmetry of the potential and the degeneracy of the t2g manifold 
is slightly lifted at zero rotations, i.e., for a cubic structure.
However, it is insignificant and we will just ignore it.

What's more important is the ....

Potential of full lattice does not change the qualitative picture.
just shifts  .... so considering only AB cages overestimate or underestimate...

If one renormalises the charges qA and qB, a
quantitative agreement with the full lattice case can be obtained.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/et2g-vs-q-beta-20}
\caption{$alpha=0$ evals vs q at $beta=20$. 
}
\label{fig:evals-q-beta}
\end{center}
\end{figure}

\section{Appendix: Rotation matrices}

\begin{gather}
\nonumber
R=
\left(
\scalemath{0.9}{
\begin{array}{ccc}
 \frac{1}{2} ((\cos \alpha+1) \cos \beta+(\cos \alpha-1) \sin \beta) & \frac{1}{2} (\cos \beta-\sin \beta-\cos \alpha (\cos \beta+\sin \beta)) & \frac{\sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} \\
 \frac{1}{2} (-\cos \alpha \cos \beta+\cos \beta+\cos \alpha \sin \beta+\sin \beta) & \frac{1}{2} (\cos \beta+\cos \alpha (\cos \beta-\sin \beta)+\sin \beta) & \frac{\sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} \\
 -\frac{\sin \alpha}{\sqrt{2}} & \frac{\sin \alpha}{\sqrt{2}} & \cos \alpha \\
\end{array}
}
\right),\\ \nonumber
\com{
\mathcal{R}=
\left(
\scalemath{0.7}{
\begin{array}{ccccc}
 R_{12} R_{21}+R_{11} R_{22} & R_{13} R_{22}+R_{12} R_{23} & \sqrt{3} R_{13} R_{23} & R_{13} R_{21}+R_{11} R_{23} & R_{11} R_{21}-R_{12} R_{22} \\
 R_{22} R_{31}+R_{21} R_{32} & R_{23} R_{32}+R_{22} R_{33} & \sqrt{3} R_{23} R_{33} & R_{23} R_{31}+R_{21} R_{33} & R_{21} R_{31}-R_{22} R_{32} \\
 \frac{-1}{\sqrt{3}}\left(R_{11} R_{12}+R_{21} R_{22}-2 R_{31} R_{32}\right) & \frac{-1}{\sqrt{3}}\left(R_{12} R_{13}+R_{22} R_{23}-2 R_{32} R_{33}\right)  & -\frac{1}{2} R_{13}^2+R_{33}^2-\frac{R_{23}^2}{2} & \frac{-1}{\sqrt{3}}\left(R_{11} R_{13}+R_{21} R_{23}-2 R_{31} R_{33}\right) & 0\\ % identically 0 in our case of specific rotation and tilt.
 %\frac{1}{2\sqrt{3}}\left(-R_{11}^2+R_{12}^2-R_{21}^2+R_{22}^2+2 R_{31}^2-2 R_{32}^2\right) \\
 R_{12} R_{31}+R_{11} R_{32} & R_{13} R_{32}+R_{12} R_{33} & \sqrt{3} R_{13} R_{33} & R_{13} R_{31}+R_{11} R_{33} & R_{11} R_{31}-R_{12} R_{32} \\
 R_{11} R_{12}-R_{21} R_{22} & R_{12} R_{13}-R_{22} R_{23} & \frac{1}{2} \sqrt{3} \left(R_{13}^2-R_{23}^2\right) & R_{11} R_{13}-R_{21} R_{23} & \frac{1}{2} \left(R_{11}^2-R_{12}^2-R_{21}^2+R_{22}^2\right) \\
\end{array}
}
\right),\\
}
\mathcal{R}=
\left(
\scalemath{0.65}{
\begin{array}{ccccc}
 \frac{1}{4} (\cos 2 \alpha+3) \cos 2 \beta & \frac{\sin \alpha (\cos \alpha \cos 2 \beta+\sin 2 \beta)}{\sqrt{2}} & -\frac{1}{2} \sqrt{3} \cos 2 \beta \sin ^2\alpha & \frac{\sin \alpha (\sin 2 \beta-\cos \alpha \cos 2 \beta)}{\sqrt{2}} & \cos \alpha \sin 2 \beta \\
 \frac{\cos \alpha \sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} & \frac{1}{2} (\cos 2 \alpha (\cos \beta-\sin \beta)+\cos \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\sin \beta-\cos \beta) & \frac{1}{2} (\cos 2 \alpha (\sin \beta-\cos \beta)+\cos \alpha (\cos \beta+\sin \beta)) & -\frac{\sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} \\
 -\frac{1}{2} \sqrt{3} \sin ^2\alpha & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & \frac{1}{4} (3 \cos 2 \alpha+1) & -\sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & 0 \\
 \frac{\cos \alpha \sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)-\cos 2 \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\cos \beta+\sin \beta) & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)+\cos 2 \alpha (\cos \beta+\sin \beta)) & \frac{\sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} \\
 -\left(\cos ^2\alpha+1\right) \cos \beta \sin \beta & \frac{\sin \alpha (\cos 2 \beta-2 \cos \alpha \cos \beta \sin \beta)}{\sqrt{2}} & \sqrt{3} \cos \beta \sin ^2\alpha \sin \beta & \frac{\sin \alpha (\cos 2 \beta+\cos \alpha \sin 2 \beta)}{\sqrt{2}} & \cos \alpha \cos 2 \beta \\
\end{array}
}
\right)
\end{gather}

\com{

\begin{align}
\mathcal{R}=&
\left(
\begin{array}{ccccc}
 R_{-1,1} R_{1,-1}+R_{-1,-1} R_{1,1} & R_{-1,0} R_{1,-1}+R_{-1,-1} R_{1,0} & \sqrt{3} R_{-1,0} R_{1,0} & R_{-1,1} R_{1,0}+R_{-1,0} R_{1,1} & R_{-1,1} R_{1,1}-R_{-1,-1} R_{1,-1} \\
 R_{-1,1} R_{0,-1}+R_{-1,-1} R_{0,1} & R_{-1,0} R_{0,-1}+R_{-1,-1} R_{0,0} & \sqrt{3} R_{-1,0} R_{0,0} & R_{-1,1} R_{0,0}+R_{-1,0} R_{0,1} & R_{-1,1} R_{0,1}-R_{-1,-1} R_{0,-1} \\
 -\frac{R_{-1,-1} R_{-1,1}-2 R_{0,-1} R_{0,1}+R_{1,-1} R_{1,1}}{\sqrt{3}} & -\frac{R_{-1,-1} R_{-1,0}-2 R_{0,-1} R_{0,0}+R_{1,-1} R_{1,0}}{\sqrt{3}} & -\frac{1}{2} R_{-1,0}^2+R_{0,0}^2-\frac{R_{1,0}^2}{2} & -\frac{R_{-1,0} R_{-1,1}-2 R_{0,0} R_{0,1}+R_{1,0} R_{1,1}}{\sqrt{3}} & \frac{R_{-1,-1}^2-R_{-1,1}^2-2 R_{0,-1}^2+2 R_{0,1}^2+R_{1,-1}^2-R_{1,1}^2}{2 \sqrt{3}} \\
 R_{0,1} R_{1,-1}+R_{0,-1} R_{1,1} & R_{0,0} R_{1,-1}+R_{0,-1} R_{1,0} & \sqrt{3} R_{0,0} R_{1,0} & R_{0,1} R_{1,0}+R_{0,0} R_{1,1} & R_{0,1} R_{1,1}-R_{0,-1} R_{1,-1} \\
 R_{1,-1} R_{1,1}-R_{-1,-1} R_{-1,1} & R_{1,-1} R_{1,0}-R_{-1,-1} R_{-1,0} & \frac{1}{2} \sqrt{3} \left(R_{1,0}^2-R_{-1,0}^2\right) & R_{1,0} R_{1,1}-R_{-1,0} R_{-1,1} & \frac{1}{2} \left(R_{-1,-1}^2-R_{-1,1}^2-R_{1,-1}^2+R_{1,1}^2\right) \\
\end{array}
\right)
\end{align}

\begin{gather}
\mathcal{R}=
\left(
\scalemath{0.6}{
\begin{array}{ccccc}
 \frac{1}{4} (\cos 2 \alpha+3) \cos 2 \beta & \frac{\sin \alpha (\cos \alpha \cos 2 \beta+\sin 2 \beta)}{\sqrt{2}} & -\frac{1}{2} \sqrt{3} \cos 2 \beta \sin ^2\alpha & \frac{\sin \alpha (\sin 2 \beta-\cos \alpha \cos 2 \beta)}{\sqrt{2}} & \cos \alpha \sin 2 \beta \\
 \frac{\cos \alpha \sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} & \frac{1}{2} (\cos 2 \alpha (\cos \beta-\sin \beta)+\cos \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\sin \beta-\cos \beta) & \frac{1}{2} (\cos 2 \alpha (\sin \beta-\cos \beta)+\cos \alpha (\cos \beta+\sin \beta)) & -\frac{\sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} \\
 -\frac{1}{2} \sqrt{3} \sin ^2\alpha & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & \frac{1}{4} (3 \cos 2 \alpha+1) & -\sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & 0 \\
 \frac{\cos \alpha \sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)-\cos 2 \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\cos \beta+\sin \beta) & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)+\cos 2 \alpha (\cos \beta+\sin \beta)) & \frac{\sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} \\
 -\left(\cos ^2\alpha+1\right) \cos \beta \sin \beta & \frac{\sin \alpha (\cos 2 \beta-2 \cos \alpha \cos \beta \sin \beta)}{\sqrt{2}} & \sqrt{3} \cos \beta \sin ^2\alpha \sin \beta & \frac{\sin \alpha (\cos 2 \beta+\cos \alpha \sin 2 \beta)}{\sqrt{2}} & \cos \alpha \cos 2 \beta \\
\end{array}
}
\right)
\end{gather}

}

\section{Appendix}
\label{append:multipoles}
\sm{
It is worth noting that $V_{l,m}^{A/B}$ can be found without 
evaluating the 
inner products between the spherical harmonics and
$V^{A/B}(\vec r;\alpha,\beta)$.
The latter can be computed 
using the simple textbook formula 
$V^{A/B}(\vec r;\alpha,\beta)=\sum_{i}1/r_i$, $\vec r_i$ is the position of the observation point $\vec r$ (measured from the JT ion/central B ion).
Once we have ${V^{A/B}(\vec r;\alpha,\beta)}$,
$V_{l,m}^{A/B}$ can be calculated by first expanding this potential
in powers of $r$, 
and then expanding the coefficient of $r^l$ 
in powers of $\cos\theta, \cos\phi$ (or $\sin\theta, \sin\phi$; or simply the spherical coordinates $\theta,\phi$ of $\hat r$) 
and comparing the terms with similar 
expansion of the formal expression on the right side of Eq.~\ref{eq:ylm_expansion} to get linear equations in $\{V_{l,m}\}$, and finally solving this system of equations.
The only relevant non-zero components of $V_{l,m}^{A/B}$ are the following.

It is worth noting that $V_{l,m}^{A/B}$ can be found without 
evaluating the 
inner products between the spherical harmonics and
$V^{A/B}(\vec r;\alpha,\beta)$.
The latter can be computed 
using the simple textbook formula 
$V^{A/B}(\vec r;\alpha,\beta)=\sum_{i}1/r_i$, $\vec r_i$ is the position of the observation point $\vec r$ (measured from the JT ion/central B ion).
Once we have ${V^{A/B}(\vec r;\alpha,\beta)}$,
$V_{l,m}^{A/B}$ can be calculated by first expanding this potential
in powers of $r$, 
and then expanding the coefficient of $r^l$ 
in powers of $\cos\theta, \cos\phi$ (or $\sin\theta, \sin\phi$; or simply the spherical coordinates $\theta,\phi$ of $\hat r$) 
and comparing the terms with similar 
expansion of the formal expression on the right side of Eq.~\ref{eq:ylm_expansion}.
The only relevant non-zero components of $V_{l,m}^{A/B}$ are the following.

\subsection{$beta=0$ case: analytical solution:}

$E_{xy},E_{yz},g,\lambda$ all have the same form as 
\begin{align}
X = -\frac{1}{a}\sum_{l=2,4}\left(q_A X^{A,l} + q_B X^{B,l}\right) D_l,
\end{align}
%where $X=E_{xy},E_{yz},g,\lambda$,
where various terms are given in the following.

%\begin{align}
%E_{xy} = -\frac{1}{a}\sum_{l=2,4}\left(q_A E_{xy}^{A,l} + q_B E_{xy}^{B,l}\right) D_l,
%\end{align}
%where $E_{xy}^{A/B,l}$ are given in the following.

%A D2
\begin{align}
E_{xy}^{A,2} =& \frac{4 \left(-72 \cos 2 \alpha -27 \cos 4 \alpha +\sqrt{6} \sqrt{\cos 2 \alpha +5} \left(15 \cos \alpha +\cos 3 \alpha -16 \sec ^3\alpha \right)+99\right)}{63 \left(\cos ^2\alpha +2\right)^{5/2}},\\
E_{yz}^{A,2} =&\frac{144 \cos 2 \alpha +54 \cos 4 \alpha +\sqrt{\frac{3}{2}} (9 \sin \alpha +\sin 3 \alpha )^2 \sqrt{\cos 2 \alpha +5} \sec ^3\alpha -198}{63 \left(\cos ^2\alpha +2\right)^{5/2}},\\
g^{A,2} =&\frac{2 \left(2 \sqrt{3} (\cos 2 \alpha +5)^{5/2}-216 \sqrt{2} \cos ^5\alpha \right) \tan \alpha  \sec \alpha }{63 \left(\cos ^2\alpha +2\right)^{5/2}},\\
\lambda^{A,2} =&\frac{216 \cos 4 \alpha -4 \sqrt{6} (\cos 2 \alpha +3) (\cos 2 \alpha +5)^{5/2} \sec ^3\alpha +3240}{252 \left(\cos ^2\alpha +2\right)^{5/2}},
\end{align}

% A D4
\begin{align}
E_{xy}^{A,4} =& \frac{1}{20412 \left(\cos ^2\alpha +2\right)^{9/2}}
\left[\frac{}{} -330480 \cos 2 \alpha +243 (2964 \cos 4 \alpha +80 \cos 6 \alpha +35 \cos 8 \alpha +5449)\right.\\
&\hspace{4cm} + \left. \sqrt{\frac{3}{2}} (180 \cos 2 \alpha -245 \cos 4 \alpha +513) (\cos 2 \alpha +5)^{9/2} \sec ^5\alpha \right],\\
E_{yz}^{A,4} =& \frac{}{10206 \left(\cos ^2\alpha +2\right)^{9/2}}
\left[660960 \cos 2 \alpha +243 (652 \cos 4 \alpha -160 \cos 6 \alpha -35 \cos 8 \alpha +407)\right.\\
&\hspace{4cm} + \left.\sqrt{\frac{3}{2}} (60 \cos 2 \alpha +245 \cos 4 \alpha -81) (\cos 2 \alpha +5)^{9/2} \sec ^5\alpha \right],\\
g^{A,4} =& \frac{5 \left(31104 \sqrt{2} \cos ^7\alpha  (8 \cos 2 \alpha +7 \cos 4 \alpha +145)-32 \sqrt{3} (\cos 2 \alpha +5)^{9/2} (49 \cos 2 \alpha -9)\right) \tan \alpha  \sec ^3\alpha }{163296 \left(\cos ^2\alpha +2\right)^{9/2}},\\
\lambda^{A,4} =& \frac{1}{10206 \left(\cos ^2\alpha +2\right)^{9/2}}
\left[5 \left(180792 \cos 2 \alpha +243 (212 \cos 4 \alpha +24 \cos 6 \alpha +7 \cos 8 \alpha +37)\right)\right.\\
&\hspace{4cm} + \left.\sqrt{\frac{3}{2}} (12 \cos 2 \alpha -49 \cos 4 \alpha -27) (\cos 2 \alpha +5)^{9/2} \sec ^5\alpha \right],
\end{align}

% B D2
\begin{align}
E_{xy}^{B,2} =& \frac{32 \cos 2 \alpha +24 \cos 4 \alpha -(3 \cos 2 \alpha +1) (\cos 2 \alpha +3)^{5/2} \sec ^3\alpha +72}{7 (\cos 2 \alpha +3)^{5/2}},\\
E_{yz}^{B,2} =&\frac{-32 \cos 2 \alpha -24 (\cos 4 \alpha +3)+(3 \cos 2 \alpha +1) (\cos 2 \alpha +3)^{5/2} \sec ^3\alpha }{14 (\cos 2 \alpha +3)^{5/2}},\\
g^{B,2} =&\frac{3 \left(40 \cos \alpha +20 \cos 3 \alpha -\sqrt{\cos 2 \alpha +3} (12 \cos 2 \alpha +\cos 4 \alpha )+4 \cos 5 \alpha -19 \sqrt{\cos 2 \alpha +3}\right) \tan \alpha  \sec \alpha }{7 \sqrt{2} (\cos 2 \alpha +3)^{5/2}},\\
\lambda^{B,2} =&-\frac{3 \left(8 \cos 2 \alpha +(\cos 2 \alpha +3)^{3/2} \tan ^2\alpha  \sec \alpha -8\right)}{7 (\cos 2 \alpha +3)^{3/2}},
\end{align}

%B D4
\begin{align}
E_{xy}^{B,4} &= \scalemath{0.6}{\frac{1}{42} \left(-\frac{4 (851 \cos 2 \alpha +10 \cos 4 \alpha -35 \cos 6 \alpha +198)}{(\cos 2 \alpha +3)^{7/2}}+19 \sec ^5\alpha -50 \sec ^3\alpha +35 \sec \alpha \right)},\\
E_{yz}^{B,4} &= \scalemath{0.6}{\frac{-3648 \cos 2 \alpha -8 (628 \cos 4 \alpha +120 \cos 6 \alpha +35 \cos 8 \alpha +297)-\frac{1}{2} (20 \cos 2 \alpha +35 \cos 4 \alpha +9) (\cos 2 \alpha +3)^{9/2} \sec ^5\alpha }{84 (\cos 2 \alpha +3)^{9/2}}},\\
g^{B,4} &= \scalemath{0.6}{\frac{5 (5 \sin \alpha +\sin 3 \alpha ) \left(-3024 \cos \alpha -1344 \cos 3 \alpha +216 \cos 7 \alpha +56 \cos (9 \alpha )+(1224 \cos 2 \alpha +676 \cos 4 \alpha +120 \cos 6 \alpha +7 \cos 8 \alpha ) \sqrt{\cos 2 \alpha +3}+21 \sqrt{\cos 2 \alpha +3}\right) \sec ^4\alpha }{672 \sqrt{2} (\cos 2 \alpha +3)^{9/2}}},\\
\lambda^{B,4} &= \scalemath{0.6}{\frac{5}{42} \left(-\frac{32 \sin ^2\alpha  (4 \cos 2 \alpha +7 \cos 4 \alpha +5)}{(\cos 2 \alpha +3)^{7/2}}-(7 \cos 2 \alpha +5) \tan ^2\alpha  \sec ^3\alpha \right).}
\end{align}

\com{
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row}
\caption{$beta=0$ case, $q_A=q_o/2$}
\label{fig:evals-alpha}
\end{center}
\end{figure}
}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-1-D24terms}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-2-D24terms}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-3-D24terms}
\caption{append fig; combine in one plot: $D_2/D_4\simeq 14$ at 
$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
}
\label{default}
\end{center}
\end{figure}

\com{
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.8\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width}
\caption{}
\label{default}
\end{center}
\end{figure}
}

\com{
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0}
\caption{append fig; combine in one plot: $D_2/D_4\simeq 14$ at 
$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
}
\label{default}
\end{center}
\end{figure}
}

\com{
\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-3-r}
\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-3-r}
\caption{append fig; combine in one plot: $D_2/D_4\simeq 14$ at 
$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
}
\label{default}
\end{center}
\end{figure}
}

}

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{System and Model}
System: perovskites ABO3;
Full model = lattice;
Toy model = cages;

\section{Analytical Results}
phi rotations; 2x2 solutions;\\
theta/phi rotations; approx 2x2 
\subsection{Violation of Jahn-Teller Theorem}
\section{Numerical Results}
Exact numerics cages [cubic];;; exact lattice [with a,b,c lattice constants]; 
\section{Effect of SOC}

\begin{figure}
\centering
%\includegraphics[width=0.5\linewidth]{cartoon}
\caption{
}
\label{fig:cartoon}
\end{figure}

 %\end{document}
\label{Bibliography}
\bibliographystyle{apsrev4-1}
%\bibliography{References}

\end{document}

\com{
$V_{oct}(\vec r)$ causes the d-orbitals to split into two manifolds,
$t_{2g}$ ($xy,yz,zx$) and $e_g$ ($z^2,x^2-y^2$)
by an amount
${\Delta_{CF}=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
The deformation and resulting $V_{dipoles}(\vec r)$
will lift the degeneracies as follows.
\begin{align}
(dE_{xy},dE_{yz},dE_{zx})&= \Delta_{\delta}
\left[(2, -1, -1)D_{2} +\frac{20}{9} 
 (-1, 4, 4) D_{4}\right],\\
(dE_{x^2-y^2},dE_{z^2})&=\Delta_{\delta}
\left[(2,-2)D_{2} +\frac{20}{9} 
 (-1,-6)D_{4}\right],\\
\Delta_{\delta}&= \frac{96}{7}
\frac{-q_o}{a}
\frac{\delta}{a}.
\end{align}
}

\begin{align}
u&=\frac{1}{4} (2+\cos\beta+\cos\alpha \cos\beta),\\
v&=\frac{1}{4}
\cos\beta(1-\cos\alpha),\\
w&=\frac{1}{2} (1+\cos\alpha),\\
x&=-1+\frac{1}{2} (1+\cos\alpha) \cos\beta,\\
\{x\to 2 (u-1),y\to 2 v,z\to 2 (w-1)\},\\
\{d\to -1+2 \sigma ,e\to -1+2 \tau ,f\to 1+2 \mu ,g\to 1-2 \tau ,h\to 1-2 \sigma \}
%y&=2v=\cos\beta \frac{1}{2} (1-\cos\alpha),\\
%z&=2(w-1)=-1+\cos\alpha.
\end{align}
we obtain the following expressions for $V_{l,m}^B$.
\begin{align}
V_{2,-2}^B &=8\sqrt{\frac{3 \pi }{5}} \frac{v \left(2 u^3-4 u^2 x-8 u v^2+v^2 x\right)}{\left(u^2+v^2\right)^{7/2}},\\
V_{2,0}^B &=12 \sqrt{\frac{ \pi }{5}} \left(\frac{u x+2 v^2}{\left(u^2+v^2\right)^{5/2}}-\frac{2(w-1)}{w^4}\right),
\end{align}
where all other $V_{2,m}^B= 0$.
Similarly,
$l=4$ components are,
\begin{align}
V_{4,4}^B&= -\frac{\sqrt{35 \pi }}{3}\frac{\left(5 u^5 x+42 u^4 v^2-46 u^3 v^2 x-92 u^2 v^4+21 u v^4 x+10 v^6\right)}{\left(u^2+v^2\right)^{11/2}},\\
V_{4,-2}^B&= -\frac{4\sqrt{5\pi}}{3}\frac{ v \left(-2 u^3+6 u^2 x+12 u v^2-v^2 x\right)}{\left(u^2+v^2\right)^{9/2}},\\
V_{4,0}^B&=-\frac{5\sqrt{\pi }}{3}  \left(\frac{3 \left(u x+2 v^2\right)}{\left(u^2+v^2\right)^{7/2}}+\frac{8(w-1)}{w^6}\right),
\end{align}

\com{
\begin{align}
\tilde V(\vec r) &=\tilde V_O(\vec r) + \tilde V_{AB}(\vec r),\\
\tilde V_O(\vec r) &= \tilde V_{oct}(\vec r),\\
\tilde V_{AB}(\vec r) &= \mathcal{R}(\alpha,\beta) V_{AB}(\vec r),\\
V_{AB}(\vec r) &= f(q_A) V_{oct}(\vec r) + 
V_{dipoles}^{AB}(\vec r;\alpha,\beta),\\
\label{eq:ylm_expansion}
V_{dipoles}^{AB}(\vec r;\alpha,\beta) &= 
\sum_{l=2,4}\sum_{m=-l}^{l}\left[V_{l,m}^{A}(\alpha,\beta)+V_{l,m}^{B}(\alpha,\beta)\right] r^l Y_{l,m}(\hat r),\\
\tilde V(\vec r) &= \sum_{l,m} \tilde V_{l,m} r^l \tilde Y_{l,m}(\hat r),\\\end{align}
\az{fix inconsistencies... in above equations.. R matix apply on a vector,,,, not a function.}.
}

### 2023-09-09 src/estatic.f90

@@ -288,6 +288,7 @@ integer :: i,j
  call scg(9,cg,indxcg,jcg)
  call makcg9(indxcg,jcg,cg,gaunt,ak)
 
+ if(1==0) then
  open(190,file='gaunt.dat',action='write')
 	do i=1,9
 	 do j=1,9
@@ -295,7 +296,7 @@ integer :: i,j
 	 enddo
 	enddo
  close(190)
-
+	endif
  
  !write(*,*)'Gaunt calculated.... '
  !write(*,'(a,100f10.3)') 'cg(1:100) = ', cg(1:100)

### 2023-09-09 src/esvar.f90

@@ -15,6 +15,7 @@ double precision, dimension(1:25,1:25,4) :: Rlmax ! up to l=4; rotation matrix f
 logical :: cage
 double precision :: qaa, fVoctO, fVoctAB
 
+double precision, dimension(5:9,5:9,3) :: B1hams
 
 !nbas,nsp,nl,nlmq,s_pot%qnu,s_ctrl%ipc,lmxl,gaunt,qpol,rho,rhoc,qmpol,mmom
 integer :: nbas, nsp, nclass

### 2023-09-09 src/fermi.f

@@ -54,9 +54,9 @@ C Local variables
 	integer        :: ik
 	integer        :: ispin
 	integer        :: iter
-	integer,  save :: nitmax = 150
+	integer,  save :: nitmax = 200
 	logical,  save :: blread = .false.
-	double precision, save :: tol = 1.0d-10
+	double precision, save :: tol = 1.0d-8
 	double precision:: sumq, emin, emax, t, drange, wkebuf, w, eik
 	double precision :: tbnspn
 

### 2023-09-09 src/hamiltonian.f

@@ -555,35 +555,6 @@
 !----------------------------------------------------------------
 
 
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
-
 ! 
 ! Seperate Hamiltonian for all TM atoms
 ! so that local eigenvalues and eigenvectors can be analysed easily. 
@@ -601,28 +572,84 @@
 	  is = atom2species(ia);
 
 	  ! Crystal field/Madelung: the same atm%dh for either spin.
-	  	tm(il,io)%ham(1:5,1:5,io,il) = atm(ia)%dh
-	  	tm(il,io)%ham(6:10,6:10,io,il) = atm(ia)%dh
+	  	tm(il,io)%ham(1:5,1:5) = atm(ia)%dh
+	  	tm(il,io)%ham(6:10,6:10) = atm(ia)%dh
 
 		!write(*,*) 'hamiltonian: il,io,dh = ',il,io,atm(ia)%dh
 		
 		! onsite energy
-		e0 = dcmplx(onsite(is),0.0d0)
-		do i=1,10
-	   tm(il,io)%ham(i,i,io,il) = tm(il,io)%ham(i,i,io,il) + e0
-	  end do
+		!e0 = dcmplx(onsite(is),0.0d0)
+		!do i=1,10
+	  ! tm(il,io)%ham(i,i) = tm(il,io)%ham(i,i) + e0
+	  !end do
 	  
 	  ! spin-orbit coupling
-	  tm(il,io)%ham(:,:,io,il)= tm(il,io)%ham(:,:,io,il) +soc(is)*Hsoc
-
-	 !write(*,*) 'getHtms:================='
-	 !write(*,'(10f8.3)') dble(tm(il,io)%ham(:,:,io,il))
+	  tm(il,io)%ham(:,:)= tm(il,io)%ham(:,:) +soc(is)*Hsoc
 	 
 	  end do ! io
 	 end do ! il
 
 	return
 	end 	subroutine getHtms
+!----------------------------------------------------------------
+
+
+
+
+! 
+! Seperate Hamiltonian for all TM atoms
+! so that local eigenvalues and eigenvectors can be analysed easily. 
+!----------------------------------------------------------------
+	subroutine getHtmsUJ(iscf)
+	implicit none
+	integer, intent(in) :: iscf
+	integer :: is,ia
+	integer :: il,io,ii,i
[…]

### 2023-09-09 src/hubbard.f90

@@ -43,6 +43,9 @@ integer :: i1,i2,i3,i4, is
 double precision :: sum1
 double precision, parameter :: fourpi=12.566370614359172954d0
 
+
+!write(*,*)'Hubb: F(k): ', Hub(1)%Fk(:)
+
 do m1=-l,l
   i1 = l+m1+1
   do m2=-l,l
@@ -199,6 +202,110 @@ end subroutine mkvmat
 
 !======================================================================
 
+!======================================================================
+! Hubbard interaction: for TM-only case: when we solve tm atoms separately:
+!======================================================================
+! calculates density matrices of tm atoms in their d-orbital-spin space
+! calculates electron-electron interaction potential matrices for all atoms
+! also calculates magnetisation of tm atoms
+! IN: global evec & wke ( & global Uz, Ur, and a lot of other indexing arrays, and sizes, etc.. )
+subroutine mkvmattm(iscf, il, io, is, evec, wke, edu) ! ddm,
+implicit none
+integer, intent(in) :: iscf, il, io, is
+double complex, dimension(10, 10), intent(in) :: evec
+double precision, dimension(10), intent(in) :: wke
+double precision, intent(out) :: edu ! ddm
+integer :: i,j,i1,i2, j1,ist, i3, i4, ia, ispin,jspin
+double complex, dimension(norbtm, nspin) :: wf
+double complex, dimension(norbtm, nspin,norbtm, nspin) :: dm, dmc !dm in real, compelx Ylm
+double complex, dimension(norbtm, nspin,norbtm, nspin) :: vmat, vmatc
+double precision, dimension(3) :: mag
+double precision :: edua
+!logical, save :: first = .true.
+
+!ddm = 0.0d0
+edu = 0.0d0;
+edua = 0.0d0;
+momtot = 0.0d0
+
+	!...............................................................
+	! calculate dm
+	!...............................................................
+	dm = 0.0d0;
+   do ist=1, 10
+    wf = 0.0d0
+    wf(1:norbtm,1) = evec(1:5,ist) ! assuming eigenvec in columns
+    wf(1:norbtm,2) = evec(6:10,ist)
+    dmc = 0.0d0;
+    do j=1,norbtm
[…]

### 2023-09-09 src/main.f

@@ -6,8 +6,9 @@
 	use readinput
 	use fermi
 	use modgaunt, only: mkdgaunt
-	use Hubbard, only: mkvee, mkvmat
-	use scf, only: groundstate, nscfgroundstate, tmgroundstate
+	use Hubbard, only: mkvee, mkvmat, rtozflm
+	use scf, only: groundstate
+	use scf, only: nscfgroundstate, tmgroundstate, tmscfground
 	use pdos
 
 	use estatic, only: setmadvar, initmadelung
@@ -62,6 +63,11 @@
 	! write GEOMETRY.OUT for visualisation with VESTA
 	call writegeom()
 
+	if(1==0) then
+	open(111,file='avecs.dat',action='write',position='append')
+	write(111,'(9G18.10)') avec(:,1),avec(:,2),avec(:,3)
+	close(111)
+	endif
 	!call writegeomxsf()
 	!write(*,*)'-------------------- 1'
 	
@@ -108,6 +114,21 @@
 	! sets some basis transformation matrices:
 	! some condition? inside an if block?
 	call setUrUz() ! sets Uz and Ur matrices
+
+	if (ham4edrixs) then ! assuming SOC is not incuded.
+
+	 !call mkhsocl2()
+	
+	 if(lcage) then
+	  call getvmdhcage4edrixs()
+	 else
+	  call getvmdhlat4edrixs()
+	 endif
+
+	 call writeB1ham4edrixs()
+	 stop
+	endif
+
 	call setUlm2j() ! sets Ulm2j, uses Ur that is set in setUrUz() call above.
 
 
@@ -117,6 +138,7 @@
 	! spin-orbit coupling universal hamiltonian in full d-orbital space of a TM atom
 	call mkhsocl2()
 
+	if(1==0) then
 	open(100,file='Hsoc.dat', action='write')
 	 do i=1,10
 	  write(100,'(10f6.2)') dble(Hsoc(i,:))
@@ -125,7 +147,7 @@
 	  write(100,'(10f6.2)') dimag(Hsoc(i,:))
 	 end do
 	close(100)
-
+	endif
 
 	! testing 
 	if (1==0) then
@@ -167,10 +189,17 @@
 
 	 if(lgs) then
 		 if (lscf) then
-	    call groundstate()
+		  if (ltmgs) then
+		   call tmscfground()
+		 	 write(*,*)'main: TM SCF ground state calculated!'
[…]

### 2023-09-09 src/modmain.f

@@ -42,6 +42,10 @@
 	! Del112 for Oxygen & Del222, Del224 for TM
 	double precision :: Del112, Del222, Del224
 
+	logical :: ham4edrixs
+	!double precision, dimension(5:9,5:9,3) :: B1hams
+	
+
 	logical :: lesH, lscf,ltmgs ! electrostatic interaction in Hamiltonian
 	integer :: maxscf ! max scf iterations
 	double precision :: toldm ! = 1.0d-6
@@ -181,7 +185,7 @@
 	 double precision, dimension(3):: mfix	! fixed spin moment
 	 double precision, dimension(3):: beff ! effective, sum of all types of bfields
 	 double precision, dimension(3):: bext	! external magnetic field at TM site
-	 double complex, allocatable, dimension(:,:,:,:):: ham ! local ham of TM atoms	 
+	 double complex, dimension(10,10):: ham ! local ham of TM atoms	 
 	end type tmatoms
 
 	type(tmatoms), allocatable, dimension(:,:) :: tm ! TM
@@ -1766,6 +1770,9 @@ C *********************************************************************
 	
 	Uz = conjg(transpose(Ur));
 
+	!write(*,'(a)') 'matmul(Uz.Ur) = '
+	!write(*,'(10f5.2)') matmul(Uz,Ur)
+
 	if(1==0) then
 	! r_{0} in z basis
 	ab = 0.0d0; ab(3,3)=1.0d0; !matmul(Uz,Ur)
@@ -1857,10 +1864,10 @@ C *********************************************************************
 !	end 	subroutine setupdm
 !======================================================================
 
-	subroutine setFk(is,U,J,fac)
+	subroutine setFk(is,fac) !U,J,
 	implicit none
 	integer, intent(in):: is
-	double precision, intent(in):: U,J,fac
+	double precision, intent(in):: fac !U,J,
 	double precision:: r1
 	  	 Hub(is)%fk(:) = 0.0d0
 	   Hub(is)%fk(0)=Hub(is)%U * fac
@@ -1869,7 +1876,6 @@ C *********************************************************************
 	   Hub(is)%fk(2)=(14.d0*Hub(is)%J*fac)/(1.d0+r1)
 	   Hub(is)%fk(4)=Hub(is)%fk(2)*r1
 	end 	subroutine setFk
-
 
 
 

### 2023-09-09 src/readinput.f

@@ -28,7 +28,7 @@
 	logical :: file_exists
 	integer :: il,i,j
 
-	integer :: ios, is, maxsp
+	integer :: ios, is, maxsp, ion_d
 	double precision :: r1, delB, DelO
 
 	!From monopoles ionic crystal, with d^0 ionic config of TM atoms,
@@ -37,6 +37,8 @@
 	DelB = 1.8376130 ! Hartree
 
 	lcage = .false.
+
+	Ham4EDRIXS = .false.
 	
 	ewalda = 1.d-7; !50.0d0 ! at the moment, k-space sum is discarded so welda has to be infinitesimal to make real space sum equal to the actual sum. of course, this also needs a larger n_r for the convergence! ewaldnr > 5 is okay, converged to 2 decimal palces for NaCl structure, calculated Madelung ==> 1.7457834017323322; converged  is 1.747565 which requires ewaldnr~30.
 	
@@ -166,6 +168,22 @@
 	case('TiltRotation')
 	   read(50,*,err=20) theta !, phii
 			phii = theta
+
+	case('RunBeastParam') ! qA, lam, d222, phi, theta
+	! assuming that this flag will be at the end of the file so that its 
+	! var are already allocated (soc) and never overwritten.
+	   read(50,*,err=20) Hub(1)%U, Hub(1)%J, ion_d, 
+     .                   qA, soc(1), Del222, phii, theta
+	   soc(1) = soc(1)*eV2Har
+	   Dcf(5,2) = Del222
+	   nds(1) = (6-qa) + ion_d
+	  ! set Hub%Fk and allocate Hub%Vee
+	  call 	setFk(1, eV2Har) !Hub(1)%U,Hub(1)%J,
+
+	case('Ham4EDRIXS') ! T/F?, cages?, qA, phi, theta
+	! assuming that this flag will be at the end of the file so that its 
+	! var are never overwritten.
+	   read(50,*,err=20) Ham4EDRIXS, lcage, qA, phii, theta
 			
 	case('Bfield')
 		read(50,*,err=20) bfieldc(1:3)
@@ -216,7 +234,7 @@
 
 	case('CalculationType','Hes')
 	 read(50,*,err=20) lesH, lscf, ltmgs 
-	 if(ltmgs) lscf = .false.
[…]

### 2023-09-09 src/scf.f90

@@ -16,8 +16,6 @@ implicit none
 
 contains
 
-
-
 !=====================================================================
 subroutine tmgroundstate()
 implicit none
@@ -39,27 +37,22 @@ open(805,file='evecs-tm.dat',action='write',position='append')
  ! Hamiltonian, eigenstates and eigenvalues: on kgrid in BZ
  !-------- -------- -------- -------- -------- -------------- 
 
- do il=1,nlayers
-  do io=1, noctl
-   if(.not. allocated(tm(il,io)%ham)) allocate(tm(il,io)%ham(10,10,2,nlayers))
-	end do
- end do
-
  call getHtms()
+ !write(*,*) '100 * h_B1: --------------------'
+ !write(*, '(20f15.6)') 100*tm(1,1)%ham(:,:) ! evec
 
- do il=1,nlayers
-  do io=1, noctl
+ do il=1,1 !nlayers
+  do io=1,1 ! noctl
    ia = tm(il,io)%ia;
 	 is = atom2species(ia);
 
-	 ham = tm(il,io)%ham(:,:,io,il)
+	 ham = tm(il,io)%ham
 	 !write(*,*) '------------'
 	 !write(*,'(10f8.3)') dble(ham)
 
-
    call zdiag(10,ham,eval,0,10)
 
-	 write(804,'(10f18.12)') eval
+	 write(804,'(10f18.12)') eval* 27.21138505d0 ! *1/eV2har
 	 write(805,*) ham ! evec
 
   end do ! io
@@ -68,12 +61,6 @@ open(805,file='evecs-tm.dat',action='write',position='append')
  close(804)
  close(805)
 
- do il=1,nlayers
-  do io=1, noctl
-   deallocate(tm(il,io)%ham)
-	end do
- end do
-
 return
 end subroutine tmgroundstate
 !=====================================================================
@@ -81,6 +68,212 @@ end subroutine tmgroundstate
 
 
 
+
+!=====================================================================
+subroutine tmscfground()
+implicit none
+double precision, dimension(10) :: eval, r
+double precision :: ddm, engyadu, ebands, engyes, energyb, edu
+double complex, dimension(10,10) :: ham
+double precision :: qtm
[…]

### 2023-09-09 src/tbeseld.f90

@@ -1,7 +1,7 @@
  module mtbeseld
  use esvar, only: nsp, nbas, nlmi, ll, ilm12, atm, struxd, & 
                   qmpol, CFM, gaunt, nbasA, struxdA, qmpolA, s_lat, &
-                  hard, qref, Rlmax, cage, qaa, fVoctO, fVoctAB
+                 hard, qref, Rlmax, cage, qaa, fVoctO, fVoctAB, B1hams
  use rotylm, only: getVoct
  implicit none
 
@@ -362,7 +362,7 @@ endif
   enddo
  enddo
  ecorr = sumV
- write(*,425) ecorr
+ !write(*,425) ecorr
  
 425	format ('   (1/2) dQ dV             : ',f12.6)
 
@@ -380,7 +380,7 @@ endif
  ! now combine the two terms to get full potential for Hij:
  vm = vm + vm1;
 
- write(*,'(a,100f10.6)') 'tbseld: vm_latt:',vm(21,1),vm(25,1),vm(25,1)/vm(21,1)
+ !write(*,'(a,100f10.6)') 'tbseld: vm_latt:',vm(21,1),vm(25,1),vm(25,1)/vm(21,1)
  
  !write(*,'(a,100f10.4)') 'Total V_0 at B2: ',vm(1,5)
  !write(*,'(a,100f10.4)') 'Total V_0 at B3: ',vm(1,9)
@@ -424,9 +424,9 @@ endif
  !do ib=1,4
   !write(*,'(i5, 100f10.5)') ib, qmpol(1,ib)
  !end do
- write(*,'(a,50f15.8)')"Layer Q0: ", (sum(qmpol(1,(ib-1)*8+1:ib*8))-2*qaa,ib=1,nbas/8)
+! write(*,'(a,50f15.8)')"Layer Q0: ", (sum(qmpol(1,(ib-1)*8+1:ib*8))-2*qaa,ib=1,nbas/8)
 
- write(*,'(8f6.2)') qmpol(1,:)
+! write(*,'(8f6.2)') qmpol(1,:)
  !write(*,*) 'TM Q0:', qmpol(1,1),qmpol(1,5)
  !write(*,*) 'TM V0:', vm(1,1), vm(1,5)
  !write(*,*) 'V0:', vm(1,:)
@@ -596,6 +596,212 @@ endif
 
 	return
 	end subroutine getvmdhcage
+
+!============================================================================
+
+ subroutine getvmdhlat4edrixs()
[…]

### 2023-09-09 src/tbmpol.f

@@ -76,7 +76,7 @@ C --- get multipole moments ---
 
 
 	if (nlmi > 1) then
-	 do ilm = 2, nlmi
+	 do ilm = 2, nlmi ! monopoles qmpol(1,ib) calc explicitily above.
 	  do ilmp = ilm12(1,it), ilm12(2,it)
 	   do  ilmpp = ilm12(1,it), ilm12(2,it)
 	    M = CFM(ll(ilmp),ll(ilmpp),ll(ilm),ic)

### 2023-09-10 manuscript/paper.tex
paper: figures updates, general t2g case A,B matrices expansions calc and included in append.

@@
 \end{abstract}
-\maketitle
+%\maketitle
 
@@
 and their average energies also shifted.
-The $t_{2g}$ now splits into two levels,
+Defining 
+$F_n(\delta) = 1-1/(1+\delta)^n$,
+we see that
+the $t_{2g}$ now splits into two levels,
 with energies
+
 \begin{align}
 E_{xy} =&
-\frac{32}{7} \left[
-\left(1-\frac{1}{(\delta +1)^3}\right) D_2
--
-\left(1-\frac{1}{(\delta +1)^5}\right) \frac{20}{9}D_4
-\right]\frac{q_o}{a},\\
-E_{yz} =& E_{zx} = -3/2 E_{xy},
+\frac{32}{7}\frac{q_o}{a} \left(
+ D_2F_3 - \frac{20}{9}D_4F_5 
+\right),\\
+E_{yz} =& E_{zx} = -\frac{1}{2} E_{xy},
 \end{align}
@@
 %\begin{align}
-$E_0^{t_{2g}} = -64q_oD_4 \left(2+(\delta +1)^{-5}\right)/9a$.
+%$E_0^{t_{2g}} = -64q_oD_4 \left(2+(\delta +1)^{-5}\right)/9a$.
+$E_0^{t_{2g}} = -64q_oD_4 \left(3-F_5\right)/9a$.
 %\frac{64}{9} \left(-\frac{1}{(\delta +1)^5}-2\right) \text{D4}
@@
 \begin{align}
-E_{x^2-y^2}=&\frac{32}{7} \left[\left(1-\frac{1}{(\delta +1)^3}\right) \text{D2}+\frac{5}{3}\left(1-\frac{1}{(\delta +1)^5}\right) \text{D4}\right]\frac{q_o}{a},\\
-E_{z^2}=&-E_{x^2-y^2},
+E_{x^2-y^2}=&
+\frac{32}{7}\frac{q_o}{a} \left(D_2F_3+\frac{5}{3} D_4F_5\right),\\
+E_{z^2}=&-E_{x^2-y^2},\\
 \end{align}
@@
 %\begin{align}
-$E_0^{e_{g}} = 32 q_oD_4 \left(2+(\delta +1)^{-5}\right)/3a$.
+%$E_0^{e_{g}} = 32 q_oD_4 \left(2+(\delta +1)^{-5}\right)/3a$.
+$E_0^{e_{g}} = 32 q_oD_4 \left(3-F_5\right)/3a$.
 %\frac{32}{3} \left(\frac{1}{(\delta +1)^5}+2\right) \text{D4}
@@
 The crystal field splitting becomes
-\begin{align}
-\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=\frac{160}{9} \left(\frac{1}{(\delta +1)^5}+2\right) D_4.
-\end{align}
-
+%\begin{align}
+$\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=
+%\frac{160}{9} \left(\frac{1}{(\delta +1)^5}+2\right) D_4.
+160q_oD_4\left(3-F_5\right)/9a$.
+%\end{align}
 At small $\delta$, 
-we can expand the above expressions
- up to first order in $\delta$.
- $E_0^{t_{2g}}$, $E_0^{e_{g}}$ and $\Delta$ are rescaled by ${1-5\delta/3}$,
- and we can write
+expanding 
+$F_3,F_5$
+ up to first order in $\delta$,
+we obtain
 \begin{align}
@@
 %\left[\frac{16}{63} (27 \text{D2}-100 \text{D4})\right]
-\left[(D_2-\frac{100}{27}  D_4)\right]\Delta_{\delta},\\
-(E_{x^2-y^2},E_{z^2})&=(2,-2)
-\left[(D_2+\frac{25}{9} D_4)\right]\Delta_{\delta}
-\end{align}
-where 
-${\Delta_{\delta}= \frac{48}{7}\frac{q_o}{a}\frac{\delta}{a}}$.
+\left[D_2-\frac{100}{27}  D_4\right]\frac{48}{7}\frac{q_o}{a}\delta,\\
+(E_{x^2-y^2},E_{z^2})&=(1,-1)
+\left[D_2+\frac{25}{9} D_4\right]\frac{96}{7}\frac{q_o}{a}\delta,
+\end{align}
+whereas
+%${\Delta_{\delta}= \frac{48}{7}\frac{q_o}{a}\frac{\delta}{a}}$.
+$E_0^{t_{2g}}$, $E_0^{e_{g}}$ and $\Delta$ are rescaled by a factor of ${1-5\delta/3}$.
 
@@
 
-\az{update the numbers,,, and quote realistic values of D2 and D4.}
+\az{update the numbers,,, and quote realistic values of D2 and D4.:
+$D_2/D_4 \simeq 1\sqrt{D_4} \simeq 15-25$ estimated from realistic field splittings, 
+$q_o=2,a=7$ bohr,
+$\Delta=0.5-3$ eV. ... check... 
+}
 Note the relative strengths of the two terms with $D_{2}$ and $D_{4}$.
@@
 
+\com{
+\begin{align}
+E_{xy} =&
+\frac{32}{7} \left[
+\left(1-\frac{1}{(\delta +1)^3}\right) D_2
+-
+\left(1-\frac{1}{(\delta +1)^5}\right) \frac{20}{9}D_4
+\right]\frac{q_o}{a},\\
+E_{yz} =& E_{zx} = -3/2 E_{xy},
+\end{align}
+as measured from their average 
+%\begin{align}
+$E_0^{t_{2g}} = -64q_oD_4 \left(2+(\delta +1)^{-5}\right)/9a$.
+%\frac{64}{9} \left(-\frac{1}{(\delta +1)^5}-2\right) \text{D4}
+%\end{align}
+Similarly, $e_g$ splits up as
+\begin{align}
+E_{x^2-y^2}=&\frac{32}{7} \left[\left(1-\frac{1}{(\delta +1)^3}\right) \text{D2}+\frac{5}{3}\left(1-\frac{1}{(\delta +1)^5}\right) \text{D4}\right]\frac{q_o}{a},\\
+E_{z^2}=&-E_{x^2-y^2},
+\end{align}
+measured from their average 
+%\begin{align}
+$E_0^{e_{g}} = 32 q_oD_4 \left(2+(\delta +1)^{-5}\right)/3a$.
+%\frac{32}{3} \left(\frac{1}{(\delta +1)^5}+2\right) \text{D4}
+%\end{align}
+The crystal field splitting becomes
+\begin{align}
+\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=\frac{160}{9} \left(\frac{1}{(\delta +1)^5}+2\right) D_4.
+\end{align}
+}
+
 \subsection{cooperative JT and orbital order}
@@
 
-\com{
-\begin{table}[htp]
-\caption{default}
-\begin{center}
-\begin{tabular}{|L|L|}
-\hline
-V^A_{2,-2}& 64 \sqrt{\frac{3 \pi }{5}} \cos ^2\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}-\frac{\sec ^3\alpha }{(\cos 2 \beta +2)^{5/2}}\right)\\ \hline
-V^A_{2,0}& 32 \sqrt{\frac{\pi }{5}} \left(\frac{2 \sec ^3\alpha  \sin ^2\beta }{(\cos 2 \beta +2)^{5/2}}-\frac{32 \sqrt{\frac{\pi }{5}} (\cos 2 \beta -\cos 2 \alpha )}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}\right)\\ \hline
-V^A_{4,-2}& \frac{128}{3} \sqrt{5 \pi } \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right)\\ \hline
-V^A_{4,0}& -\frac{16}{3} \sqrt{\pi } \left(\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}\right. \\ 
-&+\left. \frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}\right) \\ \hline
-V^A_{4,4}&\frac{1}{3} (-128) \sqrt{35 \pi } \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right)\\ \hline
-
-\end{tabular}
-\end{center}
-\label{default}
-\end{table}%
-}
-
 \rev{$V(r)=q\sum_{i}(\sqrt{ ..... r\cos... })^{-1}$}
@@
 
-\com{
-\begin{table}[htp]
-\caption{default}
-\begin{center}
-\begin{tabular}{|L|}
-\hline
-V^{B}_{2,-2}=  \frac{64 \sqrt{\frac{3 \pi }{5}} \sin ^2\alpha  \sec ^3\beta }{(\cos 2 \alpha +3)^{5/2}}\\ %\hline
-V^{B}_{2,0}=  4 \sqrt{\frac{\pi }{5}} \left(\sec ^3\alpha -\frac{8 \sec ^3\beta }{(\cos 2 \alpha +3)^{3/2}}\right)\\ %\hline
- V^{B}_{4,-2}=  -\frac{128 \sqrt{5 \pi } \sin ^2\alpha  \sec ^5\beta }{3 (\cos 2 \alpha +3)^{7/2}}\\ %\hline
-V^{B}_{4,0}= \frac{4}{3} \sqrt{\pi } \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right)\\ %\hline
- V^{B}_{4,4}=  -\frac{16 \sqrt{35 \pi } (-20 \cos 2 \alpha +\cos 4 \alpha -13) \sec ^5\beta }{3 (\cos 2 \alpha +3)^{9/2}}\\ \hline
-\end{tabular}
-\end{center}
-\label{default}
-\end{table}%
-}
-
 \az{full potential of the charges in deformed cage: }:
@@
 their Hamiltonians turn out to be diagonal.
+
+% leading order expansion in beta:
+%A 2,4: \left\{\frac{64 \beta ^2}{63 \sqrt{3}}+O\left(\beta ^3\right),\frac{40960 \beta ^2}{5103 \sqrt{3}}+O\left(\beta ^3\right)\right\}
+%B 2,4: \left\{-\frac{3 \beta ^2}{7}+O\left(\beta ^3\right),-\frac{115 \beta ^2}{63}+O\left(\beta ^3\right)\right\}
 
@@
 %from A
-\frac{64 \sin ^2\beta }{7 (\cos 2 \beta +2)^{5/2}},\\ % simplifies.... from:
+\frac{64 \sin ^2\beta }{7 (\cos 2 \beta +2)^{5/2}} % simplifies.... from:
  %\frac{16 (3 \sin \beta+\sin 3\beta)^2}{7 (\cos 2\beta+2)^{9/2}},\\
+ \simeq \frac{64}{63 \sqrt{3}}\beta ^2,\\
 \Delta_4^A =&
@@
 &  (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82),\\
+\simeq& \frac{40960}{5103 \sqrt{3}}\beta ^2,\\
 % \Delta_4^A =&
@@
  %from B
-\Delta_{2}^B =& \frac{2}{7} \left(1-\sec ^3\beta\right),\\
-  \Delta_4^B =&\frac{5}{126} \left((7 \cos 4\beta-3) \sec ^5\beta-4\right),\\
+\Delta_{2}^B =& \frac{2}{7} \left(1-\sec ^3\beta\right)
+\simeq -\frac{3}{7}\beta ^2,\\
+  \Delta_4^B =&\frac{5}{126} \left((7 \cos 4\beta-3) \sec ^5\beta-4\right)
+  \simeq -\frac{115}{63}\beta ^2,\\
  %\left( \Delta_{2}  D_2 + \Delta_4 D_4\right),\\
@@
 \begin{align}
-E_{0} =& \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a,\\
+E_{0}^{t_{2g}} =& \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a,\\
 E_{0}^A =&
  \frac{8 (92 \cos 2\beta+24 \cos 4\beta+20 \cos 6\beta+5 \cos 8\beta+51)}{9 (\cos 2\beta+2)^{9/2}},\\
+ \simeq& \frac{512}{243 \sqrt{3}}-\frac{2560 \beta ^2}{729 \sqrt{3}},\\
 E_{0}^B=&
- -\frac{1}{18} \left((5 \cos 4\beta+3) \sec ^5\beta+4\right),\\
+ -\frac{1}{18} \left((5 \cos 4\beta+3) \sec ^5\beta+4\right)
+ \simeq -\frac{2}{3}+\frac{10 \beta ^2}{9}.
  \end{align}
@@
 
-$E_D$ and $E_{\pm}$ relative to their average ${E_0= \left(E_{xy} + 2 E_{yz}\right)/3}$
+$E_D$ and $E_{\pm}$ relative to their average ${E_0^{t_{2g}}= \left(E_{xy} + 2 E_{yz}\right)/3}$
 are shown in Fig.~\ref{fig:evals-alpha}.
-$E_0$ itself shifts 
+$E_0^{t_{2g}}$ itself shifts 
 with the tilting $\alpha$, 
@@
 the change in eg-t2g gap $\Delta$.
-This shift in $E_0$ is
+This shift in $E_0^{t_{2g}}$ is
 %from its value 
@@
 also included in Fig.~\ref{fig:evals-alpha}.
-
-\com{
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-0-r}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-1-r}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-2-r}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/phi-0-q-3-r}
-\caption{d224=11.; norm should be eq to 0.00482334; d222=sqrt d224=0.0694503, d222/d224=14.3988 here. Dark state shuld b labelled, as well as pm states.
-update to q=1,3 and analytic... d224norm=0.2?? or update theta0 figs to reduce d224 to 0.005?}
-\label{default}
-\end{center}
-\end{figure}
-}
 
@@
 
-\com{
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/q-1-4-alpha-14deg-states-wts-vs-beta}
-\caption{eigenstates: weights of xy, yz, zx.}
-\label{default}
-\end{center}
-\end{figure}
-}
-
 \subsection{eg manifold}
@@
 \begin{align}
-E_0 &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a,\\
+E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a,\\
 E_0^A &=
@@
 \end{align}
-
-\com{
-\begin{align}
-\left(
-\begin{array}{cc}
- -\frac{64 \left(\alpha ^2 \left(7 \beta ^2+3\right)-6 \beta ^2\right)}{189 \sqrt{3}} & \frac{640 \left(\alpha ^2 \left(\beta ^2+16\right)-32 \beta ^2\right)}{1701 \sqrt{3}} \\
- \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right) & \frac{1}{168} (-5) \left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right) \\
-\end{array}
-\right)
-\end{align}
-
-\begin{align}
-mean=
-\left(
-\begin{array}{cc}
- 0 & \frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}} \\
- 0 & -\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1 \\
-\end{array}
-\right)
-\end{align}
-}
 
@@
 \right),\\ \nonumber
-\com{
-\mathcal{R}=
-\left(
-\scalemath{0.7}{
-\begin{array}{ccccc}
- R_{12} R_{21}+R_{11} R_{22} & R_{13} R_{22}+R_{12} R_{23} & \sqrt{3} R_{13} R_{23} & R_{13} R_{21}+R_{11} R_{23} & R_{11} R_{21}-R_{12} R_{22} \\
- R_{22} R_{31}+R_{21} R_{32} & R_{23} R_{32}+R_{22} R_{33} & \sqrt{3} R_{23} R_{33} & R_{23} R_{31}+R_{21} R_{33} & R_{21} R_{31}-R_{22} R_{32} \\
- \frac{-1}{\sqrt{3}}\left(R_{11} R_{12}+R_{21} R_{22}-2 R_{31} R_{32}\right) & \frac{-1}{\sqrt{3}}\left(R_{12} R_{13}+R_{22} R_{23}-2 R_{32} R_{33}\right)  & -\frac{1}{2} R_{13}^2+R_{33}^2-\frac{R_{23}^2}{2} & \frac{-1}{\sqrt{3}}\left(R_{11} R_{13}+R_{21} R_{23}-2 R_{31} R_{33}\right) & 0\\ % identically 0 in our case of specific rotation and tilt.
- %\frac{1}{2\sqrt{3}}\left(-R_{11}^2+R_{12}^2-R_{21}^2+R_{22}^2+2 R_{31}^2-2 R_{32}^2\right) \\
- R_{12} R_{31}+R_{11} R_{32} & R_{13} R_{32}+R_{12} R_{33} & \sqrt{3} R_{13} R_{33} & R_{13} R_{31}+R_{11} R_{33} & R_{11} R_{31}-R_{12} R_{32} \\
- R_{11} R_{12}-R_{21} R_{22} & R_{12} R_{13}-R_{22} R_{23} & \frac{1}{2} \sqrt{3} \left(R_{13}^2-R_{23}^2\right) & R_{11} R_{13}-R_{21} R_{23} & \frac{1}{2} \left(R_{11}^2-R_{12}^2-R_{21}^2+R_{22}^2\right) \\
-\end{array}
-}
-\right),\\
-}
 \mathcal{R}=
@@
 \end{gather}
-
-\com{
-
-\begin{align}
-\mathcal{R}=&
-\left(
-\begin{array}{ccccc}
- R_{-1,1} R_{1,-1}+R_{-1,-1} R_{1,1} & R_{-1,0} R_{1,-1}+R_{-1,-1} R_{1,0} & \sqrt{3} R_{-1,0} R_{1,0} & R_{-1,1} R_{1,0}+R_{-1,0} R_{1,1} & R_{-1,1} R_{1,1}-R_{-1,-1} R_{1,-1} \\
- R_{-1,1} R_{0,-1}+R_{-1,-1} R_{0,1} & R_{-1,0} R_{0,-1}+R_{-1,-1} R_{0,0} & \sqrt{3} R_{-1,0} R_{0,0} & R_{-1,1} R_{0,0}+R_{-1,0} R_{0,1} & R_{-1,1} R_{0,1}-R_{-1,-1} R_{0,-1} \\
- -\frac{R_{-1,-1} R_{-1,1}-2 R_{0,-1} R_{0,1}+R_{1,-1} R_{1,1}}{\sqrt{3}} & -\frac{R_{-1,-1} R_{-1,0}-2 R_{0,-1} R_{0,0}+R_{1,-1} R_{1,0}}{\sqrt{3}} & -\frac{1}{2} R_{-1,0}^2+R_{0,0}^2-\frac{R_{1,0}^2}{2} & -\frac{R_{-1,0} R_{-1,1}-2 R_{0,0} R_{0,1}+R_{1,0} R_{1,1}}{\sqrt{3}} & \frac{R_{-1,-1}^2-R_{-1,1}^2-2 R_{0,-1}^2+2 R_{0,1}^2+R_{1,-1}^2-R_{1,1}^2}{2 \sqrt{3}} \\
- R_{0,1} R_{1,-1}+R_{0,-1} R_{1,1} & R_{0,0} R_{1,-1}+R_{0,-1} R_{1,0} & \sqrt{3} R_{0,0} R_{1,0} & R_{0,1} R_{1,0}+R_{0,0} R_{1,1} & R_{0,1} R_{1,1}-R_{0,-1} R_{1,-1} \\
- R_{1,-1} R_{1,1}-R_{-1,-1} R_{-1,1} & R_{1,-1} R_{1,0}-R_{-1,-1} R_{-1,0} & \frac{1}{2} \sqrt{3} \left(R_{1,0}^2-R_{-1,0}^2\right) & R_{1,0} R_{1,1}-R_{-1,0} R_{-1,1} & \frac{1}{2} \left(R_{-1,-1}^2-R_{-1,1}^2-R_{1,-1}^2+R_{1,1}^2\right) \\
-\end{array}
-\right)
-\end{align}
-
-\begin{gather}
-\mathcal{R}=
-\left(
-\scalemath{0.6}{
-\begin{array}{ccccc}
- \frac{1}{4} (\cos 2 \alpha+3) \cos 2 \beta & \frac{\sin \alpha (\cos \alpha \cos 2 \beta+\sin 2 \beta)}{\sqrt{2}} & -\frac{1}{2} \sqrt{3} \cos 2 \beta \sin ^2\alpha & \frac{\sin \alpha (\sin 2 \beta-\cos \alpha \cos 2 \beta)}{\sqrt{2}} & \cos \alpha \sin 2 \beta \\
- \frac{\cos \alpha \sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} & \frac{1}{2} (\cos 2 \alpha (\cos \beta-\sin \beta)+\cos \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\sin \beta-\cos \beta) & \frac{1}{2} (\cos 2 \alpha (\sin \beta-\cos \beta)+\cos \alpha (\cos \beta+\sin \beta)) & -\frac{\sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} \\
- -\frac{1}{2} \sqrt{3} \sin ^2\alpha & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & \frac{1}{4} (3 \cos 2 \alpha+1) & -\sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & 0 \\
- \frac{\cos \alpha \sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)-\cos 2 \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\cos \beta+\sin \beta) & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)+\cos 2 \alpha (\cos \beta+\sin \beta)) & \frac{\sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} \\
- -\left(\cos ^2\alpha+1\right) \cos \beta \sin \beta & \frac{\sin \alpha (\cos 2 \beta-2 \cos \alpha \cos \beta \sin \beta)}{\sqrt{2}} & \sqrt{3} \cos \beta \sin ^2\alpha \sin \beta & \frac{\sin \alpha (\cos 2 \beta+\cos \alpha \sin 2 \beta)}{\sqrt{2}} & \cos \alpha \cos 2 \beta \\
-\end{array}
-}
-\right)
-\end{gather}
-
-}
 
@@
 
-\com{
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row}
-\caption{$beta=0$ case, $q_A=q_o/2$}
-\label{fig:evals-alpha}
-\end{center}
-\end{figure}
-}
+\subsection{general case, t2g}
+
+% using ham-approx-expansion-alpha-beta.nb: Generalt2gSplitAver[...]
+\begin{align} 
+\tilde H_{A,2} =& 
+\left(
+\begin{array}{ccc}
+ -\frac{64 \left(\alpha ^2 \left(7 \beta ^2+3\right)-6 \beta ^2\right)}{189 \sqrt{3}} & \frac{32}{21} \sqrt{\frac{2}{3}} \alpha  \beta ^2 & -\frac{32}{21} \sqrt{\frac{2}{3}} \alpha  \beta ^2 \\
+ & \frac{32 \left(\alpha ^2 (\beta  (7 \beta -12)+3)-6 \beta ^2\right)}{189 \sqrt{3}} & \frac{64 \alpha ^2 \left(3-2 \beta ^2\right)}{189 \sqrt{3}} \\
+&  & \frac{32 \left(\alpha ^2 (\beta  (7 \beta +12)+3)-6 \beta ^2\right)}{189 \sqrt{3}} \\
+\end{array}
+\right),\\
+\tilde H_{A,4} =& 
+\left(
+\begin{array}{ccc}
+ -\frac{2560 \left(\alpha ^2 \left(\beta ^2+16\right)-32 \beta ^2\right)}{5103 \sqrt{3}} & \frac{1280 \sqrt{\frac{2}{3}} \alpha  \beta  (16 \beta -7)}{1701} & -\frac{1280 \sqrt{\frac{2}{3}} \alpha  \beta  (16 \beta +7)}{1701} \\
+ & \frac{1280 \left(\alpha ^2 ((\beta -72) \beta +16)-32 \beta ^2\right)}{5103 \sqrt{3}} & -\frac{2560 \alpha ^2 \left(24 \beta ^2+1\right)}{1701 \sqrt{3}} \\
+&& \frac{1280 \left(\alpha ^2 (\beta  (\beta +72)+16)-32 \beta ^2\right)}{5103 \sqrt{3}} \\
+\end{array}
+\right),\\
+& 0,\frac{512 \left(5 \alpha ^2 \left(4 \beta ^2+1\right)+5 \beta ^2-3\right)}{729 \sqrt{3}}
+\end{align}
+
+\begin{align} 
+\tilde H_{B,2} =& 
+\left(
+\begin{array}{ccc}
+ \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right) & -\frac{9 \alpha  \beta ^2}{7 \sqrt{2}} & \frac{9 \alpha  \beta ^2}{7 \sqrt{2}} \\
+ & -\frac{3}{28} \left(\alpha ^2 (\beta  (3 \beta -8)+2)-4 \beta ^2\right) & -\frac{3}{7} \alpha ^2 \left(\beta ^2+1\right) \\
+  &  & -\frac{3}{28}\left(\alpha ^2 (\beta  (3 \beta +8)+2)-4 \beta ^2\right) \\
+\end{array}
+\right),\\
+\tilde H_{B,4} =& 
+\left(
+\begin{array}{ccc}
+ \frac{5}{126} \left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right) & \frac{5 \alpha  (14-23 \beta ) \beta }{21 \sqrt{2}} & \frac{5 \alpha  \beta  (23 \beta +14)}{21 \sqrt{2}} \\
+ & -\frac{5}{252}\left(\alpha ^2 (\beta  (37 \beta -144)+46)-92 \beta ^2\right) & \frac{5}{21} \alpha ^2 \left(31 \beta ^2+8\right) \\
+ & & -\frac{5}{252}\left(\alpha ^2 (\beta  (37 \beta +144)+46)-92 \beta ^2\right) \\
+\end{array}
+\right),\\
+&0,\frac{1}{18} \left(-5 \alpha ^2 \left(7 \beta ^2+4\right)-20 \beta ^2+12\right) 
+\end{align}
 
@@
 \end{figure}
-
-\com{
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.8\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width}
-\caption{}
-\label{default}
-\end{center}
-\end{figure}
-}
-
-\com{
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0}
-\caption{append fig; combine in one plot: $D_2/D_4\simeq 14$ at 
-$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
-}
-\label{default}
-\end{center}
-\end{figure}
-}
-
-\com{
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-3-r}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-3-r}
-\caption{append fig; combine in one plot: $D_2/D_4\simeq 14$ at 
-$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
-}
-\label{default}
-\end{center}
-\end{figure}
-}
 
@@
 }
-
-\begin{align}
-u&=\frac{1}{4} (2+\cos\beta+\cos\alpha \cos\beta),\\
-v&=\frac{1}{4}
-\cos\beta(1-\cos\alpha),\\
-w&=\frac{1}{2} (1+\cos\alpha),\\
-x&=-1+\frac{1}{2} (1+\cos\alpha) \cos\beta,\\
-\{x\to 2 (u-1),y\to 2 v,z\to 2 (w-1)\},\\
-\{d\to -1+2 \sigma ,e\to -1+2 \tau ,f\to 1+2 \mu ,g\to 1-2 \tau ,h\to 1-2 \sigma \}
-%y&=2v=\cos\beta \frac{1}{2} (1-\cos\alpha),\\
-%z&=2(w-1)=-1+\cos\alpha.
-\end{align}
-we obtain the following expressions for $V_{l,m}^B$.
-\begin{align}
-V_{2,-2}^B &=8\sqrt{\frac{3 \pi }{5}} \frac{v \left(2 u^3-4 u^2 x-8 u v^2+v^2 x\right)}{\left(u^2+v^2\right)^{7/2}},\\
-V_{2,0}^B &=12 \sqrt{\frac{ \pi }{5}} \left(\frac{u x+2 v^2}{\left(u^2+v^2\right)^{5/2}}-\frac{2(w-1)}{w^4}\right),
-\end{align}
-where all other $V_{2,m}^B= 0$.
-Similarly,
-$l=4$ components are,
-\begin{align}
-V_{4,4}^B&= -\frac{\sqrt{35 \pi }}{3}\frac{\left(5 u^5 x+42 u^4 v^2-46 u^3 v^2 x-92 u^2 v^4+21 u v^4 x+10 v^6\right)}{\left(u^2+v^2\right)^{11/2}},\\
-V_{4,-2}^B&= -\frac{4\sqrt{5\pi}}{3}\frac{ v \left(-2 u^3+6 u^2 x+12 u v^2-v^2 x\right)}{\left(u^2+v^2\right)^{9/2}},\\
-V_{4,0}^B&=-\frac{5\sqrt{\pi }}{3}  \left(\frac{3 \left(u x+2 v^2\right)}{\left(u^2+v^2\right)^{7/2}}+\frac{8(w-1)}{w^6}\right),
-\end{align}
 

### 2023-09-11 manuscript/paper.tex
JT section... elastic energy dependence in our case... multielectron configuration and arguments using single particl states

@@
 The octahedral field at the centre of the octahedron or cube  
-is given by~\cite{pavariniChap},
+is given by~\cite{pavariniChap}, [include monopole?? bcs later we incl its changes...]
 \begin{align}
@@
 %(i.e., except Kramers degeneracy)
-against structural distortions that reduce the symmetry, lift the degeneracy, thereby
-lowering the energy of the system.
+against structural distortions.
+The distortions  
+reduce the symmetry of the structure
+and lift the electronic degeneracy.
+This lowers the energy of the system proportional to
+the distortion.
+The elastic energy of the structure that increases as the square of the distortion
+competes with this linear term and the optimum structure 
+is obtained at a finite distortion.
+As long as the two competing terms have different dependence on the distortion,
+the ground state can have a finite distortion.
+We will use this argument and focus only on the changes
+ in the electronic energy throughout this paper.
+
+\az{For our main problem, the rigid octahedral rotations in perovskites,
+we will see that 
+the energies are quadratic with the tilt and rotation angles. 
+However, the unit cell volume also changes quadratically with the angles 
+so the elastic energy still goes with a doubled power of this ``distortion'',
+i.e, it should be quartic in the angles.
+So the two will lead to an optimum structure with a finite tilt and rotation.
+}
+
+\rev{
+There is one point to clarify here. 
+We consider single particle spectrum, i.e.,
+single electron energy states
+to analyse the ground state of many electron system,
+which is the lowest energy ``electronic configuration'' 
+(a combination of occupied single particle states 
+out of all available single particle states, 
+or a slater determinant of that combination to be more precise!).
+So a degenerate set of states that are completely occupied
+makes a non-degenerate many electron state because 
+only a single configuration/combination is possible.
+For a given number of electrons in the d-shell of the transition metal ion,
+we can determine the (most likely) configuration(s) or ground state(s)
+using Hund's rule and see if it is degenerate or otherwise.
+ }
+
+\com{
+Instability:\\
+ Low/high spin configurations, rules/arguments using single particle spectrum and a given low/high spin state with a given number of electrons:\\
+elastic energy vs electronic... number of electrons... multi-electron configurations.... degenerate vs non-degenerate cases...
+}
+
+In the following we 
+consider an octahedral environment around a transition metal ion 
+and 
+illustrate how the changes in the electronic energy 
+can be calculated
+ when the octahedron is elongated.
 
@@
 \begin{align}
-V_{0,0}^{JT}=& \frac{8 \sqrt{\pi } (2 \delta +3)}{\delta +1},\\
+%V_{0,0}^{JT}=& \frac{8 \sqrt{\pi } (2 \delta +3)}{\delta +1},\\
 V_{2,0}^{JT}=& -\frac{32 \sqrt{\frac{\pi }{5}} \delta  \left(\delta ^2+3 \delta +3\right)}{(\delta +1)^3},\\
 V_{4,0}^{JT}=& \frac{32}{3} \sqrt{\pi } \left(\frac{4}{(\delta +1)^5}+3\right),\\
-V_{4,4}^{JT}=& \frac{32 \sqrt{35 \pi }}{3}.
-\end{align}
-%The d-orbitals are not affected by odd-$l$ components either, here we do not have them anyway.
-%(it's non-spherical components)
-\rev{$V_{0,0}^{JT}$ rigidly shifts the whole spectrum 
-[by $\simeq 4 \sqrt{\pi } (3-\delta )q_o/a$, 
-favouring elongation ($\delta>0$) over
-compression ($\delta<0$).... filling dependent argumetns... , might confuse??
-]
+V_{4,4}^{JT}=& \frac{32 \sqrt{35 \pi }}{3},
+\end{align}
+where we only kept
+the trace preserving terms that keep the average of the whole spectrum fixed.
+%the terms that do not change the trace of the electronic Hamiltonian and thus keep the average of the whole spectrum fixed.
+We have ignored
+the monopole term $V_{0,0}^{JT}$ $[8 \sqrt{\pi } (2 \delta +3)/(\delta +1)]$,
+which rigidly shifts the whole spectrum 
+(by $\simeq 4 (3-\delta )q_o/a$)
 and
-can be assumed to be contributing to the anharmonic part of the elastic energy of the system
-that tends to prevent the structural distortion. 
-We will ignore it and focus on the shifts and splittings that keep the average of the whole spectrum fixed.
-}
+can be assumed to be contributing to the elastic energy of the system.
 
@@
 
-%\subsection{Crystal Field Splittings}
-
-\az{The deformation $\delta$
-will not couple these orbitals to each other either but 
-modify the eg-t2g splitting as
-${\Delta\to(1-\delta/3) \Delta }$,
-and lift the degeneracies, as follows.
-...
-}
 The crystal field Hamiltonian of the central B ion/JT ion
 ${H_{m',m''}^{JT} = (q_o/a)\sum_{l,m} V_{l,m}^{JT} C_{l}^{m'm''m} D_{l}}$
-still turns out to be diagonal,
+still turns out to be diagonal 
+(i.e., the deformation $\delta$
+will not couple these orbitals to each other),
 but the degeneracies of the two manifolds is lifted
-and their average energies also shifted.
+and their respective average energies also shifted.
 Defining 
@@
 with energies
-
 \begin{align}
@@
 as measured from their average 
-%\begin{align}
-%$E_0^{t_{2g}} = -64q_oD_4 \left(2+(\delta +1)^{-5}\right)/9a$.
 $E_0^{t_{2g}} = -64q_oD_4 \left(3-F_5\right)/9a$.
-%\frac{64}{9} \left(-\frac{1}{(\delta +1)^5}-2\right) \text{D4}
-%\end{align}
 Similarly, $e_g$ splits up as
@@
 \end{align}
-measured from their average 
-%\begin{align}
-%$E_0^{e_{g}} = 32 q_oD_4 \left(2+(\delta +1)^{-5}\right)/3a$.
+as measured from their average 
 $E_0^{e_{g}} = 32 q_oD_4 \left(3-F_5\right)/3a$.
-%\frac{32}{3} \left(\frac{1}{(\delta +1)^5}+2\right) \text{D4}
-%\end{align}
 The crystal field splitting becomes
-%\begin{align}
 $\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=
-%\frac{160}{9} \left(\frac{1}{(\delta +1)^5}+2\right) D_4.
 160q_oD_4\left(3-F_5\right)/9a$.
-%\end{align}
 At small $\delta$, 
@@
 \begin{align}
+\label{eq:JTt2g}
 (E_{xy},E_{yz},E_{zx})&= (2, -1, -1)
@@
 \left[D_2-\frac{100}{27}  D_4\right]\frac{48}{7}\frac{q_o}{a}\delta,\\
+\label{eq:JTeg}
 (E_{x^2-y^2},E_{z^2})&=(1,-1)
@@
 
-\az{update the numbers,,, and quote realistic values of D2 and D4.:
-$D_2/D_4 \simeq 1\sqrt{D_4} \simeq 15-25$ estimated from realistic field splittings, 
-$q_o=2,a=7$ bohr,
-$\Delta=0.5-3$ eV. ... check... 
-}
+\subsection{Parameters $D_2$ and $D_4$ of the JT ion/atom}
+
+The terms in square brackets on the right of Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}
+contain $D_2$ and $D_4$. 
+$D_4$ is proportional to the crystal field splitting $\Delta$ 
+($D_4=\frac{3a}{160q_o} \Delta$) and 
+we can estimate its value from realistic values of $\Delta$ for a give octahedron size $a$ and ion charge $q_o$. 
+Assuming $a=7.0$ bohr and $q_o=2e$ ($e$ being the elementary charge),
+$D_4$ ranges from $1 \times 10^{-3}$ to  $7 \times 10^{-3}$
+for $\Delta \simeq 0.5-3$~eV.
+Typically, ${D_{2}\approx \sqrt{D_{4}}}$,
+so $D_{2}/D_{4} \approx 1/\sqrt{D_{4}}$
+and it roughly ranges between $29$ and $12$ for $D_4$ in the above range.
+This means that, for realistic systems, 
+we should have $D_{2} > 100/27 D_{4}, 25/9 D_{4}$
+and hence it's $D_{2}$ term that determines the sign and size of the splittings in 
+Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}.
+
+\subsection{Example, given a ne, see if instability exists:}
+
+\com{
 Note the relative strengths of the two terms with $D_{2}$ and $D_{4}$.
@@
 would reverse both eg and t2g ordering for a given tetragonal distortion.
+ }
 
@@
 along with an overall shift
+\rev{E0t2g or change in it? how to define the expressions... plotted is always change in it...}
 \begin{align}
@@
 The matrix elements in this case simplify a lot.
-Defining ${Q = -\left( q_A D_2, q_A D_4, q_B D_2,q_B D_4  \right)}$,
+Defining a vector ${Q = \left( q_A D_2, q_A D_4, q_B D_2,q_B D_4  \right)}$,
  we can write them as
@@
 E_{xy}=& Q.
-\left(\frac{64 \alpha ^2}{63 \sqrt{3}},\frac{512 \left(15 \alpha ^2+7\right)}{1701 \sqrt{3}},-\frac{3\alpha ^2}{7} ,-\frac{5 \alpha ^2}{7}-\frac{2}{3}\right)\\
+\left(-\frac{64 \alpha ^2}{63 \sqrt{3}},-\frac{512 \left(15 \alpha ^2+7\right)}{1701 \sqrt{3}},\frac{3\alpha ^2}{7} ,\frac{5 \alpha ^2}{7}+\frac{2}{3}\right)\\
 E_{yz}=& Q.
-\left(-\frac{32 \alpha ^2}{63 \sqrt{3}},-\frac{512 \left(25 \alpha ^2-7\right)}{1701 \sqrt{3}},\frac{3 \alpha ^2}{14},\frac{85 \alpha ^2}{42}-\frac{2}{3}\right)\\
+\left(\frac{32 \alpha ^2}{63 \sqrt{3}},\frac{512 \left(25 \alpha ^2-7\right)}{1701 \sqrt{3}},-\frac{3 \alpha ^2}{14},-\frac{85 \alpha ^2}{42}+\frac{2}{3}\right)\\
 g=& Q.
-\left(\frac{80}{63} \sqrt{\frac{2}{3}} \alpha ^3,0,-\frac{15 \alpha ^3}{14 \sqrt{2}},-\frac{5 \alpha ^3}{2 \sqrt{2}}\right)\\
+\left(-\frac{80}{63} \sqrt{\frac{2}{3}} \alpha ^3,0,\frac{15 \alpha ^3}{14 \sqrt{2}},\frac{5 \alpha ^3}{2 \sqrt{2}}\right)\\
 \lambda=& Q.
-\left(-\frac{64 \alpha ^2}{63 \sqrt{3}},\frac{2560 \alpha ^2}{1701 \sqrt{3}},\frac{3 \alpha ^2}{7},-\frac{40 \alpha ^2}{21}\right).
+\left(\frac{64 \alpha ^2}{63 \sqrt{3}},-\frac{2560 \alpha ^2}{1701 \sqrt{3}},-\frac{3 \alpha ^2}{7},\frac{40 \alpha ^2}{21}\right).
 %E_0=& Q.\left(-\frac{16 \alpha ^2}{21 \sqrt{3}},\frac{256 \left(15 \alpha ^2-14\right)}{1701 \sqrt{3}},\frac{9 \alpha ^2}{28},\frac{2}{3}-\frac{45 \alpha ^2}{28}\right),

### 2023-09-12 manuscript/paper.tex
JT section. results section. quadratic dependence in our case...

@@
 \usepackage{mathtools}
+
+\usepackage{enumerate}
 
@@
 is obtained at a finite distortion.
-As long as the two competing terms have different dependence on the distortion,
+As long as the two competing terms have different \az{[dependence, exponent? diff order polynomial?]} on the distortion,
 the ground state can have a finite distortion.
@@
 %${\Delta_{\delta}= \frac{48}{7}\frac{q_o}{a}\frac{\delta}{a}}$.
-$E_0^{t_{2g}}$, $E_0^{e_{g}}$ and $\Delta$ are rescaled by a factor of ${1-5\delta/3}$.
+$E_0^{t_{2g}}$, $E_0^{e_{g}}$ and $\Delta$ all are rescaled by a factor of ${1-5\delta/3}$.
 
@@
 This means that, for realistic systems, 
-we should have $D_{2} > 100/27 D_{4}, 25/9 D_{4}$
-and hence it's $D_{2}$ term that determines the sign and size of the splittings in 
-Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}.
-
-\subsection{Example, given a ne, see if instability exists:}
-
-\com{
-Note the relative strengths of the two terms with $D_{2}$ and $D_{4}$.
-\az{[refine argument]}
-Typically, ${D_{2}\approx \sqrt{D_{4}}}$. 
-Since
-$D_{2}$ and $D_{4}$ are scaled with different 
-powers of $a$ ($D_l=\braket{r^l}/a^l$),
-their ratio depends on
-the octahedron's size, i.e., $D_{2}/D_{4}\propto a^2$.
-For well localised d-orbitals in a large octahedron,
-${D_{2}/D_{4} > 25/9}$ so that elongation of the octahedron raises $xy$ and lowers $yz,xz$ states.
-(Similarly, under such a condition, 
-${D_{2}/D_{4} > 20/27}$ is automatically met so
-it raises $x^2-y^2$ and lowers $z^2$).
-However, if the d-orbitals are extended and octahedron is smaller,
-a situation might result where ${20/27 < D_{2}/D_{4} < 25/9}$.
-If so,
-the ordering of the eg will be reversed as if a compression of the octahedron would have happened.
-The extreme case of ${D_{2}/D_{4} < 20/27}$ (that seems less realistic)
-would reverse both eg and t2g ordering for a given tetragonal distortion.
- }
+we should always have $D_{2}/D_{4} > 100/27, 25/9 \approx 4$
+so 
+$D_{2}$ terms in 
+Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}
+dominate and determine the sign and size of the splittings.
 
 So far, we have calculated the changes in the single particle energy levels of the B ion. 
-Whether the deformation would be energetically favourable or not will depend on the number of electrons occupying these levels.
-The magnitude of the deformation will be determined by a competition between the electronic energy gain and elastic energy required.
-
-An example here a degen and a non degen case:....
+Whether the deformation would be energetically favourable 
+or not will depend on the number of electrons occupying these levels,
+as illustrate below.
+
+\subsection{Examples}
+To complete the revision of the JT instability,
+let's consider the following two cases.
+\begin{enumerate}
+\item
+ JT/B ion with $2$ electrons:
+In the symmetric octahedron case, 
+we will have a degenerate (many electron) ground state 
+with both electron in the same spin state (Hund's rule) in the $t_{2g}$ manifold.
+Distorting the structure $\delta>0$, we lower the ground state energy because 
+we can now choose $yz,zx$ orbitals that have lower energy than the original $t_{2g}$ energy of the undistorted structure.
+\item
+ JT/B ion with $3$ electrons:
+Assuming Hund's coupling is enough to still produce complete spin polarisation,
+their is only one possible orbital configuration, one electron in each of $xy,yz,zx$ orbitals.
+This non-degenerate (many electron) ground state
+does not lower its energy if the structure is distorted 
+because the gain due to $yz,zx$ is already balanced by the loss due to picking the higher energy $xy$ state.
+\end{enumerate}
 
@@
 
-\subsection{Contribution of different ion cages in a cubic perovskite}
+\subsection{Contribution of different coordination cages in a cubic perovskite}
 \label{sec:relativeVoctABO}
 
-cube of A, octa of B, and octa of O.
-%Assuming $q_o=-2$ and charge neutrality, $q_A+q_B + 3q_o=0$.
+In a cubic perovskite ABO$_3$,
+each transition metal atom/ion B
+is surrounded by six O$^{2-}$, each at a distance $a/2$,
+ making an octahedron of size $a$ around it.
+The potential of these ions $V_{O}(\vec r)= V_{oct}(\vec r)$
+splits the degenerate d-orbitals
+by an amount ${\Delta_O=160q_oD_{4}/3a}$
+ into $t_{2g}$ and $e_g$.
+However, this is not the only crystal field potential at the B site.
+The coordination cages of next nearest neighbours, 
+Eight A atoms/cations all at the same distance $\sqrt{3}a/2$
+make a cube around the B ion,
+which also produces an octahedral field, given by 
+\begin{align}
+V_{A}(\vec r) = \frac{8}{81 \sqrt{3}}\frac{q_A}{q_o} V_{O}(\vec r).
+\end{align}
+Furthermore,
+the nearest neighbouring B ions, size of them each at a distance $a$,
+make an octahedron, with a potential 
+\begin{align}
+V_{B}(\vec r) = -\frac{1}{32}\frac{q_B}{q_o}V_{O}(\vec r).
+\end{align}
+It is interesting to note that 
+$V_{A}(\vec r)$ and $V_{B}(\vec r)$ have opposite signs
+and 
+their combined effect 
+$V_{AB}(\vec r) = V_{A}(\vec r)+ V_{B}(\vec r)$
+depends on their relative charges.
+Using the charge neutrality $q_B=3q_o-q_A$,
+we can write 
+\begin{align}
+V_{AB}(\vec r) &= f_{q_A}V_{O}(\vec r),\\
+f_{q_A} &= \left(\frac{1}{32}+\frac{8}{81 \sqrt{3}}\right)\frac{q_A}{q_o} -\frac{3}{32},
+\end{align}
+which shows that $V_{AB}(\vec r)\to 0$
+as
+${q_A/q_0\to 1458/({256 \sqrt{3}+243})\simeq 2.124}$.
+%where they cancel each other exactly.
 
@@
 where they cancel each other exactly.
-}
 
@@
 
-Including the contribution of these cages to the crystal field splitting $\Delta$, we obtain
-
-\begin{align}
-\Delta &= (1+f_{q_A})\Delta_O,
-\end{align}
-where
-${\Delta_O=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
-
-\com{
-\begin{align}
-\Delta &= \left\{\frac{29}{32} + \left(\frac{8}{81 \sqrt{3}}+\frac{1}{32}\right)
- \left|\frac{q_A}{q_o}\right|  
-\right\}\Delta_O,
-\end{align}
-}
-
+}
+
+Including the contribution of these AB cages to the crystal field,
+\begin{align}
+V(\vec r) &= V_{O}(\vec r) + V_{AB}(\vec r),\\
+V(\vec r)  &= (1+f_{q_A}) V_{O}(\vec r),
+\end{align}
+the 
+ splitting becomes
+%\begin{align}
+$\Delta = (1+f_{q_A})\Delta_O$.
+%\end{align}
+%where ${\Delta_O=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
 We see that, relative to the O octahedron,
@@
  still large enough to be ignored.
-It can be measured as $\Delta_{AB}/\Delta_O=(\Delta-\Delta_O)/\Delta_O$, 
+It can be measured by $(\Delta-\Delta_O)/\Delta_O=f_{q_A}$,
 which linearly changes from 
 $-\frac{3}{32}\simeq -10\%$ at $q_A=0$
-to $\frac{8}{27 \sqrt{3}}\simeq 17\%$ at $q_A=6$. 
+to $\frac{8}{27 \sqrt{3}}\simeq 17\%$ at $q_A=3q_o$. 
 Typical values of $q_A$ relevant for real transition metal oxides
@@
 
-\subsection{Deformation of the crystal structure}
-
-Octahedra rotation, and resulting unit cell changes:\\
-bases rotation:\\
-\az{Rotation matrices $R$ and $\mathcal{R}$ given in appendix.}
-
+\subsection{Transformation of the crystal structure}
+
+\com{
 Coordinates of the Oxygen atoms transform according to 
@@
 $\mathcal{R}$.
-
-Four adjesent octahedra in two layers along z have to rotate/tilt simultaneously in different directions...
-
+}
 \az{figure vesta structure, label octahedra 1-4.}
@@
 The O atoms in the cubic structure lie half way between the B atoms and make octahedral cages around them.
-Their positions in the deformed structure (see appendix) are not directly required for our calculations and discussion.
+Their positions in the deformed structure %(see appendix) 
+are not directly required for our calculations and discussion.
 
@@
 The structure transforms from cubic to orthorhombic under these rotation and tilting of the octahedra.
-The lattice vectors of the deformed structure and the positions of A and B atoms can be calculated easily by calculating the coordinates of all six oxygen atoms that make the octahedra (by rotating and tilting the octahedra) for all four octahedra and
-comparing them for different octahedra for the shared atoms.
-We obtain
+The rotation matrix $R$ for $(\alpha,\beta)$ case is given in the appendix~\ref{sec:appendix}. 
+The lattice vectors of the deformed structure and the positions of A and B atoms can be calculated easily by calculating the coordinates of all six oxygen atoms that make the octahedra (by rotating and tilting the octahedra) for all four octahedra in the unit cell and
+comparing the coordinates of their shared oxygen atoms.
+We obtain,
+%\az{just rescaled, not rotated. write as cos * (1,1), etc?}
 % lattice vectors:
@@
 
+\com{
+\begin{align}
+\vec a_1 & =  \cos\beta ( 1,1,0 ) ,\\
+\vec a_2 & =  \cos\alpha  \cos\beta(-1,1,0 ),\\
+\vec a_3 & =  \cos\alpha ( 0,0,2 ).
+\end{align}
+}
+
 \subsection{Deformation of the crystal field}
 
+%\subsubsection{Deformation of the crystal field due to AB cages}
+
+\com{Before we present calculations and results, let's briefly
+summarise the contribution of the AB cages towards the crystal field Hamiltonian
+....}
+
+There are two different ways the crystal field $V(\vec r)$
+\az{[at the location of a B ion... which B ion out of four in distorted structure?... pick one here...]}
+ is deformed from the ideal case $V(\vec r) \propto V_{oct}(\vec r)$
+ when the octahedra are rigidly rotated. 
+% to make an orthorhombic structure. 
+\begin{enumerate}[(i)]
+\item
+%(i) 
+The relative rotations of the AB and O frames due to
+the rigid rotation and tilting of the oxygen octahedra removes the
+choice of a set of d-orbitals where the effect of 
+AB and O cages is the same. 
+We no longer just get $e_g, t_{2g}$ manifolds in any frame but with splittings induced by the rotation.
+This generates non-octahedral but still only $l=4$ field components. 
+\item
+%(ii) 
+The rigid rotation and tilting of the octahedra keeps the octahedra symmetric but deforms the unit cell and AB ionic cages with it.
+This not only changes the $l=4$ components but also induces 
+$l=2$ field components
+that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below).
+So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see sec.~\ref{sec:relativeVoctABO}).
+\end{enumerate}
+
+\com{
 There are two different ways the crystal field $V(\vec r)$
@@
 
+}
+
 Since $V_{O}(\vec r)$ is relatively stronger, 
 we can take the octahedra's local frames (that are rotated with them)
-to describe the effect of $V_{O}(\vec r)$ first 
-(leading to eg-t2g manifolds with a splitting of $\Delta_O$) 
-and consider the effect of $V_{AB}(\vec r)$ on these later.
-$V_{AB}(\vec r)$ will then couple and mix the orbitals in the two manifolds.
-Since $\Delta_AB << \Delta_O$,
+to first describe the effect of $V_{O}(\vec r)$, i.e.,
+splitting of degenerate d-orbitals into $e_g, t_{2g}$ manifolds with 
+a gap $\Delta_O$,
+and then
+consider the effect of $V_{AB}(\vec r)$ on these manifolds.
+$V_{AB}(\vec r)$ will couple and mix the orbitals in the two manifolds.
+Since %$\Delta_AB << \Delta_O$,
+$f_{q_A} \ll 1$,
 we can even ignore the coupling between the states belonging to the 
-different manifolds.
+different manifolds $\Delta_O$ apart.
 This also makes it possible to analytically solve the problem in two limiting cases discussed later.
 
+\com{
 The total crystal field potential at the central B atom that we consider
@@
 \az{repetition.... cubic case has similar expressions.... }
+}
 
@@
 where 
-$\mathcal{R}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics that we use. It can be calculated using the method described in Ref.~\cite{evanic}.
-
-The multipole components of $V_O(\vec r)$ in the rotated frame does not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
+$\mathcal{R}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics that we use (see appendix~\ref{sec:appendix}). 
+It can be calculated using the method described in Ref.~\cite{evanic}.
+\az{next para?}
+The multipole components of $V_O(\vec r)$ in the rotated frame do not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
 These can be read off Eq.~\ref{eq:voct}.
-Similarly, its easier to obtain the components of $V(\vec r)^{AB}$
+Similarly, its easier to obtain the components of $V_{AB}(\vec r)$
 in the unrotated frame so we do that first and later transforms them to obtain the rotated frame components.
@@
 V_{l'm'}^{AB} = \left(\frac{q_A}{a} \right)V_{l'm'}^{A}   
-+ \left(\frac{q_B}{a}\right)V_{l'm'}^{B}.
++ \left(\frac{q_B}{a}\right)V_{l'm'}^{B},
 \end{gather}
 %where $q_A + q_B = 3q_o$ ensures charge neutrality.
-
+where the quantities bearing a tilde on top belong to the rotated frame.
+As described above, 
 $\tilde V_{lm}^O$ are simply octahedral field components $l=4,m=0,4$ (see Eq.~\ref{eq:voct}).
-However, $V_{lm}^{AB}$ contains the effect of the deformation of the crystal structure on two ion cages due to the octahedral rotations
+However, $V_{lm}^{AB}$ contain the effect of the deformation of the crystal structure 
+%on AB ion cages due to the octahedral rotations
 so it now has not only other $l=4$ components but also $l=2$ components; see below.
-
-\rev{$V(r)=q\sum_{i}(\sqrt{ ..... r\cos... })^{-1}$}
-
-\az{full potential of the charges in deformed cage: manually refined}:
+A procedure to obtain these multipole components without
+actually calculating the projection of the potential $V_{AB}(\vec r)$ 
+onto the spherical harmonics is described in the appendix~\ref{sec:appendix}.
+We obtain the following exact expressions for $V_{lm}^{A}$,
+%\rev{$V(r)=q\sum_{i}(\sqrt{ ..... r\cos... })^{-1}$}
+%\az{full potential of the charges in deformed cage: manually refined}:
 \begin{align}
@@
 V^A_{2,0}&= 32 \sqrt{\frac{\pi }{5}} \left(\frac{2 \sec ^3\alpha  \sin ^2\beta }{(\cos 2 \beta +2)^{5/2}}-\frac{32 \sqrt{\frac{\pi }{5}} (\cos 2 \beta -\cos 2 \alpha )}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}\right),\\
-V^A_{4,-2}&= \frac{128}{3} \sqrt{5 \pi } \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right),\\
+V^A_{4,-2}&= \frac{128}{3} \sqrt{5 \pi } \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right),\\ \nonumber
 V^A_{4,0}&= -\frac{16}{3} \sqrt{\pi } \left(\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}\right. \\
 &+\left. \frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}\right),\\
-V^A_{4,4}&=\frac{1}{3} (-128) \sqrt{35 \pi } \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right),
-\end{align}
-
-\az{full potential of the charges in deformed cage: }:
-
+V^A_{4,4}&=-\frac{128}{3} \sqrt{35 \pi } \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right),
+\end{align}
+whereas $V_{lm}^{B}$ is given by,
+%\az{full potential of the charges in deformed cage: }:
 \begin{align}
@@
 V^{B}_{4,0}&= \frac{4}{3} \sqrt{\pi } \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right),\\
- V^{B}_{4,4}&=  -\frac{16 \sqrt{35 \pi } (-20 \cos 2 \alpha +\cos 4 \alpha -13) \sec ^5\beta }{3 (\cos 2 \alpha +3)^{9/2}}
- \end{align}
-
-\com{
-$V_{l,m}^{A/B}$ are multipole components
-of the potentials ${V_{dipoles}^{A/B}(\vec r;\alpha,\beta)}$ due to the deformation of A/B cages.
-We need to include only $l=2,4$ components, $l=0$ uniformly shifts the whole spectrum (and can be taken to be part of the elastic energy of the lattice, as in JT case). [refine these arguments...]
-}
-
-\subsection{Crystal Field Hamiltonian}
+ V^{B}_{4,4}&=  -\frac{16 \sqrt{35 \pi } (-20 \cos 2 \alpha +\cos 4 \alpha -13) \sec ^5\beta }{3 (\cos 2 \alpha +3)^{9/2}}.
+ \end{align}
+
+% expansion of V^{AB} at small alpha,beta is not useful because
+% we still have to Rotate them that brings in more alpa beta dependance
+\com{
+%A
+\begin{align}
+\text{Vlm}(2,-2)&=  \frac{64}{81} \sqrt{\frac{\pi }{5}} \alpha ^2 \left(\beta ^2-6\right),\\
+\text{Vlm}(2,0)&=  \frac{64}{27} \sqrt{\frac{\pi }{15}} \left(2 \left(\alpha ^2+3\right) \beta ^2-3 \alpha ^2\right),\\
+\text{Vlm}(4,-2)&=  \frac{1}{243} (-256) \sqrt{\frac{5 \pi }{3}} \alpha ^2 \left(9 \beta ^2+5\right),\\\text{Vlm}(4,0)&=  \frac{1}{243} (-128) \sqrt{\frac{\pi }{3}} \left(5 \alpha ^2 \left(11 \beta ^2+4\right)+30 \beta ^2+14\right),\\
+\text{Vlm}(4,4)&=  \frac{1}{243} (-128) \sqrt{\frac{35 \pi }{3}} \left(\alpha ^2 \left(5 \beta ^2+4\right)+2 \left(\beta ^2+1\right)\right)
+ \end{align}
+% B
+\begin{align}
+\text{Vlm}(2,-2)&=  \sqrt{\frac{3 \pi }{5}} \alpha ^2 \left(3 \beta ^2+2\right),\\
+\text{Vlm}(2,0)&=  \frac{1}{2} (-3) \sqrt{\frac{\pi }{5}} \left(\alpha ^2 \left(3 \beta ^2-2\right)+4 \beta ^2\right),\\
+\text{Vlm}(4,-2)&=  -\frac{1}{6} \sqrt{5 \pi } \alpha ^2 \left(5 \beta ^2+2\right),\\
+\text{Vlm}(4,0)&=  \frac{1}{24} \sqrt{\pi } \left(5 \alpha ^2 \left(15 \beta ^2+22\right)+60 \beta ^2+56\right),\\
+\text{Vlm}(4,4)&=  \frac{1}{24} \sqrt{35 \pi } \left(5 \alpha ^2+4\right) \left(5 \beta ^2+2\right)
+ \end{align}
+}
+
+%\subsection{Crystal Field Hamiltonian}
+
+\com{ Considering an octahedron,.... which one?
+ why only one but not all four?
+ spectra of all octahedra are similar...???
+}
 
@@
 
-%\begin{align}
-% bcs ham for electron with charge =-e=-1; sign change here
-%\tilde H = \tilde H^O -  q_A \tilde H^A + (3q_o+q_A) \tilde H^B,
-%\end{align}
-
 \section{Results: Single particle spectrum and JT instability}
 
-\subsection{t2g manifold} %states and energies}
-
-\az{Focus on t2g:}\\
+Before we present our results,
+let's briefly describe 
+the kind of behaviour that would indicate a JT instability 
+against the tilting and rotations of the octahedra,
+and how it relates to the standard JT problem.
+As describe in sec.~\ref{sec:JT},
+the optimum structure can have a finite distortion
+as long as 
+the splitting in the single particle spectrum has a different dependence on the distortion
+than the elastic energy associated with the changes in the unit cell volume.
+
+%\subsection{Dependence of electronic spectrum on the ``distortion'' angles}
+In case of \az{names? Tetragonal distortion, or quadrupolar distortion, }
+elongation or compression of a cube of size $a$ along two of its edges, say, by $a\delta_1,a\delta_2$,
+the change in the unit cell volume would be linear in $\delta_{1,2}$
+as $\sim a^3\left(\delta_1+\delta_1\right)$.
+So the elastic energy %(for an isotropic system) 
+changes as $\sim\left(\delta_1+\delta_1\right)^2$.
+A linear change ($\propto \delta_{1/2}$) in the electronic spectrum is required to produce
+ a finite distortion in the optimum structure (or the ground state of full electron-lattice/nuclear problem).
+For example, in the case of tetragonal distortion of an octahedron,
+ the total energy has a form
+$E=-\rho\delta + K \delta^2$, where $\rho$ and $K$ are constants 
+describing the changes in the electronic and elastic energies,
+and would be optimum at $\delta=\rho/2K$.
+In our case, however,
+the unit cell volume depends on the ``distortions'' $\alpha,\beta$ as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
+and, at $\alpha,\beta\ll1$,
+it changes as $-4a^3\left(\alpha ^2+\beta ^2\right)$.
+So, the behaviour we are looking for in the electronic spectrum does not have to be linear 
+but quadratic, which would compete with a quartic elastic energy $\left[ \sim\left(\alpha ^2+\beta ^2\right)^2 \right]$
+ to produce a finite distortion in the optimum structure.
+
+\az{Focus on t2g first:}\\
+
+\subsection{$t_{2g}$ manifold} %states and energies}
+
 Let's consider three cases separately, only rotation, only tilting, and both rotation and tilting.
@@
 
-\subsection{eg manifold}
+\subsection{$e_{g}$ manifold}
 

### 2023-09-13 manuscript/paper.tex
explaining the results in the figures, t2g: alpha0 and beta0 cases...

@@
 
+\sm{
+Before we present our results,
+let's briefly describe 
+the kind of behaviour that would indicate a JT instability 
+against the tilting and rotations of the octahedra,
+and how it relates to the standard JT problem.
+As describe in sec.~\ref{sec:JT},
+the optimum structure can have a finite distortion
+as long as 
+the splitting in the single particle spectrum has a different dependence on the distortion
+than the elastic energy associated with the changes in the unit cell volume.
+
+%\subsection{Dependence of electronic spectrum on the ``distortion'' angles}
+In case of \az{names? Tetragonal distortion, or quadrupolar distortion, }
+elongation or compression of a cube of size $a$ along two of its edges, say, by $a\delta_1,a\delta_2$,
+the change in the unit cell volume would be linear in $\delta_{1,2}$
+as $\sim a^3\left(\delta_1+\delta_1\right)$.
+So the elastic energy %(for an isotropic system) 
+changes as $\sim\left(\delta_1+\delta_1\right)^2$.
+A linear change ($\propto \delta_{1/2}$) in the electronic spectrum is required to produce
+ a finite distortion in the optimum structure (or the ground state of full electron-lattice/nuclear problem).
+For example, in the case of tetragonal distortion of an octahedron,
+ the total energy has a form
+$E=-\rho\delta + K \delta^2$, where $\rho$ and $K$ are constants 
+describing the changes in the electronic and elastic energies,
+and would be optimum at $\delta=\rho/2K$.
+In our case, however,
+the unit cell volume depends on the ``distortions'' $\alpha,\beta$ as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
+and, at $\alpha,\beta\ll1$,
+it changes as $-4a^3\left(\alpha ^2+\beta ^2\right)$.
+So, the behaviour we are looking for in the electronic spectrum does not have to be linear 
+but quadratic, which would compete with a quartic elastic energy $\left[ \sim\left(\alpha ^2+\beta ^2\right)^2 \right]$
+ to produce a finite distortion in the optimum structure.
+
+}
+
 \rev{
@@
 
-\subsection{Parameters $D_2$ and $D_4$ of the JT ion/atom}
-
+%\subsection{Parameters $D_2$ and $D_4$ of the JT ion/atom}
 The terms in square brackets on the right of Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}
@@
 
-\subsection{Examples}
+%\subsection{Examples}
 To complete the revision of the JT instability,
-let's consider the following two cases.
-\begin{enumerate}
-\item
- JT/B ion with $2$ electrons:
+let's consider %the following two cases.
+%\begin{enumerate}
+%\item
+a JT/B ion with $2$ electrons.
 In the symmetric octahedron case, 
@@
 we can now choose $yz,zx$ orbitals that have lower energy than the original $t_{2g}$ energy of the undistorted structure.
-\item
- JT/B ion with $3$ electrons:
+%\item
+In case of a JT/B ion with $3$ electrons, the situation is very different.
 Assuming Hund's coupling is enough to still produce complete spin polarisation,
@@
 because the gain due to $yz,zx$ is already balanced by the loss due to picking the higher energy $xy$ state.
-\end{enumerate}
+%\end{enumerate}
 
@@
 
-\subsection{cooperative JT and orbital order}
-just a brief description...
+%\subsection{cooperative JT and orbital order}
+\az{just a brief description... cooperative JT and orbital order}
 
@@
 
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
+\caption{$alpha=0$. 
+}
+\label{fig:t2g-alpha0}
+\end{center}
+\end{figure}
+
 \section{Results: Single particle spectrum and JT instability}
 
+\com{
 Before we present our results,
@@
  to produce a finite distortion in the optimum structure.
+}
 
@@
 
+We will first focus on the $t_{2g}$ manifold
+and see how the potential of the AB cages split it when 
+the octahedra tilts and rotates.
+
 \subsection{$t_{2g}$ manifold} %states and energies}
+\label{sec:t2g}
 
@@
 \subsubsection{Only rotation: $\alpha=0,\beta\neq 0$}
-If we ignore the coupling between the eg and t2g manifolds (between $xy$ and $x^2-y^2$ at $\alpha=0$[see if it's the same at non zero alhpa?]),
+\label{sec:alpha0}
+
+%We find that $xy$ is coupled to $x^2-y^2$
+%$t_{2g}$ and $e_{g}$ manifolds are coupled.
+
+Ignore the coupling between the $e_{g}$ and $t_{2g}$ manifolds (between $xy$ and $x^2-y^2$ at $\alpha=0$,
 their Hamiltonians turn out to be diagonal.
-
-% leading order expansion in beta:
-%A 2,4: \left\{\frac{64 \beta ^2}{63 \sqrt{3}}+O\left(\beta ^3\right),\frac{40960 \beta ^2}{5103 \sqrt{3}}+O\left(\beta ^3\right)\right\}
-%B 2,4: \left\{-\frac{3 \beta ^2}{7}+O\left(\beta ^3\right),-\frac{115 \beta ^2}{63}+O\left(\beta ^3\right)\right\}
-
-% from HA
-\begin{align}
-%\tilde H^A_{xy} =& -2 \Delta_{t2g},~
-%\tilde H^A_{yz} = \tilde H^A_{zx} =\Delta_{t2g},\\
-% \Delta_{t2g}(\alpha=0,\beta)
-%\Delta_{t2g} =&\left( \Delta_{2}  D_2 + \Delta_4 D_4\right),\\
+We can write the single particle energies of $t_{2g}$ states
+as
+\begin{align}
+\label{eq:theta0-Es}
 (E_{xy},&E_{yz},E_{zx})= (2, -1, -1)
-\left[\frac{}{} \Delta_{2}  D_2 + \Delta_4 D_4\right],\\
+\left[\frac{}{} \Delta_{2}  D_2 + \Delta_4 D_4\right],
+ \end{align}
+ where $E_{yz}$ and $E_{zx}$ are degenerate and 
+\begin{align}
 \Delta_{l} =&  \left(q_A \Delta_{l}^A + q_B\Delta_{l}^B\right)/a,~(l=2,4),\\
@@
  %from B
+ \label{eq:theta0-delB2}
 \Delta_{2}^B =& \frac{2}{7} \left(1-\sec ^3\beta\right)
 \simeq -\frac{3}{7}\beta ^2,\\
+\label{eq:theta0-delB4}
   \Delta_4^B =&\frac{5}{126} \left((7 \cos 4\beta-3) \sec ^5\beta-4\right)
-  \simeq -\frac{115}{63}\beta ^2,\\
+  \simeq -\frac{115}{63}\beta ^2.
  %\left( \Delta_{2}  D_2 + \Delta_4 D_4\right),\\
  \end{align}
-along with an overall shift
-\rev{E0t2g or change in it? how to define the expressions... plotted is always change in it...}
-\begin{align}
-E_{0}^{t_{2g}} =& \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a,\\
+ We see that $\Delta_{2/4}^A>0$ while $\Delta_{2/4}^B<0$,
+ revealing a competition between the two terms 
+ that would determine the sign and size of the term
+  in the square bracket in Eq.~\ref{eq:theta0-Es} 
+%  (hence the ground state and splitting) 
+  as $q_A$ (and hence $q_B$)
+  is varied.
+The average $t_{2g}$ energy
+ also shifts from
+$-2/5\Delta$ by an amount
+%\rev{E0t2g or change in it? how to define the expressions... plotted is always change in it...}
+\begin{align}
+\label{eq:theta0-E0}
+E_{0}^{t_{2g}} =& \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a
+-(2/5)f_{q_A}\Delta_{O},\\
 E_{0}^A =&
@@
 
-\begin{align}
-\end{align}
-
-Ignoring the coupling between t2g and eg states due to their large energetic difference, we still see that the hamiltonian seems to couple yz and zx if written in terms of multipoles compoments.
- it's only when we substitute Vlm in terms of alpha beta, 
- we see that i
-
-  and since in a degenrate manifold any linear combination can be taken as a valid eigenstate set, we we can take yz and zx as degenerate eigenstates.
-
-$D_2/D_4\simeq 14$ at 
-$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
-
-\az{$D_4=<r^4>=12.005$ at $a=7$ gives normalised $D_4=<r^4>/a^4=1/200$ that gives $\Delta=15/4 (q_o/a)$.}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
-\caption{$alpha=0$. 
-}
-\label{fig:evals-beta}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
-\caption{$beta=0$ case, $q_A=q_o/2$}
-\label{fig:evals-alpha}
-\end{center}
-\end{figure}
-
-\rev{
-
+The results in Eqs.~\ref{eq:theta0-Es},\ref{eq:theta0-E0}
+are summarised in Fig.~\ref{fig:t2g-alpha0},
+where $E_{xy}$, $E_{yz/zx}$ and $E_0^{t_{2g}}$ are shown
+as a function of $\beta$
+at three different values of $q_A/q_o=1/2,1,2$.
+We have 
+assumed $D_2=\sqrt{D_4}$ and
+taken $\Delta_o=4q_o/15a$ throughout this paper,
+which fixes the value of $D_4=1/200$, 
+and corresponds to $\Delta= 2.073$ eV at 
+$q_o=2$ e and $a=7.0$ bohr.
+We present the energies as a percentage of $\Delta_o$
+by calculating all quantities at the above values of $q_o,a$.
+Fig.~\ref{fig:t2g-alpha0} shows that
+the the competition between A and B cages
+determines the ground state and the size of the splitting between the 
+$t_{2g}$ states
+$E_{xy}$, and $E_{yz/zx}$.
+In Fig.~\ref{fig:t2g-alpha0}(a),
+where $q_A/q_o=1/2$ ($q_B/q_o=5/2$),
+the effect of B cage dominates.
+Since it's negative (see Eqs.~\ref{eq:theta0-delB2},\ref{eq:theta0-delB4}),
+it reverses the order in Eq.~\ref{eq:theta0-Es}
+and $E_{ex}$ becomes the lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $15^\circ$.
+When A cage dominates at large $q_A/q_o$,
+as shown in Fig.~\ref{fig:t2g-alpha0}(c) for $q_A/q_o=2$,
+$E_{yz/zx}$ are the single particle ground states (again with a splitting of $\sim6\%$ of $\Delta_o$ at $15^\circ$),
+whereas in the net effect of both cages
+is reduced in Fig.~\ref{fig:t2g-alpha0}(b)
+that corresponds to $q_A/q_o=1$
+and we only obtain a splitting of $\sim2\%$ of $\Delta_o$ at $15^\circ$
+between $E_{xy}$ and $E_{yz/zx}$ levels.
+Obviously, there will also be a point near 
+$q_A/q_o=1$ where A and B completely 
+cancel each others effect (not shown in Fig.~\ref{fig:t2g-alpha0}).
+We also see that $E_0^{t_{2g}}$ shows slight negative shift to a slight positive shift
+when as $q_A/q_o$ increases when going from Fig.~\ref{fig:t2g-alpha0}(a)
+to Fig.~\ref{fig:t2g-alpha0}(c).
+This is because the rotation suppresses the
+effect of AB cages on the
+gap $\Delta$ between $e_{g}$ and $t_{2g}$.
+Since A supports O while B opposes it,
+$\Delta$ slightly widens at small $q_A$ and shrinks at large $q_A$,
+shifting $E_0^{t_{2g}}$ slightly down or up with $\beta$.
+
+These results also indicate that in case of a superlattice with $q_A$ alternating
+between the two regimes shown in Figs.~\ref{fig:t2g-alpha0})(a,c),
+we should obtain a corresponding orbital order if the octahedra are rotated.
+
+\com{
 $\eta=\left(\frac{a\Delta_{O}}{q_o}\right)=\frac{4}{15}$
 at $D_4=1/200$\\
-
 $a=7$ bohr, and $\braket{r^4}=11.5809$ gives $2eV$ crystal field gap: $D_4=11.5809/a^4=0.004823365264473\simeq0.005=1/200=5\times10^{-3}$,
@@
 }
-
-\az{$D_2/D_4$ ranges between $15$-$20$ for typical gaps of $2$-$1$ eV and $a\simeq 7$ bohr (and $q_o=2e$). 
-It decreases with increasing gap as $1/\sqrt(gap)$, but is still $10$ at $gap=3.5$eV.}
+\com{$D_2/D_4$ ranges between $15$-$20$ for typical gaps of $2$-$1$ eV and $a\simeq 7$ bohr (and $q_o=2e$). 
+It decreases with increasing gap as $1/\sqrt(gap)$, but is still $10$ at $gap=3.5$eV.
+}
 
 \subsubsection{Only tilting: $\alpha\neq 0,\beta = 0$}
-
-The Hamiltonian still has a simple structure, 
+\label{sec:t2g-beta0}
+
+In this case, the situation gets slightly complicated as
+the couplings between the three states become finite. 
+However, 
+the Hamiltonian still has a simple structure, 
 \begin{align} 
@@
 \end{align}
-where the matrix elements have relatively long expressions and are can be found in the appendix. An approximation at small $\alpha,\beta$ is given later in this section.
-
-$\tilde H$ can be simplified by rotating the basis in $\{\ket{yz},\ket{zx}\}$ space,
+where the matrix elements have relatively long expressions and can be found in the appendix. An approximation at small $\alpha,\beta$ is given later in this section. 
+$\tilde H$ can be simplified by rotating the bases in $\{\ket{yz},\ket{zx}\}$ space
+to obtain bright and dark states
 as follows.
@@
 The state $\ket{D}$ at energy ${E_D= E_{yz}+\lambda}$ decouples 
-from the rest and the state $\ket{B}$ at energy ${E_{yz}-\lambda}$ obtains the enhanced collective coupling $\sqrt{2} g$, 
+from the rest (so is already an eigenstate of $\tilde H$) 
+and the state $\ket{B}$ at energy ${E_{yz}-\lambda}$ obtains the enhanced collective coupling $\sqrt{2} g$. 
 \com{
@@
 }
-and can be solved analytically to
-obtain the 
-the eigenstates
+The Hamiltonian can thus be solved analytically to
+obtain the remaining two
+eigenstates
 \begin{gather}
-\ket{+} = \cos\gamma \ket{xy} + \sin\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
-\ket{-} = \sin\gamma \ket{xy} - \cos\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
+%\ket{+} = \cos\gamma \ket{xy} + \sin\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
+%\ket{-} = \sin\gamma \ket{xy} - \cos\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
+\ket{+} = \cos\gamma \ket{xy} + \sin\gamma \ket{B},\\
+\ket{-} = \sin\gamma \ket{xy} - \cos\gamma \ket{B},\\
 \tan2\gamma = \sqrt{8}g/(E_{xy}-E_{yz}+\lambda)
@@
 
-$E_D$ and $E_{\pm}$ relative to their average ${E_0^{t_{2g}}= \left(E_{xy} + 2 E_{yz}\right)/3}$
-are shown in Fig.~\ref{fig:evals-alpha}.
-$E_0^{t_{2g}}$ itself shifts 
-with the tilting $\alpha$, 
-reflecting 
-the change in eg-t2g gap $\Delta$.
-This shift in $E_0^{t_{2g}}$ is
-%from its value 
-%$\frac{D_4}{3} \left(\frac{512q}{81 \sqrt{3}}-2 (6-q)\right)$\\
-%$\left(\frac{2}{729} \left(256 \sqrt{3}+243\right) q-4\right)D_4 $
-%at $\alpha=0=\beta$, 
-also included in Fig.~\ref{fig:evals-alpha}.
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
+\caption{$beta=0$ case, $q_A=q_o/2$}
+\label{fig:t2g-beta0}
+\end{center}
+\end{figure}
+
+$E_D, E_{\pm}$ relative to their average
+and the weight of $xy$ state $W_{xy}$ in $E_{\pm}$,
+as a function of $\alpha$ at $q_A/q_o=1/2,1,2$ (and $\Delta=15q_o/4a$)
+are shown in Fig.~\ref{fig:t2g-beta0}.
+The average shifts slightly with $\alpha,q_A$ by 
+$E_0^{t_{2g}}= \left(E_{xy} + 2 E_{yz}\right)/3-(2/5)f_{q_A}\Delta_{O}$,
+again reflecting 
+a change in the gap $\Delta$,
+and is also included in Fig.~\ref{fig:t2g-beta0}.
+Apart from the mixing between the three states $xy,yz,zx$ in $\ket{\pm}$ at finite $\alpha$, 
+Fig.~\ref{fig:t2g-beta0} shows a similar trend as in Fig.~\ref{fig:t2g-alpha0}
+but with an interesting twist.
+%Fig.~\ref{fig:evals-alpha} reveals another interesting point.
+In contrast to $\alpha=0$ case discussed in previous section,
+$W_{xy}$ is the largest in the highest (lowest) energy state at small (large) $q_A/q_o$,
+as shown in Fig.~\ref{fig:t2g-beta0}(a,c).
+$\alpha$ and $\beta$ would thus tend to produce different ordering
+(details in the next section).
+The splittings are also abut the same magnitude, between $4$-$6\%$ at $\alpha=15^\circ$
+at $q_A/q_o=1/2,2$ [Fig.~\ref{fig:t2g-beta0}(a,c)] and about $2\%$ at $q_A/q_o=1$ [Fig.~\ref{fig:t2g-beta0}(b)].
+The mixing is sizeable but still far from perfect ($50/50\%$) even at the largest $\alpha$ shown ($W_{xy}=0.25$-$0.35$ at $20^\circ$).
+% At unrealistically large $\alpha\sim30-40^\circ$, 
+Overall, at finite $\alpha$,
+the lowest energy state is either purely $xy/yz$,
+or contains at least some fraction of these,
+but it is never pure $xy$.
 

### 2023-09-13 manuscript/paper.tex
t2g gen case. figs explained and discussed.

@@
 %Fig.~\ref{fig:evals-alpha} reveals another interesting point.
-In contrast to $\alpha=0$ case discussed in previous section,
+In contrast to $\alpha=0$ case discussed in the previous section,
 $W_{xy}$ is the largest in the highest (lowest) energy state at small (large) $q_A/q_o$,
@@
 
-\subsubsection{Rotation and tilting: $\alpha,\beta\neq 0$}
-
-The t2g Hamiltonian in the general case cannot be solve analytically
- so there is no longer any advantage of ignoring the coupling between 
- the eg and t2g manifolds.
-We can thus keep these couplings and numerically solve 
-the full Hamiltonian instead.
-
 \begin{figure}[htbp]
@@
 \caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
-\label{default}
+\label{fig:t2g-ge-Es}
 \end{center}
@@
 \caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
-\label{default}
+\label{fig:t2g-ge-wts}
 \end{center}
 \end{figure}
+
+\subsubsection{Rotation and tilting: $\alpha,\beta\neq 0$}
+\label{sec:t2g-gen}
+
+The $t_{2g}$ Hamiltonian in the general case $\alpha,\beta\neq 0$ cannot be solve analytically
+ so there is no longer any advantage of ignoring the coupling between 
+ the $e_{g}$ and $t_{2g}$ manifolds.
+Even though their effect should be negligible due to a large gap $\Delta$ between the two manifolds,
+here we keep these couplings 
+and numerically solve
+the full Hamiltonian.
+Figure~\ref{fig:t2g-ge-Es}
+shows the energies at $\alpha=10^\circ$
+as a function of $\beta$
+at $q_A/q_o=1,2$ and $\Delta_o=4q_o/15a$ again.
+All states in the $t_{2g}$ mix up to make the eigenstates $\ket{E_i}, i=1,2,3$
+at energies $E_i, i=1,2,3$.
+\az{E0, can we show E0 only in the first fig and not all of them?}
+At $\beta=0$, these results correspond to $\alpha=10^\circ$ 
+in Figs.~\ref{fig:t2g-beta0}(a,c),
+so the lowest state at $\beta=0$
+here is $\ket{D}$ in Figs.~\ref{fig:t2g-ge-Es}(a)
+while it is the highest in Figs.~\ref{fig:t2g-ge-Es}(b).
+We see two anticrossings or level repulsion in either of Figs.~\ref{fig:t2g-ge-Es}(a,b)
+in different orders.
+In Figs.~\ref{fig:t2g-ge-Es}(a), 
+the anticorssing between the highest two states occurs at smaller $\beta$,
+while the situation is the opposite in Figs.~\ref{fig:t2g-ge-Es}(b) where 
+it occurs between the lowest pair at smaller $\beta$.
+From the results in the previous two sections,
+we know that not only A and B but also $\alpha$ and $\beta$ tend to establish different orders.
+To get more insight, the weights of these three $t_{2g}$ states in the three eigenstates 
+% in Fig.~\ref{fig:t2g-ge-Es}
+are shown in Fig.~\ref{fig:t2g-ge-wts}.
+Let's first focus on the left column ($q_A/q_o=1/2$). 
+Fig.~\ref{fig:t2g-ge-wts}(a)
+shows that, while $\ket{E_1}\to \ket{D}$ as $\beta\to 0$,
+$\ket{E_1}$ practically stays in $yz,xz$ subspace
+for $\beta<7^\circ$ and it quickly becomes $xy$
+as $\beta\alpha=10^\circ$.
+Fig.~\ref{fig:t2g-ge-wts}(b,c)
+show a complimentary behaviour 
+between $xy$ and $yz,xz$,
+where $\ket{E_3}$
+transforms from almost pure $xy$ at $\beta=0$
+to almost complete $yz,xz$ at $\beta\gtrsim\alpha=10^\circ$.
+The right column
+in Fig.~\ref{fig:t2g-ge-wts} ($q_A/q_o=2$),
+shows the opposite behaviour 
+about the ``resonance'' $\beta\sim\alpha$.
+Fig.~\ref{fig:t2g-ge-wts}(b,e)
+show an interesting aspect,
+the $W_{xy}$ peaking in the middle state $\ket{E_2}$
+around before it transfers between $\ket{E_1}$ and $\ket{E_2}$
+around $\beta\sim\alpha$,
+i.e., at $\beta$
+between the two anticrossings in 
+Fig.~\ref{fig:t2g-ge-Es},
+which makes sense if we imagine the continuation of various energy surfaces/curves
+in 
+the spectra in Fig.~\ref{fig:t2g-ge-Es}
+ignoring their anticorssings:
+$xy$ starts from the top and goes down in 
+Fig.~\ref{fig:t2g-ge-Es}(a),
+while it starts from the bottom and goes up
+in Fig.~\ref{fig:t2g-ge-Es}(b).
 

### 2023-09-14 manuscript/paper.tex
full lattice vs AB cages, comparison fig expalined.

@@
 as
-${q_A/q_0\to 1458/({256 \sqrt{3}+243})\simeq 2.124}$.
+${q_A/q_0\to 729/({256 \sqrt{3}+243})\simeq 1.062}$.
 %where they cancel each other exactly.
@@
 \end{align}
-whereas $V_{lm}^{B}$ is given by,
+whereas $V_{lm}^{B}$ are given by,
 %\az{full potential of the charges in deformed cage: }:
@@
 
-Ignore the coupling between the $e_{g}$ and $t_{2g}$ manifolds (between $xy$ and $x^2-y^2$ at $\alpha=0$,
+Ignoring the coupling between the $e_{g}$ and $t_{2g}$ manifolds (between $xy$ and $x^2-y^2$ at $\alpha=0$),
 their Hamiltonians turn out to be diagonal.
@@
 it reverses the order in Eq.~\ref{eq:theta0-Es}
-and $E_{ex}$ becomes the lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $15^\circ$.
+and $E_{xy}$ becomes lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $15^\circ$.
 When A cage dominates at large $q_A/q_o$,
@@
 $E_{yz/zx}$ are the single particle ground states (again with a splitting of $\sim6\%$ of $\Delta_o$ at $15^\circ$),
-whereas in the net effect of both cages
+whereas the net effect of both cages
 is reduced in Fig.~\ref{fig:t2g-alpha0}(b)
@@
 cancel each others effect (not shown in Fig.~\ref{fig:t2g-alpha0}).
-We also see that $E_0^{t_{2g}}$ shows slight negative shift to a slight positive shift
-when as $q_A/q_o$ increases when going from Fig.~\ref{fig:t2g-alpha0}(a)
+We also see that $E_0^{t_{2g}}$ changes from a slight negative shift to a slight positive shift
+with an increase in $q_A/q_o$ as we
+go from Fig.~\ref{fig:t2g-alpha0}(a)
 to Fig.~\ref{fig:t2g-alpha0}(c).
@@
 \end{align}
-where the matrix elements have relatively long expressions and can be found in the appendix. An approximation at small $\alpha,\beta$ is given later in this section. 
+where the matrix elements have relatively long expressions and 
+only an approximation at small $\alpha,\beta$ is given later in this section.
+%\com{are not given here \az{[?? can be found in the appendix.]} An approximation at small $\alpha,\beta$ is given later in this section.}
 $\tilde H$ can be simplified by rotating the bases in $\{\ket{yz},\ket{zx}\}$ space
@@
 (details in the next section).
-The splittings are also abut the same magnitude, between $4$-$6\%$ at $\alpha=15^\circ$
+The splittings are also about the same magnitude, between $4$-$6\%$ at $\alpha=15^\circ$
 at $q_A/q_o=1/2,2$ [Fig.~\ref{fig:t2g-beta0}(a,c)] and about $2\%$ at $q_A/q_o=1$ [Fig.~\ref{fig:t2g-beta0}(b)].
@@
 \includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
-\caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
+\caption{
+\az{Wts of eg in these states $\lesssim0.2\%$...} 
+$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
 \label{fig:t2g-ge-wts}
@@
 as a function of $\beta$
-at $q_A/q_o=1,2$ and $\Delta_o=4q_o/15a$ again.
+at $q_A/q_o=1/2,2$ and $\Delta_o=4q_o/15a$ again.
 All states in the $t_{2g}$ mix up to make the eigenstates $\ket{E_i}, i=1,2,3$
@@
 
-2x2 system so analytical sol always possible...
-either theta or phi 0 givens no couplings but just shifts and eg orbitals stays as the eigenstates....
+\com{
+So we consider the general case of
 
@@
 so 2x3 panel figure.
-
-\begin{align}
+}
+
+Since $e_{g}$ has only two states,
+ignoring the coupling between $e_{g}$ and $t_{2g}$,
+we can always analytically diagonalise it.
+The expressions for the
+matrix elements of the Hamiltonian are long however,
+so we present the expansion at small angles in the following.
+The diagonal terms with reference to the average $e_g$ energy are given by
+\begin{align}
+\label{eq:eg-hiix}
 (H_{x^2-y^2},&H_{z^2}) = (1,-1)
@@
 \Omega_{2}^B =&  \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right),\\
-\Omega_{4}^B =& \frac{1}{168} (-5) \left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right)
-\end{align}
-
-\begin{align}
-E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a,\\
+\Omega_{4}^B =& -\frac{5}{168}\left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right),
+\end{align}
+whereas the coupling between the two states is,
+\begin{align}
+\label{eq:eg-hijx}
+H_{x^2-y^2,z^2}&=
+\frac{2\alpha ^2 \beta}{567} 
+\left(128 q_A (3 D_2-20 D_4) - 81 \sqrt{3} q_B (2 D_2 -5 D_4)\right),
+%&=\frac{2\alpha ^2 \beta}{567} \left(384 ( D_2-\frac{20}{3} D_4)q_A  - 162 \sqrt{3} (D_2 -\frac{5}{2} D_4)q_B \right)
+\end{align}
+which vanishes if 
+either of $\alpha,\beta$ is zero.
+
+%Similar to the $t_{2g}$ case, 
+The average energy slightly shifts at nonzero $\alpha,\beta$
+from $3/5\Delta$ by an amount
+\begin{align}
+E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a - (3/5)f_{q_A}\Delta_o,\\
 E_0^A &=
@@
 
-\begin{align}
-H_{x^2-y^2,z^2}&=
-\frac{2\alpha ^2 \beta}{567} 
-\left(128 q_A (3 D_2-20 D_4) - 81 \sqrt{3} q_B (2 D_2 -5 D_4)\right)
-%&=\frac{2\alpha ^2 \beta}{567} \left(384 ( D_2-\frac{20}{3} D_4)q_A  - 162 \sqrt{3} (D_2 -\frac{5}{2} D_4)q_B \right)
-\end{align}
-
 \begin{figure}[htbp]
@@
 
+Diagonalising the Hamiltonian 
+(using the exact expressions instead 
+of the expansion in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx}),
+we obtain two eigenstates $\ket{\pm}$
+at energies $E_{\pm}$.
+Figure~\ref{fig:e-wts-eg}
+shows $E_{\pm}$ and weights $W_{x^2-y^2}$ of $x^2-y^2$ orbital
+in the two states
+as a function of $\beta$
+at $\alpha=10^\circ$, $\Delta_o=4q_o/15a$,
+and 
+$q_A/q_o=1/2,2$.
+We get the same ordering of orbitals with and without $z$ as in $t_{2g}$ case,
+i.e.,
+at $q_A/q_o=1/2$,
+$\beta$ tends to lower
+$x^2-y^2$ while $\alpha$ tend to lower $z^2$ orbitals,
+as indicated by the behaviour of $W_{x^2-y^2}$,
+which is almost zero in $\ket{E_{-}}$ at $\beta\lesssim 5^\circ \ll \alpha=10^\circ$,
+while it approaches unity at 
+at $\beta\gtrsim \alpha$.
+Similarly, at $q_A/q_o=2$,
+$W_{x^2-y^2}$ shows this behaviour for $\ket{E_{+}}$.
+This is also evident from the signs of the $\Omega_l$
+in Eqs.~\ref{eq:eg-hiix}.
+We see that $l=2$ terms have the same signs as $t_{2g}$ case but 
+$l=4$ terms have switched the signs. 
+Since $D_4$ is much smaller than $D_2$,
+we will still get find the same ordering as in $t_{2g}$ case.
+The splitting is much smaller in this case though, only $\sim 0.5\%$ of $\Delta_o$
+at $\beta=10^\circ$ in either case shown.
+To see how well
+the expansions in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx})
+can approximate the exact results,
+Fig.~\ref{fig:e-wts-eg} included
+them as Approx., which are almost indistinguishable from the exact results
+at $q_A/q_o=1/2$, but deviate at $q_A/q_o=2$ as their
+``resonance point'' is shifted towards larger $\beta$.
+
+\az{
+Summarise the results of $t_{2g},e_{g}$:
+1. splitting depending on the relative sizes of $q_A,q_B$
+2. local orbital ordering:\\
+two sets of competing factors:
+A vs B, and alpha vs beta.
+under the influence of A, alpha pushes xy down while yz/zx up.
+but beta does the opposite.
+Under the influence of B,
+the effect of alpha and beta are reversed, alpha pushes xy up while yz/zx down, etc.
+
+Does this picture survive when we consider the potential of the full ionic lattice at the site of B atom?
+Yes.... qualitatively, the same behaviour. just quantitative differences, the balance between A/B cages shifts towards lower $q_A$...
+
+}
+
 \subsection{Effect of the full lattice}
 
-In a crystal, obviously not only the nearest AB ions matter but other ions at longer distances also participate in the effect described in the prev sec.
-
-We can numerically calculate the multipole components of the potential of the full lattice by following the recipe in Ref.~\cite{PaxtonNotes, book?}
+In a crystal, obviously, not only the nearest coordination cage of A,B ions but also
+ the other ions (including O) at longer distances
+  participate in the effect considered in this paper.
+To see how much our results change when 
+%the potential of 
+ the full lattice (FL) is considered instead of just the nearest AB cages,
+we numerically calculate the multipole components of the potential
+ of the full lattice by following the recipe in Ref.~\cite{PaxtonNotes, book?}
 and Ewald summation method~\cite{Ewald}.
@@
 
-First,
+\com{First,
 FL does not preserve the cubic symmetry of the potential and the degeneracy of the t2g manifold 
 is slightly lifted at zero rotations, i.e., for a cubic structure.
-However, it is insignificant and we will just ignore it.
-
-What's more important is the ....
-
-Potential of full lattice does not change the qualitative picture.
-just shifts  .... so considering only AB cages overestimate or underestimate...
-
-If one renormalises the charges qA and qB, a
-quantitative agreement with the full lattice case can be obtained.
+However, it is insignificant and we will not discuss it further.
+What's more important is that the
+potential of the full lattice does not change the qualitative picture we resented
+but merely shifts the balance between A and B cages towards smaller $q_A$.
+}
+
+We find that the
+potential of the FL does not change the qualitative picture we presented
+but merely shifts the balance between A and B cages towards smaller $q_A$.
+This can be seen in Fig.~\ref{fig:t2g-lattice}
+where the energies of the $t_{2g}$ states as a function of $q_A/q_o$
+are compared for the two cases
+at $\alpha=0$, $\beta=20^\circ$ (and $\Delta=4q_o/15a$).
+In case of AB cages, the crossing of the 
+($xy$ and $yz/zx$)
+energy levels occurs 
+at $q_A/q_o\simeq1.1$,
+whereas the FL moves it to $q_A/q_o\simeq0.3$.
+The slopes of the lines are almost the same in both cases,
+meaning that the splitting due to octahedral rotations 
+would be the same in both cases if $q_A$ is measured 
+from their crossing points.
+The shift towards smaller $q_A$ in case of FL
+can be explained by noting that
+the next coordination cage beyond the first AB cages
+has O ions
+(at distances $\sqrt{5}a/2$ at $\alpha,\beta=0$) %and $\sqrt{5/2}a$ at $\alpha,\beta=0$),....
+%\az{both of which supports the A cage potential.??? plot and see... }
+that supports A cage
+against the B cage, lowering the value of $q_A$ that balances it
+at the crossing in Fig.~\ref{fig:t2g-lattice}.
+It increases the agreement between the two cases presented significantly,
+by moving the crossing point 
+to $q_A/q_o\simeq0.8$ (not shown in Fig.~\ref{fig:t2g-lattice}).
+
+From the above results, we also see that
+a comparison between the rotation induced splittings
+ in the two
+cases (FL vs AB cages)
+at a fixed value of $q_A$
+would show an underestimation or an overestimation 
+depending on whether $q_A$ lies to the right or the left side of the 
+middle point of the two crossings.
+The character of the eigenstates, however,
+would still be is disagreement at $q_A$
+between the two crossings.
+
+\com{
+Since the qualitative picture stays the same
+in FL case,
+we can 
+think of the effect of the rest of the ions in the lattice
+still in terms of the AB cages by renormalising $q_A$.
+}
 
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/et2g-vs-q-beta-20}
+\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
 \caption{$alpha=0$ evals vs q at $beta=20$. 
 }
-\label{fig:evals-q-beta}
+\label{fig:t2g-lattice}
 \end{center}

### 2023-09-14 src/main.f

@@ -691,7 +691,7 @@
 	ntot = noct*norbtms + noct*3*norbos;
 	ntottm = noct*norbtms;
 
-	write(*,*)'ntot, ntottm, qtot,a = ', ntot, ntottm, qtot, a
+	write(*,*)'ntot, ntottm, qtot,a = ', ntot, ntottm, qtotqtot, a
 	!i = noct*1 + noct*6*norbos
 	!write(*,*)'TM d^1: nelec = ', i
 	!write(*,*)'if only one spin, filled bands ~ ',0.5*i

### 2023-09-14 src/readinput.f

@@ -177,6 +177,7 @@
 	   soc(1) = soc(1)*eV2Har
 	   Dcf(5,2) = Del222
 	   nds(1) = (6-qa) + ion_d
+	   write(*,*)'WARNING: not resetting qtot using given qa, ion_d'
 	  ! set Hub%Fk and allocate Hub%Vee
 	  call 	setFk(1, eV2Har) !Hub(1)%U,Hub(1)%J,
 

### 2023-09-15 manuscript/paper.tex
full lattice vs AB. abstract.

@@
 
-\title{Cooperative Jahn-Teller effect with rigid octahedral rotations in perovskites}
+\title{Jahn-Teller effect with rigid octahedral rotations in perovskites} %Cooperative
 
@@
 \begin{abstract}
+
+\com{INTRO:
+The octahedral rotations and tilting in ABO$_3$ perovskites
+are usually explained in terms of 
+%a tolerance factor that depends on
+the relative sizes 
+of the three types of ions involved.
+}
+
+We consider
+rigid rotation and tilting of the 
+%BO$_{6/2}$ 
+octahedra
+ in ABO$_3$ perovskites
+and study the
+effect of the crystal field of the nearest A and B ion cages 
+%that immediately surround the octahedra
+on the single electron spectrum of the 
+central 
+transition metal ions.
+While the crystal field of the octahedra 
+that 
+% quenches the orbital angular momentum of the central B ion and 
+creates $e_g$ and $t_{2g}$ manifolds
+do not change with such rigid rotations, 
+the field of 
+%A and B ionic cages %that immediately surround the octahedra
+A and B cages
+deforms significantly %with the octahedral rotations 
+from the ideal octahedral field,
+leading to sizeable splittings in the $e_g$ and $t_{2g}$ manifolds of the central B ion.
+%Similar to the Jahn-Teller problem,
+The lowering of the ground state energy
+of a given many-electron configuration
+due to these splittings
+can thus be an important driving force behind the octahedral rotations 
+and associated structural transformations.
+We find that the size of the splitting and the local orbital ordering are
+determined by a competition between the A and B cages, 
+as well as a competition between the tilt and rotation angles.
+
+\com{
+SUM:
+While B and tilting tend to bring $xy,x^2-y^2$ down in energy,
+A and rotations do the opposite.
+}
+
+\com{
 
@@
 So... it is a strong perturbation to the octahedral field... and couples eg and t2g manifolds... and in lifts their degeneracies.... 
+}
 
 \end{abstract}
-%\maketitle
+\maketitle
 
@@
 middle point of the two crossings.
-The character of the eigenstates, however,
-would still be is disagreement at $q_A$
+Besides, the characters of the eigenstates
+would be in a disagreement at $q_A$
 between the two crossings.
@@
 \end{figure}
+
+\end{document}
 

### 2023-09-16 manuscript/paper.tex
intro paragraphs... literatiure... SOJT effect, nick etc. our appraach...

@@
-\documentclass[a4paper,prb]{revtex4-1}  %,twocolumn
+\documentclass[a4paper,prb,twocolumn]{revtex4-1}  %,twocolumn
 %\documentclass[preprint]{revtex4-1}
@@
 \maketitle
+
+\com{
+para1: 
+perovskites .. imp\\
+octa rot imp...
+
+para2: rot understood in terms of a tolerance factor... relative sizes of ions...\\
+nothing substantial exists in the literature to explore the cause/reasons ... rotations...\\
+except only recently, nick paper,... hydrogen bonding etc...
+
+para3:
+JT, ...
+}
+
+Perovskites are
+technologically important materials 
+that exhibit a rich variety of electronic, magnetic and optical properties
+due to the interplay between \az{[refine...]}
+orbital, spin, correlations, charge and structure.
+
+orbital ordering... 
+orbital-structure interplay.... structure-property relationships...
+
+ \com{https://www.frontiersin.org/articles/10.3389/fchem.2020.550625/full:\\
+advanced functional materials including photocatalysis, electrocatalysts
+ high-temperature superconductors, multiferroics, magnetic and magnetoresistive materials, materials for solar cell energy and photoluminescence
+}
+
+\com{https://www.perovskite-info.com/introduction:\\
+Perovskite materials exhibit intriguing and unusual physical properties that have been extensively studied for both practical applications and theoretical modeling and the materials science and applications of perovskites have been a broad research area open to many revolutionary discoveries for new device concepts.
+Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
+}
+
+Their crystal structures have a common formula unit ABX$_3$,
+where 
+%positive ions A and negative ions X form a cube and an octahedron around positive ion B.
+A and B are positive ions while X are negative ions 
+%whose six-fold coordination forms octahedra around B.
+that form octahedra around  B.
+In a cubic perovskite,
+the octahedra are symmetric, 
+but they can distort or simply rotate to lower the symmetry
+and produce a tetragonal or orthorhombic structure.
+While the tetragonal distortion of the octahedra is associated with
+a (cooperative) Jahn-Teller effect
+(i.e., the orbital degeneracy of the metal ion coordinated by the anionic octahedron
+is lifted, which stabilises the distortion),
+%[as it distorts the octahedral field at the central site that split its electronic states],
+the rotation and tilting of the octahedra are almost always 
+explained in terms of 
+the relative sizes of the three ions
+with the
+Goldschmidt tolerance factor. 
+%[probably because rigid rotation of the octahedra do not change its potential at the central site]
+%We only find two exceptions.
+
+%\az{terminology: tilting, rotation.... vague is ok here...}
+
+Based on density functional theory (DFT) calculations,
+a few recent works
+~\cite{garcia-fernandezJPCL2010,CammarataJCP2014,nick2016,YoshidaPRL21}, 
+however, 
+suggest that the octahedral rotation and tilting is 
+a second order Jahn-Teller effect
+%\az{describe SOJT in a sentence: coupling to the low lying unoccupied states on the JT ion, or orbital hybridisation with other ions, coupling between bands...}
+(i.e., the distortion is stabilised by a coupling between the ground and excited adiabatic potential energy surfaces).
+% garcia-fernandezJPCL2010
+Garcia-Fernandez et. al.
+study
+potassium fluoride perovskite family KMF$_3$ (M$=$Ca$^{2+}$ or a $3$d transition metal)
+and found that the tilting angle
+depends on the covalent bonding through the mixing of occupied and 
+low-lying unoccupied orbitals of the transition metal~\cite{garcia-fernandezJPCL2010}.
+% CammarataJCP2014
+Cammarata and Rondinelli
+find a negative correlation between metal-oxygen bond covalency 
+and octahedral rotation in orthorhombic perovskites oxides~\cite{CammarataJCP2014}.
+% Lee, nick2016
+Lee et. al. find 
+similar results for metal-iodine bonding in
+lead iodide perovskites,
+where the role of 
+the hydrogen bonding 
+in a hybrid perovskite with
+organic ammonium ions at A sites
+is also found to be crucial~\cite{nick2016}.
+Yoshida et. al.
+use DFT along with 
+representation theory analysis 
+and 
+indicate that 
+the rotations are induced by bonding interaction 
+between the valence and conduction band Bloch states at different wavevectors
+that are mapped onto each other on Brillouin zone folding
+ for the associated lattice distortion~\cite{YoshidaPRL21}.
+
+We take a completely different approach to this problem.
+We go back to the basics
+and see 
+what is it that lifts 
+ the orbital degeneracy in the classical JT effect?
+It is a deformation of the crystal field at the transition metal (JT ion) site.
+Does the same happen in the case of octahedral tilting and rotations?
+While the potential of the octahedral anion cage does not change in case of 
+rigid rotations for obvious reason,
+the net crystal field 
+does change indeed
+because the rest of the lattice is not only rotated (that turns its non-spherical potential)
+in a given octahedron's frame but also distorted.
+So, in principle, there should be a (first order) JT effect at play.
+Using this insight
+and elements of
+crystal field theory,
+here in this manuscript
+we explore this problem in detail and 
+find that the magnitude of this JT effect is sizeable for typical systems.
+
+%1-liner summaries:\\
+calcu sumamry...\\
+analysis summary\\
+results summary\\
+We analytical results... numerical results... full lattice...
+
+we explore states and energies of JT ion as a function of rotation and tilting angles...
+
+and find that the
+magnitude of the effect depends on the relative 
+charges on the two cations involved, A and B,
+and is sizeable for typical systems.
+
+\com{
+What is it that lifts the degeneracy in the classical JT effect?
+its a deformation of the crystal field at the transition metal/JT ion site.
+Does a deformation happen in the case of octahedral tilting and rotations?
+Ridig octahedral.... octaherdal field of the octahedral anions cage is not changed 
+... but... AB cages and the rest of the lattice is rotated and deformed... so... of course the CF should deform...
+So there are in principle clear signs that there should be a (first order) JT effect at play.
+}
+
+\az{
+Here, we .... just like the classical JT effect, where octahedral potential deforms....
+....
+
+we consider Pbnm.... other tilting and rotation.. glazer notation...???
+}
+
+\rev{structure of the paper:\\
+
+}
 

### 2023-09-16 manuscript/paper.tex
intro, our approach,,,, details... tilting/rotations... summary of calc and results in intro...

@@
 
+\az{
 orbital ordering... 
 orbital-structure interplay.... structure-property relationships... 
+}
 
@@
  the orbital degeneracy in the classical JT effect?
-It is a deformation of the crystal field at the transition metal (JT ion) site.
+It is a specific 
+deformation of the crystal field 
+%(${\sim z^2}$)
+at the transition metal (JT ion) site.
 Does the same happen in the case of octahedral tilting and rotations?
-While the potential of the octahedral anion cage does not change in case of 
+While the potential of an octahedral anion cage 
+in its own frame
+does not change 
+%in case of 
+with
 rigid rotations for obvious reason,
-the net crystal field 
-does change indeed
-because the rest of the lattice is not only rotated (that turns its non-spherical potential)
-in a given octahedron's frame but also distorted.
-So, in principle, there should be a (first order) JT effect at play.
+the total crystal field 
+does deform indeed
+because
+ the rest of the lattice is not only rotated
+  in a given octahedron's frame (that turns its non-spherical potential)
+ but also distorted owing to the accompanying structural transformation.
+%So, in principle, there should be a (first order) JT effect at play.
 Using this insight
@@
 here in this manuscript
-we explore this problem in detail and 
-find that the magnitude of this JT effect is sizeable for typical systems.
-
-%1-liner summaries:\\
-calcu sumamry...\\
-analysis summary\\
-results summary\\
-We analytical results... numerical results... full lattice...
-
-we explore states and energies of JT ion as a function of rotation and tilting angles...
-
-and find that the
-magnitude of the effect depends on the relative 
-charges on the two cations involved, A and B,
-and is sizeable for typical systems.
+we explore this problem in detail
+and find that,
+just like a first order JT effect,
+ the deformed crystal field 
+in this case also lifts the orbital degeneracy,
+by a significant amount for typical system parameters,
+signalling the instability against the rotations.
+
+% cooperative: pairs of alpha beta....
+% terminnology: rotation vs tilt
+% coop/consistent rotations/tilting then makes Pbnm etc...
+
+Since the octahedra are connected to each other 
+(making a 3-dimensional network in the perovskite structure),
+rotating one octahedron rotates all other in the crystal in a consistent fashion.
+We consider an octahedral \emph{rotation} $\beta$ around $001$ direction
+(that transforms the structure from cubic Pm$\bar 3$m to tetragonal P4/mbm)
+%({No.~$127$})
+followed by a \emph{tilting} $\alpha$ around the new $110$ direction
+(transforming to orthorhombic Pbnm, 
+%({No.~$62$})
+or Imma 
+%({No.~$74$})
+ at ${\beta=0}$).
+We use the rotation and tilt terminology for these 
+two angles throughout the rest of the manuscript.
+
+Beyond the anion octahedron,
+each transition metal ion B in a cubic perovskite
+is coordinated by two cation cages,
+a cube of A and an octahedron of B.
+Including the 
+%electrostatic 
+potential of these two ion cages
+into the 
+crystal field Hamiltonian of 
+the central ion B,
+we explore the effect 
+of the rotation and tilting on 
+the splittings in/of? its $t_{2g}$ and $e_g$ manifolds,
+created primarily by the anion's octahedral potential.
+We find that the size of the splitting 
+and local orbital ordering
+depend
+on the relative charges on the two types of cations
+and a competition between rotation and tilting.
+At typical parameter values,
+the splitting is large enough 
+to play a major role in 
+the corresponding structural instability. 
+The qualitative picture developed by our calculations 
+holds even when the potential of the full lattice is considered.
+
+\az{
+structure of the paper:\\
+}
+
+% 3 dim hilbert space of t2g, 2 dim hipbert space of eg
+% the mixing of t2g states due to rot and tilting is equiv to an artifact in cubic phase
+% so it's not similar to SOCJT states at diff energy mix due to distortion.
+% exlain it in the results/discussion section.....???
+
+\com{
+$\alpha=0, \beta \neq 0$\\
+Tetragonal:
+127. P 4 / m b m
+$\alpha \neq 0,\beta=0$\\
+Orthorhombic:
+74. I m m a
+$\alpha,\beta \neq 0$\\
+Orthorhombic:
+62. Pbnm
+}
 
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
+\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
 \caption{$alpha=0$. 
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
+\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
 \caption{$beta=0$ case, $q_A=q_o/2$}
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
+\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
 \caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
+\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
 \caption{
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
+\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
 \caption{$alpha=10^\circ$ case, $q_A=q_o/2,2q_o$}
@@
 \begin{center}
-\includegraphics[width=0.5\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
+\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
 \caption{$alpha=0$ evals vs q at $beta=20$. 
@@
 \end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \centering
-%\includegraphics[width=0.5\linewidth]{cartoon}
+%\includegraphics[width=1.0\linewidth]{cartoon}
 \caption{

### 2023-09-17 manuscript/paper.tex
intro completed

@@
 deforms significantly %with the octahedral rotations 
-from the ideal octahedral field,
-leading to sizeable splittings in the $e_g$ and $t_{2g}$ manifolds of the central B ion.
+from the ideal octahedral field
+in a way that
+leads to sizeable splittings in the $e_g$ and $t_{2g}$ manifolds of the central B ion.
 %Similar to the Jahn-Teller problem,
@@
 
-\com{
-para1: 
-perovskites .. imp\\
-octa rot imp...
-
-para2: rot understood in terms of a tolerance factor... relative sizes of ions...\\
-nothing substantial exists in the literature to explore the cause/reasons ... rotations...\\
-except only recently, nick paper,... hydrogen bonding etc...
-
-para3:
-JT, ...
-}
-
-Perovskites are
-technologically important materials 
-that exhibit a rich variety of electronic, magnetic and optical properties
-due to the interplay between \az{[refine...]}
-orbital, spin, correlations, charge and structure.
-
-\az{
-orbital ordering... 
-orbital-structure interplay.... structure-property relationships... 
+Perovskites  
+exhibit a rich variety of intriguing 
+electronic, magnetic and optical properties
+due to the interplay between
+spin, orbital, and structural degrees of freedom
+and widely varying electronic correlations.
+These materials 
+are important
+both for practical applications in all sorts of modern devices 
+and 
+fundamental understanding of various physical phenomena.
+
+\com{
+Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
 }
@@
 
-Their crystal structures have a common formula unit ABX$_3$,
+%Their crystal structures 
+The perovskite structures
+have a common formula unit ABX$_3$,
 where 
@@
 the rotation and tilting of the octahedra are almost always 
-explained in terms of 
+explained empirically in terms of 
 the relative sizes of the three ions
@@
 % garcia-fernandezJPCL2010
-Garcia-Fernandez et. al.
+Garcia-Fernandez~et~al.
 study
@@
 % Lee, nick2016
-Lee et. al. find 
+Lee~et~al. find 
 similar results for metal-iodine bonding in
@@
 is also found to be crucial~\cite{nick2016}.
-Yoshida et. al.
+Yoshida~et~al.
 use DFT along with 
@@
 Using this insight
-and elements of
-crystal field theory,
-here in this manuscript
-we explore this problem in detail
+and elements of crystal field theory,
+here in this manuscript,
+we 
+consider next two coordination cages around an octahedron
+% explore this problem in detail
 and find that,
@@
 of the rotation and tilting on 
-the splittings in/of? its $t_{2g}$ and $e_g$ manifolds,
+the splittings in its $t_{2g}$ and $e_g$ manifolds
+that are
 created primarily by the anion's octahedral potential.
@@
 
-\az{
-structure of the paper:\\
-}
-
 % 3 dim hilbert space of t2g, 2 dim hipbert space of eg
@@
 
-\com{
-What is it that lifts the degeneracy in the classical JT effect?
-its a deformation of the crystal field at the transition metal/JT ion site.
-Does a deformation happen in the case of octahedral tilting and rotations?
-Ridig octahedral.... octaherdal field of the octahedral anions cage is not changed 
-... but... AB cages and the rest of the lattice is rotated and deformed... so... of course the CF should deform...
-So there are in principle clear signs that there should be a (first order) JT effect at play.
-}
-
-\az{
-Here, we .... just like the classical JT effect, where octahedral potential deforms....
-....
-
-we consider Pbnm.... other tilting and rotation.. glazer notation...???
-}
-
-\rev{structure of the paper:\\
-
-}
+The paper is organised as follows.
+Section~\ref{sec:formalistm}
+presents the formalism and 
+sec.~\ref{sec:JT} reviews the Jahn-Teller effect to
+introduce the notation and concepts involved
+by considering tetragonal distortion of an octahedron.
+%\az{[.... multiple subsections?]}
+The model and calculations are presented
+in sec.~\ref{sec:calc},
+where
+we first discuss the relative contributions of the three closest ion cages,
+in the cubic structure, to
+the crystal field at the central transition metal site 
+and crystal field splitting between its $e_g$ and $t_{2g}$ manifolds
+(sec.~\ref{sec:relativeVoctABO}),
+and then 
+describe the deformation effects of 
+rigid octahedral rotations (sec.~\ref{sec:rotation})
+on
+the structure (sec.~\ref{sec:structure}) 
+and crystal field (sec.~\ref{sec:deformCF}).
+The results are in sec.~\ref{sec:results},
+where we seperately
+present the splitting in the single particle spectrum
+belonging to the $t_{2g}$ (sec.~\ref{sec:t2g})
+and $e_g$ (sec.~\ref{sec:eg-gen}) manifolds,
+and finally describe the effect of the full lattice (sec.~\ref{sec:FL}).
+\az{appendix?}
 
 \section{Formalism: Crystal field Hamiltonian using multipole expansion of the crystal field potential}
+\label{sec:formalistm}
 
@@
 \section{Janh-Teller Effect}
+\label{sec:JT}
 
@@
 \section{Model and calculations of ABO$_3$ Perovskites}%}
+\label{sec:calc}
 
@@
 \subsection{Rigid octahedral rotations}
+\label{sec:rotation}
 
 \subsection{Transformation of the crystal structure}
+\label{sec:structure}
 
@@
 \subsection{Deformation of the crystal field}
+\label{sec:deformCF}
 
@@
 \section{Results: Single particle spectrum and JT instability}
+\label{sec:results}
 
@@
 \subsection{$e_{g}$ manifold}
+\label{sec:eg-gen}
 
@@
 \subsection{Effect of the full lattice}
+\label{sec:FL}
 
@@
 \section{Appendix: Rotation matrices}
+\label{sec:append}
 

### 2023-09-17 manuscript/paper.tex
JT elect vs elastic... our case elastic and elec , squared alpha beta....

@@
 \begin{abstract}
-
-\com{INTRO:
-The octahedral rotations and tilting in ABO$_3$ perovskites
-are usually explained in terms of 
-%a tolerance factor that depends on
-the relative sizes 
-of the three types of ions involved.
-}
 
@@
 as well as a competition between the tilt and rotation angles.
-
-\com{
-SUM:
-While B and tilting tend to bring $xy,x^2-y^2$ down in energy,
-A and rotations do the opposite.
-}
-
-\com{
-
-Rigid octahedral rotations in a perovskite structure 
-deform the crystal field ... from the symmetric octahedral ...
-
-AB ions: cubic and octahedral cages....
-O ions: octahedral cage....
-Cubic structure: octahedral fields of AB and O are aligned... oriented 
-Tilting and rotation of the O octahedra.... change their relative orientation....
-and the the combined field is no more octahedral but has a lower symmetry. 
-AB lattice: V: -10 to 17 percent of V of O lattice....
-So... it is a strong perturbation to the octahedral field... and couples eg and t2g manifolds... and in lifts their degeneracies.... 
-}
 
@@
 is obtained at a finite distortion.
-As long as the two competing terms have different \az{[dependence, exponent? diff order polynomial?]} on the distortion,
-the ground state can have a finite distortion.
-We will use this argument and focus only on the changes
- in the electronic energy throughout this paper.
-
-\az{For our main problem, the rigid octahedral rotations in perovskites,
-we will see that 
-the energies are quadratic with the tilt and rotation angles. 
-However, the unit cell volume also changes quadratically with the angles 
-so the elastic energy still goes with a doubled power of this ``distortion'',
-i.e, it should be quartic in the angles.
-So the two will lead to an optimum structure with a finite tilt and rotation.
-}
-
-\sm{
-Before we present our results,
-let's briefly describe 
-the kind of behaviour that would indicate a JT instability 
-against the tilting and rotations of the octahedra,
-and how it relates to the standard JT problem.
-As describe in sec.~\ref{sec:JT},
-the optimum structure can have a finite distortion
-as long as 
-the splitting in the single particle spectrum has a different dependence on the distortion
-than the elastic energy associated with the changes in the unit cell volume.
-
-%\subsection{Dependence of electronic spectrum on the ``distortion'' angles}
-In case of \az{names? Tetragonal distortion, or quadrupolar distortion, }
-elongation or compression of a cube of size $a$ along two of its edges, say, by $a\delta_1,a\delta_2$,
-the change in the unit cell volume would be linear in $\delta_{1,2}$
-as $\sim a^3\left(\delta_1+\delta_1\right)$.
-So the elastic energy %(for an isotropic system) 
-changes as $\sim\left(\delta_1+\delta_1\right)^2$.
-A linear change ($\propto \delta_{1/2}$) in the electronic spectrum is required to produce
- a finite distortion in the optimum structure (or the ground state of full electron-lattice/nuclear problem).
-For example, in the case of tetragonal distortion of an octahedron,
+
+%\subsection{Dependence of electronic and elastic energies on the distortion}
+
+The dependence of the elastic energy on the distortion can be roughly explained
+as follows.
+Consider an 
+elongation or a compression of an octahedron along one of its axes by $a\delta$,
+where $a$ is the lattice constant of the cubic structure.
+The corresponding change in the unit cell volume would be linear in $\delta$
+as $\sim a^3 \delta$
+so the elastic energy
+would change as $\sim\delta^2$.
+Assuming a linear change 
+ in the electronic spectrum,
   the total energy has a form
@@
 and would be optimum at $\delta=\rho/2K$.
-In our case, however,
-the unit cell volume depends on the ``distortions'' $\alpha,\beta$ as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
-and, at $\alpha,\beta\ll1$,
-it changes as $-4a^3\left(\alpha ^2+\beta ^2\right)$.
-So, the behaviour we are looking for in the electronic spectrum does not have to be linear 
-but quadratic, which would compete with a quartic elastic energy $\left[ \sim\left(\alpha ^2+\beta ^2\right)^2 \right]$
- to produce a finite distortion in the optimum structure.
-
-}
-
-\rev{
-There is one point to clarify here. 
-We consider single particle spectrum, i.e.,
-single electron energy states
-to analyse the ground state of many electron system,
+In general, as long as the two competing terms 
+are not the same degree monomial in the distortion,
+the ground state can have a finite distortion.
+We will use this argument and focus only on the changes
+ in the electronic energy throughout this paper.
+
+\com{
+The dependence of the elastic energy on the distortion can be roughly explained
+as follows.
+Consider a 
+hypothetical 
+distortion of an octahedron 
+along two of its axes, say, by $a\delta_1,a\delta_2$,
+where $a$ is the lattice constant of the cubic structure.
+The corresponding change in the unit cell volume would be linear in $\delta_{1,2}$
+as $\sim a^3\left(\delta_1+\delta_1\right)$
+so the elastic energy %(for an isotropic system) 
+changes as $\sim\left(\delta_1+\delta_1\right)^2$.
+A linear change ($\propto \delta_{1/2}$) in the electronic spectrum is required to produce
+ a finite distortion in the optimum structure (or the ground state of full electron-lattice/nuclear problem).
+}
+
+It is worth reminding that, in the Jahn-Teller problem,
+we usually consider single particle spectrum, i.e.,
+single electron energy states,
+to analyse the ground state of a many electron system,
 which is the lowest energy ``electronic configuration'' 
@@
 using Hund's rule and see if it is degenerate or otherwise.
- }
 
@@
 \label{sec:results}
+
+Before we present our results,
+let's briefly describe 
+the kind of behaviour that would indicate a JT instability 
+against the tilting and rotations of the octahedra,
+and how it relates to the standard JT problem.
+As describe in sec.~\ref{sec:JT},
+the optimum structure can have a finite distortion
+as long as 
+the splitting in the single particle spectrum has a different dependence on the distortion
+than the elastic energy associated with the changes in the unit cell volume.
+In contrast to 
+%hypothetical 
+elongations or compressions 
+$a\delta_1,a\delta_2$ 
+of an octahedron along its axes,
+where the 
+ the unit cell volume changes
+as $\sim a^3\left(\delta_1+\delta_1\right)$
+and thus the elastic energy approximately goes
+as $\sim\left(\delta_1+\delta_1\right)^2$,
+the unit cell volume,
+in case of octahedral rotation and tilting,
+ depends on the ``distortions'' $\alpha,\beta$ 
+as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
+and, at $\alpha,\beta\ll1$,
+it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$
+leading to a quartic elastic energy that should roughly be
+$\sim\left(\alpha ^2+\beta ^2\right)^2$.
+So, the behaviour we are looking for in the electronic spectrum 
+is not linear
+but quadratic, 
+which would compete with such a quartic elastic energy
+ to produce a finite distortion in the optimum structure.
+Thinking of squared angles as the basic variables,
+the order of the electronic and elastic energy terms
+matches to the standard JT problem.
 

### 2023-09-17 manuscript/paper.tex
formalism, overview para.

@@
 The results are in sec.~\ref{sec:results},
-where we seperately
+where we %seperately
 present the splitting in the single particle spectrum
@@
 
+Let us introduce the basic formalism we use throughout this manuscript.
+The spectrum of an atom or ion
+changes in the presence of nearby charged species.
+This is described by the crystal field Hamiltonian of the atom
+that contains the coupling between its atomic orbitals and/or their energy shifts
+induced by the electrostatic potential of those charges.
+Since the angular part of atomic orbitals are described by 
+the spherical harmonics,
+an expansion of the potential at the atom's site 
+in the same bases simplify the analysis.
+This is because
+the effect of various multipole components of the potential
+is governed by certain selection rules 
+(enforced by the symmetries of the spherical harmonics
+through Gaunt coefficients, see below).
+
 If we have an arrangement of ions with charge $q$ around a given site,
@@
 $C_{l}^{m'm''m}=\braket{Y_{2,m'}| Y_{l,m}| Y_{2,m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
-and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the d-orbitals, assumed to be the same for all d-orbitals, i.e., the radial part of all d-orbitals is assumed to the same~\cite{paxton-notes}.
+and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the d-orbitals, assumed to be the same for all d-orbitals, i.e., the radial part of all d-orbitals is assumed the same~\cite{paxton-notes}.
 
@@
 Consider six O ions each of charge $-q_o$ making an octahedron of size $a$ (placed at the face centres of a cube of edge length $a$).
-The octahedral field at the centre of the octahedron or cube  
-is given by~\cite{pavariniChap}, [include monopole?? bcs later we incl its changes...]
+The non-spherical part of the potential they
+ produce at the centre of the octahedron
+ relevant for the d-orbitals contains 
+ only two $l=4$ components
+  in a specific ratio (${V_{4,0}:V_{4,4}=1:\sqrt{5/7}}$)
+ and called octahedral field. 
+It is given by~\cite{pavariniChap},
 \begin{align}
@@
 %where the monopole and $l>4$ components have been dropped
-The crystal field Hamiltonian of a transition metal ion B at the centre 
-turns out to be diagonal
-and splits the energy levels into two manifolds,
+The crystal field Hamiltonian of a transition metal ion B 
+%at the centre 
+in the field $V_{oct}(\vec r)$
+turns out to be diagonal,
+with its states split into two manifolds $\Delta$ apart:
 $H_{m,m} = -\Delta/3$ for $m\in\{-2,-1,1\}$ ($xy,yz,zx$ orbitals)
@@
 
-\section{Janh-Teller Effect}
+\section{Jahn-Teller Effect}
 \label{sec:JT}

### 2023-09-17 manuscript/paper.tex
JT, cooperative...

@@
 %\subsection{Examples}
-To complete the revision of the JT instability,
-let's consider %the following two cases.
+Let us consider %the following two cases.
 %\begin{enumerate}
 %\item
-a JT/B ion with $2$ electrons.
+a JT/B ion with two electrons.
 In the symmetric octahedron case, 
@@
 %\item
-In case of a JT/B ion with $3$ electrons, the situation is very different.
+In case of a JT/B ion with three electrons, the situation is very different.
 Assuming Hund's coupling is enough to still produce complete spin polarisation,
@@
 %\end{enumerate}
+
+%\subsection{cooperative JT and orbital order}
+%\az{just a brief description... cooperative JT and orbital order}
+To complete the revision of the JT instability,
+it is worth mentioning that
+JT effect occurs in all kinds of systems, molecules, clusters and crystals.
+In crystals, e.g., perovskites, it becomes a cooperative effect where the
+elongation of one octahedron is accompanied by a compression of adjacent octahedron,
+which minimises the changes in the unit cell volume and hence elastic energy cost of the transformation.
+Such alternate elongations and compressions also lead to 
+an interesting long range orbital ordering where alternate orbitals
+are populated on the adjacent JT sites.
 
@@
 }
-
-%\subsection{cooperative JT and orbital order}
-\az{just a brief description... cooperative JT and orbital order}
 

### 2023-09-18 manuscript/paper.tex
structrue and cages figure. and its caption

@@
-\documentclass[a4paper,prb,twocolumn]{revtex4-1}  %,twocolumn
+\documentclass[a4paper,prb,twocolumn]{revtex4-1}  %a4paper,prb,twocolumn
 %\documentclass[preprint]{revtex4-1}
+
+%\documentclass[12pt]{report}
 
@@
 \newcommand\scalemath[2]{\scalebox{#1}{\mbox{\ensuremath{\displaystyle #2}}}}
+
+%\usepackage[paperheight=18cm,paperwidth=14cm,textwidth=12cm]{geometry}
+%\usepackage{setspace}
+%\doublespacing
 
@@
 
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-1}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15}\\
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-z}
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-z}
+%\includegraphics[height=6.cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/AB-cages-deformed}
+\caption{
+Crystal structures and coordination cages.
+%Crystal structure of cubic and orthorhombic perovskites (a-b) and ion coordination cages around B ions (c-d).
+Crystal structures of cubic (a) and orthorhombic (b) perovskites.
+The anions (red) form the shown octahedra around 
+the B cations (gold), while the A cations (green) sit in the voids between the octahedra.
+In the orthorhombic structure shown here (b),
+ the octahedra are rotated and tilted by $15^\circ$.
+(c-d)
+The coordination cages of A %(green) 
+and B 
+%(golden) 
+cations just next to the anion 
+%(red) 
+octahedron
+around a B ion in cubic %(c)
+ and orthorhombic %(d)
+  perovskites.
+In the anion octahedron's frame,
+the cages are symmetric and aligned to the octahedron in the cubic perovskites (c),
+while they are rotated and slightly distorted in the orthorhombic perovskites (d).
+}
+\label{fig:cages}
+\end{center}
+\end{figure}
+
 \section{Formalism: Crystal field Hamiltonian using multipole expansion of the crystal field potential}
@@
 Assuming we only have d-orbitals ($l=2$) on the central atom,
-the matrix elements of the crystal field Hamiltonian of this system 
+the matrix elements of its crystal field Hamiltonian
 are given by,
@@
  produce at the centre of the octahedron
+ %that is 
  relevant for the d-orbitals contains 
@@
   in a specific ratio (${V_{4,0}:V_{4,4}=1:\sqrt{5/7}}$)
- and called octahedral field. 
+ and is called octahedral field. 
 It is given by~\cite{pavariniChap},
@@
 it is worth mentioning that
-JT effect occurs in all kinds of systems, molecules, clusters and crystals.
+JT effect occurs in all kinds of systems---molecules, clusters and crystals.
 In crystals, e.g., perovskites, it becomes a cooperative effect where the
 elongation of one octahedron is accompanied by a compression of adjacent octahedron,
-which minimises the changes in the unit cell volume and hence elastic energy cost of the transformation.
+which minimises the changes in the unit cell volume and hence the elastic energy cost of the transformation.
 Such alternate elongations and compressions also lead to 
@@
 to the unit cell of the orthorhombic structure under octahedral rotation and tilting.
-Assuming $\vec a_1,\vec a_2,\vec a_3$ to be the lattice vectors,
+Assuming 
+%$\vec a_1,\vec a_2,\vec a_3$
+$\textbf{a},\textbf{b},\textbf{c}$
+ to be the lattice vectors,
 two A and two B atoms in a layer are situated at
-$(\vec a_1 + \vec a_3/2)/2$, $(\vec a_2+ \vec a_3/2)/2$,
-and $(0,0,0)$, $(\vec a_1 + \vec a_2)/2$, 
-while similar atoms in the second layer are shifted by $\vec a_3/2$ from these.
+%$(\vec a_1 + \vec a_3/2)/2$, $(\vec a_2+ \vec a_3/2)/2$,
+$(\textbf{a} + \textbf{c}/2)/2$, $(\textbf{b}+ \textbf{c}/2)/2$,
+and $(0,0,0)$, 
+%$(\vec a_1 + \vec a_2)/2$, 
+$(\textbf{a}  + \textbf{b} )/2$, 
+while similar atoms in the second layer are shifted by 
+%$\vec a_3/2$
+$\textbf{c} /2$
+ from these.
 While the lattice vectors change under the rotation and tilting of the octahedra, 
@@
 \begin{array}{c}
-\vec a_1 \\
-\vec a_2\\
-\vec a_3\\
+%\vec a_1 \\
+%\vec a_2\\
+%\vec a_3\\
+\textbf{a}\\
+\textbf{b}\\
+\textbf{c}
 \end{array}
@@
  spectra of all octahedra are similar...???
+}
+
+\az{V20, JT:\\
+V2-2, V4-2, couple yz and zx.
+But... rotation.... produce all m components in general, ....
 }

### 2023-09-18 manuscript/paper.tex
bib file added... some citations added to tex.

@@
 a few recent works
-~\cite{garcia-fernandezJPCL2010,CammarataJCP2014,nick2016,YoshidaPRL21}, 
+~\cite{garcia-fernandezJPCL10,CammarataJCP14,LeeCM16,YoshidaPRL21}, 
 however, 
@@
 depends on the covalent bonding through the mixing of occupied and 
-low-lying unoccupied orbitals of the transition metal~\cite{garcia-fernandezJPCL2010}.
+low-lying unoccupied orbitals of the transition metal~\cite{garcia-fernandezJPCL10}.
 % CammarataJCP2014
@@
 find a negative correlation between metal-oxygen bond covalency 
-and octahedral rotation in orthorhombic perovskites oxides~\cite{CammarataJCP2014}.
+and octahedral rotation in orthorhombic perovskites oxides~\cite{CammarataJCP14}.
 % Lee, nick2016
@@
 organic ammonium ions at A sites
-is also found to be crucial~\cite{nick2016}.
+is also found to be crucial~\cite{LeeCM16}.
 Yoshida~et~al.
@@
  for the associated lattice distortion~\cite{YoshidaPRL21}.
+
+\begin{figure}[htbp]
+\begin{center}
+%\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-1}
+\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-2}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15}\\
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-z}
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-z}
+%\includegraphics[height=6.cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/AB-cages-deformed}
+\caption{
+Crystal structures and coordination cages.
+%Crystal structure of cubic and orthorhombic perovskites (a-b) and ion coordination cages around B ions (c-d).
+Crystal structures of cubic (a) and orthorhombic (b) perovskites.
+The anions (red) form the shown octahedra around 
+the B cations (gold), while the A cations (green) sit in the voids between the octahedra.
+In the orthorhombic structure shown here (b),
+ the octahedra are rotated and tilted by $15^\circ$.
+(c-d)
+The coordination cages of A %(green) 
+and B 
+%(golden) 
+cations just next to the anion 
+%(red) 
+octahedron
+around a B ion in cubic %(c)
+ and orthorhombic %(d)
+  perovskites.
+In the anion octahedron's frame,
+the cages are symmetric and aligned to the octahedron in the cubic perovskites (c),
+while they are rotated and slightly distorted in the orthorhombic perovskites (d).
+}
+\label{fig:struc}
+\end{center}
+\end{figure}
 
@@
 (making a 3-dimensional network in the perovskite structure),
-rotating one octahedron rotates all other in the crystal in a consistent fashion.
+rotating one octahedron rotates all other in the crystal in a consistent fashion;
+ see Figs.~\ref{fig:struc}(a,b).
 We consider an octahedral \emph{rotation} $\beta$ around $001$ direction
@@
 is coordinated by two cation cages,
-a cube of A and an octahedron of B.
+a cube of A and an octahedron of B, as shown in Figs.~\ref{fig:struc}(c,d).
 Including the 
@@
 
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-1}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15}\\
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-z}
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-z}
-%\includegraphics[height=6.cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/AB-cages-deformed}
-\caption{
-Crystal structures and coordination cages.
-%Crystal structure of cubic and orthorhombic perovskites (a-b) and ion coordination cages around B ions (c-d).
-Crystal structures of cubic (a) and orthorhombic (b) perovskites.
-The anions (red) form the shown octahedra around 
-the B cations (gold), while the A cations (green) sit in the voids between the octahedra.
-In the orthorhombic structure shown here (b),
- the octahedra are rotated and tilted by $15^\circ$.
-(c-d)
-The coordination cages of A %(green) 
-and B 
-%(golden) 
-cations just next to the anion 
-%(red) 
-octahedron
-around a B ion in cubic %(c)
- and orthorhombic %(d)
-  perovskites.
-In the anion octahedron's frame,
-the cages are symmetric and aligned to the octahedron in the cubic perovskites (c),
-while they are rotated and slightly distorted in the orthorhombic perovskites (d).
-}
-\label{fig:cages}
-\end{center}
-\end{figure}
-
 \section{Formalism: Crystal field Hamiltonian using multipole expansion of the crystal field potential}
@@
 $C_{l}^{m'm''m}=\braket{Y_{2,m'}| Y_{l,m}| Y_{2,m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
-and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the d-orbitals, assumed to be the same for all d-orbitals, i.e., the radial part of all d-orbitals is assumed the same~\cite{paxton-notes}.
+and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the d-orbitals, assumed to be the same for all d-orbitals, i.e., the radial part of all d-orbitals is assumed the same~\cite{PaxtonNotes}.
 
@@
 rigid rotation/tilting: orthorhombic deformation... 
-typically associated with the relative sizes of the A, B,O ions.~\cite{goodenoughPRL05}.
+typically associated with the relative sizes of the A, B,O ions.~\cite{ZhouPRL05}.
 
@@
 $\mathcal{R}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics that we use (see appendix~\ref{sec:appendix}). 
-It can be calculated using the method described in Ref.~\cite{evanic}.
+It can be calculated using the method described in Ref.~\cite{IvanicJPC96}.
 \az{next para?}
@@
 we numerically calculate the multipole components of the potential
- of the full lattice by following the recipe in Ref.~\cite{PaxtonNotes, book?}
+ of the full lattice by following the recipe in Ref.~\cite{FinnisPRL98,PaxtonPRB08,PaxtonNotes}
 and Ewald summation method~\cite{Ewald}.
 To do this, 
-we borrow relevant routines from the Tight Binding code TBE [confirm the names] in Questaal~\cite{https://www.questaal.org/} that implements these methods.
+we borrow relevant routines from the tight binding package in Questaal suite~\cite{Questaal} that implements these methods.
 
@@
 
+\label{Bibliography}
+\bibliographystyle{apsrev4-1}
+\bibliography{perovskites}
+
 \end{document}

### 2023-09-19 manuscript/paper.tex
intro ... many references...

@@
  in ABO$_3$ perovskites
+ from the viewpoint of Jahn-Teller problem
  and study the
@@
 
+\com{
+Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
+}
+
+ \com{https://www.frontiersin.org/articles/10.3389/fchem.2020.550625/full:\\
+advanced functional materials including photocatalysis, electrocatalysts
+ high-temperature superconductors, multiferroics, magnetic and magnetoresistive materials, materials for solar cell energy and photoluminescence
+}
+
+\com{https://www.perovskite-info.com/introduction:\\
+Perovskite materials exhibit intriguing and unusual physical properties that have been extensively studied for both practical applications and theoretical modeling and the materials science and applications of perovskites have been a broad research area open to many revolutionary discoveries for new device concepts.
+Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
+}
+
 Perovskites  
@@
 
-\com{
-Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
-}
-
- \com{https://www.frontiersin.org/articles/10.3389/fchem.2020.550625/full:\\
-advanced functional materials including photocatalysis, electrocatalysts
- high-temperature superconductors, multiferroics, magnetic and magnetoresistive materials, materials for solar cell energy and photoluminescence
-}
-
-\com{https://www.perovskite-info.com/introduction:\\
-Perovskite materials exhibit intriguing and unusual physical properties that have been extensively studied for both practical applications and theoretical modeling and the materials science and applications of perovskites have been a broad research area open to many revolutionary discoveries for new device concepts.
-Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
-}
-
 %Their crystal structures 
@@
 the octahedra are symmetric, 
-but they can distort or simply rotate to lower the symmetry
-and produce a tetragonal or orthorhombic structure.
+but they can 
+distort~\cite{
+BersukerCCR75,
+KugelSPU82,
+MillisN98,
+TerakuraPMS07,
+HalcrowRSC13,
+LufasoAC04}
+or simply 
+rotate~\cite{
+GlazerAC72, ThomasAC96,
+WoodwardAC97a,WoodwardAC97b,
+HowardAC98,StokesAC02,AngelPRL05}
+ to lower the symmetry
+and produce, e.g., a rhombohedral, tetragonal or orthorhombic structure.
+% cubic perovskite [spacegroup 221] can transform to:
+% crystal system: spacegroups
+% triclinic: 2
+% monoclinic: 11,12,15
+% orthorhombic: 59,62,63,71,74
+% tetragonal 127,139,140
+% rhombohedral/trigonal: 167
+% cubic: 204, 221 
+Octahedral rotations also occur in other perovskite related structures
+and
+have been extensively 
+studied
+due to their crucial role in determining various physical properties,
+e.g., in 
+ferroelectric~\cite{GhosezNM11,
+SchickPRB14,
+SimPRB14,
+LeePRL17,
+WangPRL22,
+ZhouPRB22,
+GaoPRB23} and 
+multiferroic~\cite{BenedekPRL11,
+YangPRL14,
+YePRB18,
+ZhangPRL20,
+ZhangYajunPRL20, 
+ZhouPRB21,
+ZhangPRL22}
+systems.
+The interplay of octahedral rotations
+and 
+spin-orbit coupling~\cite{AmatNL14,KrachJPCM23},
+breathing distortions~\cite{BalachandranPRB13},
+strain~\cite{Aguado-PuentePRL11},
+defects~\cite{JiaPRB22}, and
+pressure~\cite{XiangPRB17},
+and 
+their role in
+magnetostructural phase transitions~\cite{JohnsonPRL20},
+orbital order~\cite{OgawaPRL12,ChenPRL19}, orbital anisotropy~\cite{HuangPRB21}, 
+and
+%surface electronic structure under in-plane uniaxial compression~\cite{MoralesPRL23}
+surface electronic structure~\cite{MoralesPRL23},
+has also been investigated.
+% JT interacting with octa tilting:
+Since, usually, the octahedra are not just %(Jahn-Teller) 
+distorted or rotated but a combination of both,
+the influence of these two 
+structural mutations %instabilities 
+on each other has recently been explored by many authors~\cite{LufasoAC04,CarpenterAC09,ChenPRL19}.
+
+\com{---a cooperative Jahn-Teller 
+effect~\cite{JahnPRSL37,JahnPRSL38,
+OpikRS57,
+Sturge68,
+GehringRPP75,
+BersukerCCR75,
+KugelSPU82,
+MillisN98,
+LufasoAC04,
+TerakuraPMS07,
+HalcrowRSC13,
+PavariniChap}
+whereby the orbital degeneracy of the B ions
+is lifted that stabilises the distortion---
+}
+
 While the tetragonal distortion of the octahedra is associated with
-a (cooperative) Jahn-Teller effect
+a (cooperative) Jahn-Teller 
+effect~\cite{JahnPRSL37,JahnPRSL38,
+OpikRS57,
+Sturge68,
+GehringRPP75,
+BersukerCCR75,
+KugelSPU82,
+MillisN98,
+LufasoAC04,
+TerakuraPMS07,
+HalcrowRSC13,
+PavariniChap}
 (i.e., the orbital degeneracy of the metal ion coordinated by the anionic octahedron
@@
 with the
-Goldschmidt tolerance factor. 
+Goldschmidt tolerance factor~\cite{Goldschmidt1926,KieslichCS15}. 
 %[probably because rigid rotation of the octahedra do not change its potential at the central site]
@@
 
-%\az{terminology: tilting, rotation.... vague is ok here...}
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-bonds-labelled-1}
+%\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-2}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15}\\
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-z}
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-z}
+%\includegraphics[height=6.cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/AB-cages-deformed}
+\caption{
+Crystal structures and coordination cages.
+Crystal structures of cubic (a) and orthorhombic (b) perovskites.
+The anions (red) form the shown octahedra around 
+the B cations (gold), while the A cations (green) sit in the voids between the octahedra.
+In the orthorhombic structure shown here (b),
+ the octahedra are rotated and tilted by $15^\circ$.
+(c-d)
+The coordination cages of A %(green) 
+and B 
+%(golden) 
+cations just next to the anion 
+%(red) 
+octahedron
+around a B ion in cubic %(c)
+ and orthorhombic %(d)
+  perovskites.
+In the anion octahedron's frame,
+the cages are symmetric and aligned to the octahedron in the cubic perovskites (c),
+while they are rotated and slightly distorted in the orthorhombic perovskites (d).
+}
+\label{fig:struc}
+\end{center}
+\end{figure}
 
@@
 a second order Jahn-Teller effect
+~\cite{HerzbergZPC33,BersukerPL66,KristoffelPSSB67,PearsonJMS83,FultonJCP04,BersukerCR13}
 %\az{describe SOJT in a sentence: coupling to the low lying unoccupied states on the JT ion, or orbital hybridisation with other ions, coupling between bands...}
@@
 
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-1}
-\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-2}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15}\\
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-z}
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-z}
-%\includegraphics[height=6.cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/AB-cages-deformed}
-\caption{
-Crystal structures and coordination cages.
-%Crystal structure of cubic and orthorhombic perovskites (a-b) and ion coordination cages around B ions (c-d).
-Crystal structures of cubic (a) and orthorhombic (b) perovskites.
-The anions (red) form the shown octahedra around 
-the B cations (gold), while the A cations (green) sit in the voids between the octahedra.
-In the orthorhombic structure shown here (b),
- the octahedra are rotated and tilted by $15^\circ$.
-(c-d)
-The coordination cages of A %(green) 
-and B 
-%(golden) 
-cations just next to the anion 
-%(red) 
-octahedron
-around a B ion in cubic %(c)
- and orthorhombic %(d)
-  perovskites.
-In the anion octahedron's frame,
-the cages are symmetric and aligned to the octahedron in the cubic perovskites (c),
-while they are rotated and slightly distorted in the orthorhombic perovskites (d).
-}
-\label{fig:struc}
-\end{center}
-\end{figure}
+\com{
+We take a completely different approach to this problem.
+We go back to the basics
+and explore the octahedral rotations from the perspective
+of (first order) JT effect itself
+}
 
@@
 Using this insight
-and elements of crystal field theory,
+and elements of crystal field theory~\cite{BetheAP29,VanVleckPR32,PavariniChap},
 here in this manuscript,
@@
 (making a 3-dimensional network in the perovskite structure),
-rotating one octahedron rotates all other in the crystal in a consistent fashion;
+rotating one octahedron rotates all other in the crystal in a consistent fashion~\cite{GlazerAC72};
  see Figs.~\ref{fig:struc}(a,b).
@@
  and is called octahedral field. 
-It is given by~\cite{pavariniChap},
+It is given by~\cite{PavariniChap},
 \begin{align}
@@
 
-The Jahn--Teller effect~\cite{Jahn-Teller} describes the 
+The Jahn--Teller effect~\cite{JahnPRSL37,JahnPRSL38,OpikRS57,Sturge68,GehringRPP75,KugelSPU82,PavariniChap} describes the 
 geometric and electronic instability of a %non-linear 
@@
   the total energy has a form
-$E=-\rho\delta + K \delta^2$, where $\rho$ and $K$ are constants 
+$E=-\rho\delta + K \delta^2$, where $\rho$ and $K$ are positive constants 
 describing the changes in the electronic and elastic energies,
@@
 we obtain the
- octahedral potential for a symmetric octahedron~\cite{pavariniChap},
+ octahedral potential for a symmetric octahedron~\cite{PavariniChap},
 \begin{align}
@@
  of the full lattice by following the recipe in Ref.~\cite{FinnisPRL98,PaxtonPRB08,PaxtonNotes}
-and Ewald summation method~\cite{Ewald}.
+and Ewald summation method~\cite{Ewald1921}.
 To do this, 
@@
 at the crossing in Fig.~\ref{fig:t2g-lattice}.
-It increases the agreement between the two cases presented significantly,
+It significantly increases the agreement between the two cases presented
 by moving the crossing point 
@@
 \label{Bibliography}
-\bibliographystyle{apsrev4-1}
+%\bibliographystyle{apsrev4-1}
 \bibliography{perovskites}

### 2023-09-20 manuscript/paper.tex
longer equations inside widetext -some minor changes

@@
 %that immediately surround the octahedra
-on the single electron spectrum of the 
+on the single electron spectrum of B, the 
 central 
@@
 % quenches the orbital angular momentum of the central B ion and 
-creates $e_g$ and $t_{2g}$ manifolds
+creates degenerate manifolds $e_g$ and $t_{2g}$ 
 do not change with such rigid rotations, 
@@
 in a way that
-leads to sizeable splittings in the $e_g$ and $t_{2g}$ manifolds of the central B ion.
+leads to sizeable splittings in 
+%the $e_g$ and $t_{2g}$ manifolds of the central B ion.
+these manifolds.
 %Similar to the Jahn-Teller problem,
@@
 structural mutations %instabilities 
-on each other has recently been explored by many authors~\cite{LufasoAC04,CarpenterAC09,ChenPRL19}.
+on each other has recently been explored by many authors~\cite{LufasoAC04,CarpenterAC09,ChenPRL19}
+as well.
 
@@
 of the rotation and tilting on 
-the splittings in its $t_{2g}$ and $e_g$ manifolds
+%the splittings in 
+its $t_{2g}$ and $e_g$ manifolds
 that are
 created primarily by the anion's octahedral potential.
-We find that the size of the splitting 
+We find that the degeneracy of $t_{2g}$ and $e_g$
+is lifted, and
+the size of the splitting 
 and local orbital ordering
@@
 where
-we first discuss the relative contributions of the three closest ion cages,
-in the cubic structure, to
+we first discuss the relative contributions of the three closest ion cages
+in the cubic structure
+ to
 the crystal field at the central transition metal site 
@@
 \end{align}
-which shows that $V_{AB}(\vec r)\to 0$
-as
-${q_A/q_0\to 729/({256 \sqrt{3}+243})\simeq 1.062}$.
+which shows that ${V_{AB}(\vec r)}$ vanishes
+at
+$q_A/q_o=729/({256 \sqrt{3}+243}) {\simeq 1.062}$.
 %where they cancel each other exactly.
@@
 We obtain the following exact expressions for $V_{lm}^{A}$,
+\begin{widetext}
 %\rev{$V(r)=q\sum_{i}(\sqrt{ ..... r\cos... })^{-1}$}
@@
 V^A_{2,0}&= 32 \sqrt{\frac{\pi }{5}} \left(\frac{2 \sec ^3\alpha  \sin ^2\beta }{(\cos 2 \beta +2)^{5/2}}-\frac{32 \sqrt{\frac{\pi }{5}} (\cos 2 \beta -\cos 2 \alpha )}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}\right),\\
-V^A_{4,-2}&= \frac{128}{3} \sqrt{5 \pi } \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right),\\ \nonumber
-V^A_{4,0}&= -\frac{16}{3} \sqrt{\pi } \left(\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}\right. \\
-&+\left. \frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}\right),\\
-V^A_{4,4}&=-\frac{128}{3} \sqrt{35 \pi } \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right),
-\end{align}
+V^A_{4,-2}&= \frac{128\sqrt{5 \pi } }{3} \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right),\\ \nonumber
+V^A_{4,0}&= \frac{16\sqrt{\pi } }{3} \left(
+\frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}
+-
+\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}
+\right),\\
+V^A_{4,4}&=-\frac{128\sqrt{35 \pi } }{3} \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right),
+\end{align}
+\end{widetext}
 whereas $V_{lm}^{B}$ are given by,
@@
 \begin{align}
-V^{B}_{2,-2}&=  \frac{64 \sqrt{\frac{3 \pi }{5}} \sin ^2\alpha  \sec ^3\beta }{(\cos 2 \alpha +3)^{5/2}},
+V^{B}_{2,-2}&= 64 \sqrt{\frac{3 \pi }{5}}  \frac{\sin ^2\alpha  \sec ^3\beta }{(\cos 2 \alpha +3)^{5/2}},
  \\ V^{B}_{2,0}&=  4 \sqrt{\frac{\pi }{5}} \left(\sec ^3\alpha -\frac{8 \sec ^3\beta }{(\cos 2 \alpha +3)^{3/2}}\right),\\
- V^{B}_{4,-2}&=  -\frac{128 \sqrt{5 \pi } \sin ^2\alpha  \sec ^5\beta }{3 (\cos 2 \alpha +3)^{7/2}},\\ 
-V^{B}_{4,0}&= \frac{4}{3} \sqrt{\pi } \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right),\\
- V^{B}_{4,4}&=  -\frac{16 \sqrt{35 \pi } (-20 \cos 2 \alpha +\cos 4 \alpha -13) \sec ^5\beta }{3 (\cos 2 \alpha +3)^{9/2}}.
+ V^{B}_{4,-2}&=  - \frac{128 \sqrt{5 \pi } }{3} \frac{\sin ^2\alpha  \sec ^5\beta }{ (\cos 2 \alpha +3)^{7/2}},\\ 
+V^{B}_{4,0}&= \frac{4\sqrt{\pi } }{3} \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right),\\
+ V^{B}_{4,4}&=  - \frac{16 \sqrt{35 \pi } }{3} \frac{(-20 \cos 2 \alpha +\cos 4 \alpha -13) %\sec ^5\beta }
+ }
+ {(\cos 2 \alpha +3)^{9/2} \cos^5\beta}.
  \end{align}
@@
  \simeq \frac{64}{63 \sqrt{3}}\beta ^2,\\
+ \nonumber
 \Delta_4^A =&
  \frac{160 \sin ^2\beta}{63 (\cos 2\beta+2)^{9/2}} \times \\
-&  (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82),\\
+&  (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82)\\
 \simeq& \frac{40960}{5103 \sqrt{3}}\beta ^2,\\
@@
 \label{eq:theta0-E0}
-E_{0}^{t_{2g}} =& \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a
--(2/5)f_{q_A}\Delta_{O},\\
+E_{0}^{t_{2g}} = \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a
+-(2/5)f_{q_A}\Delta_{O},
+ \end{align}
+ where
+\begin{align}
+\nonumber
 E_{0}^A =&
- \frac{8 (92 \cos 2\beta+24 \cos 4\beta+20 \cos 6\beta+5 \cos 8\beta+51)}{9 (\cos 2\beta+2)^{9/2}},\\
+ \frac{8 (92 \cos 2\beta+24 \cos 4\beta+20 \cos 6\beta+5 \cos 8\beta+51)}{9 (\cos 2\beta+2)^{9/2}}\\
  \simeq& \frac{512}{243 \sqrt{3}}-\frac{2560 \beta ^2}{729 \sqrt{3}},\\
+ \nonumber
 E_{0}^B=&
- -\frac{1}{18} \left((5 \cos 4\beta+3) \sec ^5\beta+4\right)
- \simeq -\frac{2}{3}+\frac{10 \beta ^2}{9}.
+ -\frac{1}{18} \left((5 \cos 4\beta+3) \sec ^5\beta+4\right)\\
+ \simeq& -\frac{2}{3}+\frac{10 \beta ^2}{9}.
  \end{align}

### 2023-09-20 manuscript/paper.tex
a lot of new references added in bib file. gen reviews ref to perovskite added to tex. some imp reviews ref missed before also included.

@@
 \com{
-Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
-}
-
- \com{https://www.frontiersin.org/articles/10.3389/fchem.2020.550625/full:\\
-advanced functional materials including photocatalysis, electrocatalysts
- high-temperature superconductors, multiferroics, magnetic and magnetoresistive materials, materials for solar cell energy and photoluminescence
-}
-
-\com{https://www.perovskite-info.com/introduction:\\
-Perovskite materials exhibit intriguing and unusual physical properties that have been extensively studied for both practical applications and theoretical modeling and the materials science and applications of perovskites have been a broad research area open to many revolutionary discoveries for new device concepts.
-Perovskite?s potential applications are varied and include uses in sensors and catalyst electrodes, certain types of fuel cells, solar cells, lasers, memory devices and spintronics applications.
+%---------------------------------------------------------
+% REVIEWS:
+WangS03, %REVIEW
+%{Epitaxial BiFeO<sub>3</sub> Multiferroic Thin Film Heterostructures}
+DagottoS05,
+%{Complexity in Strongly Correlated Electronic Systems},
+SchlomARMR07,
+%Strain Tuning of Ferroelectric Thin Films}
+KhomskiiPhys09
+%Classifying multiferroics: Mechanisms and effects}
+ZubkoARCMP11,
+%{Interface Physics in Complex Oxide Heterostructures},
+HwangNM12, 
+%{Emergent phenomena at oxide interfaces},
+
+BhattacharyaARMR14,
+%{Magnetic Oxide Heterostructures},
+HellmanRMP17,
+%{Interface-induced phenomena in magnetism},
+  ChenJPCM17
+ % {Charge transfer driven emergent phenomena in oxide heterostructures},
+DagottoMRSB08,
+  %{Strongly Correlated Electronic Materials: Present and Future},
+
+SalamonRMP01, 
+%The physics of manganites: Structure and transport},
+DawberRMP05,
+% Physics of thin-film ferroelectric oxides},
+KosterRMP12,
+%Structure, physical properties, and applications of ${\mathrm{SrRuO}}_{3}$ thin films},
+
+%electronic correlations:
+~\cite{DagottoS05,DagottoMRSB08}
+
+%applications:
+~\cite{SalamonRMP01,
+WangS03
+DawberRMP05,
+SchlomARMR07,
+KosterRMP12}
+
+% understanding:
+~\cite{ZubkoARCMP11,
+HwangNM12, 
+BhattacharyaARMR14,
+HellmanRMP17,
+ChenJPCM17}
+
+%---------------------------------------------------------
+
+LiN19,
+% Superconductivity in an infinite-layer nickelate},
+LeeN10,
+%{A strong ferroelectric ferromagnet created by means of spin--lattice coupling},
+BousquetN08,
+%{Improper ferroelectricity in perovskite oxide artificial superlattices},
+
+OjaPRL12,
+%{${d}^{0}$ Ferromagnetic Interface between Nonmagnetic Perovskites},
+
+WangPRX16,
+% {Stabilization of Highly Polar ${\mathrm{BiFeO}}_{3}$-like Structure: A New Interface Design Route for Enhanced Ferroelectricity in Artificial Perovskite Superlattices}
+CavigliaPRL12,
+%{Ultrafast Strain Engineering in Complex Oxide Heterostructures},
+XiaPRB09,
+%{Critical thickness for itinerant ferromagnetism in ultrathin films of ${\text{SrRuO}}_{3}$},
+
+BenedekPRL11,
+%{Hybrid Improper Ferroelectricity: A Mechanism for Controllable Polarization-Magnetization Coupling},
+GarrityPRL14,
+% {Hyperferroelectrics: Proper Ferroelectrics with Persistent Polarization},
+KobayashiPRL12,
+%{Electronic Ferroelectricity in a Molecular Crystal with Large Polarization Directing Antiparallel to Ionic Displacement},
+
+HarrisPRB07,
+% {Landau analysis of the symmetry of the magnetic structure and magnetoelectric interaction in multiferroics},
+LeePRL10,
+%{Epitaxial-Strain-Induced Multiferroicity in ${\mathrm{SrMnO}}_{3}$ from First Principles},
+WangPRL15,
+%{Observation of Magnetoelectric Multiferroicity in a Cubic Perovskite System: ${\mathrm{LaMn}}_{3}{\mathrm{Cr}}_{4}{\mathrm{O}}_{12}$},
+
+ChenPRL22,
+%{Optically Controlled Femtosecond Polariton Switch at Room Temperature}
+ChoiPRL10,
+% {Cross-Control of Magnetization and Polarization by Electric and Magnetic Fields with Competing Multiferroic and Weak-Ferromagnetic Phases},
+KidaPRB08,
+%{Electrically driven spin excitation in the ferroelectric magnet ${\text{DyMnO}}_{3}$},
+ChoPRL16,
+%{Laser Particle Stimulated Emission Microscopy},
+deJongPRL12,
+%{Coherent Control of the Route of an Ultrafast Magnetic Phase Transition via Low-Amplitude Spin Precession},
+
+ShirakoPRB11,
+%{Integer spin-chain antiferromagnetism of the 4$d$ oxide CaRuO${}_{3}$ with post-perovskite structure},
+DikinPRL11,
+% {Coexistence of Superconductivity and Ferromagnetism in Two Dimensions},
+ChoudhuryPRL12,
+%{Near-Room-Temperature Colossal Magnetodielectricity and Multiglass Properties in Partially Disordered ${\mathrm{La}}_{2}{\mathrm{NiMnO}}_{6}$},
+
+LeePRL11,
+%  {Electrolyte Gate-Controlled Kondo Effect in ${\mathrm{SrTiO}}_{3}$},
+
 }
@@
 exhibit a rich variety of intriguing 
-electronic, magnetic and optical properties
+electronic,
+magnetic
+ and optical
+properties~\cite{ZubkoARCMP11,
+HwangNM12, 
+BhattacharyaARMR14,
+HellmanRMP17,
+ChenJPCM17,DagottoS05,DagottoMRSB08}
 due to the interplay between
-spin, orbital, and structural degrees of freedom
-and widely varying electronic correlations.
+spin, orbital, and structural degrees of 
+freedom
+and widely varying electronic 
+correlations.
 These materials 
@@
 and 
-fundamental understanding of various physical phenomena.
+fundamental understanding of various physical 
+phenomena~\cite{SalamonRMP01,
+WangS03,
+DawberRMP05,
+SchlomARMR07,
+KosterRMP12}.
 
@@
 ferroelectric~\cite{GhosezNM11,
+RondinelliAM12,
 SchickPRB14,
@@
 GaoPRB23} and 
-multiferroic~\cite{BenedekPRL11,
+multiferroic~\cite{KhomskiiPhys09,
+BenedekPRL11,
 YangPRL14,
@@
 HalcrowRSC13,
-PavariniChap}
+PavariniChap,
+KhomskiiCR21}
 (i.e., the orbital degeneracy of the metal ion coordinated by the anionic octahedron

### 2023-09-20 manuscript/paper.tex
summary. almost done

@@
 \maketitle
-
-\com{
-%---------------------------------------------------------
-% REVIEWS:
-WangS03, %REVIEW
-%{Epitaxial BiFeO<sub>3</sub> Multiferroic Thin Film Heterostructures}
-DagottoS05,
-%{Complexity in Strongly Correlated Electronic Systems},
-SchlomARMR07,
-%Strain Tuning of Ferroelectric Thin Films}
-KhomskiiPhys09
-%Classifying multiferroics: Mechanisms and effects}
-ZubkoARCMP11,
-%{Interface Physics in Complex Oxide Heterostructures},
-HwangNM12, 
-%{Emergent phenomena at oxide interfaces},
-
-BhattacharyaARMR14,
-%{Magnetic Oxide Heterostructures},
-HellmanRMP17,
-%{Interface-induced phenomena in magnetism},
-  ChenJPCM17
- % {Charge transfer driven emergent phenomena in oxide heterostructures},
-DagottoMRSB08,
-  %{Strongly Correlated Electronic Materials: Present and Future},
-
-SalamonRMP01, 
-%The physics of manganites: Structure and transport},
-DawberRMP05,
-% Physics of thin-film ferroelectric oxides},
-KosterRMP12,
-%Structure, physical properties, and applications of ${\mathrm{SrRuO}}_{3}$ thin films},
-
-%electronic correlations:
-~\cite{DagottoS05,DagottoMRSB08}
-
-%applications:
-~\cite{SalamonRMP01,
-WangS03
-DawberRMP05,
-SchlomARMR07,
-KosterRMP12}
-
-% understanding:
-~\cite{ZubkoARCMP11,
-HwangNM12, 
-BhattacharyaARMR14,
-HellmanRMP17,
-ChenJPCM17}
-
-%---------------------------------------------------------
-
-LiN19,
-% Superconductivity in an infinite-layer nickelate},
-LeeN10,
-%{A strong ferroelectric ferromagnet created by means of spin--lattice coupling},
-BousquetN08,
-%{Improper ferroelectricity in perovskite oxide artificial superlattices},
-
-OjaPRL12,
-%{${d}^{0}$ Ferromagnetic Interface between Nonmagnetic Perovskites},
-
-WangPRX16,
-% {Stabilization of Highly Polar ${\mathrm{BiFeO}}_{3}$-like Structure: A New Interface Design Route for Enhanced Ferroelectricity in Artificial Perovskite Superlattices}
-CavigliaPRL12,
-%{Ultrafast Strain Engineering in Complex Oxide Heterostructures},
-XiaPRB09,
-%{Critical thickness for itinerant ferromagnetism in ultrathin films of ${\text{SrRuO}}_{3}$},
-
-BenedekPRL11,
-%{Hybrid Improper Ferroelectricity: A Mechanism for Controllable Polarization-Magnetization Coupling},
-GarrityPRL14,
-% {Hyperferroelectrics: Proper Ferroelectrics with Persistent Polarization},
-KobayashiPRL12,
-%{Electronic Ferroelectricity in a Molecular Crystal with Large Polarization Directing Antiparallel to Ionic Displacement},
-
-HarrisPRB07,
-% {Landau analysis of the symmetry of the magnetic structure and magnetoelectric interaction in multiferroics},
-LeePRL10,
-%{Epitaxial-Strain-Induced Multiferroicity in ${\mathrm{SrMnO}}_{3}$ from First Principles},
-WangPRL15,
-%{Observation of Magnetoelectric Multiferroicity in a Cubic Perovskite System: ${\mathrm{LaMn}}_{3}{\mathrm{Cr}}_{4}{\mathrm{O}}_{12}$},
-
-ChenPRL22,
-%{Optically Controlled Femtosecond Polariton Switch at Room Temperature}
-ChoiPRL10,
-% {Cross-Control of Magnetization and Polarization by Electric and Magnetic Fields with Competing Multiferroic and Weak-Ferromagnetic Phases},
-KidaPRB08,
-%{Electrically driven spin excitation in the ferroelectric magnet ${\text{DyMnO}}_{3}$},
-ChoPRL16,
-%{Laser Particle Stimulated Emission Microscopy},
-deJongPRL12,
-%{Coherent Control of the Route of an Ultrafast Magnetic Phase Transition via Low-Amplitude Spin Precession},
-
-ShirakoPRB11,
-%{Integer spin-chain antiferromagnetism of the 4$d$ oxide CaRuO${}_{3}$ with post-perovskite structure},
-DikinPRL11,
-% {Coexistence of Superconductivity and Ferromagnetism in Two Dimensions},
-ChoudhuryPRL12,
-%{Near-Room-Temperature Colossal Magnetodielectricity and Multiglass Properties in Partially Disordered ${\mathrm{La}}_{2}{\mathrm{NiMnO}}_{6}$},
-
-LeePRL11,
-%  {Electrolyte Gate-Controlled Kondo Effect in ${\mathrm{SrTiO}}_{3}$},
-
-}
 
@@
 
-\com{---a cooperative Jahn-Teller 
-effect~\cite{JahnPRSL37,JahnPRSL38,
-OpikRS57,
-Sturge68,
-GehringRPP75,
-BersukerCCR75,
-KugelSPU82,
-MillisN98,
-LufasoAC04,
-TerakuraPMS07,
-HalcrowRSC13,
-PavariniChap}
-whereby the orbital degeneracy of the B ions
-is lifted that stabilises the distortion---
-}
-
 While the tetragonal distortion of the octahedra is associated with
@@
 
-\com{
-We take a completely different approach to this problem.
-We go back to the basics
-and explore the octahedral rotations from the perspective
-of (first order) JT effect itself
-}
-
 We take a completely different approach to this problem.
@@
 
-The Jahn--Teller effect~\cite{JahnPRSL37,JahnPRSL38,OpikRS57,Sturge68,GehringRPP75,KugelSPU82,PavariniChap} describes the 
+The Jahn--Teller 
+effect~\cite{JahnPRSL37,JahnPRSL38,
+OpikRS57,
+Sturge68,
+GehringRPP75,
+BersukerCCR75,
+KugelSPU82,
+MillisN98,
+LufasoAC04,
+TerakuraPMS07,
+HalcrowRSC13,
+PavariniChap,
+KhomskiiCR21}
+ describes the 
 geometric and electronic instability of a %non-linear 
@@
 
-\az{
-Summarise the results of $t_{2g},e_{g}$:
-1. splitting depending on the relative sizes of $q_A,q_B$
-2. local orbital ordering:\\
-two sets of competing factors:
-A vs B, and alpha vs beta.
-under the influence of A, alpha pushes xy down while yz/zx up.
-but beta does the opposite.
-Under the influence of B,
-the effect of alpha and beta are reversed, alpha pushes xy up while yz/zx down, etc.
-
-Does this picture survive when we consider the potential of the full ionic lattice at the site of B atom?
-Yes.... qualitatively, the same behaviour. just quantitative differences, the balance between A/B cages shifts towards lower $q_A$...
-
-}
-
 \subsection{Effect of the full lattice}
@@
 
+\az{
+Summarise the results of $t_{2g},e_{g}$:
+1. splitting depending on the relative sizes of $q_A,q_B$
+2. local orbital ordering:\\
+two sets of competing factors:
+A vs B, and alpha vs beta.
+under the influence of A, alpha pushes xy down while yz/zx up.
+but beta does the opposite.
+Under the influence of B,
+the effect of alpha and beta are reversed, alpha pushes xy up while yz/zx down, etc.
+
+Does this picture survive when we consider the potential of the full ionic lattice at the site of B atom?
+Yes.... qualitatively, the same behaviour. just quantitative differences, the balance between A/B cages shifts towards lower $q_A$... 
+}
+
+\rev{
+consider a few diff $d^{n}$ cases:
+1 e: for a given qa,qb; there might be incentives to prefer one angle over the other....
+but more interesting cases:
+where one angle does not lower the energy of many-electron ground state
+while the other does. so, obviously, such systems would take the energetically favorable path...
+}
+
+\section{Summary and Conclusion}
+We consider the effects of octahedral rotations and tilting in perovskites
+on the $t_{2g}$ and $e_g$ manifolds of the central transition metal ions
+and find significant splitting in these levels
+caused by the distortions in the crystal field of nearest A and B ion cages,
+which
+essentially amounts to a 
+Jahn-Teller instability.
+A competition between the two ion cages
+determines the sign and strength of this effect
+depending on the proportion of charges $q_A,q_B$ on A and B ions.
+The tilt 
+%$\alpha$ 
+and rotation 
+%$\beta$
+also tend to establish different ground states
+that depends on which ion cage dominates.
+If A cage dominates (i.e., $q_A$ is larger than a critical value),
+%$\alpha$
+tilting lowers
+$xy,x^2-y^2$ orbitals
+and raises $yz,zx,z^2$,
+while 
+%$\beta$
+rotation tends to do the opposite;
+the whole situation reverses if B cage dominates.
+
+In a given material,
+assuming
+the charges on A and B are fixed
+and either A or B dominating,
+one type of distortion 
+would be energetically preferred
+over the other
+for certain
+numbers of electrons in 
+the $d$-orbitals of the Jahn-Teller ion B.
+For example,
+assuming B cage dominating,
+a $d^2$ configuration
+should prefer tilting over rotation
+because it stabilizes two occupied orbitals 
+while rotation stabilizes one and destabilizes the other occupied orbital.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-09-20 manuscript/paper.tex
sumamry done. discussion and outlook, rough ideas added.

@@
 There are two different ways the crystal field $V(\vec r)$
-\az{[at the location of a B ion... which B ion out of four in distorted structure?... pick one here...]}
+\az{[at the location of a B ion... which B ion out of four in distorted structure?... pick one here...]
+We consider the B ion at $(0,0,0)$....
+energies/splittings are practically the same for all B ions... 
+but their eigenstates differ considerably that creates interesting orbital ordering as discussed later in the discussion section, sec.~\ref{sec:discussion}.
+
+}
  is deformed from the ideal case $V(\vec r) \propto V_{oct}(\vec r)$
@@
 V^{B}_{4,0}&= \frac{4\sqrt{\pi } }{3} \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right),\\
- V^{B}_{4,4}&=  - \frac{16 \sqrt{35 \pi } }{3} \frac{(-20 \cos 2 \alpha +\cos 4 \alpha -13) %\sec ^5\beta }
- }
- {(\cos 2 \alpha +3)^{9/2} \cos^5\beta}.
+ V^{B}_{4,4}&=  \frac{16 \sqrt{35 \pi } }{3} \frac{(20 \cos 2 \alpha -\cos 4 \alpha +13) 
+ \sec ^5\beta }
+ {(\cos 2 \alpha +3)^{9/2}}.
  \end{align}
@@
 
-\az{
-Summarise the results of $t_{2g},e_{g}$:
-1. splitting depending on the relative sizes of $q_A,q_B$
-2. local orbital ordering:\\
-two sets of competing factors:
-A vs B, and alpha vs beta.
-under the influence of A, alpha pushes xy down while yz/zx up.
-but beta does the opposite.
-Under the influence of B,
-the effect of alpha and beta are reversed, alpha pushes xy up while yz/zx down, etc.
-
-Does this picture survive when we consider the potential of the full ionic lattice at the site of B atom?
-Yes.... qualitatively, the same behaviour. just quantitative differences, the balance between A/B cages shifts towards lower $q_A$... 
-}
-
-\rev{
-consider a few diff $d^{n}$ cases:
-1 e: for a given qa,qb; there might be incentives to prefer one angle over the other....
-but more interesting cases:
-where one angle does not lower the energy of many-electron ground state
-while the other does. so, obviously, such systems would take the energetically favorable path...
-}
-
 \section{Summary and Conclusion}
+
 We consider the effects of octahedral rotations and tilting in perovskites
-on the $t_{2g}$ and $e_g$ manifolds of the central transition metal ions
-and find significant splitting in these levels
+on the $t_{2g}$ and $e_g$ manifolds of the central transition metal ions.
+We find significant splitting in these levels
 caused by the distortions in the crystal field of nearest A and B ion cages,
@@
 Jahn-Teller instability.
-A competition between the two ion cages
-determines the sign and strength of this effect
-depending on the proportion of charges $q_A,q_B$ on A and B ions.
+The sign and strength of this effect is 
+determined by
+a competition between the two ion cages.
+%depending on the proportion of charges $q_A,q_B$ on A and B ions.
 The tilt 
@@
 also tend to establish different ground states
-that depends on which ion cage dominates.
+%that depends 
+depending
+on which ion cage dominates.
+While the tilting alone can mix $t_{2g}$ states,
+$e_g$ states
+do not mix unless both rotation and tilting are non-zero.
+Despite such mixing, we can see which orbitals are stabilized or destabilized.
 If A cage dominates (i.e., $q_A$ is larger than a critical value),
@@
 the whole situation reverses if B cage dominates.
-
+Considering the crystal field of the full lattice 
+only shifts the balance towards A cage
+but does not qualitatively change the results.
+
+\section{Discussion and Outlook}
+
+% tilt vs rotation, preference
 In a given material,
@@
 the charges on A and B are fixed
-and either A or B dominating,
+and either A or B dominates,
 one type of distortion 
@@
 For example,
-assuming B cage dominating,
+if B cage dominates,
 a $d^2$ configuration
@@
 while rotation stabilizes one and destabilizes the other occupied orbital.
+
+% orbital ordering
+We have focused on the B ion at $(0,0,0)$ but 
+there are three more B ions in the unit cell 
+at finite octahedral rotations.
+We find that the splittings in the spectra
+of all B ions are
+practically identical.
+However, their eigenstates 
+are different in a way that 
+creates interesting orbital ordering
+which depends on the tilt and rotation angles,
+unlike what happens in 
+tetragonal Jahn-Teller distortions (elongation and compression) 
+such as seen in KCuF$_3$, 
+where the orbital ordering does not depend on the size of the distortion.
+A detailed study of orbital ordering in this case is out of scope of this manuscript and is left for future work.
+
+Of course, beside the crystal field we considered in our simplistic model,
+in real materials,
+ there would be other local effects like
+electronic correlations (Hubbard and Hund's interaction), 
+and spin-orbit interaction, 
+as well as band structure effects arising from
+the electron hopping between the B ions.
+The interplay between these and the crystal field (or JT) effect 
+we discussed in this manuscript is also an interesting future work.
+
+Based on our analysis of A and B cages,
+we expect that,
+in case of atomic scale perovskite superlattices
+with cations having different charges in alternating layers,
+the crystal field at B sites will bear the exact same deformation as in case of 
+a tetragonal distortion of the octahedra,
+and should lead to 
+a JT like splitting even 
+in the symmetric structure, i.e., with no structural distortion.
+Considering the charge as a dynamic variable,
+it should then also be possible that in 
+simple perovskites structure,
+the system might encounter charge instabilities similar to the structural ones (i.e., JT),
+where the system is stabilised by a charge transfer from one site to another
+that lowers the electronic energy and costs 
+the ``elastic'' energy proportional the chemical hardness of the ions involved.
 

### 2023-09-20 src/main.f

@@ -691,7 +691,7 @@
 	ntot = noct*norbtms + noct*3*norbos;
 	ntottm = noct*norbtms;
 
-	write(*,*)'ntot, ntottm, qtot,a = ', ntot, ntottm, qtotqtot, a
+	write(*,*)'ntot, ntottm, qtot,a = ', ntot, ntottm, qtot, a
 	!i = noct*1 + noct*6*norbos
 	!write(*,*)'TM d^1: nelec = ', i
 	!write(*,*)'if only one spin, filled bands ~ ',0.5*i

### 2023-09-20 src/scf.f90

@@ -41,6 +41,8 @@ open(805,file='evecs-tm.dat',action='write',position='append')
  !write(*,*) '100 * h_B1: --------------------'
  !write(*, '(20f15.6)') 100*tm(1,1)%ham(:,:) ! evec
 
+ call writeHamOctaFrame()
+
  do il=1,1 !nlayers
   do io=1,1 ! noctl
    ia = tm(il,io)%ia;
@@ -64,6 +66,50 @@ open(805,file='evecs-tm.dat',action='write',position='append')
 return
 end subroutine tmgroundstate
 !=====================================================================
+
+
+
+
+
+!====================================================================
+	subroutine writeHamOctaFrame()
+	implicit none
+	integer ::i,ia,il,io,is
+	character*50 :: fname ='beast-tm-ham-octa-frame.dat'
+	character*50 :: fname2 ='beast-tm-ham.dat'
+
+	double precision, dimension(5,5) :: h, R, RT
+
+	open(10,file=trim(fname),action='write',position='append')
+	open(11,file=trim(fname2),action='write',position='append')
+
+	do il=1, 2
+	do io=1, 2
+   ia = tm(il,io)%ia;
+	 is = atom2species(ia);
+
+	 h = tm(il,io)%ham(1:5,1:5) ! just up spin block
+	 write(11,'(5f18.12)') h * 27.21138505d0 ! write 5x5 matrices as an array of 25 elements
+
+	 i = (il-1)*2 + io
+	 R = Rlmax(5:9,5:9,i) ! Rlmax is rotation matrix for Ylm of TM atom i
+	 RT = transpose(R);
+	  ! transform to rotated frame of the octagedron 1 
+	  ! R^T.h.R
+	  h = matmul(RT,h)
+	  h = matmul(h,R) ! 
+	
+	 write(10,'(5f18.12)') h * 27.21138505d0 ! write 5x5 matrices as an array of 25 elements
+
+  end do !io
+  end do ! il
+
+	close(10)
+	close(11)	
+	return
+	end 	subroutine WriteHamOctaFrame
+!----------------------------------------------------------------
+
 
 
 

### 2023-09-21 manuscript/paper.tex
discussion and outlook. appendix: multipoles.

@@
 = \sum_{l,m} \tilde V_{lm} r^l \tilde Y_{lm}(\hat r),\\
-\tilde V_{lm} &= \sum_{l',m'}\mathcal{R}_{lm,l'm'}V_{l'm'},
+%\tilde V_{lm} &= \sum_{l',m'}\mathcal{R}_{lm,l'm'}V_{l'm'},
+\tilde V_{lm} &= \sum_{m'=-l}^{l}\mathcal{R}^{l}_{m,m'}V_{lm'},
 \end{align}
 where 
-$\mathcal{R}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics that we use (see appendix~\ref{sec:appendix}). 
+$\mathcal{R}^{l}=\mathcal{R}^{l}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics 
+of degree $l$ (see appendix~\ref{sec:appendix}).
 It can be calculated using the method described in Ref.~\cite{IvanicJPC96}.
@@
 \begin{gather}
-\tilde V_{lm} = \tilde V_{lm}^O + \sum_{l',m'}\mathcal{R}_{lm,l'm'} V_{l'm'}^{AB},\\
-V_{l'm'}^{AB} = \left(\frac{q_A}{a} \right)V_{l'm'}^{A}   
-+ \left(\frac{q_B}{a}\right)V_{l'm'}^{B},
+\tilde V_{lm} = \tilde V_{lm}^O + \sum_{m'=-l}^{l}\mathcal{R}^{l}_{m,m'} V_{lm'}^{AB},\\
+V_{lm}^{AB} = \left(\frac{q_A}{a} \right)V_{lm}^{A}   
++ \left(\frac{q_B}{a}\right)V_{lm}^{B},
 \end{gather}
@@
 
+\az{
+
+Summarise t2g results here.\\
+
+copy from summary section...??
+
+tilt vs rotation, preference:\\
+
+In a given material,
+assuming
+the charges on A and B are fixed
+and either A or B dominates,
+one type of distortion 
+would be energetically preferred
+over the other
+for certain
+numbers of electrons in 
+the $d$-orbitals of the Jahn-Teller ion B.
+For example,
+if B cage dominates,
+a $d^2$ configuration
+should prefer tilting over rotation
+because it stabilises two occupied orbitals 
+while rotation stabilises one and destabilises the other occupied orbital.
+
+}
+
 \subsection{$e_{g}$ manifold}
@@
 \begin{align}
-\label{eq:eg-hijx}
-H_{x^2-y^2,z^2}&=
+\nonumber
+H_{x^2-y^2,z^2}=
 \frac{2\alpha ^2 \beta}{567} 
-\left(128 q_A (3 D_2-20 D_4) - 81 \sqrt{3} q_B (2 D_2 -5 D_4)\right),
+&\left(\frac{}{}128 q_A (3 D_2-20 D_4) \right. \\ \label{eq:eg-hijx}
+&~~\left. - 81 \sqrt{3} q_B (2 D_2 -5 D_4)\right),
 %&=\frac{2\alpha ^2 \beta}{567} \left(384 ( D_2-\frac{20}{3} D_4)q_A  - 162 \sqrt{3} (D_2 -\frac{5}{2} D_4)q_B \right)
@@
 
-% tilt vs rotation, preference
-In a given material,
-assuming
-the charges on A and B are fixed
-and either A or B dominates,
-one type of distortion 
-would be energetically preferred
-over the other
-for certain
-numbers of electrons in 
-the $d$-orbitals of the Jahn-Teller ion B.
-For example,
-if B cage dominates,
-a $d^2$ configuration
-should prefer tilting over rotation
-because it stabilizes two occupied orbitals 
-while rotation stabilizes one and destabilizes the other occupied orbital.
-
-% orbital ordering
-We have focused on the B ion at $(0,0,0)$ but 
-there are three more B ions in the unit cell 
-at finite octahedral rotations.
-We find that the splittings in the spectra
-of all B ions are
-practically identical.
-However, their eigenstates 
-are different in a way that 
-creates interesting orbital ordering
-which depends on the tilt and rotation angles,
-unlike what happens in 
-tetragonal Jahn-Teller distortions (elongation and compression) 
-such as seen in KCuF$_3$, 
-where the orbital ordering does not depend on the size of the distortion.
-A detailed study of orbital ordering in this case is out of scope of this manuscript and is left for future work.
-
-Of course, beside the crystal field we considered in our simplistic model,
-in real materials,
- there would be other local effects like
-electronic correlations (Hubbard and Hund's interaction), 
-and spin-orbit interaction, 
-as well as band structure effects arising from
-the electron hopping between the B ions.
-The interplay between these and the crystal field (or JT) effect 
-we discussed in this manuscript is also an interesting future work.
-
+\com{
+% beside the hardness, the Madelung energy will increase due to an increased repulsion between the two ions that take part in the charge transfer.
+Consider that q1^2+q2^2 with constant that q1+q2=2q=fixed is min when q1=q2=q.
+% so the electronic energy gain will have to fight against both the chem hardness and the Madelung energy.
 Based on our analysis of A and B cages,
@@
 simple perovskites structure,
-the system might encounter charge instabilities similar to the structural ones (i.e., JT),
+the system might encounter charge instabilities similar to the structural ones,
 where the system is stabilised by a charge transfer from one site to another
 that lowers the electronic energy and costs 
-the ``elastic'' energy proportional the chemical hardness of the ions involved.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+the ``elastic'' energy proportional to the chemical hardness of the ions involved.
+Such considerations might be useful in studying polaron formation and dynamics.
+}
+
+% orbital ordering
+We have only focused on the spectrum of the B ion at 
+%position ${(0,0,0)}$
+origin
+ in the cell 
+described in sec.~\ref{sec:structure}
+but 
+there are three more \emph{distinct} B ions in the unit cell 
+at finite octahedral rotations that also 
+need to be considered simultaneously.
+We find that the splittings in the spectra
+of all B ions are
+practically identical.
+However, their eigenstates 
+are different in a way that can
+create interesting orbital ordering
+that depends on the tilt and rotation angles,
+unlike what happens in 
+tetragonal Jahn-Teller distortions (elongation and compression) 
+such as seen in KCuF$_3$, 
+where the orbital ordering does not depend on the size of the distortion.
+The eigenstates' components in the local bases attached to the octahedra's frame
+also vary between different B sites 
+so the dependence on the rotation and tilt angle is not trivial,
+which is understandable because different B sites in the unit cell have different environments. 
+A detailed study of orbital ordering in this case is out of scope of this manuscript and is left for future work.
+
+Of course, beside the crystal field we consider in our simplistic model,
+in real materials,
+ there would be other local effects like
+electronic correlations (Hubbard and Hund's interaction), 
+and spin-orbit interaction, 
+as well as band structure effects arising from
+the electron hopping between the B ions.
+The interplay between these and the crystal field (or JT) effect 
+we discussed in this manuscript is also an interesting future work.
+
+%\begin{acknowledgements}
+%\end{acknowledgements}
+
+\appendix*
+\section{Computing $V_{l,m}^{A/B}$}
+\label{append:multipoles}
+
+Here we describe the procedure to obtain the multipole components 
+$V_{l,m}^{A/B}$ of potentials $V^{A/B}(\vec r)$ of $A/B$ ion cages 
+at a position $\vec r$ around a JT ion.
+That is, we like to expand the potentials $V^{A/B}(\vec r)$
+in spherical harmonics as
+\begin{align}
+\label{eq:ylm_compA}
+V^{A}(\vec r) =& \sum_{l,m} V_{lm}^{A} r^l Y_{lm}(\hat r),\\
+\label{eq:ylm_compB}
+V^{B}(\vec r) =& \sum_{l,m} V_{lm}^{B} r^l Y_{lm}(\hat r).
+\end{align}
+It is worth noting that $V_{l,m}^{A/B}$ can be found without 
+evaluating the 
+inner products between the spherical harmonics and
+$V^{A/B}(\vec r)=V^{A/B}(\vec r;\alpha,\beta)$, as follows.
+
+First we calculate
+$V^{A/B}(\vec r)$
+using the simple textbook formula.
+$V^{A}(\vec r;\alpha,\beta)=\sum_{i}1/|\vec r^A_i-\vec r |$, 
+where $\vec r^A_i$ is the position of $i$-th A ion
+and 
+$\vec r$ is the position of the observation point 
+measured from the JT ion.
+Similarly,
+$V^{B}(\vec r;\alpha,\beta)=\sum_{i}1/|\vec r^B_i-\vec r |$.
+Writing cartesian components of $\vec r$ as
+$\vec r=r(\cos\phi\sin\theta,\sin\theta\sin\phi,\cos\theta)$,
+where $(r,\theta,\phi)$ 
+are the spherical coordinates in the frame of JT ion,
+and expanding 
+${V^{A/B}(\vec r;\alpha,\beta)}$
+in powers of $r$, 
+we can separate 
+coefficient of $r^l$
+that give degree $l$ components.
+We can now consider each degree $l$ term individually,
+and resolve it in its $(2l+1)$ $m$-components.
+This can be done by 
+expanding such a coefficient of $r^l$
+in powers of $\cos\theta, \cos\phi$ 
+(or $\sin\theta, \sin\phi$, or simply $\theta,\phi$) 
+and comparing the terms with a similar expansion of 
+the formal expression on the right side 
+of Eq.~\ref{eq:ylm_compA} or Eq.~\ref{eq:ylm_compB}.
+This gives a set of
+linear equations in $\{V_{l,m}^{A/B}\}$ (for a fixed value of $l$)
+ that can be easily solved.
+The whole procedure can be performed
+ on Mathematica~\cite{Mathematica}
+or a similar software.
 
@@
 \end{document}
-
-\section{Appendix: Rotation matrices}
-\label{sec:append}
-
-\begin{gather}
-\nonumber
-R=
-\left(
-\scalemath{0.9}{
-\begin{array}{ccc}
- \frac{1}{2} ((\cos \alpha+1) \cos \beta+(\cos \alpha-1) \sin \beta) & \frac{1}{2} (\cos \beta-\sin \beta-\cos \alpha (\cos \beta+\sin \beta)) & \frac{\sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} \\
- \frac{1}{2} (-\cos \alpha \cos \beta+\cos \beta+\cos \alpha \sin \beta+\sin \beta) & \frac{1}{2} (\cos \beta+\cos \alpha (\cos \beta-\sin \beta)+\sin \beta) & \frac{\sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} \\
- -\frac{\sin \alpha}{\sqrt{2}} & \frac{\sin \alpha}{\sqrt{2}} & \cos \alpha \\
-\end{array}
-}
-\right),\\ \nonumber
-\mathcal{R}=
-\left(
-\scalemath{0.65}{
-\begin{array}{ccccc}
- \frac{1}{4} (\cos 2 \alpha+3) \cos 2 \beta & \frac{\sin \alpha (\cos \alpha \cos 2 \beta+\sin 2 \beta)}{\sqrt{2}} & -\frac{1}{2} \sqrt{3} \cos 2 \beta \sin ^2\alpha & \frac{\sin \alpha (\sin 2 \beta-\cos \alpha \cos 2 \beta)}{\sqrt{2}} & \cos \alpha \sin 2 \beta \\
- \frac{\cos \alpha \sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} & \frac{1}{2} (\cos 2 \alpha (\cos \beta-\sin \beta)+\cos \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\sin \beta-\cos \beta) & \frac{1}{2} (\cos 2 \alpha (\sin \beta-\cos \beta)+\cos \alpha (\cos \beta+\sin \beta)) & -\frac{\sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} \\
- -\frac{1}{2} \sqrt{3} \sin ^2\alpha & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & \frac{1}{4} (3 \cos 2 \alpha+1) & -\sqrt{\frac{3}{2}} \cos \alpha \sin \alpha & 0 \\
- \frac{\cos \alpha \sin \alpha (\cos \beta+\sin \beta)}{\sqrt{2}} & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)-\cos 2 \alpha (\cos \beta+\sin \beta)) & \sqrt{\frac{3}{2}} \cos \alpha \sin \alpha (\cos \beta+\sin \beta) & \frac{1}{2} (\cos \alpha (\cos \beta-\sin \beta)+\cos 2 \alpha (\cos \beta+\sin \beta)) & \frac{\sin \alpha (\sin \beta-\cos \beta)}{\sqrt{2}} \\
- -\left(\cos ^2\alpha+1\right) \cos \beta \sin \beta & \frac{\sin \alpha (\cos 2 \beta-2 \cos \alpha \cos \beta \sin \beta)}{\sqrt{2}} & \sqrt{3} \cos \beta \sin ^2\alpha \sin \beta & \frac{\sin \alpha (\cos 2 \beta+\cos \alpha \sin 2 \beta)}{\sqrt{2}} & \cos \alpha \cos 2 \beta \\
-\end{array}
-}
-\right)
-\end{gather}
-
-\section{Appendix}
-\label{append:multipoles}
-\sm{
-It is worth noting that $V_{l,m}^{A/B}$ can be found without 
-evaluating the 
-inner products between the spherical harmonics and
-$V^{A/B}(\vec r;\alpha,\beta)$.
-The latter can be computed 
-using the simple textbook formula 
-$V^{A/B}(\vec r;\alpha,\beta)=\sum_{i}1/r_i$, $\vec r_i$ is the position of the observation point $\vec r$ (measured from the JT ion/central B ion).
-Once we have ${V^{A/B}(\vec r;\alpha,\beta)}$,
-$V_{l,m}^{A/B}$ can be calculated by first expanding this potential
-in powers of $r$, 
-and then expanding the coefficient of $r^l$ 
-in powers of $\cos\theta, \cos\phi$ (or $\sin\theta, \sin\phi$; or simply the spherical coordinates $\theta,\phi$ of $\hat r$) 
-and comparing the terms with similar 
-expansion of the formal expression on the right side of Eq.~\ref{eq:ylm_expansion} to get linear equations in $\{V_{l,m}\}$, and finally solving this system of equations.
-The only relevant non-zero components of $V_{l,m}^{A/B}$ are the following.
-
-It is worth noting that $V_{l,m}^{A/B}$ can be found without 
-evaluating the 
-inner products between the spherical harmonics and
-$V^{A/B}(\vec r;\alpha,\beta)$.
-The latter can be computed 
-using the simple textbook formula 
-$V^{A/B}(\vec r;\alpha,\beta)=\sum_{i}1/r_i$, $\vec r_i$ is the position of the observation point $\vec r$ (measured from the JT ion/central B ion).
-Once we have ${V^{A/B}(\vec r;\alpha,\beta)}$,
-$V_{l,m}^{A/B}$ can be calculated by first expanding this potential
-in powers of $r$, 
-and then expanding the coefficient of $r^l$ 
-in powers of $\cos\theta, \cos\phi$ (or $\sin\theta, \sin\phi$; or simply the spherical coordinates $\theta,\phi$ of $\hat r$) 
-and comparing the terms with similar 
-expansion of the formal expression on the right side of Eq.~\ref{eq:ylm_expansion}.
-The only relevant non-zero components of $V_{l,m}^{A/B}$ are the following.
-
-\subsection{$beta=0$ case: analytical solution:}
-
-$E_{xy},E_{yz},g,\lambda$ all have the same form as 
-\begin{align}
-X = -\frac{1}{a}\sum_{l=2,4}\left(q_A X^{A,l} + q_B X^{B,l}\right) D_l,
-\end{align}
-%where $X=E_{xy},E_{yz},g,\lambda$,
-where various terms are given in the following.
-
-%\begin{align}
-%E_{xy} = -\frac{1}{a}\sum_{l=2,4}\left(q_A E_{xy}^{A,l} + q_B E_{xy}^{B,l}\right) D_l,
-%\end{align}
-%where $E_{xy}^{A/B,l}$ are given in the following.
-
-%A D2
-\begin{align}
-E_{xy}^{A,2} =& \frac{4 \left(-72 \cos 2 \alpha -27 \cos 4 \alpha +\sqrt{6} \sqrt{\cos 2 \alpha +5} \left(15 \cos \alpha +\cos 3 \alpha -16 \sec ^3\alpha \right)+99\right)}{63 \left(\cos ^2\alpha +2\right)^{5/2}},\\
-E_{yz}^{A,2} =&\frac{144 \cos 2 \alpha +54 \cos 4 \alpha +\sqrt{\frac{3}{2}} (9 \sin \alpha +\sin 3 \alpha )^2 \sqrt{\cos 2 \alpha +5} \sec ^3\alpha -198}{63 \left(\cos ^2\alpha +2\right)^{5/2}},\\
-g^{A,2} =&\frac{2 \left(2 \sqrt{3} (\cos 2 \alpha +5)^{5/2}-216 \sqrt{2} \cos ^5\alpha \right) \tan \alpha  \sec \alpha }{63 \left(\cos ^2\alpha +2\right)^{5/2}},\\
-\lambda^{A,2} =&\frac{216 \cos 4 \alpha -4 \sqrt{6} (\cos 2 \alpha +3) (\cos 2 \alpha +5)^{5/2} \sec ^3\alpha +3240}{252 \left(\cos ^2\alpha +2\right)^{5/2}},
-\end{align}
-
-% A D4
-\begin{align}
-E_{xy}^{A,4} =& \frac{1}{20412 \left(\cos ^2\alpha +2\right)^{9/2}}
-\left[\frac{}{} -330480 \cos 2 \alpha +243 (2964 \cos 4 \alpha +80 \cos 6 \alpha +35 \cos 8 \alpha +5449)\right.\\
-&\hspace{4cm} + \left. \sqrt{\frac{3}{2}} (180 \cos 2 \alpha -245 \cos 4 \alpha +513) (\cos 2 \alpha +5)^{9/2} \sec ^5\alpha \right],\\
-E_{yz}^{A,4} =& \frac{}{10206 \left(\cos ^2\alpha +2\right)^{9/2}}
-\left[660960 \cos 2 \alpha +243 (652 \cos 4 \alpha -160 \cos 6 \alpha -35 \cos 8 \alpha +407)\right.\\
-&\hspace{4cm} + \left.\sqrt{\frac{3}{2}} (60 \cos 2 \alpha +245 \cos 4 \alpha -81) (\cos 2 \alpha +5)^{9/2} \sec ^5\alpha \right],\\
-g^{A,4} =& \frac{5 \left(31104 \sqrt{2} \cos ^7\alpha  (8 \cos 2 \alpha +7 \cos 4 \alpha +145)-32 \sqrt{3} (\cos 2 \alpha +5)^{9/2} (49 \cos 2 \alpha -9)\right) \tan \alpha  \sec ^3\alpha }{163296 \left(\cos ^2\alpha +2\right)^{9/2}},\\
-\lambda^{A,4} =& \frac{1}{10206 \left(\cos ^2\alpha +2\right)^{9/2}}
-\left[5 \left(180792 \cos 2 \alpha +243 (212 \cos 4 \alpha +24 \cos 6 \alpha +7 \cos 8 \alpha +37)\right)\right.\\
-&\hspace{4cm} + \left.\sqrt{\frac{3}{2}} (12 \cos 2 \alpha -49 \cos 4 \alpha -27) (\cos 2 \alpha +5)^{9/2} \sec ^5\alpha \right],
-\end{align}
-
-% B D2
-\begin{align}
-E_{xy}^{B,2} =& \frac{32 \cos 2 \alpha +24 \cos 4 \alpha -(3 \cos 2 \alpha +1) (\cos 2 \alpha +3)^{5/2} \sec ^3\alpha +72}{7 (\cos 2 \alpha +3)^{5/2}},\\
-E_{yz}^{B,2} =&\frac{-32 \cos 2 \alpha -24 (\cos 4 \alpha +3)+(3 \cos 2 \alpha +1) (\cos 2 \alpha +3)^{5/2} \sec ^3\alpha }{14 (\cos 2 \alpha +3)^{5/2}},\\
-g^{B,2} =&\frac{3 \left(40 \cos \alpha +20 \cos 3 \alpha -\sqrt{\cos 2 \alpha +3} (12 \cos 2 \alpha +\cos 4 \alpha )+4 \cos 5 \alpha -19 \sqrt{\cos 2 \alpha +3}\right) \tan \alpha  \sec \alpha }{7 \sqrt{2} (\cos 2 \alpha +3)^{5/2}},\\
-\lambda^{B,2} =&-\frac{3 \left(8 \cos 2 \alpha +(\cos 2 \alpha +3)^{3/2} \tan ^2\alpha  \sec \alpha -8\right)}{7 (\cos 2 \alpha +3)^{3/2}},
-\end{align}
-
-%B D4
-\begin{align}
-E_{xy}^{B,4} &= \scalemath{0.6}{\frac{1}{42} \left(-\frac{4 (851 \cos 2 \alpha +10 \cos 4 \alpha -35 \cos 6 \alpha +198)}{(\cos 2 \alpha +3)^{7/2}}+19 \sec ^5\alpha -50 \sec ^3\alpha +35 \sec \alpha \right)},\\
-E_{yz}^{B,4} &= \scalemath{0.6}{\frac{-3648 \cos 2 \alpha -8 (628 \cos 4 \alpha +120 \cos 6 \alpha +35 \cos 8 \alpha +297)-\frac{1}{2} (20 \cos 2 \alpha +35 \cos 4 \alpha +9) (\cos 2 \alpha +3)^{9/2} \sec ^5\alpha }{84 (\cos 2 \alpha +3)^{9/2}}},\\
-g^{B,4} &= \scalemath{0.6}{\frac{5 (5 \sin \alpha +\sin 3 \alpha ) \left(-3024 \cos \alpha -1344 \cos 3 \alpha +216 \cos 7 \alpha +56 \cos (9 \alpha )+(1224 \cos 2 \alpha +676 \cos 4 \alpha +120 \cos 6 \alpha +7 \cos 8 \alpha ) \sqrt{\cos 2 \alpha +3}+21 \sqrt{\cos 2 \alpha +3}\right) \sec ^4\alpha }{672 \sqrt{2} (\cos 2 \alpha +3)^{9/2}}},\\
-\lambda^{B,4} &= \scalemath{0.6}{\frac{5}{42} \left(-\frac{32 \sin ^2\alpha  (4 \cos 2 \alpha +7 \cos 4 \alpha +5)}{(\cos 2 \alpha +3)^{7/2}}-(7 \cos 2 \alpha +5) \tan ^2\alpha  \sec ^3\alpha \right).}
-\end{align}
-
-\subsection{general case, t2g}
-
-% using ham-approx-expansion-alpha-beta.nb: Generalt2gSplitAver[...]
-\begin{align} 
-\tilde H_{A,2} =& 
-\left(
-\begin{array}{ccc}
- -\frac{64 \left(\alpha ^2 \left(7 \beta ^2+3\right)-6 \beta ^2\right)}{189 \sqrt{3}} & \frac{32}{21} \sqrt{\frac{2}{3}} \alpha  \beta ^2 & -\frac{32}{21} \sqrt{\frac{2}{3}} \alpha  \beta ^2 \\
- & \frac{32 \left(\alpha ^2 (\beta  (7 \beta -12)+3)-6 \beta ^2\right)}{189 \sqrt{3}} & \frac{64 \alpha ^2 \left(3-2 \beta ^2\right)}{189 \sqrt{3}} \\
-&  & \frac{32 \left(\alpha ^2 (\beta  (7 \beta +12)+3)-6 \beta ^2\right)}{189 \sqrt{3}} \\
-\end{array}
-\right),\\
-\tilde H_{A,4} =& 
-\left(
-\begin{array}{ccc}
- -\frac{2560 \left(\alpha ^2 \left(\beta ^2+16\right)-32 \beta ^2\right)}{5103 \sqrt{3}} & \frac{1280 \sqrt{\frac{2}{3}} \alpha  \beta  (16 \beta -7)}{1701} & -\frac{1280 \sqrt{\frac{2}{3}} \alpha  \beta  (16 \beta +7)}{1701} \\
- & \frac{1280 \left(\alpha ^2 ((\beta -72) \beta +16)-32 \beta ^2\right)}{5103 \sqrt{3}} & -\frac{2560 \alpha ^2 \left(24 \beta ^2+1\right)}{1701 \sqrt{3}} \\
-&& \frac{1280 \left(\alpha ^2 (\beta  (\beta +72)+16)-32 \beta ^2\right)}{5103 \sqrt{3}} \\
-\end{array}
-\right),\\
-& 0,\frac{512 \left(5 \alpha ^2 \left(4 \beta ^2+1\right)+5 \beta ^2-3\right)}{729 \sqrt{3}}
-\end{align}
-
-\begin{align} 
-\tilde H_{B,2} =& 
-\left(
-\begin{array}{ccc}
- \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right) & -\frac{9 \alpha  \beta ^2}{7 \sqrt{2}} & \frac{9 \alpha  \beta ^2}{7 \sqrt{2}} \\
- & -\frac{3}{28} \left(\alpha ^2 (\beta  (3 \beta -8)+2)-4 \beta ^2\right) & -\frac{3}{7} \alpha ^2 \left(\beta ^2+1\right) \\
-  &  & -\frac{3}{28}\left(\alpha ^2 (\beta  (3 \beta +8)+2)-4 \beta ^2\right) \\
-\end{array}
-\right),\\
-\tilde H_{B,4} =& 
-\left(
-\begin{array}{ccc}
- \frac{5}{126} \left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right) & \frac{5 \alpha  (14-23 \beta ) \beta }{21 \sqrt{2}} & \frac{5 \alpha  \beta  (23 \beta +14)}{21 \sqrt{2}} \\
- & -\frac{5}{252}\left(\alpha ^2 (\beta  (37 \beta -144)+46)-92 \beta ^2\right) & \frac{5}{21} \alpha ^2 \left(31 \beta ^2+8\right) \\
- & & -\frac{5}{252}\left(\alpha ^2 (\beta  (37 \beta +144)+46)-92 \beta ^2\right) \\
-\end{array}
-\right),\\
-&0,\frac{1}{18} \left(-5 \alpha ^2 \left(7 \beta ^2+4\right)-20 \beta ^2+12\right) 
-\end{align}
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-1-D24terms}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-2-D24terms}
-\includegraphics[width=0.48\textwidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/code-rigid-rotation/figs/theta-0-q-3-D24terms}
-\caption{append fig; combine in one plot: $D_2/D_4\simeq 14$ at 
-$a=7$ bohr and $2eV$ crystal field gap ($\braket{r^4}=11.5809$, $D_4\simeq0.005$, $D_2=\sqrt{D_4}\simeq0.07$.)
-}
-\label{default}
-\end{center}
-\end{figure}
-
-}
-
-\end{document}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{System and Model}
-System: perovskites ABO3;
-Full model = lattice;
-Toy model = cages;
-
-\section{Analytical Results}
-phi rotations; 2x2 solutions;\\
-theta/phi rotations; approx 2x2 
-\subsection{Violation of Jahn-Teller Theorem}
-\section{Numerical Results}
-Exact numerics cages [cubic];;; exact lattice [with a,b,c lattice constants]; 
-\section{Effect of SOC}
-
-\begin{figure}
-\centering
-%\includegraphics[width=1.0\linewidth]{cartoon}
-\caption{
-}
-\label{fig:cartoon}
-\end{figure}
-
- %\end{document}
-\label{Bibliography}
-\bibliographystyle{apsrev4-1}
-%\bibliography{References}
-
-\end{document}
-
-\com{
-$V_{oct}(\vec r)$ causes the d-orbitals to split into two manifolds,
-$t_{2g}$ ($xy,yz,zx$) and $e_g$ ($z^2,x^2-y^2$)
-by an amount
-${\Delta_{CF}=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
-The deformation and resulting $V_{dipoles}(\vec r)$
-will lift the degeneracies as follows.
-\begin{align}
-(dE_{xy},dE_{yz},dE_{zx})&= \Delta_{\delta}
-\left[(2, -1, -1)D_{2} +\frac{20}{9} 
- (-1, 4, 4) D_{4}\right],\\
-(dE_{x^2-y^2},dE_{z^2})&=\Delta_{\delta}
-\left[(2,-2)D_{2} +\frac{20}{9} 
- (-1,-6)D_{4}\right],\\
-\Delta_{\delta}&= \frac{96}{7}
-\frac{-q_o}{a}
-\frac{\delta}{a}.
-\end{align}
-}
-
-\com{
-\begin{align}
-\tilde V(\vec r) &=\tilde V_O(\vec r) + \tilde V_{AB}(\vec r),\\
-\tilde V_O(\vec r) &= \tilde V_{oct}(\vec r),\\
-\tilde V_{AB}(\vec r) &= \mathcal{R}(\alpha,\beta) V_{AB}(\vec r),\\
-V_{AB}(\vec r) &= f(q_A) V_{oct}(\vec r) + 
-V_{dipoles}^{AB}(\vec r;\alpha,\beta),\\
-\label{eq:ylm_expansion}
-V_{dipoles}^{AB}(\vec r;\alpha,\beta) &= 
-\sum_{l=2,4}\sum_{m=-l}^{l}\left[V_{l,m}^{A}(\alpha,\beta)+V_{l,m}^{B}(\alpha,\beta)\right] r^l Y_{l,m}(\hat r),\\
-\tilde V(\vec r) &= \sum_{l,m} \tilde V_{l,m} r^l \tilde Y_{l,m}(\hat r),\\\end{align}
-\az{fix inconsistencies... in above equations.. R matix apply on a vector,,,, not a function.}.
-}

### 2023-09-21 manuscript/paper.tex
captons. 2,3 done.

@@
 and associated structural transformations.
-We find that the size of the splitting and the local orbital ordering are
+We find that the size of the splitting and the 
+%local orbital ordering 
+order of the orbitals
+are
 determined by a competition between the A and B cages, 
@@
 the size of the splitting 
-and local orbital ordering
+and 
+%local orbital ordering
+the order of the orbitals
 depend
@@
 \includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
-\caption{$alpha=0$. 
+\caption{
+Splitting in $t_{2g}$ manifold induced by the
+octahedral rotations.
+%The changes in the energies of $t_{2g}$ states 
+$E_{xy},E_{yz},E_{zx}$ 
+%and the average of $t_{2g}$ energy
+and $E_0^{t_{2g}}$
+as a function of the rotation angel $\beta$
+at $\alpha=0$ (no tilting),
+$\Delta=4q_o/15a$ ($D_4=1/200$), $D_2=\sqrt{D_4}$,
+and three values of $q_A/q_o$.
+(a)
+The B cage dominates at $q_A/q_o=1/2$
+and lowers $xy$ state and raises $yz,zx$ states
+with increasing $\beta$.
+As $q_A/q_o$ increases to $1$, 
+(b)
+A cage almost cancels the effect of B cage reducing the splitting,
+while it dominates at $q_A/q_o=2$ (c) where it switches the order of the states. 
 }
@@
 \includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
-\caption{$beta=0$ case, $q_A=q_o/2$}
+\caption{
+Splitting and mixing in $t_{2g}$ manifold induced by octahedral tilting.
+(a-c) 
+$E_D, E_{\pm}$ and $E_0^{t_{2g}}$
+as a function of $\alpha$
+at 
+$\beta=0$,
+and other parameters the same as in Fig.~\ref{fig:t2g-alpha0}.
+(d-f) Weight $W_{xy}$ of $xy$ orbital in 
+$\ket{E_{\pm}}$ states 
+shown in (a-c).
+The $xy$ orbital predominantly
+contributes to 
+$\ket{E_{+}}$
+at $q_A/q_o=1/2,1$ (a,b,d,e), 
+but to   
+$\ket{E_{-}}$
+at $q_A/q_o=2$ (c,f).
+}
 \label{fig:t2g-beta0}

### 2023-09-22 manuscript/paper.tex
caption, fig 4,5

@@
 \includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
-\caption{$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
+\caption{
+Splitting in $t_{2g}$ manifold due to octahedral rotation and tilting.
+$t_{2g}$ energies as a function of $\beta$ at $\alpha=10^\circ$
+at same value of other parameters as in Figs.~\ref{fig:t2g-alpha0},\ref{fig:t2g-beta0}.
+There are two anticrossings between the three states around $\beta\sim\alpha$.
+The character of the states depends on 
+the competition between the two angles and 
+the two ion cages.
+}
 \label{fig:t2g-ge-Es}
@@
 \caption{
-\az{Wts of eg in these states $\lesssim0.2\%$...} 
-$\alpha=10^\circ$ case: exact numerical results. solution of full 5x5}
+The dependence of the character of the $t_{2g}$ states
+on the competitions between
+$\alpha,\beta$ and 
+A,B ion cages.
+Weights of the three $t_{2g}$ orbitals in the three 
+$t_{2g}$ eigenstates 
+shown in
+Fig.~\ref{fig:t2g-ge-Es}
+(at the same parameters).
+At $q_A=q_o/2$, B cage dominates and
+$\ket{E_1}$ is predominantly $yz,zx$ at $\beta\sim 0\ll\alpha=10^\circ$, but 
+becomes $\sim xy$ at $\beta\gtrsim10^\circ$ (a).
+The situation flips when A cage dominates at $q_A=2q_o$ (d).
+Similarly, the character of $\ket{E_3}$ at 
+$q_A=q_o/2$
+resembles 
+that of $\ket{E_1}$ at $q_A=2q_o$  [compare (c) with (d)], and vice versa [compare (f) with (a)].
+The character of the middle state $\ket{E_2}$ (b,e)
+becomes $\sim xy$ only around the ``resonance'' region
+$\beta\sim \alpha$.
+}
 \label{fig:t2g-ge-wts}

### 2023-09-22 manuscript/paper.tex
caption, eg fig.

@@
 \begin{align}
+\label{eq:eg-E0}
 E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a - (3/5)f_{q_A}\Delta_o,\\
@@
 \includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
-\caption{$alpha=10^\circ$ case, $q_A=q_o/2,2q_o$}
+\caption{
+Energies and character of $e_g$ states.
+$E_{\pm}$ and $E_0^{e_g}$
+as a function of $\beta$ at $\alpha=10$, 
+and same parameters as in Fig.~\ref{fig:t2g-ge-Es}.
+At $q_A=q_o/2$ (a,c) where B cage dominates,
+$\alpha$ tends to make $\ket{E_{+}}$
+more $x^2-y^2$ (see small $\beta$ region),
+while $\beta$ tends to do the opposite 
+(see large $\beta$ region).
+The roles of $\alpha,\beta$ switch
+at $q_A=2q_o$ (b,d), where A cage dominates.
+We see that the splitting is relatively small as compared to $t_{2g}$ manifold.
+Approximate results obtained by a second order expansion of the Hamiltonian given in Eqs.\ref{eq:eg-hiix}-\ref{eq:eg-E0}
+are also shown for comparison.
+}
 \label{fig:e-wts-eg}

### 2023-09-24 manuscript/paper.tex
revision... fixing minor issues highlighted prev.

@@
 \begin{center}
-\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-bonds-labelled-1}
-%\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-labelled-2}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15}\\
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-z}
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-z}
-%\includegraphics[height=6.cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/AB-cages-deformed}
+\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-bonds-labelled-2}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic-bonds}
+%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15-bonds}\\
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-final}
+%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-final}
 \caption{
@@
 and finally describe the effect of the full lattice (sec.~\ref{sec:FL}).
-\az{appendix?}
+%\az{appendix?}
 
@@
 If we have an arrangement of ions with charge $q$ around a given site,
-we can express their (crystal field) potential in terms of spherical harmonics~(see \ref{append:multipoles}), 
+we can express their (crystal field) potential in terms of spherical harmonics~\cite{PavariniChap}, 
 \begin{align}
@@
 \end{align}
-and calculate the crystal field hamiltonian of the central ion/atom.
-Assuming we only have d-orbitals ($l=2$) on the central atom,
+where $a$ sets the length scale
+and $V_{l,m}$ are multipole components of the potential
+ (for the given site as origin and a chosen orientation).
+%and calculate the crystal field hamiltonian of the central ion/atom.
+Assuming we have a transition metal atom/ion
+at the central site
+with
+only $d$-orbitals ($l=2$),
 the matrix elements of its crystal field Hamiltonian
-are given by,
+are then given by,
 \begin{align}
@@
 $C_{l}^{m'm''m}=\braket{Y_{2,m'}| Y_{l,m}| Y_{2,m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
-and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the d-orbitals, assumed to be the same for all d-orbitals, i.e., the radial part of all d-orbitals is assumed the same~\cite{PaxtonNotes}.
+and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the $d$-orbitals, assumed to be the same for all $d$-orbitals, i.e., the radial part of all $d$-orbitals is assumed the same~\cite{PaxtonNotes}.
+The sum is restricted to even values of $l\leq 4$ as 
+$C_{l}^{m'm''m}=0$ otherwise.
 
@@
 \label{sec:egt2g}
-Consider six O ions each of charge $-q_o$ making an octahedron of size $a$ (placed at the face centres of a cube of edge length $a$).
+Consider six oxygen (O) ions each with a charge $-q_o$ making an octahedron of size $a$ (placed at the face centres of a cube of edge length $a$).
 The non-spherical part of the potential they
@@
  %that is 
- relevant for the d-orbitals contains 
+ relevant for the $d$-orbitals contains 
  only two $l=4$ components
-  in a specific ratio (${V_{4,0}:V_{4,4}=1:\sqrt{5/7}}$)
+  in a specific ratio (${V_{4,0}:V_{4,4}=1:\sqrt{5/7}}$),
  and is called octahedral field. 
@@
 turns out to be diagonal,
-with its states split into two manifolds $\Delta$ apart:
+with its states split into two manifolds: 
+% $\Delta$ apart:
 $H_{m,m} = -\Delta/3$ for $m\in\{-2,-1,1\}$ ($xy,yz,zx$ orbitals)
@@
 the ground state can have a finite distortion.
-We will use this argument and focus only on the changes
+We use this argument to focus only on the changes
  in the electronic energy throughout this paper.
@@
 
-In the following we 
+In the following, we 
 consider an octahedral environment around a transition metal ion 
@@
 
-Let's consider elongation of an octahedron in sec.~\ref{sec:egt2g} 
+Let us consider elongation of an octahedron in sec.~\ref{sec:egt2g} 
 along one of its O-B-O bond. 
-Align the cartesian axes along O-B-O bonds and stretch the two bonds along z-axis equally by an amount $a\delta$.
+Align the cartesian axes along O-B-O bonds and stretch the two bonds along $z$-axis equally by an amount $a\delta$.
 %where $a$ is the size of the octahedron (the distance between the O-O along any cartesian axes).
-The electric potential at the central B-site (JT ion) of this deformed octahedron can be calculated 
-and expanded in terms of (real) spherical harmonics as
-\begin{align}
-V^{JT}(\vec r) &= \frac{-q_o}{a}\sum_{lm}V_{l,m}^{JT}~\left(\frac{r}{a}\right)^l \ylm{l,m}.
-\end{align}
-%where the charge on O ion is taken as $-q_o$ ($q_o>0$, for brevity and clarity).
-Only few multipole components are non-zero due to their strict symmetries.
-The components %$V_{l,m}$ 
-up to $l=4$, which are relevant for d-orbitals with $l=2$, are given by
-~(see \ref{append:multipoles})
+The potential $V^{JT}(\vec r)$ at the central B site (JT ion) of this deformed octahedron 
+still contains only a few non-zero components.
+Not only the ratio 
+$V_{4,0}^{JT}:V_{4,4}^{JT}$ now deviates from
+ ideal 
+octahedral field as in Eq.~\ref{eq:voct},
+there is an $l=2$ component induced due to the deformation,
 \begin{align}
@@
 V_{4,0}^{JT}=& \frac{32}{3} \sqrt{\pi } \left(\frac{4}{(\delta +1)^5}+3\right),\\
-V_{4,4}^{JT}=& \frac{32 \sqrt{35 \pi }}{3},
-\end{align}
-where we only kept
-the trace preserving terms that keep the average of the whole spectrum fixed.
-%the terms that do not change the trace of the electronic Hamiltonian and thus keep the average of the whole spectrum fixed.
-We have ignored
-the monopole term $V_{0,0}^{JT}$ $[8 \sqrt{\pi } (2 \delta +3)/(\delta +1)]$,
-which rigidly shifts the whole spectrum 
-(by $\simeq 4 (3-\delta )q_o/a$)
-and
-can be assumed to be contributing to the elastic energy of the system.
+V_{4,4}^{JT}=& \frac{32 \sqrt{35 \pi }}{3}.
+\end{align}
 
@@
 ($D_4=\frac{3a}{160q_o} \Delta$) and 
-we can estimate its value from realistic values of $\Delta$ for a give octahedron size $a$ and ion charge $q_o$. 
+we can estimate its value from realistic values of $\Delta$ for a given octahedron of size $a$ and ion charge $q_o$. 
 Assuming $a=7.0$ bohr and $q_o=2e$ ($e$ being the elementary charge),
@@
 Assuming Hund's coupling is enough to still produce complete spin polarisation,
-their is only one possible orbital configuration, one electron in each of $xy,yz,zx$ orbitals.
+there is only one possible orbital configuration, one electron in each of $xy,yz,zx$ orbitals.
 This non-degenerate (many electron) ground state
@@
 
-cubic ABO3 crystal Structure... 
-rigid rotation/tilting: orthorhombic deformation... 
-typically associated with the relative sizes of the A, B,O ions.~\cite{ZhouPRL05}.
+We now turn to our model and calculations of the splittings in the 
+$t_{2g}$ and $e_{g}$ manifolds due to the deformations produced 
+in the crystal field as the octahedra rotate or tilt.
+First, let us consider the cubic perovskite and see 
+how much A and B cages contribute to the octahedral crystal field and associated splitting $\Delta$ between $t_{2g}$ and $e_{g}$ manifolds.
 
@@
 splits the degenerate d-orbitals
-by an amount ${\Delta_O=160q_oD_{4}/3a}$
+by an amount ${\Delta_o=160q_oD_{4}/3a}$
  into $t_{2g}$ and $e_g$.
@@
 The coordination cages of next nearest neighbours, 
-Eight A atoms/cations all at the same distance $\sqrt{3}a/2$
+eight A atoms/cations all at the same distance $\sqrt{3}a/2$
 make a cube around the B ion,
@@
 Furthermore,
-the nearest neighbouring B ions, size of them each at a distance $a$,
+the nearest neighbouring B ions, six of them each at a distance $a$,
 make an octahedron, with a potential 
@@
 Including the contribution of these AB cages to the crystal field,
-\begin{align}
-V(\vec r) &= V_{O}(\vec r) + V_{AB}(\vec r),\\
+we obtain
+\begin{align}
+%V(\vec r) &= V_{O}(\vec r) + V_{AB}(\vec r),\\
 V(\vec r)  &= (1+f_{q_A}) V_{O}(\vec r),
 \end{align}
-the 
+whereas the 
  splitting becomes
 %\begin{align}
-$\Delta = (1+f_{q_A})\Delta_O$.
+$\Delta = (1+f_{q_A})\Delta_o$.
 %\end{align}
@@
  still large enough to be ignored.
-It can be measured by $(\Delta-\Delta_O)/\Delta_O=f_{q_A}$,
+It can be measured by $(\Delta-\Delta_o)/\Delta_o=f_{q_A}$,
 which linearly changes from 
@@
 and $q_A=4$ still contributing just above $8\%$.
-% Delta_AB expression... and plot....
-\az{Not just this pot, deformation induces $l=2$ V2m that can couple much more strongly.... bcs of larger D222. 
-}
+We will see that these with the octahedral rotations and tilting, 
+these potentials rotate and deform.
+The deformation also induces $l=2$ components, which couple to the 
+$d$-orbitals of the B ion much more strongly. 
+%due to a much larger $D_{l=2}$.
 
@@
 }
-\az{figure vesta structure, label octahedra 1-4.}
 
@@
 $\sqrt{2}\times\sqrt{2}\times 2$ unit cell of the cubic structure that transforms
-to the unit cell of the orthorhombic structure under octahedral rotation and tilting.
+to the unit cell of the orthorhombic structure under octahedral rotation and tilting,
+as shown in Fig.~\ref{fig:struc}.
 Assuming 
@@
  to be the lattice vectors,
-two A and two B atoms in a layer are situated at
-%$(\vec a_1 + \vec a_3/2)/2$, $(\vec a_2+ \vec a_3/2)/2$,
-$(\textbf{a} + \textbf{c}/2)/2$, $(\textbf{b}+ \textbf{c}/2)/2$,
-and $(0,0,0)$, 
-%$(\vec a_1 + \vec a_2)/2$, 
-$(\textbf{a}  + \textbf{b} )/2$, 
-while similar atoms in the second layer are shifted by 
-%$\vec a_3/2$
-$\textbf{c} /2$
- from these.
+two B atoms in a layer are situated at
+%$(0,0,0)$, 
+$\textbf{a}/2$, $\textbf{b}/2$,
+%$(\textbf{a}  + \textbf{b} )/2$, 
+while two A atoms in the same layer are at
+% all coor shifted by a/2 to match to those in Fig.1 [vesta: unit cell transformation]:
+%$(\textbf{a} + \textbf{c}/2)/2$, $(\textbf{b}+ \textbf{c}/2)/2$,
+$\textbf{c}/4$, $(\textbf{a}+\textbf{b})/2 + \textbf{c}/4$.
+Similar atoms in the second layer are simply shifted by 
+$\textbf{c} /2$.
 While the lattice vectors change under the rotation and tilting of the octahedra, 
@@
 and then tilt it by rotating it about new $110$ by an angle $\alpha$.
-Four octahedra have to be rotated and tilted clockwise or counter closckwise
+The four octahedra in the cell 
+have to be rotated and tilted clockwise or counter clockwise
 consistently. For example, %$\alpha  \{1,-1,-1,1\}$, $\beta  \{1,-1,1,-1\}$.
@@
 $(\alpha,-\beta)$
-for the atoms labelled $1$ through $4$ in Fig.~\ref{fig:structure}.
+for the octaherda labelled $1$ through $4$ in Fig.~\ref{fig:struc}(b).
 The structure transforms from cubic to orthorhombic under these rotation and tilting of the octahedra.
-The rotation matrix $R$ for $(\alpha,\beta)$ case is given in the appendix~\ref{sec:appendix}. 
+%The rotation matrix $R$ for $(\alpha,\beta)$ case is given in the appendix~\ref{sec:appendix}. 
 The lattice vectors of the deformed structure and the positions of A and B atoms can be calculated easily by calculating the coordinates of all six oxygen atoms that make the octahedra (by rotating and tilting the octahedra) for all four octahedra in the unit cell and
@@
 There are two different ways the crystal field $V(\vec r)$
-\az{[at the location of a B ion... which B ion out of four in distorted structure?... pick one here...]
-We consider the B ion at $(0,0,0)$....
-energies/splittings are practically the same for all B ions... 
-but their eigenstates differ considerably that creates interesting orbital ordering as discussed later in the discussion section, sec.~\ref{sec:discussion}.
-
-}
  is deformed from the ideal case $V(\vec r) \propto V_{oct}(\vec r)$
@@
 splitting of degenerate d-orbitals into $e_g, t_{2g}$ manifolds with 
-a gap $\Delta_O$,
+a gap $\Delta_o$,
 and then
@@
 we can even ignore the coupling between the states belonging to the 
-different manifolds $\Delta_O$ apart.
+different manifolds $\Delta_o$ apart.
 This also makes it possible to analytically solve the problem in two limiting cases discussed later.
@@
 $\mathcal{R}^{l}=\mathcal{R}^{l}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics 
-of degree $l$ (see appendix~\ref{sec:appendix}).
+of degree $l$. % (see appendix~\ref{sec:appendix}).
 It can be calculated using the method described in Ref.~\cite{IvanicJPC96}.
-\az{next para?}
 The multipole components of $V_O(\vec r)$ in the rotated frame do not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
@@
 so it now has not only other $l=4$ components but also $l=2$ components; see below.
-A procedure to obtain these multipole components without
+A procedure to obtain these multipole components, without
 actually calculating the projection of the potential $V_{AB}(\vec r)$ 
-onto the spherical harmonics is described in the appendix~\ref{sec:appendix}.
+onto the spherical harmonics, is described in the appendix. %~\ref{append:multipoles}.
+
+We find that the splittings due to octahedral rotation and tilting are practically the same for all B ions
+(but their eigenstates differ considerably, which creates interesting orbital ordering as discussed later in the discussion in sec.~\ref{sec:discussion}),
+so we consider the octahedron $1$ with central B ion at $\text{a}/2$
+in the calculations that follow.
 We obtain the following exact expressions for $V_{lm}^{A}$,
@@
 
-\az{V20, JT:\\
+\com{V20, JT:\\
 V2-2, V4-2, couple yz and zx.
@@
 at $\alpha=0$ (no tilting),
-$\Delta=4q_o/15a$ ($D_4=1/200$), $D_2=\sqrt{D_4}$,
+$\Delta_o=4q_o/15a$ ($D_4=1/200$), $D_2=\sqrt{D_4}$,
 and three values of $q_A/q_o$.
 (a)
-The B cage dominates at $q_A/q_o=1/2$
-and lowers $xy$ state and raises $yz,zx$ states
+The B cage dominates at $q_A/q_o=1/2$;
+it lowers $xy$ state and raises $yz,zx$ states
 with increasing $\beta$.
@@
 Before we present our results,
-let's briefly describe 
+let us briefly describe 
 the kind of behaviour that would indicate a JT instability 
@@
 
-\az{Focus on t2g first:}\\
+%\az{Focus on t2g first:}\\
 
@@
 \ket{-} = \sin\gamma \ket{xy} - \cos\gamma \ket{B},\\
-\tan2\gamma = \sqrt{8}g/(E_{xy}-E_{yz}+\lambda)
+\tan2\gamma = \sqrt{8}g/(E_{xy}-E_{yz}+\lambda),
 \end{gather}
@@
 E_{xy}=& Q.
-\left(-\frac{64 \alpha ^2}{63 \sqrt{3}},-\frac{512 \left(15 \alpha ^2+7\right)}{1701 \sqrt{3}},\frac{3\alpha ^2}{7} ,\frac{5 \alpha ^2}{7}+\frac{2}{3}\right)\\
+\left(-\frac{64 \alpha ^2}{63 \sqrt{3}},-\frac{512 \left(15 \alpha ^2+7\right)}{1701 \sqrt{3}},\frac{3\alpha ^2}{7} ,\frac{5 \alpha ^2}{7}+\frac{2}{3}\right),\\
 E_{yz}=& Q.
-\left(\frac{32 \alpha ^2}{63 \sqrt{3}},\frac{512 \left(25 \alpha ^2-7\right)}{1701 \sqrt{3}},-\frac{3 \alpha ^2}{14},-\frac{85 \alpha ^2}{42}+\frac{2}{3}\right)\\
+\left(\frac{32 \alpha ^2}{63 \sqrt{3}},\frac{512 \left(25 \alpha ^2-7\right)}{1701 \sqrt{3}},-\frac{3 \alpha ^2}{14},-\frac{85 \alpha ^2}{42}+\frac{2}{3}\right),\\
 g=& Q.
-\left(-\frac{80}{63} \sqrt{\frac{2}{3}} \alpha ^3,0,\frac{15 \alpha ^3}{14 \sqrt{2}},\frac{5 \alpha ^3}{2 \sqrt{2}}\right)\\
+\left(-\frac{80}{63} \sqrt{\frac{2}{3}} \alpha ^3,0,\frac{15 \alpha ^3}{14 \sqrt{2}},\frac{5 \alpha ^3}{2 \sqrt{2}}\right),\\
 \lambda=& Q.
@@
 and the weight of $xy$ state $W_{xy}$ in $E_{\pm}$,
-as a function of $\alpha$ at $q_A/q_o=1/2,1,2$ (and $\Delta=15q_o/4a$)
+as a function of $\alpha$ at $q_A/q_o=1/2,1,2$ (and $\Delta_o=4q_o/15a$)
 are shown in Fig.~\ref{fig:t2g-beta0}.
 The average shifts slightly with $\alpha,q_A$ by 
-$E_0^{t_{2g}}= \left(E_{xy} + 2 E_{yz}\right)/3-(2/5)f_{q_A}\Delta_{O}$,
+$E_0^{t_{2g}}= \left(E_{xy} + 2 E_{yz}\right)/3-(2/5)f_{q_A}\Delta_{o}$,
 again reflecting 
@@
 at energies $E_i, i=1,2,3$.
-\az{E0, can we show E0 only in the first fig and not all of them?}
+%\az{E0, can we show E0 only in the first fig and not all of them?}
 At $\beta=0$, these results correspond to $\alpha=10^\circ$ 
@@
 so the lowest state at $\beta=0$
-here is $\ket{D}$ in Figs.~\ref{fig:t2g-ge-Es}(a)
-while it is the highest in Figs.~\ref{fig:t2g-ge-Es}(b).
+here is $\ket{D}$ in Fig.~\ref{fig:t2g-ge-Es}(a)
+while it is the highest in Fig.~\ref{fig:t2g-ge-Es}(b).
 We see two anticrossings or level repulsion in either of Figs.~\ref{fig:t2g-ge-Es}(a,b)
 in different orders.
-In Figs.~\ref{fig:t2g-ge-Es}(a), 
+In Fig.~\ref{fig:t2g-ge-Es}(a), 
 the anticorssing between the highest two states occurs at smaller $\beta$,
-while the situation is the opposite in Figs.~\ref{fig:t2g-ge-Es}(b) where 
+while the situation is the opposite in Fig.~\ref{fig:t2g-ge-Es}(b) where 
 it occurs between the lowest pair at smaller $\beta$.
@@
 for $\beta<7^\circ$ and it quickly becomes $xy$
-as $\beta\alpha=10^\circ$.
-Fig.~\ref{fig:t2g-ge-wts}(b,c)
+as $\beta\to\alpha=10^\circ$.
+Figs.~\ref{fig:t2g-ge-wts}(b,c)
 show a complimentary behaviour 
@@
 about the ``resonance'' $\beta\sim\alpha$.
-Fig.~\ref{fig:t2g-ge-wts}(b,e)
+Figs.~\ref{fig:t2g-ge-wts}(b,e)
 show an interesting aspect,
@@
 E_0^A &=
-\frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}}\\
+\frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}},\\
 E_0^B &=
-(-\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1).
+-\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1.
 \end{align}
@@
 as indicated by the behaviour of $W_{x^2-y^2}$,
-which is almost zero in $\ket{E_{-}}$ at $\beta\lesssim 5^\circ \ll \alpha=10^\circ$,
+which is almost zero in $\ket{E_{-}}$ at $\beta\lesssim 5^\circ$
+ ($\ll \alpha=10^\circ$),
 while it approaches unity at 
@@
 This is also evident from the signs of the $\Omega_l$
-in Eqs.~\ref{eq:eg-hiix}.
+in Eq.~\ref{eq:eg-hiix}.
 We see that $l=2$ terms have the same signs as $t_{2g}$ case but 
@@
 To see how well
-the expansions in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx})
+the expansions in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx}
 can approximate the exact results,
@@
 are compared for the two cases
-at $\alpha=0$, $\beta=20^\circ$ (and $\Delta=4q_o/15a$).
+at $\alpha=0$, $\beta=20^\circ$ (and $\Delta_o=4q_o/15a$).
 In case of AB cages, the crossing of the 
@@
 \includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
-\caption{$alpha=0$ evals vs q at $beta=20$. 
+\caption{
+The effect of the potential of full ionic lattice.
+$t_{2g}$ spectrum computed using the potential of full lattice compared with that obtained from only A,B cages (and the anion octahedron itself),
+shown as a function of $q_A/q_o$ at 
+$\alpha=0,\beta=20^\circ$, $\Delta_o=4q_o/15a$.
+Full lattice only shifts the balance between the two cation cages towards A but keeps the qualitative picture the same.
 }
@@
 \section{Discussion and Outlook}
+\label{sec:discussion}
 

### 2023-09-24 manuscript/paper.tex
highlighted points resolved

@@
 which fixes the value of $D_4=1/200$, 
-and corresponds to $\Delta= 2.073$ eV at 
+and corresponds to $\Delta_o= 2.073$ eV at 
 $q_o=2$ e and $a=7.0$ bohr.
@@
 
-\az{
-
+\com{
 Summarise t2g results here.\\
-
 copy from summary section...??
-
 tilt vs rotation, preference:\\
+ }
 
@@
 while rotation stabilises one and destabilises the other occupied orbital.
-
-}
 

### 2023-09-26 manuscript/paper.tex
revision.. TODO: results

@@
 
+\author{Kashif Sabeeh}
+\affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}
+
 \date{\today}
@@
 %BO$_{6/2}$ 
-octahedra
+anion octahedra around the transition metal ions
  in ABO$_3$ perovskites
@@
 effect of the crystal field of the nearest A and B ion cages 
-%that immediately surround the octahedra
-on the single electron spectrum of B, the 
+on the single electron spectrum of the 
 central 
-transition metal ions.
-While the crystal field of the octahedra 
-that 
+transition metal B ions.
+While the crystal field of the octahedra,
+which
 % quenches the orbital angular momentum of the central B ion and 
-creates degenerate manifolds $e_g$ and $t_{2g}$
+creates degenerate manifolds $e_g$ and $t_{2g}$,
 do not change with such rigid rotations, 
@@
 surface electronic structure~\cite{MoralesPRL23},
-has also been investigated.
+have also been investigated.
 % JT interacting with octa tilting:
@@
 find a negative correlation between metal-oxygen bond covalency 
-and octahedral rotation in orthorhombic perovskites oxides~\cite{CammarataJCP14}.
+and octahedral rotation in orthorhombic perovskite oxides~\cite{CammarataJCP14}.
 % Lee, nick2016
@@
 We find that the degeneracy of $t_{2g}$ and $e_g$
-is lifted, and
-the size of the splitting 
+is lifted. 
+The size of the splitting 
 and 
@@
 describe the deformation effects of 
-rigid octahedral rotations (sec.~\ref{sec:rotation})
+rigid octahedral rotations %(sec.~\ref{sec:rotation})
 on
@@
 If we have an arrangement of ions with charge $q$ around a given site,
-we can express their (crystal field) potential in terms of spherical harmonics~\cite{PavariniChap}, 
+we can express their %(crystal field) 
+potential in terms of spherical harmonics~\cite{PavariniChap}, 
 \begin{align}
@@
 $C_{l}^{m'm''m}=\braket{Y_{2,m'}| Y_{l,m}| Y_{2,m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
-and $D_{l}=\braket{(r/a)^l}$ is the expectation value for the $d$-orbitals, assumed to be the same for all $d$-orbitals, i.e., the radial part of all $d$-orbitals is assumed the same~\cite{PaxtonNotes}.
+and $D_{l}=\braket{(r/a)^l}$
+is the expectation of $(r/a)^l$ evaluated in the $d$-orbitals bases
+assuming the same radial dependence for all orbitals~\cite{PaxtonNotes}.
 The sum is restricted to even values of $l\leq 4$ as 
-$C_{l}^{m'm''m}=0$ otherwise.
+$C_{l}^{m'm''m}=0$ otherwise,
+with $-l \leq m \leq l$.
+
+We consider transition metal oxides as an example perovskite system throughout the rest of the manuscript,
+but our calculations and results are general and also apply to perovskite transition metal compounds with other anions, e.g., halides and chalcogenides.
 
@@
 \label{sec:egt2g}
-Consider six oxygen (O) ions each with a charge $-q_o$ making an octahedron of size $a$ (placed at the face centres of a cube of edge length $a$).
+Consider six oxygen (O) ions each with a charge $-q_o$ making an octahedron of size $a$ (where these anions are placed at the face centres of a cube of edge length $a$).
 The non-spherical part of the potential they
@@
  relevant for the $d$-orbitals contains 
- only two $l=4$ components
+ only two $l=4$ components, 
   in a specific ratio (${V_{4,0}:V_{4,4}=1:\sqrt{5/7}}$),
@@
 elongation or a compression of an octahedron along one of its axes by $a\delta$,
-where $a$ is the lattice constant of the cubic structure.
+where $a$ is the size of the octahedron and lattice constant of the cubic perovskite structure.
 The corresponding change in the unit cell volume would be linear in $\delta$
@@
 \subsection{Tetragonal distortion of an octahedron}
-
-Let us consider elongation of an octahedron in sec.~\ref{sec:egt2g} 
-along one of its O-B-O bond. 
+\label{sec:JTtertagonal}
+
+Let us consider elongation of an octahedron % in sec.~\ref{sec:egt2g} 
+along one of its O-B-O bonds. 
 Align the cartesian axes along O-B-O bonds and stretch the two bonds along $z$-axis equally by an amount $a\delta$.
@@
  ideal 
-octahedral field as in Eq.~\ref{eq:voct},
+octahedral field in Eq.~\ref{eq:voct},
 there is an $l=2$ component induced due to the deformation,
@@
 
-The crystal field Hamiltonian of the central B ion/JT ion
-${H_{m',m''}^{JT} = (q_o/a)\sum_{l,m} V_{l,m}^{JT} C_{l}^{m'm''m} D_{l}}$
+The crystal field Hamiltonian of the JT ion,
+${H_{m',m''}^{JT} = (q_o/a)\sum_{l,m} V_{l,m}^{JT} C_{l}^{m'm''m} D_{l}}$,
 still turns out to be diagonal 
@@
 We now turn to our model and calculations of the splittings in the 
-$t_{2g}$ and $e_{g}$ manifolds due to the deformations produced 
-in the crystal field as the octahedra rotate or tilt.
+$t_{2g}$ and $e_{g}$ manifolds due to the deformations 
+in the crystal field that are produced as the octahedra rotate or tilt.
 First, let us consider the cubic perovskite and see 
@@
 and $q_A=4$ still contributing just above $8\%$.
-We will see that these with the octahedral rotations and tilting, 
-these potentials rotate and deform.
+We will see that,
+as the anion octahedra rotate or tilt,
+$V_{AB}(\vec r)$ rotate in its frame and deform as well.
 The deformation also induces $l=2$ components, which couple to the 
@@
 
-\subsection{Rigid octahedral rotations}
-\label{sec:rotation}
-
-\subsection{Transformation of the crystal structure}
+%\subsection{Rigid octahedral rotations}
+%\label{sec:rotation}
+
+\subsection{Rigid octahedral rotations: Transformation of the crystal structure}
 \label{sec:structure}
@@
 We rotate the octahedra by an angle $\beta$ about $\hat z \equiv 001$
-and then tilt it by rotating it about new $110$ by an angle $\alpha$.
+and then tilt it about the new $110$ by an angle $\alpha$~\cite{CarterPRB12}.
 The four octahedra in the cell 
@@
 AB and O cages is the same. 
-We no longer just get $e_g, t_{2g}$ manifolds in any frame but with splittings induced by the rotation.
-This generates non-octahedral but still only $l=4$ field components. 
+We no longer just get $e_g, t_{2g}$ manifolds in any frame but with splittings induced by the rotation,
+which generates non-octahedral but still only $l=4$ field components. 
 \item
@@
 $l=2$ field components
-that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below).
+that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below Eq.~\ref{eq:JTeg} in sec.~\ref{sec:JTtertagonal}).
 So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see sec.~\ref{sec:relativeVoctABO}).
@@
 $f_{q_A} \ll 1$,
-we can even ignore the coupling between the states belonging to the 
-different manifolds $\Delta_o$ apart.
+we can even ignore the coupling between the states belonging to
+different manifolds that are $\Delta_o$ apart.
 This also makes it possible to analytically solve the problem in two limiting cases discussed later.
@@
 %$V$ is as a vector %of length $(l_{max}+1)^2=25$ for $l_{max}=4$.
-in the spherical harmonics basis, so
-we can calculate it in one basis as per our convenience and then transform it to another.
+in the spherical harmonics bases, so
+we can calculate it in one bases as per our convenience and then transform it to another.
 %Its components in the new basis.
@@
 of degree $l$. % (see appendix~\ref{sec:appendix}).
-It can be calculated using the method described in Ref.~\cite{IvanicJPC96}.
+It can be calculated using the method 
+devised by Ivanic and Ruedenberg~\cite{IvanicJPC96}.
 The multipole components of $V_O(\vec r)$ in the rotated frame do not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
-These can be read off Eq.~\ref{eq:voct}.
-Similarly, its easier to obtain the components of $V_{AB}(\vec r)$
+These can be directly read off Eq.~\ref{eq:voct}.
+Similarly, it is easier to obtain the components of $V_{AB}(\vec r)$
 in the unrotated frame so we do that first and later transforms them to obtain the rotated frame components.
@@
 %where $q_A + q_B = 3q_o$ ensures charge neutrality.
-where the quantities bearing a tilde on top belong to the rotated frame.
+where the quantities bearing a tilde on top belong to the rotated (octahedron's) frame.
 As described above, 
-$\tilde V_{lm}^O$ are simply octahedral field components $l=4,m=0,4$ (see Eq.~\ref{eq:voct}).
+$\tilde V_{lm}^O$ are simply octahedral field components 
+with $l=4,m=0,4$ (see Eq.~\ref{eq:voct}).
 However, $V_{lm}^{AB}$ contain the effect of the deformation of the crystal structure 
@@
 (but their eigenstates differ considerably, which creates interesting orbital ordering as discussed later in the discussion in sec.~\ref{sec:discussion}),
-so we consider the octahedron $1$ with central B ion at $\text{a}/2$
+so we consider the octahedron $1$ with central B ion at $\textbf{a}/2$
 in the calculations that follow.
@@
 the crystal field of the AB cages 
-in the octahedron's local frame (rotated frame)
+in the octahedron's frame %(rotated frame)
 are given by,
@@
 Here we describe the procedure to obtain the multipole components 
-$V_{l,m}^{A/B}$ of potentials $V^{A/B}(\vec r)$ of $A/B$ ion cages 
+$V_{l,m}$ of a potentials $V(\vec r)$ %of $A/B$ ion cages 
 at a position $\vec r$ around a JT ion.
-That is, we like to expand the potentials $V^{A/B}(\vec r)$
+Let's consider $V^{A}(\vec r)$ to illustrate the idea. 
+$V^{B}(\vec r)$ and $V^{JT}(\vec r)$ can also be dealt the same way.
+
+We like to expand the potentials $V^{A}(\vec r)$
 in spherical harmonics as
@@
 \label{eq:ylm_compA}
-V^{A}(\vec r) =& \sum_{l,m} V_{lm}^{A} r^l Y_{lm}(\hat r),\\
-\label{eq:ylm_compB}
-V^{B}(\vec r) =& \sum_{l,m} V_{lm}^{B} r^l Y_{lm}(\hat r).
-\end{align}
-It is worth noting that $V_{l,m}^{A/B}$ can be found without 
+V^{A}(\vec r) =& \frac{q_A}{a}\sum_{l,m} V_{lm}^{A} \left(\frac{r}{a}\right)^l Y_{lm}(\hat r),
+\end{align}
+where we have assumed $a$ as a length scale and 
+taken out the factor $\frac{q_A}{a}$ for clarity.
+It is worth noting that $V_{l,m}^{A}$ can be found without 
 evaluating the 
 inner products between the spherical harmonics and
-$V^{A/B}(\vec r)=V^{A/B}(\vec r;\alpha,\beta)$, as follows.
+$V^{A}(\vec r)=V^{A}(\vec r;\alpha,\beta)$, as follows.
 
 First we calculate
-$V^{A/B}(\vec r)$
+$V^{A}(\vec r)$
 using the simple textbook formula.
-$V^{A}(\vec r;\alpha,\beta)=\sum_{i}1/|\vec r^A_i-\vec r |$, 
+$V^{A}(\vec r;\alpha,\beta)=q_A\sum_{i}1/|\vec r^A_i-\vec r |$, 
 where $\vec r^A_i$ is the position of $i$-th A ion
@@
 measured from the JT ion.
-Similarly,
-$V^{B}(\vec r;\alpha,\beta)=\sum_{i}1/|\vec r^B_i-\vec r |$.
 Writing cartesian components of $\vec r$ as
@@
 and expanding 
-${V^{A/B}(\vec r;\alpha,\beta)}$
+${V^{A}(\vec r;\alpha,\beta)}$
 in powers of $r$, 
@@
 in powers of $\cos\theta, \cos\phi$ 
-(or $\sin\theta, \sin\phi$, or simply $\theta,\phi$) 
+(or $\sin\theta, \sin\phi$) 
 and comparing the terms with a similar expansion of 
 the formal expression on the right side 
-of Eq.~\ref{eq:ylm_compA} or Eq.~\ref{eq:ylm_compB}.
+of Eq.~\ref{eq:ylm_compA}.
 This gives a set of
-linear equations in $\{V_{l,m}^{A/B}\}$ (for a fixed value of $l$)
+linear equations in $\{V_{l,m}^{A}\}$ (for a fixed value of $l$)
  that can be easily solved.

### 2023-09-26 manuscript/paper.tex
first draft done. will share with KSabeeh and see if he likes something to change.

@@
 \begin{align}
-V(\vec r) &= \frac{q}{a}\sum_{lm}V_{l,m}~\left(\frac{r}{a}\right)^l \ylm{l,m},
+V(\vec r) &= \frac{q}{a}\sum_{lm}V_{lm}~\left(\frac{r}{a}\right)^l \ylm{lm},
 \end{align}
@@
 \begin{align}
-H_{m',m''} &= -\frac{q}{a}\sum_{l,m} V_{l,m} C_{l}^{m'm''m} D_{l} ,
+H_{m' m''} &= -\frac{q}{a}\sum_{l,m} V_{lm} C_{l}^{m'm''m} D_{l} ,
 \end{align}
 where 
-$C_{l}^{m'm''m}=\braket{Y_{2,m'}| Y_{l,m}| Y_{2,m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
+$C_{l}^{m'm''m}=\braket{Y_{2m'}| Y_{lm}| Y_{2m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
 and $D_{l}=\braket{(r/a)^l}$
@@
 % $\Delta$ apart:
-$H_{m,m} = -\Delta/3$ for $m\in\{-2,-1,1\}$ ($xy,yz,zx$ orbitals)
+$H_{mm} = -\Delta/3$ for $m\in\{-2,-1,1\}$ ($xy,yz,zx$ orbitals)
 called $t_{2g}$,
 and 
-$H_{m,m} = +2\Delta/3$ for $m\in\{2,0\}$ ($x^2-y^2,z^2$ orbitals)
+$H_{mm} = +2\Delta/3$ for $m\in\{2,0\}$ ($x^2-y^2,z^2$ orbitals)
 called $e_g$.
@@
 The potential $V^{JT}(\vec r)$ at the central B site (JT ion) of this deformed octahedron 
-still contains only a few non-zero components.
+still contains only a few non-zero components (see appendix for a method to calculate $V_{lm}^{JT}$).
 Not only the ratio 
@@
 The crystal field Hamiltonian of the JT ion,
-${H_{m',m''}^{JT} = (q_o/a)\sum_{l,m} V_{l,m}^{JT} C_{l}^{m'm''m} D_{l}}$,
+${H_{m' m''}^{JT} = (q_o/a)\sum_{l,m} V_{lm}^{JT} C_{l}^{m'm''m} D_{l}}$,
 still turns out to be diagonal 
@@
 which linearly changes from 
-$-\frac{3}{32}\simeq -10\%$ at $q_A=0$
-to $\frac{8}{27 \sqrt{3}}\simeq 17\%$ at $q_A=3q_o$. 
+$-3/32\simeq -10\%$ at $q_A=0$
+to $8/{27 \sqrt{3}}\simeq 17\%$ at $q_A=3q_o$. 
 Typical values of $q_A$ relevant for real transition metal oxides
@@
 \begin{gather}
-\tilde V_{lm} = \tilde V_{lm}^O + \sum_{m'=-l}^{l}\mathcal{R}^{l}_{m,m'} V_{lm'}^{AB},\\
+\tilde V_{lm} = \tilde V_{lm}^O + \sum_{m'=-l}^{l}\mathcal{R}^{l}_{m m'} V_{lm'}^{AB},\\
 V_{lm}^{AB} = \left(\frac{q_A}{a} \right)V_{lm}^{A}   
@@
 \begin{align}
-\tilde H_{m',m''} &= \sum_{l,m} \tilde V_{l,m} \tilde C_{l}^{m'm''m} D_{l} ,
+\tilde H_{m' m''} &= \sum_{l,m} \tilde V_{l m} \tilde C_{l}^{m'm''m} D_{l} ,
 %C_{l}^{m'm''m} &= \braket{\tilde Y_{2,m'}|\tilde Y_{l,m}|\tilde Y_{2,m''}},
@@
 where %$C_{l}^{m'm''m}$ 
-$\tilde C_{l}^{m'm''m}=\braket{\tilde Y_{2,m'}|\tilde Y_{l,m}|\tilde Y_{2,m''}}= C_{l}^{m'm''m}$. 
+$\tilde C_{l}^{m'm''m}=\braket{\tilde Y_{2m'}|\tilde Y_{lm}|\tilde Y_{2m''}}= C_{l}^{m'm''m}$. 
 % are again the Gaunt coefficients for the real spherical harmonics.
@@
 %hypothetical 
-elongations or compressions 
-$a\delta_1,a\delta_2$ 
-of an octahedron along its axes,
-where the 
+elongations or 
+compressions---$a\delta_1,a\delta_2$ 
+of an octahedron along two of its axes---where the 
  the unit cell volume changes
@@
 as $\sim\left(\delta_1+\delta_1\right)^2$,
-the unit cell volume,
-in case of octahedral rotation and tilting,
+the unit cell volume
+in case of octahedral rotation and tilting
  depends on the ``distortions'' $\alpha,\beta$ 
@@
 it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$
-leading to a quartic elastic energy that should roughly be
+leading to a \emph{quartic} elastic energy that should roughly behave as
 $\sim\left(\alpha ^2+\beta ^2\right)^2$.
@@
  to produce a finite distortion in the optimum structure.
-Thinking of squared angles as the basic variables,
+Thinking of squared angles 
+$\alpha ^2,\beta ^2$
+as the basic distortion variables,
 the order of the electronic and elastic energy terms
@@
 and see how the potential of the AB cages split it when 
-the octahedra tilts and rotates.
+the octahedra tilt and rotate.
 
@@
 E_{0}^{t_{2g}} = \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a
--(2/5)f_{q_A}\Delta_{O},
+-(2/5)f_{q_A}\Delta_{o},
  \end{align}
@@
 as a function of $\beta$
-at three different values of $q_A/q_o=1/2,1,2$.
+at three values of $q_A/q_o=1/2,1,2$.
 We have 
@@
 Fig.~\ref{fig:t2g-alpha0} shows that
-the the competition between A and B cages
+the competition between A and B cages
 determines the ground state and the size of the splitting between the 
 $t_{2g}$ states
-$E_{xy}$, and $E_{yz/zx}$.
+$E_{xy}$ and $E_{yz/zx}$.
 In Fig.~\ref{fig:t2g-alpha0}(a),
@@
 it reverses the order in Eq.~\ref{eq:theta0-Es}
-and $E_{xy}$ becomes lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $15^\circ$.
+and $E_{xy}$ becomes lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $\beta=15^\circ$.
 When A cage dominates at large $q_A/q_o$,
 as shown in Fig.~\ref{fig:t2g-alpha0}(c) for $q_A/q_o=2$,
-$E_{yz/zx}$ are the single particle ground states (again with a splitting of $\sim6\%$ of $\Delta_o$ at $15^\circ$),
+$E_{yz/zx}$ are the single particle ground states
+ (with a splitting of the same order), %$\sim6\%$ of $\Delta_o$ at $15^\circ$),
 whereas the net effect of both cages
@@
 that corresponds to $q_A/q_o=1$
-and we only obtain a splitting of $\sim2\%$ of $\Delta_o$ at $15^\circ$
-between $E_{xy}$ and $E_{yz/zx}$ levels.
+and we only obtain a splitting of $\sim2\%$ of $\Delta_o$ at $\beta=15^\circ$.
+%between $E_{xy}$ and $E_{yz/zx}$ levels.
 Obviously, there will also be a point near 
 $q_A/q_o=1$ where A and B completely 
-cancel each others effect (not shown in Fig.~\ref{fig:t2g-alpha0}).
-We also see that $E_0^{t_{2g}}$ changes from a slight negative shift to a slight positive shift
+cancel the effect of each other (not shown in Fig.~\ref{fig:t2g-alpha0}).
+We also see that $E_0^{t_{2g}}$ changes from a small negative to a small positive value
 with an increase in $q_A/q_o$ as we
@@
 $\Delta$ slightly widens at small $q_A$ and shrinks at large $q_A$,
-shifting $E_0^{t_{2g}}$ slightly down or up with $\beta$.
+shifting the $t_{2g}$ manifold slightly down or up with $\beta$.
 
 These results also indicate that in case of a superlattice with $q_A$ alternating
-between the two regimes shown in Figs.~\ref{fig:t2g-alpha0})(a,c),
-we should obtain a corresponding orbital order if the octahedra are rotated.
+between the two regimes shown in Figs.~\ref{fig:t2g-alpha0}(a,c),
+we should obtain an alternating orbital order if the octahedra are rotated.
 
@@
 at 
-$\beta=0$,
-and other parameters the same as in Fig.~\ref{fig:t2g-alpha0}.
+$\beta=0$;
+other parameters are the same as in Fig.~\ref{fig:t2g-alpha0}.
 (d-f) Weight $W_{xy}$ of $xy$ orbital in 
@@
 at $q_A/q_o=1/2,2$ [Fig.~\ref{fig:t2g-beta0}(a,c)] and about $2\%$ at $q_A/q_o=1$ [Fig.~\ref{fig:t2g-beta0}(b)].
-The mixing is sizeable but still far from perfect ($50/50\%$) even at the largest $\alpha$ shown ($W_{xy}=0.25$-$0.35$ at $20^\circ$).
+The mixing is sizeable but still far from perfect ($50/50\%$) even at the largest $\alpha$ shown ($W_{xy}=0.25$-$0.35$ at $\alpha=20^\circ$).
 % At unrealistically large $\alpha\sim30-40^\circ$, 
@@
 $t_{2g}$ energies as a function of $\beta$ at $\alpha=10^\circ$
-at same value of other parameters as in Figs.~\ref{fig:t2g-alpha0},\ref{fig:t2g-beta0}.
+at the same values of other parameters as in Figs.~\ref{fig:t2g-alpha0},\ref{fig:t2g-beta0}.
 There are two anticrossings between the three states around $\beta\sim\alpha$.
@@
 shown in
-Fig.~\ref{fig:t2g-ge-Es}
-(at the same parameters).
+Fig.~\ref{fig:t2g-ge-Es}.
+%(at the same parameters).
 At $q_A=q_o/2$, B cage dominates and
@@
 
-The $t_{2g}$ Hamiltonian in the general case $\alpha,\beta\neq 0$ cannot be solve analytically
+The $t_{2g}$ Hamiltonian in the general case $\alpha,\beta\neq 0$ cannot be solved analytically
  so there is no longer any advantage of ignoring the coupling between 
@@
 at $q_A/q_o=1/2,2$ and $\Delta_o=4q_o/15a$ again.
-All states in the $t_{2g}$ mix up to make the eigenstates $\ket{E_i}, i=1,2,3$
-at energies $E_i, i=1,2,3$.
+All states in the $t_{2g}$ mix up to make the eigenstates $\{\ket{E_i}\}$
+at energies $\{E_i\}, i=1,2,3$.
 %\az{E0, can we show E0 only in the first fig and not all of them?}
@@
 are shown in Fig.~\ref{fig:t2g-ge-wts}.
-Let's first focus on the left column ($q_A/q_o=1/2$). 
+Let us first focus on the left column ($q_A/q_o=1/2$). 
 Fig.~\ref{fig:t2g-ge-wts}(a)
@@
 the $W_{xy}$ peaking in the middle state $\ket{E_2}$
-around before it transfers between $\ket{E_1}$ and $\ket{E_2}$
+before it is transferred between $\ket{E_1}$ and $\ket{E_2}$
 around $\beta\sim\alpha$,
@@
 Since $e_{g}$ has only two states,
-ignoring the coupling between $e_{g}$ and $t_{2g}$,
-we can always analytically diagonalise it.
+we can always analytically diagonalise it
+if we
+ignore its coupling to the $t_{2g}$ states.
 The expressions for the
@@
 \caption{
-Energies and character of $e_g$ states.
+Energies and characters of $e_g$ states.
 $E_{\pm}$ and $E_0^{e_g}$
-as a function of $\beta$ at $\alpha=10$, 
-and same parameters as in Fig.~\ref{fig:t2g-ge-Es}.
+as a function of $\beta$ at $\alpha=10^\circ$, 
+and the same parameters as in Fig.~\ref{fig:t2g-ge-Es}.
 At $q_A=q_o/2$ (a,c) where B cage dominates,
@@
 
-Diagonalising the Hamiltonian 
-(using the exact expressions instead 
-of the expansion in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx}),
+Diagonalising the Hamiltonian,
 we obtain two eigenstates $\ket{\pm}$
 at energies $E_{\pm}$.
+We present the results obtained using 
+ the exact expressions instead 
+of the expansions in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx}.
 Figure~\ref{fig:e-wts-eg}
@@
 $q_A/q_o=1/2,2$.
-We get the same ordering of orbitals with and without $z$ as in $t_{2g}$ case,
+We get the same ordering of orbitals ``with and without $z$''
+ as in $t_{2g}$ case,
 i.e.,
@@
 $\beta$ tends to lower
-$x^2-y^2$ while $\alpha$ tend to lower $z^2$ orbitals,
+$x^2-y^2$ while $\alpha$ tend to lower $z^2$ orbital,
 as indicated by the behaviour of $W_{x^2-y^2}$,
@@
  ($\ll \alpha=10^\circ$),
-while it approaches unity at 
+while it approaches unity
 at $\beta\gtrsim \alpha$.
@@
 Since $D_4$ is much smaller than $D_2$,
-we will still get find the same ordering as in $t_{2g}$ case.
+we will still get the same ordering as in $t_{2g}$ case.
 The splitting is much smaller in this case though, only $\sim 0.5\%$ of $\Delta_o$
@@
 can approximate the exact results,
-Fig.~\ref{fig:e-wts-eg} included
-them as Approx., which are almost indistinguishable from the exact results
+Fig.~\ref{fig:e-wts-eg} includes
+them as thin dotted lines that are collectively labelled Approx.,
+ which are almost indistinguishable from the exact results
 at $q_A/q_o=1/2$, but deviate at $q_A/q_o=2$ as their
@@
 
-In a crystal, obviously, not only the nearest coordination cage of A,B ions but also
+In a crystal, obviously, not only the nearest coordination cages of A,B ions but also
  the other ions (including O) at longer distances
-  participate in the effect considered in this paper.
+all have finite contributions to the crystal field and hence the JT effect.
 To see how much our results change when 
@@
 has O ions
-(at distances $\sqrt{5}a/2$ at $\alpha,\beta=0$) %and $\sqrt{5/2}a$ at $\alpha,\beta=0$),....
+($24$ of them at a distance of $\sqrt{5}a/2$ at $\alpha,\beta=0$) %and $\sqrt{5/2}a$ at $\alpha,\beta=0$),....
 %\az{both of which supports the A cage potential.??? plot and see... }
@@
 The effect of the potential of full ionic lattice.
-$t_{2g}$ spectrum computed using the potential of full lattice compared with that obtained from only A,B cages (and the anion octahedron itself),
+$t_{2g}$ spectrum computed using the potential of full lattice 
+and that obtained from only nearest AB cages (and the anion octahedron itself)
+are
 shown as a function of $q_A/q_o$ at 
 $\alpha=0,\beta=20^\circ$, $\Delta_o=4q_o/15a$.
-Full lattice only shifts the balance between the two cation cages towards A but keeps the qualitative picture the same.
+Full lattice only shifts the balance between the two cation cages towards A 
+(i.e, the crossing point, where the two cages balance each other, moves to smaller $q_A$)
+but keeps the qualitative picture the same.
 }
@@
 % orbital ordering
-We have only focused on the spectrum of the B ion at 
+We have only focused on the spectrum of 
+the B ion at 
 %position ${(0,0,0)}$
-origin
+$\textbf{a}/2$
  in the cell 
@@
 tetragonal Jahn-Teller distortions (elongation and compression) 
-such as seen in KCuF$_3$, 
+such as seen in KCuF$_3$~\cite{LiechtensteinPRB95}, 
 where the orbital ordering does not depend on the size of the distortion.
@@
 \appendix*
-\section{Computing $V_{l,m}^{A/B}$}
+\section{Computing $V_{lm}$}
 \label{append:multipoles}
 
-Here we describe the procedure to obtain the multipole components 
-$V_{l,m}$ of a potentials $V(\vec r)$ %of $A/B$ ion cages 
+Here we describe a procedure to obtain the multipole components 
+$V_{lm}$ of a potentials $V(\vec r)$ %of $A/B$ ion cages 
 at a position $\vec r$ around a JT ion.
+It is worth noting that this can be done without 
+evaluating the 
+inner products between the spherical harmonics and
+$V(\vec r)$.
+
 Let's consider $V^{A}(\vec r)$ to illustrate the idea. 
-$V^{B}(\vec r)$ and $V^{JT}(\vec r)$ can also be dealt the same way.
-
+$V^{B}(\vec r)$ and $V^{JT}(\vec r)$ can also be dealt in the same way.
 We like to expand the potentials $V^{A}(\vec r)$
@@
 where we have assumed $a$ as a length scale and 
-taken out the factor $\frac{q_A}{a}$ for clarity.
-It is worth noting that $V_{l,m}^{A}$ can be found without 
-evaluating the 
-inner products between the spherical harmonics and
-$V^{A}(\vec r)=V^{A}(\vec r;\alpha,\beta)$, as follows.
+taken out the factor $q_A/a$ for clarity.
 
@@
 that give degree $l$ components.
-We can now consider each degree $l$ term individually,
+We can then consider each degree $l$ term individually,
 and resolve it in its $(2l+1)$ $m$-components.
@@
 This gives a set of
-linear equations in $\{V_{l,m}^{A}\}$ (for a fixed value of $l$)
+linear equations in $\{V_{lm}^{A}\}$ (for a fixed value of $l$)
  that can be easily solved.

### 2023-09-28 manuscript/paper.tex
minor typos

@@
  there would be other local effects like
-electronic correlations (Hubbard and Hund's interaction), 
+electronic correlations (Hubbard and Hund's interaction)
 and spin-orbit interaction, 

### 2023-10-12 src/estatic.f90
before-K-ashif-Shb-minor-changes

@@ -101,6 +101,7 @@ end do
 !	qmpol(1,noct*4+io) = -2.0d0
 !end do
 
+
 allocate(hard(0:nsptm))
 hard = hardU ! hardU [modmain] read from the input file [readinput]
 
@@ -120,6 +121,9 @@ do is=1,nsptm
 q0(1:nsptm) = nds  !+ 2.0d0; ! +2 for TM s electrons;
                             ! for qmpol, q0 is assumed shperical symmetric, so consistent with s orbit.
 end do
+
+write(*,'(a,100f10.3)') 'estatic: qmpol(1,:) = ',qmpol(1,:)
+write(*,'(a,100f10.3)') 'estatic: q0(0:nsptm) = ',q0(0:nsptm)
 
 
 ! ion cages: octahedra and cubes

### 2023-10-12 src/fermi.f

@@ -112,7 +112,9 @@ C If the Fermi level was found.....................
 	    ebands = ebands + wke(ik,ie)*e(ik,ie)
 	   end do
 	  end do
-	  
+
+		write(6,*) 'test: Fermid: qtot,sumq=',qtot,sumq
+  
 	  return
 	 endif
 

### 2023-10-12 src/hamiltonian.f

@@ -542,11 +542,6 @@
 	endif
 
 
-
-
-
-
-
 	!............................................	 
 	endif ! iscf .le. 1 .and. ... 
 
@@ -651,6 +646,7 @@
 	return
 	end 	subroutine getHtmsUJ
 !----------------------------------------------------------------
+
 
 
 	end module hamiltonian

### 2023-10-12 src/hubbard.f90

@@ -145,6 +145,8 @@ do il=1,nlayers
 		call rtozflm(dm(:,jspin,:,ispin),dmc(:,jspin,:,ispin))
 	 end do
 	end do
+	! save dmc
+	tm(il,io)%dmc = dmc
 	!...............................................................
 	! vmat in complex spherical harmonics using dm and vee
 	! FLL double counting correction, also calc mag

### 2023-10-12 src/main.f

@@ -206,6 +206,8 @@
 	 endif
 
 
+	write(*,*)'main: groundstate has been calculated.... '
+
 	if(1==0) then
 	 open(10,file='LayerQ0.OUT',form='FORMATTED',action='write', 
      .                              position='append')
@@ -327,8 +329,9 @@
 	end if
 
 	
-	!if(lpdos) call getpdos(efermi) ! mine, maxe, nwplot
+	if(lpdos) call getpdos(efermi) ! mine, maxe, nwplot
 
+	
 	if(lbands) then
 	 call getbands()
 	 call writebands()
@@ -835,7 +838,16 @@
 	phis = (/+1,-1,+1,-1/) * phi;
 	do i=1,4
 	 call getRlmax(ths(i), phis(i), Rlmax(:,:,i))
+
+	! set Rl2, Rl2T:
+	! up spin block
+	Rl2(1:5,1:5,i) = Rlmax(5:9,5:9,i)
+	! down spin block
+	Rl2(6:10,6:10,i) = Rl2(1:5,1:5,i)
+	Rl2T(:,:,i) = transpose(Rl2(:,:,i)) ! Rlmax is real
+
 	end do
+
 
 	! unit cell rescales with the tilt/rotation:
 	

### 2023-10-12 src/modmain.f

@@ -42,6 +42,8 @@
 	! Del112 for Oxygen & Del222, Del224 for TM
 	double precision :: Del112, Del222, Del224
 
+	double precision, dimension(10,10,4) :: Rl2,Rl2T
+	
 	logical :: ham4edrixs
 	!double precision, dimension(5:9,5:9,3) :: B1hams
 	
@@ -186,6 +188,9 @@
 	 double precision, dimension(3):: beff ! effective, sum of all types of bfields
 	 double precision, dimension(3):: bext	! external magnetic field at TM site
 	 double complex, dimension(10,10):: ham ! local ham of TM atoms	 
+	 double complex, dimension(10,10):: UT ! local ham of TM atoms, Cong transposed 
+	 double complex, dimension(5,2,5,2):: dmc ! dm of TM atoms in complex Ylm
+	 
 	end type tmatoms
 
 	type(tmatoms), allocatable, dimension(:,:) :: tm ! TM

### 2023-10-12 src/pdos.f90

@@ -16,15 +16,15 @@ implicit none
 !double precision, intent(in) :: mine, maxe
 real(8), intent(in) :: ef
 real(4), allocatable :: bc(:,:,:,:,:)
-real(4), allocatable :: bcj(:,:,:,:)
+real(4), allocatable :: bcj(:,:,:,:),bcl(:,:,:,:)
 
 real(8), allocatable :: w(:), es(:,:), dos(:)
-real(8), allocatable :: gc(:,:,:), gcj(:,:)
+real(8), allocatable :: gc(:,:,:), gcj(:,:),gcl(:,:)
 
 integer :: natomtm, iw, itm
 double precision :: nbymaxe, dw
 integer :: ik, ist, il, io, ia,i1,i4
-double complex, dimension(10) :: wf
+double complex, dimension(10) :: wf,wf2
 
 natomtm = natoms/4;
 
@@ -33,8 +33,10 @@ allocate(w(nwplot))
 allocate(dos(nwplot))
 allocate(gc(nwplot,norbtm,nspin))
 allocate(gcj(nwplot,norbtm*nspin))
+allocate(gcl(nwplot,norbtm*nspin))
 allocate(bc(norbtm,nspin,natomtm,ntot,ntotk))
 allocate(bcj(norbtm*nspin,natomtm,ntot,ntotk))
+allocate(bcl(norbtm*nspin,natomtm,ntot,ntotk))
 
 ! to get index easily of a state in the energy bins array
 !mine = minval(eval);
@@ -82,13 +84,19 @@ if(lpdos) then
    do ik=1,ntotk
     wf = evec(ik,i1:i4,ist)
     ! band character in real Ylm,spin basis (our basis)
-	  bc(:,1,itm,ist,ik) = abs(wf(1:5))**2  ! up
-	  bc(:,2,itm,ist,ik) = abs(wf(6:10))**2 ! down
+	  bc(:,1,itm,ist,ik) = zabs(wf(1:5))**2  ! up
+	  bc(:,2,itm,ist,ik) = zabs(wf(6:10))**2 ! down
     ! change the basis to J,Jz
-	  wf = matmul(Ulm2j,wf) 
-	  bcj(:,itm,ist,ik) = abs(wf)**2; ! in J,Jz basis 
+	  wf2 = matmul(Ulm2j,wf) 
+	  bcj(:,itm,ist,ik) = zabs(wf2)**2; ! in J,Jz basis 
[…]

### 2023-10-12 src/readinput.f

@@ -177,7 +177,10 @@
 	   soc(1) = soc(1)*eV2Har
 	   Dcf(5,2) = Del222
 	   nds(1) = (6-qa) + ion_d
-	   write(*,*)'WARNING: not resetting qtot using given qa, ion_d'
+	   qtot = 4*nds(1) + 4*qA + nlayers*2*3*4
+	   write(*,*)'WARNING: RunBeastParam works only at nsptm=1'
+	   write(*,*)'WARNING: modify it for superlattices '
+	   
 	  ! set Hub%Fk and allocate Hub%Vee
 	  call 	setFk(1, eV2Har) !Hub(1)%U,Hub(1)%J,
 

### 2023-10-12 src/scf.f90

@@ -94,7 +94,7 @@ end subroutine tmgroundstate
 	 i = (il-1)*2 + io
 	 R = Rlmax(5:9,5:9,i) ! Rlmax is rotation matrix for Ylm of TM atom i
 	 RT = transpose(R);
-	  ! transform to rotated frame of the octagedron 1 
+	  ! transform to rotated frame of the octagedron i 
 	  ! R^T.h.R
 	  h = matmul(RT,h)
 	  h = matmul(h,R) ! 
@@ -437,7 +437,8 @@ integer :: iscf, ik
 double precision, dimension(3) :: kvec
 double precision :: ddmold, ddm, engyadu, ebands, engyes, energyb
 integer :: il,io,i
-
+double precision, dimension(10) :: evall
+integer:: jspn, ispn
 ! some large number
 ddmold = 1.0d8;
 
@@ -603,6 +604,75 @@ write(6,'("Ebs, Euj, Eq, Eb = ", 4e20.6)') ebands, engyadu, engyes, energyb
 write(6,'("Etot = ", 1e20.6)') ebands + engyadu + engyes + energyb
 
 end do! iscf
+
+
+
+!-----------------------------------------------------------------
+! calc local ham and its eigenvectors for pdoc abd band characters
+ call getHtmsUJ(10) ! iscf>1 will include tm%vmat
+ 
+ open(115,file='localeig.dat', action='write',position='append')
+ do il=1,nlayers
+  do io=1, noctl
+   call zdiag(10,tm(il,io)%ham,evall,0,10)
+   tm(il,io)%UT = transpose(dconjg(tm(il,io)%ham))
+
+   ! write only 5 eval, up spin 
+   write(115,'(a,10f15.10)') 'Eigenvalues, spin up: ',evall(1:10:2)
+   ! in bases aligned with lattice/global axes
+   ! write(115,'(20f15.10)') tm(il,io)%ham
+
+   ! assuming spin degen, separate diff spin comp
+   call spinseparate(tm(il,io)%ham)
+   ! local eigenvectors in local rotated bases 
+   i = (il-1)*2 + io;
+
+   !write(115,'(a)')'------ global axes bases ---------'
+   !write(115,'(5f15.10)') dble(tm(il,io)%ham(1:5,1:5))
+
[…]

### 2023-10-12 manuscript/paper.tex
before-K-ashif-Shb-minor-changes
KS sabeeh typos etc. + Eq., Sec. styles updated.

@@
 the total crystal field 
-does deform indeed
+does deform %indeed
 because
@@
 and elements of crystal field theory~\cite{BetheAP29,VanVleckPR32,PavariniChap},
-here in this manuscript,
+%here in this manuscript,
 we 
@@
 presents the formalism and 
-sec.~\ref{sec:JT} reviews the Jahn-Teller effect to
+Sec.~\ref{sec:JT} reviews the Jahn-Teller effect to
 introduce the notation and concepts involved
@@
 The model and calculations are presented
-in sec.~\ref{sec:calc},
+in Sec.~\ref{sec:calc},
 where
@@
 and crystal field splitting between its $e_g$ and $t_{2g}$ manifolds
-(sec.~\ref{sec:relativeVoctABO}),
+(Sec.~\ref{sec:relativeVoctABO}),
 and then 
 describe the deformation effects of 
-rigid octahedral rotations %(sec.~\ref{sec:rotation})
+rigid octahedral rotations %(Sec.~\ref{sec:rotation})
 on
-the structure (sec.~\ref{sec:structure}) 
-and crystal field (sec.~\ref{sec:deformCF}).
-The results are in sec.~\ref{sec:results},
+the structure (Sec.~\ref{sec:structure}) 
+and crystal field (Sec.~\ref{sec:deformCF}).
+The results are in Sec.~\ref{sec:results},
 where we %seperately
 present the splitting in the single particle spectrum
-belonging to the $t_{2g}$ (sec.~\ref{sec:t2g})
-and $e_g$ (sec.~\ref{sec:eg-gen}) manifolds,
-and finally describe the effect of the full lattice (sec.~\ref{sec:FL}).
+belonging to the $t_{2g}$ (Sec.~\ref{sec:t2g})
+and $e_g$ (Sec.~\ref{sec:eg-gen}) manifolds,
+and finally describe the effect of the full lattice (Sec.~\ref{sec:FL}).
 %\az{appendix?}
@@
 an expansion of the potential at the atom's site 
-in the same bases simplify the analysis.
+in the same bases simplifies the analysis.
 This is because
@@
 \end{align}
-where $a$ sets the length scale
+where $a$ sets the length scale, $\hat r=\vec r/r$ is the direction of $\vec r$,
 and $V_{l,m}$ are multipole components of the potential
@@
 competes with this linear term and the optimum structure 
-is obtained at a finite distortion.
+is obtained at a finite distortion, as described below.
 
@@
 
-Let us consider elongation of an octahedron % in sec.~\ref{sec:egt2g} 
+Let us consider elongation of an octahedron % in Sec.~\ref{sec:egt2g} 
 along one of its O-B-O bonds. 
@@
  ideal 
-octahedral field in Eq.~\ref{eq:voct},
+octahedral field in \eref{eq:voct},
 there is an $l=2$ component induced due to the deformation,
@@
 or not will depend on the number of electrons occupying these levels,
-as illustrate below.
+as illustrated below.
 
@@
 %\az{just a brief description... cooperative JT and orbital order}
-To complete the revision of the JT instability,
+To complete the discussion of the JT instability,
 it is worth mentioning that
@@
 elongation of one octahedron is accompanied by a compression of adjacent octahedron,
-which minimises the changes in the unit cell volume and hence the elastic energy cost of the transformation.
+which minimizes the changes in the unit cell volume and hence the elastic energy cost of the transformation.
 Such alternate elongations and compressions also lead to 
@@
  is relatively small at any $q_A$ but
- still large enough to be ignored.
+ %still large enough to be ignored.
+ still too large to be ignored.
 It can be measured by $(\Delta-\Delta_o)/\Delta_o=f_{q_A}$,
@@
 $l=2$ field components
-that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below Eq.~\ref{eq:JTeg} in sec.~\ref{sec:JTtertagonal}).
-So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see sec.~\ref{sec:relativeVoctABO}).
+that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below \eref{eq:JTeg} in Sec.~\ref{sec:JTtertagonal}).
+So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see Sec.~\ref{sec:relativeVoctABO}).
 \end{enumerate}
@@
 that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below).
-So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see sec.~\ref{sec:relativeVoctABO}).
+So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see Sec.~\ref{sec:relativeVoctABO}).
 \end{enumerate}
@@
 The multipole components of $V_O(\vec r)$ in the rotated frame do not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
-These can be directly read off Eq.~\ref{eq:voct}.
+These can be directly read off \eref{eq:voct}.
 Similarly, it is easier to obtain the components of $V_{AB}(\vec r)$
@@
 $\tilde V_{lm}^O$ are simply octahedral field components 
-with $l=4,m=0,4$ (see Eq.~\ref{eq:voct}).
+with $l=4,m=0,4$ (see \eref{eq:voct}).
 However, $V_{lm}^{AB}$ contain the effect of the deformation of the crystal structure 
@@
 We find that the splittings due to octahedral rotation and tilting are practically the same for all B ions
-(but their eigenstates differ considerably, which creates interesting orbital ordering as discussed later in the discussion in sec.~\ref{sec:discussion}),
+(but their eigenstates differ considerably, which creates interesting orbital ordering as discussed later in the discussion in Sec.~\ref{sec:discussion}),
 so we consider the octahedron $1$ with central B ion at $\textbf{a}/2$
@@
 and how it relates to the standard JT problem.
-As describe in sec.~\ref{sec:JT},
+As describe in Sec.~\ref{sec:JT},
 the optimum structure can have a finite distortion
@@
  that would determine the sign and size of the term
-  in the square bracket in Eq.~\ref{eq:theta0-Es} 
+  in the square bracket in \eref{eq:theta0-Es} 
 %  (hence the ground state and splitting) 
@@
 Since it's negative (see Eqs.~\ref{eq:theta0-delB2},\ref{eq:theta0-delB4}),
-it reverses the order in Eq.~\ref{eq:theta0-Es}
+it reverses the order in \eref{eq:theta0-Es}
 and $E_{xy}$ becomes lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $\beta=15^\circ$.
@@
 \begin{gather}
-E_{\pm} = \frac{E_{xy}+E_{yz}-\lambda}{2}  \pm \sqrt{(E_{xy}-E_{yz}+\lambda)^2 + 8g^2 }.
+E_{\pm} = \frac{E_{xy}+E_{yz}-\lambda}{2}  \pm \frac{1}{2}\sqrt{(E_{xy}-E_{yz}+\lambda)^2 + 8g^2 }.
 %\delta = E_{xy}-e_z+\lambda.
@@
 This is also evident from the signs of the $\Omega_l$
-in Eq.~\ref{eq:eg-hiix}.
+in \eref{eq:eg-hiix}.
 We see that $l=2$ terms have the same signs as $t_{2g}$ case but 
@@
  in the cell 
-described in sec.~\ref{sec:structure}
+described in Sec.~\ref{sec:structure}
 but 
@@
 
-Here we describe a procedure to obtain the multipole components 
+Here we describe a method to obtain the multipole components 
 $V_{lm}$ of a potentials $V(\vec r)$ %of $A/B$ ion cages 
@@
 the formal expression on the right side 
-of Eq.~\ref{eq:ylm_compA}.
+of \eref{eq:ylm_compA}.
 This gives a set of
@@
  that can be easily solved.
-The whole procedure can be performed
+The whole calculation can be performed
  on Mathematica~\cite{Mathematica}

### 2023-12-11 manuscript/paper.tex
saving snapshot

@@
 %\documentclass[12pt]{report}
+
+%\usepackage{orcidlink}
 
@@
 \affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}
+\email{ahsan.zeb@hotmail.com}
+%\orcidlink{https://orcid.org/0000-0002-3448-2357}
 
@@
 \label{Bibliography}
-%\bibliographystyle{apsrev4-1}
-\bibliography{perovskites}
+\bibliographystyle{apsrev4-1}
+%\bibliography{perovskites}
+
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (8) initials jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (-1) disabled
+%Control: page (0) single
+%Control: year (1) truncated
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{83}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Zubko}\ \emph {et~al.}(2011)\citenamefont {Zubko},
+  \citenamefont {Gariglio}, \citenamefont {Gabay}, \citenamefont {Ghosez},\
+  and\ \citenamefont {Triscone}}]{ZubkoARCMP11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Zubko}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Gariglio}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Gabay}}, \bibinfo
+  {author} {\bibfnamefont {P.}~\bibnamefont {Ghosez}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.-M.}\ \bibnamefont {Triscone}},\ }\href {\doibase
+  10.1146/annurev-conmatphys-062910-140445} {\bibfield  {journal} {\bibinfo
+  {journal} {Annual Review of Condensed Matter Physics}\ }\textbf {\bibinfo
+  {volume} {2}},\ \bibinfo {pages} {141} (\bibinfo {year} {2011})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Hwang}\ \emph {et~al.}(2012)\citenamefont {Hwang},
+  \citenamefont {Iwasa}, \citenamefont {Kawasaki}, \citenamefont {Keimer},
+  \citenamefont {Nagaosa},\ and\ \citenamefont {Tokura}}]{HwangNM12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~Y.}\ \bibnamefont
+  {Hwang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Iwasa}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kawasaki}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Keimer}}, \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Nagaosa}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Tokura}},\ }\href {\doibase
+  10.1038/nmat3223} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Materials}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {103}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bhattacharya}\ and\ \citenamefont
+  {May}(2014)}]{BhattacharyaARMR14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Bhattacharya}}\ and\ \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
+  {May}},\ }\href {\doibase 10.1146/annurev-matsci-070813-113447} {\bibfield
+  {journal} {\bibinfo  {journal} {Annual Review of Materials Research}\
+  }\textbf {\bibinfo {volume} {44}},\ \bibinfo {pages} {65} (\bibinfo {year}
+  {2014})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1146/annurev-matsci-070813-113447}
+  {https://doi.org/10.1146/annurev-matsci-070813-113447} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hellman}\ \emph {et~al.}(2017)\citenamefont
+  {Hellman}, \citenamefont {Hoffmann}, \citenamefont {Tserkovnyak},
+  \citenamefont {Beach}, \citenamefont {Fullerton}, \citenamefont {Leighton},
+  \citenamefont {MacDonald}, \citenamefont {Ralph}, \citenamefont {Arena},
+  \citenamefont {D\"urr}, \citenamefont {Fischer}, \citenamefont {Grollier},
+  \citenamefont {Heremans}, \citenamefont {Jungwirth}, \citenamefont {Kimel},
+  \citenamefont {Koopmans}, \citenamefont {Krivorotov}, \citenamefont {May},
+  \citenamefont {Petford-Long}, \citenamefont {Rondinelli}, \citenamefont
+  {Samarth}, \citenamefont {Schuller}, \citenamefont {Slavin}, \citenamefont
+  {Stiles}, \citenamefont {Tchernyshyov}, \citenamefont {Thiaville},\ and\
+  \citenamefont {Zink}}]{HellmanRMP17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Hellman}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Hoffmann}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Tserkovnyak}}, \bibinfo
+  {author} {\bibfnamefont {G.~S.~D.}\ \bibnamefont {Beach}}, \bibinfo {author}
+  {\bibfnamefont {E.~E.}\ \bibnamefont {Fullerton}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Leighton}}, \bibinfo {author}
+  {\bibfnamefont {A.~H.}\ \bibnamefont {MacDonald}}, \bibinfo {author}
+  {\bibfnamefont {D.~C.}\ \bibnamefont {Ralph}}, \bibinfo {author}
+  {\bibfnamefont {D.~A.}\ \bibnamefont {Arena}}, \bibinfo {author}
+  {\bibfnamefont {H.~A.}\ \bibnamefont {D\"urr}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Fischer}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Grollier}}, \bibinfo {author} {\bibfnamefont {J.~P.}\
+  \bibnamefont {Heremans}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Jungwirth}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
+  {Kimel}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Koopmans}},
+  \bibinfo {author} {\bibfnamefont {I.~N.}\ \bibnamefont {Krivorotov}},
+  \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {May}}, \bibinfo
+  {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Petford-Long}}, \bibinfo
+  {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Rondinelli}}, \bibinfo
+  {author} {\bibfnamefont {N.}~\bibnamefont {Samarth}}, \bibinfo {author}
+  {\bibfnamefont {I.~K.}\ \bibnamefont {Schuller}}, \bibinfo {author}
+  {\bibfnamefont {A.~N.}\ \bibnamefont {Slavin}}, \bibinfo {author}
+  {\bibfnamefont {M.~D.}\ \bibnamefont {Stiles}}, \bibinfo {author}
+  {\bibfnamefont {O.}~\bibnamefont {Tchernyshyov}}, \bibinfo {author}
+  {\bibfnamefont {A.}~\bibnamefont {Thiaville}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {B.~L.}\ \bibnamefont {Zink}},\ }\href {\doibase
+  10.1103/RevModPhys.89.025006} {\bibfield  {journal} {\bibinfo  {journal}
+  {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages}
+  {025006} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ and\ \citenamefont
+  {Millis}(2017)}]{ChenJPCM17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Chen}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Millis}},\
+  }\href {\doibase 10.1088/1361-648X/aa6efe} {\bibfield  {journal} {\bibinfo
+  {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo {volume}
+  {29}},\ \bibinfo {pages} {243001} (\bibinfo {year} {2017})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dagotto}(2005)}]{DagottoS05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Dagotto}},\ }\href {\doibase 10.1126/science.1107559} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {309}},\ \bibinfo
+  {pages} {257} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dagotto}\ and\ \citenamefont
+  {Tokura}(2008)}]{DagottoMRSB08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Dagotto}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Tokura}},\ }\href {\doibase 10.1557/mrs2008.223} {\bibfield  {journal}
+  {\bibinfo  {journal} {MRS Bulletin}\ }\textbf {\bibinfo {volume} {33}},\
+  \bibinfo {pages} {1037} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Salamon}\ and\ \citenamefont
+  {Jaime}(2001)}]{SalamonRMP01}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
+  {Salamon}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Jaime}},\ }\href {\doibase 10.1103/RevModPhys.73.583} {\bibfield  {journal}
+  {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\
+  \bibinfo {pages} {583} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2003)\citenamefont {Wang},
+  \citenamefont {Neaton}, \citenamefont {Zheng}, \citenamefont {Nagarajan},
+  \citenamefont {Ogale}, \citenamefont {Liu}, \citenamefont {Viehland},
+  \citenamefont {Vaithyanathan}, \citenamefont {Schlom}, \citenamefont
+  {Waghmare}, \citenamefont {Spaldin}, \citenamefont {Rabe}, \citenamefont
+  {Wuttig},\ and\ \citenamefont {Ramesh}}]{WangS03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {Neaton}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zheng}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Nagarajan}}, \bibinfo {author}
+  {\bibfnamefont {S.~B.}\ \bibnamefont {Ogale}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Viehland}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Vaithyanathan}}, \bibinfo {author} {\bibfnamefont {D.~G.}\
+  \bibnamefont {Schlom}}, \bibinfo {author} {\bibfnamefont {U.~V.}\
+  \bibnamefont {Waghmare}}, \bibinfo {author} {\bibfnamefont {N.~A.}\
+  \bibnamefont {Spaldin}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
+  \bibnamefont {Rabe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Wuttig}}, \ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Ramesh}},\ }\href {\doibase 10.1126/science.1080615} {\bibfield  {journal}
+  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {299}},\ \bibinfo
+  {pages} {1719} (\bibinfo {year} {2003})},\ \Eprint
+  {http://arxiv.org/abs/https://www.science.org/doi/pdf/10.1126/science.1080615}
+  {https://www.science.org/doi/pdf/10.1126/science.1080615} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dawber}\ \emph {et~al.}(2005)\citenamefont {Dawber},
+  \citenamefont {Rabe},\ and\ \citenamefont {Scott}}]{DawberRMP05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Dawber}}, \bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Rabe}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Scott}},\ }\href
+  {\doibase 10.1103/RevModPhys.77.1083} {\bibfield  {journal} {\bibinfo
+  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
+  {pages} {1083} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schlom}\ \emph {et~al.}(2007)\citenamefont {Schlom},
+  \citenamefont {Chen}, \citenamefont {Eom}, \citenamefont {Rabe},
+  \citenamefont {Streiffer},\ and\ \citenamefont {Triscone}}]{SchlomARMR07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~G.}\ \bibnamefont
+  {Schlom}}, \bibinfo {author} {\bibfnamefont {L.-Q.}\ \bibnamefont {Chen}},
+  \bibinfo {author} {\bibfnamefont {C.-B.}\ \bibnamefont {Eom}}, \bibinfo
+  {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Rabe}}, \bibinfo {author}
+  {\bibfnamefont {S.~K.}\ \bibnamefont {Streiffer}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.-M.}\ \bibnamefont {Triscone}},\ }\href {\doibase
+  10.1146/annurev.matsci.37.061206.113016} {\bibfield  {journal} {\bibinfo
+  {journal} {Annual Review of Materials Research}\ }\textbf {\bibinfo {volume}
+  {37}},\ \bibinfo {pages} {589} (\bibinfo {year} {2007})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Koster}\ \emph {et~al.}(2012)\citenamefont {Koster},
+  \citenamefont {Klein}, \citenamefont {Siemons}, \citenamefont {Rijnders},
+  \citenamefont {Dodge}, \citenamefont {Eom}, \citenamefont {Blank},\ and\
+  \citenamefont {Beasley}}]{KosterRMP12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Koster}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Klein}},
+  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Siemons}}, \bibinfo
+  {author} {\bibfnamefont {G.}~\bibnamefont {Rijnders}}, \bibinfo {author}
+  {\bibfnamefont {J.~S.}\ \bibnamefont {Dodge}}, \bibinfo {author}
+  {\bibfnamefont {C.-B.}\ \bibnamefont {Eom}}, \bibinfo {author} {\bibfnamefont
+  {D.~H.~A.}\ \bibnamefont {Blank}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {M.~R.}\ \bibnamefont {Beasley}},\ }\href {\doibase
+  10.1103/RevModPhys.84.253} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {253}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bersuker}(1975)}]{BersukerCCR75}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Bersuker}},\ }\href {\doibase https://doi.org/10.1016/S0010-8545(00)80266-0}
+  {\bibfield  {journal} {\bibinfo  {journal} {Coordination Chemistry Reviews}\
+  }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {357} (\bibinfo {year}
+  {1975})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kugel}\ and\ \citenamefont {Khomski{\u
+  i}}(1982)}]{KugelSPU82}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~I.}\ \bibnamefont
+  {Kugel}}\ and\ \bibinfo {author} {\bibfnamefont {D.~I.}\ \bibnamefont
+  {Khomski{\u i}}},\ }\href {\doibase 10.1070/PU1982v025n04ABEH004537}
+  {\bibfield  {journal} {\bibinfo  {journal} {Soviet Physics Uspekhi}\ }\textbf
+  {\bibinfo {volume} {25}},\ \bibinfo {pages} {231} (\bibinfo {year}
+  {1982})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Millis}(1998)}]{MillisN98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+  {Millis}},\ }\href {\doibase 10.1038/32348} {\bibfield  {journal} {\bibinfo
+  {journal} {Nature}\ }\textbf {\bibinfo {volume} {392}},\ \bibinfo {pages}
+  {147} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Terakura}(2007)}]{TerakuraPMS07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Terakura}},\ }\href {\doibase https://doi.org/10.1016/j.pmatsci.2006.10.007}
+  {\bibfield  {journal} {\bibinfo  {journal} {Progress in Materials Science}\
+  }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {388} (\bibinfo {year}
+  {2007})},\ \bibinfo {note} {modelling electrons and atoms for materials
+  science}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Halcrow}(2013)}]{HalcrowRSC13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Halcrow}},\ }\href {\doibase 10.1039/C2CS35253B} {\bibfield  {journal}
+  {\bibinfo  {journal} {Chemical Society Reviews}\ }\textbf {\bibinfo {volume}
+  {42}},\ \bibinfo {pages} {1784} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Lufaso}\ and\ \citenamefont
+  {Woodward}(2004)}]{LufasoAC04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
+  {Lufaso}}\ and\ \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Woodward}},\ }\href {\doibase 10.1107/S0108768103026661} {\bibfield
+  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
+  {\bibinfo {volume} {60}},\ \bibinfo {pages} {10} (\bibinfo {year}
+  {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Glazer}(1972)}]{GlazerAC72}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Glazer}},\ }\href {\doibase 10.1107/S0567740872007976} {\bibfield  {journal}
+  {\bibinfo  {journal} {Acta Crystallogr., Sect. B: Struct. Crystallogr. Cryst.
+  Chem.}\ }\textbf {\bibinfo {volume} {28}},\ \bibinfo {pages} {3384} (\bibinfo
+  {year} {1972})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Thomas}(1996)}]{ThomasAC96}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~W.}\ \bibnamefont
+  {Thomas}},\ }\href {\doibase 10.1107/S0108768195006100} {\bibfield  {journal}
+  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo
+  {volume} {52}},\ \bibinfo {pages} {16} (\bibinfo {year} {1996})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Woodward}(1997{\natexlab{a}})}]{WoodwardAC97a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Woodward}},\ }\href {\doibase 10.1107/S0108768196010713} {\bibfield
+  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
+  {\bibinfo {volume} {53}},\ \bibinfo {pages} {32} (\bibinfo {year}
+  {1997}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Woodward}(1997{\natexlab{b}})}]{WoodwardAC97b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Woodward}},\ }\href {\doibase 10.1107/S0108768196012050} {\bibfield
+  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
+  {\bibinfo {volume} {53}},\ \bibinfo {pages} {44} (\bibinfo {year}
+  {1997}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Howard}\ and\ \citenamefont
+  {Stokes}(1998)}]{HowardAC98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Howard}}\ and\ \bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
+  {Stokes}},\ }\href {\doibase 10.1107/S0108768198004200} {\bibfield  {journal}
+  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo
+  {volume} {54}},\ \bibinfo {pages} {782} (\bibinfo {year} {1998})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Stokes}\ \emph {et~al.}(2002)\citenamefont {Stokes},
+  \citenamefont {Kisi}, \citenamefont {Hatch},\ and\ \citenamefont
+  {Howard}}]{StokesAC02}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
+  {Stokes}}, \bibinfo {author} {\bibfnamefont {E.~H.}\ \bibnamefont {Kisi}},
+  \bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Hatch}}, \ and\
+  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Howard}},\ }\href
+  {\doibase 10.1107/S0108768102015756} {\bibfield  {journal} {\bibinfo
+  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo {volume}
+  {58}},\ \bibinfo {pages} {934} (\bibinfo {year} {2002})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Angel}\ \emph {et~al.}(2005)\citenamefont {Angel},
+  \citenamefont {Zhao},\ and\ \citenamefont {Ross}}]{AngelPRL05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+  {Angel}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}}, \ and\
+  \bibinfo {author} {\bibfnamefont {N.~L.}\ \bibnamefont {Ross}},\ }\href
+  {\doibase 10.1103/PhysRevLett.95.025503} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
+  {pages} {025503} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ghosez}\ and\ \citenamefont
+  {Triscone}(2011)}]{GhosezNM11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Ghosez}}\ and\ \bibinfo {author} {\bibfnamefont {J.-M.}\ \bibnamefont
+  {Triscone}},\ }\href {\doibase 10.1038/nmat3003} {\bibfield  {journal}
+  {\bibinfo  {journal} {Nature Materials}\ }\textbf {\bibinfo {volume} {10}},\
+  \bibinfo {pages} {269} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rondinelli}\ and\ \citenamefont
+  {Fennie}(2012)}]{RondinelliAM12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {Rondinelli}}\ and\ \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Fennie}},\ }\href {\doibase https://doi.org/10.1002/adma.201104674}
+  {\bibfield  {journal} {\bibinfo  {journal} {Advanced Materials}\ }\textbf
+  {\bibinfo {volume} {24}},\ \bibinfo {pages} {1961} (\bibinfo {year}
+  {2012})},\ \Eprint
+  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/adma.201104674}
+  {https://onlinelibrary.wiley.com/doi/pdf/10.1002/adma.201104674} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Schick}\ \emph {et~al.}(2014)\citenamefont {Schick},
+  \citenamefont {Jiang}, \citenamefont {Saldana-Greco},\ and\ \citenamefont
+  {Rappe}}]{SchickPRB14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
+  {Schick}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jiang}},
+  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Saldana-Greco}}, \ and\
+  \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont {Rappe}},\ }\href
+  {\doibase 10.1103/PhysRevB.89.195304} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo
+  {pages} {195304} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sim}\ and\ \citenamefont {Kim}(2014)}]{SimPRB14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Sim}}\ and\ \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Kim}},\
+  }\href {\doibase 10.1103/PhysRevB.89.144114} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo
+  {pages} {144114} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lee}\ \emph {et~al.}(2017)\citenamefont {Lee},
+  \citenamefont {Chang}, \citenamefont {Huang}, \citenamefont {Guo},
+  \citenamefont {Gao}, \citenamefont {Chen}, \citenamefont {Cheong},\ and\
+  \citenamefont {Chu}}]{LeePRL17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont
+  {Lee}}, \bibinfo {author} {\bibfnamefont {C.-P.}\ \bibnamefont {Chang}},
+  \bibinfo {author} {\bibfnamefont {F.-T.}\ \bibnamefont {Huang}}, \bibinfo
+  {author} {\bibfnamefont {G.~Y.}\ \bibnamefont {Guo}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Gao}}, \bibinfo {author} {\bibfnamefont
+  {C.~H.}\ \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {S.-W.}\
+  \bibnamefont {Cheong}}, \ and\ \bibinfo {author} {\bibfnamefont {M.-W.}\
+  \bibnamefont {Chu}},\ }\href {\doibase 10.1103/PhysRevLett.119.157601}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {119}},\ \bibinfo {pages} {157601} (\bibinfo {year}
+  {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2022)\citenamefont {Wang},
+  \citenamefont {Tang}, \citenamefont {Stengel}, \citenamefont {Xiang},
+  \citenamefont {An}, \citenamefont {Low},\ and\ \citenamefont
+  {Wu}}]{WangPRL22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Tang}}, \bibinfo
+  {author} {\bibfnamefont {M.}~\bibnamefont {Stengel}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont
+  {Q.}~\bibnamefont {An}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Low}}, \ and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Wu}},\
+  }\href {\doibase 10.1103/PhysRevLett.128.197601} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {128}},\
+  \bibinfo {pages} {197601} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2022)\citenamefont {Zhou},
+  \citenamefont {Dong}, \citenamefont {Shan}, \citenamefont {Ji},\ and\
+  \citenamefont {Zhang}}]{ZhouPRB22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhou}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Dong}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Shan}}, \bibinfo {author}
+  {\bibfnamefont {K.}~\bibnamefont {Ji}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {J.}~\bibnamefont {Zhang}},\ }\href {\doibase
+  10.1103/PhysRevB.105.075408} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {105}},\ \bibinfo {pages}
+  {075408} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gao}\ \emph {et~al.}(2023)\citenamefont {Gao},
+  \citenamefont {Paillard},\ and\ \citenamefont {Bellaiche}}]{GaoPRB23}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Gao}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Paillard}}, \
+  and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\href
+  {\doibase 10.1103/PhysRevB.107.104109} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {107}},\ \bibinfo
+  {pages} {104109} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Khomskii}(2009)}]{KhomskiiPhys09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Khomskii}},\ }\href {\doibase 10.1103/Physics.2.20} {\bibfield  {journal}
+  {\bibinfo  {journal} {Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo
+  {pages} {20} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Benedek}\ and\ \citenamefont
+  {Fennie}(2011)}]{BenedekPRL11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
+  {Benedek}}\ and\ \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Fennie}},\ }\href {\doibase 10.1103/PhysRevLett.106.107204} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {106}},\ \bibinfo {pages} {107204} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2014)\citenamefont {Yang},
+  \citenamefont {\'I\~niguez}, \citenamefont {Mao},\ and\ \citenamefont
+  {Bellaiche}}]{YangPRL14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Yang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {\'I\~niguez}},
+  \bibinfo {author} {\bibfnamefont {A.-J.}\ \bibnamefont {Mao}}, \ and\
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\href
+  {\doibase 10.1103/PhysRevLett.112.057202} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo
+  {pages} {057202} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ye}\ \emph {et~al.}(2018)\citenamefont {Ye},
+  \citenamefont {Wang}, \citenamefont {Sheng}, \citenamefont {Hoffmann},
+  \citenamefont {Gu}, \citenamefont {Xiang}, \citenamefont {Tian},
+  \citenamefont {Molaison}, \citenamefont {dos Santos}, \citenamefont
+  {Matsuda}, \citenamefont {Chakoumakos}, \citenamefont {Fernandez-Baca},
+  \citenamefont {Tong}, \citenamefont {Gao}, \citenamefont {Kim},\ and\
+  \citenamefont {Cheong}}]{YePRB18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
+  {Ye}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wang}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Sheng}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Hoffmann}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Gu}}, \bibinfo {author} {\bibfnamefont
+  {H.~J.}\ \bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont
+  {W.}~\bibnamefont {Tian}}, \bibinfo {author} {\bibfnamefont {J.~J.}\
+  \bibnamefont {Molaison}}, \bibinfo {author} {\bibfnamefont {A.~M.}\
+  \bibnamefont {dos Santos}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Matsuda}}, \bibinfo {author} {\bibfnamefont {B.~C.}\
+  \bibnamefont {Chakoumakos}}, \bibinfo {author} {\bibfnamefont {J.~A.}\
+  \bibnamefont {Fernandez-Baca}}, \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Tong}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
+  {Gao}}, \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont {Kim}}, \ and\
+  \bibinfo {author} {\bibfnamefont {S.-W.}\ \bibnamefont {Cheong}},\ }\href
+  {\doibase 10.1103/PhysRevB.97.041112} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
+  {pages} {041112} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph
+  {et~al.}(2020{\natexlab{a}})\citenamefont {Zhang}, \citenamefont {Shen},
+  \citenamefont {Wang}, \citenamefont {Ji}, \citenamefont {Zhou}, \citenamefont
+  {Wang}, \citenamefont {Huang},\ and\ \citenamefont {Lu}}]{ZhangPRL20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Shen}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {C.}~\bibnamefont {Ji}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Huang}}, \ and\
+  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Lu}},\ }\href {\doibase
+  10.1103/PhysRevLett.125.017601} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\ \bibinfo {pages}
+  {017601} (\bibinfo {year} {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph
+  {et~al.}(2020{\natexlab{b}})\citenamefont {Zhang}, \citenamefont {Wang},\
+  and\ \citenamefont {Ghosez}}]{ZhangYajunPRL20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wang}}, \ and\
+  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Ghosez}},\ }\href
+  {\doibase 10.1103/PhysRevLett.125.157601} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\ \bibinfo
+  {pages} {157601} (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2021)\citenamefont {Zhou},
+  \citenamefont {Chen}, \citenamefont {Wu}, \citenamefont {Shen}, \citenamefont
+  {Wang}, \citenamefont {Zhang},\ and\ \citenamefont {Sun}}]{ZhouPRB21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Zhou}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Chen}}, \bibinfo
+  {author} {\bibfnamefont {Z.}~\bibnamefont {Wu}}, \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Zhang}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sun}},\
+  }\href {\doibase 10.1103/PhysRevB.103.224409} {\bibfield  {journal} {\bibinfo
+   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo
+  {pages} {224409} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2022)\citenamefont {Zhang},
+  \citenamefont {Zhou}, \citenamefont {Wang}, \citenamefont {Shen},
+  \citenamefont {Wang},\ and\ \citenamefont {Lu}}]{ZhangPRL22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Zhou}},
+  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Wang}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {X.}~\bibnamefont {Lu}},\ }\href {\doibase 10.1103/PhysRevLett.129.117603}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {129}},\ \bibinfo {pages} {117603} (\bibinfo {year}
+  {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Amat}\ \emph {et~al.}(2014)\citenamefont {Amat},
+  \citenamefont {Mosconi}, \citenamefont {Ronca}, \citenamefont {Quarti},
+  \citenamefont {Umari}, \citenamefont {Nazeeruddin}, \citenamefont {Gratzel},\
+  and\ \citenamefont {De~Angelis}}]{AmatNL14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Amat}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Mosconi}},
+  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Ronca}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Quarti}}, \bibinfo {author}
+  {\bibfnamefont {P.}~\bibnamefont {Umari}}, \bibinfo {author} {\bibfnamefont
+  {M.~K.}\ \bibnamefont {Nazeeruddin}}, \bibinfo {author} {\bibfnamefont
+  {M.}~\bibnamefont {Gratzel}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {F.}~\bibnamefont {De~Angelis}},\ }\href {\doibase 10.1021/nl5012992}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nano Letters}\ }\textbf {\bibinfo
+  {volume} {14}},\ \bibinfo {pages} {3608} (\bibinfo {year} {2014})},\ \bibinfo
+  {note} {pMID: 24797342},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/nl5012992}
+  {https://doi.org/10.1021/nl5012992} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Krach}\ \emph {et~al.}(2023)\citenamefont {Krach},
+  \citenamefont {Forero-Correa}, \citenamefont {Biega}, \citenamefont
+  {Reyes-Lillo},\ and\ \citenamefont {Leppert}}]{KrachJPCM23}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Krach}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Forero-Correa}}, \bibinfo {author} {\bibfnamefont {R.-I.}\ \bibnamefont
+  {Biega}}, \bibinfo {author} {\bibfnamefont {S.~E.}\ \bibnamefont
+  {Reyes-Lillo}}, \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Leppert}},\ }\href {\doibase 10.1088/1361-648X/acbd0c} {\bibfield  {journal}
+  {\bibinfo  {journal} {Journal of Physics: Condensed Matter}\ }\textbf
+  {\bibinfo {volume} {35}},\ \bibinfo {pages} {174001} (\bibinfo {year}
+  {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Balachandran}\ and\ \citenamefont
+  {Rondinelli}(2013)}]{BalachandranPRB13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~V.}\ \bibnamefont
+  {Balachandran}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {Rondinelli}},\ }\href {\doibase 10.1103/PhysRevB.88.054101} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {88}},\ \bibinfo {pages} {054101} (\bibinfo {year} {2013})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Aguado-Puente}\ \emph {et~al.}(2011)\citenamefont
+  {Aguado-Puente}, \citenamefont {Garc\'{\i}a-Fern\'andez},\ and\ \citenamefont
+  {Junquera}}]{Aguado-PuentePRL11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Aguado-Puente}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Garc\'{\i}a-Fern\'andez}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Junquera}},\ }\href {\doibase
+  10.1103/PhysRevLett.107.217601} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {107}},\ \bibinfo {pages}
+  {217601} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jia}\ \emph {et~al.}(2022)\citenamefont {Jia},
+  \citenamefont {He}, \citenamefont {Akhtar}, \citenamefont {Herranz},\ and\
+  \citenamefont {Pruneda}}]{JiaPRB22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Jia}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {He}}, \bibinfo
+  {author} {\bibfnamefont {A.}~\bibnamefont {Akhtar}}, \bibinfo {author}
+  {\bibfnamefont {G.}~\bibnamefont {Herranz}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {M.}~\bibnamefont {Pruneda}},\ }\href {\doibase
+  10.1103/PhysRevB.105.224112} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {105}},\ \bibinfo {pages}
+  {224112} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Xiang}\ \emph {et~al.}(2017)\citenamefont {Xiang},
+  \citenamefont {Guennou}, \citenamefont {\'I\~niguez}, \citenamefont
+  {Kreisel},\ and\ \citenamefont {Bellaiche}}]{XiangPRB17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont
+  {Xiang}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Guennou}},
+  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {\'I\~niguez}}, \bibinfo
+  {author} {\bibfnamefont {J.}~\bibnamefont {Kreisel}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\href {\doibase
+  10.1103/PhysRevB.96.054102} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {054102}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Johnson}\ \emph {et~al.}(2020)\citenamefont
+  {Johnson}, \citenamefont {Khalyavin}, \citenamefont {Manuel}, \citenamefont
+  {Zhang}, \citenamefont {Yamaura},\ and\ \citenamefont
+  {Belik}}]{JohnsonPRL20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont
+  {Johnson}}, \bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
+  {Khalyavin}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Manuel}},
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zhang}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Yamaura}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Belik}},\ }\href {\doibase
+  10.1103/PhysRevLett.125.097601} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\ \bibinfo {pages}
+  {097601} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ogawa}\ \emph {et~al.}(2012)\citenamefont {Ogawa},
+  \citenamefont {Ogimoto}, \citenamefont {Ida}, \citenamefont {Nomura},
+  \citenamefont {Arita},\ and\ \citenamefont {Miyano}}]{OgawaPRL12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Ogawa}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Ogimoto}},
+  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Ida}}, \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Nomura}}, \bibinfo {author} {\bibfnamefont
+  {R.}~\bibnamefont {Arita}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {K.}~\bibnamefont {Miyano}},\ }\href {\doibase
+  10.1103/PhysRevLett.108.157603} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {108}},\ \bibinfo {pages}
+  {157603} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2019)\citenamefont {Chen},
+  \citenamefont {Xu}, \citenamefont {Tian}, \citenamefont {Xiang},
+  \citenamefont {\'I\~niguez}, \citenamefont {Yang},\ and\ \citenamefont
+  {Bellaiche}}]{ChenPRL19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Chen}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Xu}}, \bibinfo
+  {author} {\bibfnamefont {H.}~\bibnamefont {Tian}}, \bibinfo {author}
+  {\bibfnamefont {H.}~\bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {\'I\~niguez}}, \bibinfo {author} {\bibfnamefont
+  {Y.}~\bibnamefont {Yang}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {L.}~\bibnamefont {Bellaiche}},\ }\href {\doibase
+  10.1103/PhysRevLett.122.247701} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages}
+  {247701} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2021)\citenamefont {Huang},
+  \citenamefont {Liu}, \citenamefont {Shao}, \citenamefont {Feng},
+  \citenamefont {Zhang}, \citenamefont {Fu}, \citenamefont {Lee}, \citenamefont
+  {Shen}, \citenamefont {Chuang},\ and\ \citenamefont {Liu}}]{HuangPRB21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Huang}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Liu}}, \bibinfo
+  {author} {\bibfnamefont {Y.-C.}\ \bibnamefont {Shao}}, \bibinfo {author}
+  {\bibfnamefont {X.}~\bibnamefont {Feng}}, \bibinfo {author} {\bibfnamefont
+  {N.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
+  {J.}~\bibnamefont {Fu}}, \bibinfo {author} {\bibfnamefont {J.-M.}\
+  \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Shen}}, \bibinfo {author} {\bibfnamefont {Y.-D.}\ \bibnamefont {Chuang}}, \
+  and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Liu}},\ }\href
+  {\doibase 10.1103/PhysRevB.104.075156} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {104}},\ \bibinfo
+  {pages} {075156} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abarca~Morales}\ \emph {et~al.}(2023)\citenamefont
+  {Abarca~Morales}, \citenamefont {Siemann}, \citenamefont {Zivanovic},
+  \citenamefont {Murgatroyd}, \citenamefont {Markovi\ifmmode~\acute{c}\else
+  \'{c}\fi{}}, \citenamefont {Edwards}, \citenamefont {Hooley}, \citenamefont
+  {Sokolov}, \citenamefont {Kikugawa}, \citenamefont {Cacho}, \citenamefont
+  {Watson}, \citenamefont {Kim}, \citenamefont {Hicks}, \citenamefont
+  {Mackenzie},\ and\ \citenamefont {King}}]{MoralesPRL23}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Abarca~Morales}}, \bibinfo {author} {\bibfnamefont {G.-R.}\ \bibnamefont
+  {Siemann}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zivanovic}},
+  \bibinfo {author} {\bibfnamefont {P.~A.~E.}\ \bibnamefont {Murgatroyd}},
+  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Markovi\ifmmode~\acute{c}\else \'{c}\fi{}}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Edwards}}, \bibinfo {author} {\bibfnamefont
+  {C.~A.}\ \bibnamefont {Hooley}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
+  \bibnamefont {Sokolov}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Kikugawa}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Cacho}},
+  \bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Watson}}, \bibinfo
+  {author} {\bibfnamefont {T.~K.}\ \bibnamefont {Kim}}, \bibinfo {author}
+  {\bibfnamefont {C.~W.}\ \bibnamefont {Hicks}}, \bibinfo {author}
+  {\bibfnamefont {A.~P.}\ \bibnamefont {Mackenzie}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {P.~D.~C.}\ \bibnamefont {King}},\ }\href {\doibase
+  10.1103/PhysRevLett.130.096401} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\ \bibinfo {pages}
+  {096401} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carpenter}\ and\ \citenamefont
+  {Howard}(2009)}]{CarpenterAC09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
+  {Carpenter}}\ and\ \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Howard}},\ }\href {\doibase 10.1107/S0108768109000974} {\bibfield  {journal}
+  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo
+  {volume} {65}},\ \bibinfo {pages} {134} (\bibinfo {year} {2009})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Jahn}\ \emph {et~al.}(1937)\citenamefont {Jahn},
+  \citenamefont {Teller},\ and\ \citenamefont {Donnan}}]{JahnPRSL37}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.}\ \bibnamefont
+  {Jahn}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Teller}}, \ and\
+  \bibinfo {author} {\bibfnamefont {F.~G.}\ \bibnamefont {Donnan}},\ }\href
+  {\doibase 10.1098/rspa.1937.0142} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the Royal Society of London. Series A - Mathematical and
+  Physical Sciences}\ }\textbf {\bibinfo {volume} {161}},\ \bibinfo {pages}
+  {220} (\bibinfo {year} {1937})},\ \Eprint
+  {http://arxiv.org/abs/https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1937.0142}
+  {https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1937.0142}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jahn}\ and\ \citenamefont
+  {Bragg}(1938)}]{JahnPRSL38}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.}\ \bibnamefont
+  {Jahn}}\ and\ \bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
+  {Bragg}},\ }\href {\doibase 10.1098/rspa.1938.0008} {\bibfield  {journal}
+  {\bibinfo  {journal} {Proceedings of the Royal Society of London. Series A -
+  Mathematical and Physical Sciences}\ }\textbf {\bibinfo {volume} {164}},\
+  \bibinfo {pages} {117} (\bibinfo {year} {1938})},\ \Eprint
+  {http://arxiv.org/abs/https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1938.0008}
+  {https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1938.0008}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {\"Opik}\ and\ \citenamefont
+  {Pryce}(1957)}]{OpikRS57}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
+  {\"Opik}}\ and\ \bibinfo {author} {\bibfnamefont {M.~H.~L.}\ \bibnamefont
+  {Pryce}},\ }\href {http://www.jstor.org/stable/100101} {\bibfield  {journal}
+  {\bibinfo  {journal} {Proceedings of the Royal Society of London. Series A,
+  Mathematical and Physical Sciences}\ }\textbf {\bibinfo {volume} {238}},\
+  \bibinfo {pages} {425} (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sturge}(1968)}]{Sturge68}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Sturge}}\ }(\bibinfo  {publisher} {Academic Press},\ \bibinfo {year}
+  {1968})\ pp.\ \bibinfo {pages} {91--211}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gehring}\ and\ \citenamefont
+  {Gehring}(1975)}]{GehringRPP75}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~A.}\ \bibnamefont
+  {Gehring}}\ and\ \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont
+  {Gehring}},\ }\href {\doibase 10.1088/0034-4885/38/1/001} {\bibfield
+  {journal} {\bibinfo  {journal} {Reports on Progress in Physics}\ }\textbf
+  {\bibinfo {volume} {38}},\ \bibinfo {pages} {1} (\bibinfo {year}
+  {1975})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pavarini}(2016)}]{PavariniChap}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Pavarini}},\ }\href {https://juser.fz-juelich.de/record/819465} {\emph
+  {\bibinfo {title} {{Q}uantum {M}aterials: {E}xperiments and {T}heory}}},\
+  edited by\ \bibinfo {editor} {\bibfnamefont {E.}~\bibnamefont {Pavarini}},
+  \bibinfo {editor} {\bibfnamefont {E.}~\bibnamefont {Koch}}, \bibinfo {editor}
+  {\bibfnamefont {J.}~\bibnamefont {van~den Brink}}, \ and\ \bibinfo {editor}
+  {\bibfnamefont {G.}~\bibnamefont {Sawatzky}},\ \bibinfo {series} {Schriften
+  des Forschungszentrums J\"ulich. Reihe modeling and simulation},
+  Vol.~\bibinfo {volume} {6}\ (\bibinfo  {publisher} {Forschungszentrum
+  J\"ulich GmbH Zentralbibliothek, Verlag},\ \bibinfo {address} {J\"ulich},\
+  \bibinfo {year} {2016})\ p.\ \bibinfo {pages} {420 S.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Khomskii}\ and\ \citenamefont
+  {Streltsov}(2021)}]{KhomskiiCR21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~I.}\ \bibnamefont
+  {Khomskii}}\ and\ \bibinfo {author} {\bibfnamefont {S.~V.}\ \bibnamefont
+  {Streltsov}},\ }\href {\doibase 10.1021/acs.chemrev.0c00579} {\bibfield
+  {journal} {\bibinfo  {journal} {Chemical Reviews}\ }\textbf {\bibinfo
+  {volume} {121}},\ \bibinfo {pages} {2992} (\bibinfo {year} {2021})},\
+  \bibinfo {note} {pMID: 33314912},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/acs.chemrev.0c00579}
+  {https://doi.org/10.1021/acs.chemrev.0c00579} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goldschmidt}(1926)}]{Goldschmidt1926}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Goldschmidt}},\ }\href {\doibase 10.1007/BF01507527} {\bibfield  {journal}
+  {\bibinfo  {journal} {Naturwissenschaften}\ }\textbf {\bibinfo {volume}
+  {14}},\ \bibinfo {pages} {477} (\bibinfo {year} {1926})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Kieslich}\ \emph {et~al.}(2015)\citenamefont
+  {Kieslich}, \citenamefont {Sun},\ and\ \citenamefont
+  {Cheetham}}]{KieslichCS15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Kieslich}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sun}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Cheetham}},\
+  }\href {\doibase 10.1039/C5SC00961H} {\bibfield  {journal} {\bibinfo
+  {journal} {Chem. Sci.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
+  {3430} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Garcia-Fernandez}\ \emph {et~al.}(2010)\citenamefont
+  {Garcia-Fernandez}, \citenamefont {Aramburu}, \citenamefont {Barriuso},\ and\
+  \citenamefont {Moreno}}]{garcia-fernandezJPCL10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Garcia-Fernandez}}, \bibinfo {author} {\bibfnamefont {J.~a.}\ \bibnamefont
+  {Aramburu}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+  {Barriuso}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Moreno}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Phys. Chem. Lett.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {647}
+  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cammarata}\ and\ \citenamefont
+  {Rondinelli}(2014)}]{CammarataJCP14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Cammarata}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
+  {Rondinelli}},\ }\href {\doibase 10.1063/1.4895967} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {141}},\ \bibinfo {pages} {114704} (\bibinfo {year} {2014})},\
+  \Eprint
+  {http://arxiv.org/abs/https://pubs.aip.org/aip/jcp/article-pdf/doi/10.1063/1.4895967/15484681/114704\_1\_online.pdf}
+  {https://pubs.aip.org/aip/jcp/article-pdf/doi/10.1063/1.4895967/15484681/114704\_1\_online.pdf}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lee}\ \emph {et~al.}(2016)\citenamefont {Lee},
+  \citenamefont {Bristowe}, \citenamefont {Lee}, \citenamefont {Lee},
+  \citenamefont {Bristowe}, \citenamefont {Cheetham},\ and\ \citenamefont
+  {Jang}}]{LeeCM16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-H.}\ \bibnamefont
+  {Lee}}, \bibinfo {author} {\bibfnamefont {N.~C.}\ \bibnamefont {Bristowe}},
+  \bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont {Lee}}, \bibinfo
+  {author} {\bibfnamefont {S.-H.}\ \bibnamefont {Lee}}, \bibinfo {author}
+  {\bibfnamefont {P.~D.}\ \bibnamefont {Bristowe}}, \bibinfo {author}
+  {\bibfnamefont {A.~K.}\ \bibnamefont {Cheetham}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {H.~M.}\ \bibnamefont {Jang}},\ }\href {\doibase
+  10.1021/acs.chemmater.6b00968} {\bibfield  {journal} {\bibinfo  {journal}
+  {Chemistry of Materials}\ }\textbf {\bibinfo {volume} {28}},\ \bibinfo
+  {pages} {4259} (\bibinfo {year} {2016})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/acs.chemmater.6b00968}
+  {https://doi.org/10.1021/acs.chemmater.6b00968} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yoshida}\ \emph {et~al.}(2021)\citenamefont
+  {Yoshida}, \citenamefont {Akamatsu},\ and\ \citenamefont
+  {Hayashi}}]{YoshidaPRL21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
+  {Yoshida}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Akamatsu}}, \
+  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Hayashi}},\ }\href
+  {\doibase 10.1103/PhysRevLett.127.215701} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {127}},\ \bibinfo
+  {pages} {215701} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Herzberg}\ and\ \citenamefont
+  {Teller}(1933)}]{HerzbergZPC33}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Herzberg}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Teller}},\ }\href {\doibase doi:10.1515/zpch-1933-2136} {\bibfield
+  {journal} {\bibinfo  {journal} {Zeitschrift f\"ur Physikalische Chemie}\
+  }\textbf {\bibinfo {volume} {21B}},\ \bibinfo {pages} {410} (\bibinfo {year}
+  {1933})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bersuker}(1966)}]{BersukerPL66}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
+  {Bersuker}},\ }\href {\doibase https://doi.org/10.1016/0031-9163(66)91127-9}
+  {\bibfield  {journal} {\bibinfo  {journal} {Physics Letters}\ }\textbf
+  {\bibinfo {volume} {20}},\ \bibinfo {pages} {589} (\bibinfo {year}
+  {1966})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kristoffel}\ and\ \citenamefont
+  {Konsin}(1967)}]{KristoffelPSSB67}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Kristoffel}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Konsin}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Status Solidi B}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {K39}
+  (\bibinfo {year} {1967})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pearson}(1983)}]{PearsonJMS83}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Pearson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
+  Mol. Struct.: THEOCHEM}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo
+  {pages} {25} (\bibinfo {year} {1983})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Fulton}\ and\ \citenamefont
+  {Gouterman}(2004)}]{FultonJCP04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
+  {Fulton}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Gouterman}},\ }\href {\doibase 10.1063/1.1701181} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
+  {volume} {35}},\ \bibinfo {pages} {1059} (\bibinfo {year} {2004})},\ \Eprint
+  {http://arxiv.org/abs/https://pubs.aip.org/aip/jcp/article-pdf/35/3/1059/8125554/1059\_1\_online.pdf}
+  {https://pubs.aip.org/aip/jcp/article-pdf/35/3/1059/8125554/1059\_1\_online.pdf}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bersuker}(2013)}]{BersukerCR13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~B.}\ \bibnamefont
+  {Bersuker}},\ }\href {\doibase 10.1021/cr300279n} {\bibfield  {journal}
+  {\bibinfo  {journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {113}},\
+  \bibinfo {pages} {1351} (\bibinfo {year} {2013})},\ \bibinfo {note} {pMID:
+  23301718},\ \Eprint {http://arxiv.org/abs/https://doi.org/10.1021/cr300279n}
+  {https://doi.org/10.1021/cr300279n} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bethe}(1929)}]{BetheAP29}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Bethe}},\ }\href {\doibase https://doi.org/10.1002/andp.19293950202}
+  {\bibfield  {journal} {\bibinfo  {journal} {Annalen der Physik}\ }\textbf
+  {\bibinfo {volume} {395}},\ \bibinfo {pages} {133} (\bibinfo {year}
+  {1929})},\ \Eprint
+  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/andp.19293950202}
+  {https://onlinelibrary.wiley.com/doi/pdf/10.1002/andp.19293950202}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Van~Vleck}(1932)}]{VanVleckPR32}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+  {Van~Vleck}},\ }\href {\doibase 10.1103/PhysRev.41.208} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {41}},\
+  \bibinfo {pages} {208} (\bibinfo {year} {1932})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Paxton}(2009{\natexlab{a}})}]{PaxtonNotes}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont
+  {Paxton}},\ }\href {https://tonypaxton.org/Notes/TB.pdf} {\emph {\bibinfo
+  {title} {Multiscale Simulation Methods in Molecular Sciences}}},\ edited by\
+  \bibinfo {editor} {\bibfnamefont {J.}~\bibnamefont {Grotendorst}}, \bibinfo
+  {editor} {\bibfnamefont {N.}~\bibnamefont {Attig}}, \bibinfo {editor}
+  {\bibfnamefont {S.}~\bibnamefont {Bl\"ugel}}, \ and\ \bibinfo {editor}
+  {\bibfnamefont {D.}~\bibnamefont {Marx}},\ Vol.~\bibinfo {volume} {42}\
+  (\bibinfo  {publisher} {Academic Press, Institute for Advanced Simulation,
+  Forschungszentrum J\"ulich},\ \bibinfo {year} {2009})\ pp.\ \bibinfo {pages}
+  {145--176}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carter}\ \emph {et~al.}(2012)\citenamefont {Carter},
+  \citenamefont {Shankar}, \citenamefont {Zeb},\ and\ \citenamefont
+  {Kee}}]{CarterPRB12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-M.}\ \bibnamefont
+  {Carter}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont {Shankar}},
+  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Zeb}}, \ and\
+  \bibinfo {author} {\bibfnamefont {H.-Y.}\ \bibnamefont {Kee}},\ }\href
+  {\doibase 10.1103/PhysRevB.85.115105} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo
+  {pages} {115105} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ivanic}\ and\ \citenamefont
+  {Ruedenberg}(1996)}]{IvanicJPC96}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Ivanic}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Ruedenberg}},\ }\href {\doibase 10.1021/jp953350u} {\bibfield  {journal}
+  {\bibinfo  {journal} {The Journal of Physical Chemistry}\ }\textbf {\bibinfo
+  {volume} {100}},\ \bibinfo {pages} {6342} (\bibinfo {year} {1996})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/jp953350u}
+  {https://doi.org/10.1021/jp953350u} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Finnis}\ \emph {et~al.}(1998)\citenamefont {Finnis},
+  \citenamefont {Paxton}, \citenamefont {Methfessel},\ and\ \citenamefont {van
+  Schilfgaarde}}]{FinnisPRL98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
+  {Finnis}}, \bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont {Paxton}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Methfessel}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {van Schilfgaarde}},\
+  }\href {\doibase 10.1103/PhysRevLett.81.5149} {\bibfield  {journal} {\bibinfo
+   {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
+  {pages} {5149} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Paxton}\ and\ \citenamefont
+  {Finnis}(2008)}]{PaxtonPRB08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont
+  {Paxton}}\ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
+  {Finnis}},\ }\href {\doibase 10.1103/PhysRevB.77.024428} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {77}},\ \bibinfo {pages} {024428} (\bibinfo {year} {2008})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Ewald}(1921)}]{Ewald1921}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~P.}\ \bibnamefont
+  {Ewald}},\ }\href {\doibase https://doi.org/10.1002/andp.19213690304}
+  {\bibfield  {journal} {\bibinfo  {journal} {Annalen der Physik}\ }\textbf
+  {\bibinfo {volume} {369}},\ \bibinfo {pages} {253} (\bibinfo {year}
+  {1921})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Paxton}(2009{\natexlab{b}})}]{Questaal}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
+  {Paxton}},\ }\href {https://www.questaal.org/docs/code/tbe/} {\enquote
+  {\bibinfo {title} {{TBE code}},}\ } (\bibinfo {year}
+  {2009}{\natexlab{b}})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liechtenstein}\ \emph {et~al.}(1995)\citenamefont
+  {Liechtenstein}, \citenamefont {Anisimov},\ and\ \citenamefont
+  {Zaanen}}]{LiechtensteinPRB95}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont
+  {Liechtenstein}}, \bibinfo {author} {\bibfnamefont {V.~I.}\ \bibnamefont
+  {Anisimov}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Zaanen}},\ }\href {\doibase 10.1103/PhysRevB.52.R5467} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {52}},\
+  \bibinfo {pages} {R5467} (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Inc.}()}]{Mathematica}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~R.}\ \bibnamefont
+  {Inc.}},\ }\href {https://www.wolfram.com/mathematica} {\enquote {\bibinfo
+  {title} {Mathematica, {V}ersion 13.3},}\ }\bibinfo {note} {Champaign, IL,
+  2023}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2023-12-11 src/estatic.f90

@@ -15,7 +15,7 @@ subroutine setmadvar()
 use modmain, only: oct, natoms, noctl, nlayers, avec, bvec, a, &
                   twopi, omega, nsptm, atom2species, nds, nspin, Dcf, &
                   ainv, ewalda, ewaldnr, ewaldnk, hardU, nround, &
-                  pos, posA, noct, qa, lcage
+                  pos, posA, noct, qa, lcage, lOnlyOcta	
 implicit none
 integer :: ilm, i,l, m, io, il, ib, itm, is, ia, it, i1, i2
 !integer :: nvevEwalsR, nvevEwalsK
@@ -94,6 +94,7 @@ do ib=1,nbas
 end do
 
  cage = lcage
+ OnlyOcta	 = lOnlyOcta	
  qaa = qa
 
 ! extra normal atoms

### 2023-12-11 src/esvar.f90

@@ -12,8 +12,9 @@ double precision, allocatable, dimension(:,:,:) :: struxdA ! for A-sites atoms
 double precision :: decimal ! to round the struxd, struxdA
 
 double precision, dimension(1:25,1:25,4) :: Rlmax ! up to l=4; rotation matrix for spherical harmonics; for all 4 B atoms
-logical :: cage
+logical :: cage, OnlyOcta
 double precision :: qaa, fVoctO, fVoctAB
+
 
 double precision, dimension(5:9,5:9,3) :: B1hams
 

### 2023-12-11 src/fermi.f

@@ -113,8 +113,8 @@ C If the Fermi level was found.....................
 	   end do
 	  end do
 
-		write(6,*) 'test: Fermid: qtot,sumq=',qtot,sumq
-  
+		write(6,*) 'test: Fermid: qtot,sumq=',qtot,sumq, ebands
+		  
 	  return
 	 endif
 

### 2023-12-11 src/modmain.f

@@ -21,6 +21,7 @@
 	integer :: norbtms, norbos ! number of spin-space orbitals on a TM/O atom
 	integer :: ntot ! hilbert space size
 	logical :: tmnn2, oxnn2, singlesk, lsoc, lhu, lspin, xsf, lcage
+	logical :: lOnlyOcta	
 	integer :: ntottm
 	double precision :: qtot , qa
 	double complex, parameter :: iota = dcmplx(0.0d0,1.0d0)
@@ -41,7 +42,7 @@
 	double precision, dimension(7,2) :: Dcf ! crystal field parameters... assumed same for all species?
 	! Del112 for Oxygen & Del222, Del224 for TM
 	double precision :: Del112, Del222, Del224
-
+	double precision :: skscale ! slater-koster global scale factor
 	double precision, dimension(10,10,4) :: Rl2,Rl2T
 	
 	logical :: ham4edrixs

### 2023-12-11 src/readinput.f

@@ -37,7 +37,9 @@
 	DelB = 1.8376130 ! Hartree
 
 	lcage = .false.
-
+	lOnlyOcta	= .false.
+	skscale = 1.0d0
+	
 	Ham4EDRIXS = .false.
 	
 	ewalda = 1.d-7; !50.0d0 ! at the moment, k-space sum is discarded so welda has to be infinitesimal to make real space sum equal to the actual sum. of course, this also needs a larger n_r for the convergence! ewaldnr > 5 is okay, converged to 2 decimal palces for NaCl structure, calculated Madelung ==> 1.7457834017323322; converged  is 1.747565 which requires ewaldnr~30.
@@ -169,15 +171,19 @@
 	   read(50,*,err=20) theta !, phii
 			phii = theta
 
-	case('RunBeastParam') ! qA, lam, d222, phi, theta
+	case('RunBeastParam') ! qA, lam, d222, phi, theta, skscale
 	! assuming that this flag will be at the end of the file so that its 
 	! var are already allocated (soc) and never overwritten.
 	   read(50,*,err=20) Hub(1)%U, Hub(1)%J, ion_d, 
-     .                   qA, soc(1), Del222, phii, theta
+     .                   qA, soc(1), Del222, phii, theta, skscale
 	   soc(1) = soc(1)*eV2Har
 	   Dcf(5,2) = Del222
 	   nds(1) = (6-qa) + ion_d
 	   qtot = 4*nds(1) + 4*qA + nlayers*2*3*4
+	   skbo = skscale * skbo;
+	   skbb = skscale * skbb;
+	   skoo = skscale * skoo;
+	   
 	   write(*,*)'WARNING: RunBeastParam works only at nsptm=1'
 	   write(*,*)'WARNING: modify it for superlattices '
 	   
@@ -241,7 +247,7 @@
 	 !if(ltmgs) lscf = .false.
 
 	case('CrystalField')
-	 read(50,*,err=20) lcage, Del112, Del222, Del224
+	 read(50,*,err=20) lcage, Del112, Del222, Del224, lOnlyOcta
 	 Dcf(2,1) = Del112 ! Oxygen
 	 Dcf(5,2) = Del222 ! TM
 	 Dcf(7,2) = Del224 ! TM

### 2023-12-11 src/scf.f90

@@ -352,7 +352,7 @@ do i=1,2 !natoms,4
 	write(*,'(5f10.5)') atm(i)%dh
 enddo
 
-open(804,file='evals.dat',action='write',position='append')
+!open(804,file='evals.dat',action='write',position='append')
  !-------- -------- -------- -------- -------- -------------- 
  ! Hamiltonian, eigenstates and eigenvalues: on kgrid in BZ
  !-------- -------- -------- -------- -------- -------------- 
@@ -372,10 +372,10 @@ open(804,file='evals.dat',action='write',position='append')
   !call useeigdata(ntot,hk) ! calc whatever we like at this k-point
   ! will take a weighted average after the k-loop completes.
 
-	write(804,*) eval(ik,:)
+!	write(804,*) eval(ik,:)
   
  end do ! ik
- close(804)
+! close(804)
  
  !-------- -------- -------- -------- -------- -------------- 
  ! find the Fermi level and wke = occupation weighted by wk 
@@ -384,6 +384,10 @@ open(804,file='evals.dat',action='write',position='append')
                       qtot, wke, efermi, nspin, ebands)
  !write(*,'(a,f15.6)') "N_electron = ", qtot
  write(*,'(a, 3f15.10)') "Fermi energy = ", efermi
+
+	open(456,file='ebands.dat',action='write',position='append')
+	write(456,*) ebands
+	close(456)
 
  !--------------------------------------------------------
   ! calculate rhoc etc to be used for Qmpol

### 2023-12-11 src/tbeseld.f90

@@ -1,7 +1,8 @@
  module mtbeseld
  use esvar, only: nsp, nbas, nlmi, ll, ilm12, atm, struxd, & 
                   qmpol, CFM, gaunt, nbasA, struxdA, qmpolA, s_lat, &
-                 hard, qref, Rlmax, cage, qaa, fVoctO, fVoctAB, B1hams
+                 hard, qref, Rlmax, cage, qaa, fVoctO, fVoctAB, &
+                 B1hams, OnlyOcta
  use rotylm, only: getVoct
  implicit none
 
@@ -523,6 +524,7 @@ endif
 !============================================================================
 	subroutine getvmdhcage() ! only l=4 potential, in unrotated frame.
 	implicit none
+	!logical, intent(in) :: lOnlyOcta
 	double precision, dimension(25,4) :: vm, vm1
 	double precision, parameter :: dsqrt57= dsqrt(5.0d0/7.0d0)
 	integer :: ibb, ib, ic,it, ilm, ilmp, ilmpp, isp,l
@@ -538,9 +540,10 @@ endif
 		vm(17:25,ib) = vm(17:25,ib) * fVoctO! fVoctO=(35.0d0/4.0d0)*(2.0d0/dc**5) ! prefactor: Pavarini, orbital order notes
 	end do
 
+ if (.not. OnlyOcta) then
 	!write(*,*) 'Rlmax(17:25,21,1) = ',Rlmax(17:25,21,1)
 
- write(*,*) 'tbseld: fVoctAB = ',fVoctAB
+ 	write(*,*) 'tbseld: fVoctAB = ',fVoctAB
 
 	! A+B potential in original frame (it is independent of rotation)
 	vm1 = 0.0d0
@@ -551,6 +554,8 @@ endif
 
  vm = vm + vm1; ! combine to get total crystal field
 
+ endif ! not Only Oxygen Octahedral Field
+	
 
  ! beast/TB V_L are normalised by a factor of 4pi/(2l+1)
  ! that is balanced by the same factor in crystal field Delta's [array CFM]

### 2023-12-16 manuscript/prb-submitted/paper.tex
revised paper JT

--- 2023-12-11 manuscript/paper.tex
@@
 \begin{center}
-\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-bonds-labelled-2}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-cubic-bonds}
-%\includegraphics[height=5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cell-pbnm-15-15-bonds}\\
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-cubic-final}
-%\includegraphics[height=4.5cm,keepaspectratio]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/cages-rotated-15-15-final}
+%\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-bonds-labelled-2}
+\includegraphics[width=1\linewidth]{structures-combined-bonds-labelled-2}
 \caption{
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
+%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
+\includegraphics[width=1.0\linewidth]{energy-vs-beta-alpha-0-width-row}
 \caption{
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
+%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
+\includegraphics[width=1.0\linewidth]{energy-vs-alpha-beta-0-width-row-character}
 \caption{
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
+%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
+\includegraphics[width=1.0\linewidth]{energy-vs-beta-alpha-10-width-row-beta-0-15}
 \caption{
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
+%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
+\includegraphics[width=1.0\linewidth]{wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
 \caption{
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
+%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
+\includegraphics[width=1.0\linewidth]{energy-wts-eg}
 \caption{
@@
 \begin{center}
-\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
+%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
+\includegraphics[width=1.0\linewidth]{full-lattice-vs-AB}
 \caption{
@@
 we discussed in this manuscript is also an interesting future work.
+However, a few remarks are in order. 
+Unlike the electronic correlations and spin-orbit interaction,
+ the hybridization between 
+the orbitals localized on different B sites are not
+rotationally invariant.
+Assuming the crystal field splitting to be the largest energy scale,
+the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra,
+and
+the hybridization between the orbitals localized on different B sites
+(and the electronic band structure arising from them)
+are modified as the octahedra rotate.
+
+To shed some light on the 
+role of these band structure effects,
+we consider the nearest neighbor hopping between the B sites
+using the Slater-Koster method~\cite{SlaterKoster}
+and
+calculate the change in the energy of two configurations
+$t_{2g}^1$ and $e_g^1$
+as the octahedra rotate
+in three cases: with either the crystal field or the hopping only and with both of these simultaneously.
+Figure~\ref{fig:hybrid}(a)
+shows the change in the energy 
+as a function of $\beta$ for the first two cases
+for the crystal-field-only (black curves, left y-axis;
+$\alpha=0$, $q=2q_o$, $\Delta_o=4q_o/15a$)
+and for the hopping-only case (red/gray curves, right y-axis).
+We use Slater-Koster hopping parameters
+$(t_{\sigma},t_{\pi},t_{\delta})=(0.15,-0.1,0.025)$~eV, 
+$a=7$~bohr, $q_o=2$~e,
+and consider only the crystal field of O octahedra that creates
+$t_{2g}$ and $e_g$ manifolds.
+While both $t_{2g}^1$ and $e_g^1$ configurations 
+show a lowering of energy 
+due to
+the crystal field 
+as $\beta$ 
+increases---consistent with the results presented 
+before---the energy of $e_g^1$ increases when only hopping is considered 
+(the effect scales with the hopping parameters or the bandwidth).
+This is due to a reduced hybridization leading to narrower $e_g$ bands.
+In contrast, the energy of $t_{2g}^1$ decreases due band widening arising from 
+an enhanced hybridization.
+The crystal field and these band structure effects are not additive however.
+The rotation induced splitting of the $t_{2g}$/$e_g$ manifolds
+suppresses the effectiveness of the hopping in creating 
+the dispersion in the energy states, 
+and thus reduces the bandwidths and
+affects the associated rotation induced energetic changes.
+
+To show the validity regime of our crystal field model 
+presented in this manuscript,
+Fig.~\ref{fig:hybrid}(b)
+presents  
+the ratio of the
+ change in the energy 
+at $\beta=20^\circ$ (i.e., the energy difference from the cubic case)
+at finite hopping $E(W)$ to that of our simplistic crystal field model $E(0)$
+as a function of the average bandwidth $W$ of $t_{2g}$ and $e_g$ bands.
+Here we scale the Slater-Koster parameters used for Fig.~\ref{fig:hybrid}(a)
+to tune the bandwidth $W$.
+We see that $E(W)/E(0)$ decreases from unity at $W=0$
+to half its value for $t_{2g}^1$ configuration at $W/\Delta_o\gtrsim0.3$,
+and even becomes negative for $e_g^1$ configuration around 
+$W/\Delta_o\gtrsim0.15$ (showing the dominance of the band structure effects).
+From this analysis, we conclude that the results of our crystal field model 
+hold unambiguously only for narrower bands, $W/\Delta_o\ll1$.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1.0\linewidth]{hybrid}
+\caption{The effect of dispersion due to the electron hopping between B sites.
+(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
+as a function of $\beta$ when either the crystal field or the hopping is considered alone.
+In the latter case, the energy changes are scaled with the bandwidth $W$.
+(b) Considering both the crystal field and the hopping simultaneously,
+the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
+as a function of the average bandwidth $W$ 
+for the same two configurations
+$t_{2g}^1$ and $e_g^1$.
+The results of the crystal field model presented in this manuscript 
+hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
+}
+\label{fig:hybrid}
+\end{center}
+\end{figure}
 

### 2023-12-25 manuscript/prb-submitted/paper.tex
hopping effects included. references, titles included

--- 2023-10-12 manuscript/paper.tex
@@
-\documentclass[a4paper,prb,twocolumn]{revtex4-1}  %a4paper,prb,twocolumn
+\documentclass[a4paper,prb,twocolumn,longbibliography]{revtex4-1}  %a4paper,prb,twocolumn
 %\documentclass[preprint]{revtex4-1}
@@
 we discussed in this manuscript is also an interesting future work.
+A discussion 
+about the role of 
+electron hopping 
+along with some preliminary results 
+follows.
+
+Assuming the crystal field splitting to be the largest energy scale,
+the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra.
+The electron hopping between these orbitals that are 
+localized on different B sites 
+%(that creates electronic bands)
+depends on the relative orientation of the orbitals.
+As the octahedra rotate (or tilt),
+the hybridization between the
+neighboring sites
+change,
+modifying
+the electronic bands and associated band energy.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1.0\linewidth]{hybrid}
+\caption{The effect of electron hopping between B sites.
+(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
+as a function of $\beta$ when either the crystal field or the hopping is considered alone.
+In the latter case, the energy changes are scaled with the bandwidth $W$.
+(b) Considering both the crystal field and the hopping simultaneously,
+the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
+as a function of the average bandwidth $W$, 
+for the same two configurations
+$t_{2g}^1$ and $e_g^1$.
+The results of the crystal field model presented in this manuscript 
+hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
+}
+\label{fig:hybrid}
+\end{center}
+\end{figure}
+
+To shed some light on the 
+role of these band structure effects,
+we consider the nearest neighbor hopping between the B sites
+using the Slater-Koster method~\cite{SlaterPR54}
+and
+calculate the change in the energy of 
+the system
+as the octahedra rotate.
+We do this for three cases: with either the crystal field or the hopping only,
+ and with both of these simultaneously.
+%
+Figure~\ref{fig:hybrid}(a)
+shows the change in the energy 
+of two (spinless) configurations $t_{2g}^1$ and $e_g^1$
+as a function of $\beta$ for the first two cases
+for the crystal-field-only (black curves, left y-axis;
+$\alpha=0$, $q=2q_o$, $\Delta_o=4q_o/15a$)
+and for the hopping-only case (red/gray curves, right y-axis).
+We
+use Slater-Koster hopping parameters
+$(t_{\sigma},t_{\pi},t_{\delta})=(0.15,-0.1,0.025)$~eV, 
+% W = \{0.0330745,0.0385869,0.0358307\} Hartree
+% W = {0.900005, 1.05, 0.975004} eV
+%$(t_{\sigma},t_{\pi},t_{\delta})/W= {0.153846, -0.102564, 0.0256409}$
+$a=7$~bohr, $q_o=2$~e,
+and consider only the crystal field of O octahedra that creates
+$t_{2g}$ and $e_g$ manifolds.
+(These parameters produce an average
+bandwidth $W=0.97$~eV for the two manifolds).
+While both $t_{2g}^1$ and $e_g^1$ configurations 
+show a lowering of energy 
+due to
+the crystal field 
+as $\beta$ 
+increases---consistent with the results presented 
+before---the energy of $e_g^1$ increases when only hopping is considered 
+(the effect scales with the hopping parameters or the bandwidth).
+This is due to a reduced hybridization leading to narrower $e_g$ bands.
+In contrast, the energy of $t_{2g}^1$ decreases due to a band widening arising from 
+an enhanced hybridization.
+The crystal field and these band structure effects are not additive however.
+The rotation induced splitting of the $t_{2g}$/$e_g$ manifolds
+arising from the crystal field
+suppresses the effectiveness of the hopping in creating 
+the dispersion in the energy states, 
+and thus reduces the bandwidths and the
+the associated rotation induced energetic changes.
+
+To show the validity regime of our crystal field model 
+presented in this manuscript,
+Fig.~\ref{fig:hybrid}(b)
+presents  
+the ratio of the
+ change in the energy 
+at $\beta=20^\circ$ (i.e., the energy difference from the cubic case)
+at finite hopping $E(W)$ to that of our simplistic crystal field model $E(0)$
+as a function of the average bandwidth $W$ of $t_{2g}$ and $e_g$ bands.
+Here we scale the Slater-Koster parameters used for Fig.~\ref{fig:hybrid}(a)
+to tune the bandwidth $W$.
+We see that $E(W)/E(0)$ decreases from unity at $W=0$
+to half its value for $t_{2g}^1$ configuration at $W/\Delta_o\gtrsim0.3$,
+and even becomes negative for $e_g^1$ configuration around 
+$W/\Delta_o\gtrsim0.15$ (showing the dominance of the band structure effects).
+From this analysis, we conclude that the results of our crystal field model 
+hold unambiguously only for narrower bands, $W/\Delta_o\ll1$,
+while a detailed further study is required to understand the interplay of the two effects
+at larger bandwidths.
 
@@
 %\bibliographystyle{apsrev4-1}
-\bibliography{perovskites}
+%\bibliography{perovskites}
+
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (0) dotless jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (1) range
+%Control: year (0) verbatim
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{84}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Zubko}\ \emph {et~al.}(2011)\citenamefont {Zubko},
+  \citenamefont {Gariglio}, \citenamefont {Gabay}, \citenamefont {Ghosez},\
+  and\ \citenamefont {Triscone}}]{ZubkoARCMP11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Pavlo}\ \bibnamefont
+  {Zubko}}, \bibinfo {author} {\bibfnamefont {Stefano}\ \bibnamefont
+  {Gariglio}}, \bibinfo {author} {\bibfnamefont {Marc}\ \bibnamefont {Gabay}},
+  \bibinfo {author} {\bibfnamefont {Philippe}\ \bibnamefont {Ghosez}}, \ and\
+  \bibinfo {author} {\bibfnamefont {Jean-Marc}\ \bibnamefont {Triscone}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Interface physics in complex
+  oxide heterostructures},}\ }\href {\doibase
+  10.1146/annurev-conmatphys-062910-140445} {\bibfield  {journal} {\bibinfo
+  {journal} {Annual Review of Condensed Matter Physics}\ }\textbf {\bibinfo
+  {volume} {2}},\ \bibinfo {pages} {141--165} (\bibinfo {year}
+  {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hwang}\ \emph {et~al.}(2012)\citenamefont {Hwang},
+  \citenamefont {Iwasa}, \citenamefont {Kawasaki}, \citenamefont {Keimer},
+  \citenamefont {Nagaosa},\ and\ \citenamefont {Tokura}}]{HwangNM12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~Y.}\ \bibnamefont
+  {Hwang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Iwasa}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kawasaki}}, \bibinfo
+  {author} {\bibfnamefont {B.}~\bibnamefont {Keimer}}, \bibinfo {author}
+  {\bibfnamefont {N.}~\bibnamefont {Nagaosa}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Y.}~\bibnamefont {Tokura}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Emergent phenomena at oxide interfaces},}\ }\href
+  {\doibase 10.1038/nmat3223} {\bibfield  {journal} {\bibinfo  {journal}
+  {Nature Materials}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages}
+  {103--113} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bhattacharya}\ and\ \citenamefont
+  {May}(2014)}]{BhattacharyaARMR14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Anand}\ \bibnamefont
+  {Bhattacharya}}\ and\ \bibinfo {author} {\bibfnamefont {Steven~J.}\
+  \bibnamefont {May}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Magnetic oxide heterostructures},}\ }\href {\doibase
+  10.1146/annurev-matsci-070813-113447} {\bibfield  {journal} {\bibinfo
+  {journal} {Annual Review of Materials Research}\ }\textbf {\bibinfo {volume}
+  {44}},\ \bibinfo {pages} {65--90} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1146/annurev-matsci-070813-113447}
+  {https://doi.org/10.1146/annurev-matsci-070813-113447} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hellman}\ \emph {et~al.}(2017)\citenamefont
+  {Hellman}, \citenamefont {Hoffmann}, \citenamefont {Tserkovnyak},
+  \citenamefont {Beach}, \citenamefont {Fullerton}, \citenamefont {Leighton},
+  \citenamefont {MacDonald}, \citenamefont {Ralph}, \citenamefont {Arena},
+  \citenamefont {D\"urr}, \citenamefont {Fischer}, \citenamefont {Grollier},
+  \citenamefont {Heremans}, \citenamefont {Jungwirth}, \citenamefont {Kimel},
+  \citenamefont {Koopmans}, \citenamefont {Krivorotov}, \citenamefont {May},
+  \citenamefont {Petford-Long}, \citenamefont {Rondinelli}, \citenamefont
+  {Samarth}, \citenamefont {Schuller}, \citenamefont {Slavin}, \citenamefont
+  {Stiles}, \citenamefont {Tchernyshyov}, \citenamefont {Thiaville},\ and\
+  \citenamefont {Zink}}]{HellmanRMP17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Frances}\ \bibnamefont
+  {Hellman}}, \bibinfo {author} {\bibfnamefont {Axel}\ \bibnamefont
+  {Hoffmann}}, \bibinfo {author} {\bibfnamefont {Yaroslav}\ \bibnamefont
+  {Tserkovnyak}}, \bibinfo {author} {\bibfnamefont {Geoffrey S.~D.}\
+  \bibnamefont {Beach}}, \bibinfo {author} {\bibfnamefont {Eric~E.}\
+  \bibnamefont {Fullerton}}, \bibinfo {author} {\bibfnamefont {Chris}\
+  \bibnamefont {Leighton}}, \bibinfo {author} {\bibfnamefont {Allan~H.}\
+  \bibnamefont {MacDonald}}, \bibinfo {author} {\bibfnamefont {Daniel~C.}\
+  \bibnamefont {Ralph}}, \bibinfo {author} {\bibfnamefont {Dario~A.}\
+  \bibnamefont {Arena}}, \bibinfo {author} {\bibfnamefont {Hermann~A.}\
+  \bibnamefont {D\"urr}}, \bibinfo {author} {\bibfnamefont {Peter}\
+  \bibnamefont {Fischer}}, \bibinfo {author} {\bibfnamefont {Julie}\
+  \bibnamefont {Grollier}}, \bibinfo {author} {\bibfnamefont {Joseph~P.}\
+  \bibnamefont {Heremans}}, \bibinfo {author} {\bibfnamefont {Tomas}\
+  \bibnamefont {Jungwirth}}, \bibinfo {author} {\bibfnamefont {Alexey~V.}\
+  \bibnamefont {Kimel}}, \bibinfo {author} {\bibfnamefont {Bert}\ \bibnamefont
+  {Koopmans}}, \bibinfo {author} {\bibfnamefont {Ilya~N.}\ \bibnamefont
+  {Krivorotov}}, \bibinfo {author} {\bibfnamefont {Steven~J.}\ \bibnamefont
+  {May}}, \bibinfo {author} {\bibfnamefont {Amanda~K.}\ \bibnamefont
+  {Petford-Long}}, \bibinfo {author} {\bibfnamefont {James~M.}\ \bibnamefont
+  {Rondinelli}}, \bibinfo {author} {\bibfnamefont {Nitin}\ \bibnamefont
+  {Samarth}}, \bibinfo {author} {\bibfnamefont {Ivan~K.}\ \bibnamefont
+  {Schuller}}, \bibinfo {author} {\bibfnamefont {Andrei~N.}\ \bibnamefont
+  {Slavin}}, \bibinfo {author} {\bibfnamefont {Mark~D.}\ \bibnamefont
+  {Stiles}}, \bibinfo {author} {\bibfnamefont {Oleg}\ \bibnamefont
+  {Tchernyshyov}}, \bibinfo {author} {\bibfnamefont {Andr\'e}\ \bibnamefont
+  {Thiaville}}, \ and\ \bibinfo {author} {\bibfnamefont {Barry~L.}\
+  \bibnamefont {Zink}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Interface-induced phenomena in magnetism},}\ }\href {\doibase
+  10.1103/RevModPhys.89.025006} {\bibfield  {journal} {\bibinfo  {journal}
+  {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages}
+  {025006} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ and\ \citenamefont
+  {Millis}(2017)}]{ChenJPCM17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Hanghui}\ \bibnamefont
+  {Chen}}\ and\ \bibinfo {author} {\bibfnamefont {Andrew}\ \bibnamefont
+  {Millis}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Charge transfer
+  driven emergent phenomena in oxide heterostructures},}\ }\href {\doibase
+  10.1088/1361-648X/aa6efe} {\bibfield  {journal} {\bibinfo  {journal} {Journal
+  of Physics: Condensed Matter}\ }\textbf {\bibinfo {volume} {29}},\ \bibinfo
+  {pages} {243001} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dagotto}(2005)}]{DagottoS05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elbio}\ \bibnamefont
+  {Dagotto}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Complexity in
+  strongly correlated electronic systems},}\ }\href {\doibase
+  10.1126/science.1107559} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {309}},\ \bibinfo {pages} {257--262}
+  (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Dagotto}\ and\ \citenamefont
+  {Tokura}(2008)}]{DagottoMRSB08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Dagotto}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
+  {Tokura}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Strongly
+  correlated electronic materials: Present and future},}\ }\href {\doibase
+  10.1557/mrs2008.223} {\bibfield  {journal} {\bibinfo  {journal} {MRS
+  Bulletin}\ }\textbf {\bibinfo {volume} {33}},\ \bibinfo {pages} {1037--1045}
+  (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Salamon}\ and\ \citenamefont
+  {Jaime}(2001)}]{SalamonRMP01}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Myron~B.}\
+  \bibnamefont {Salamon}}\ and\ \bibinfo {author} {\bibfnamefont {Marcelo}\
+  \bibnamefont {Jaime}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+  physics of manganites: Structure and transport},}\ }\href {\doibase
+  10.1103/RevModPhys.73.583} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\ \bibinfo {pages} {583--628}
+  (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2003)\citenamefont {Wang},
+  \citenamefont {Neaton}, \citenamefont {Zheng}, \citenamefont {Nagarajan},
+  \citenamefont {Ogale}, \citenamefont {Liu}, \citenamefont {Viehland},
+  \citenamefont {Vaithyanathan}, \citenamefont {Schlom}, \citenamefont
+  {Waghmare}, \citenamefont {Spaldin}, \citenamefont {Rabe}, \citenamefont
+  {Wuttig},\ and\ \citenamefont {Ramesh}}]{WangS03}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {Neaton}},
+  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zheng}}, \bibinfo
+  {author} {\bibfnamefont {V.}~\bibnamefont {Nagarajan}}, \bibinfo {author}
+  {\bibfnamefont {S.~B.}\ \bibnamefont {Ogale}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont
+  {D.}~\bibnamefont {Viehland}}, \bibinfo {author} {\bibfnamefont
+  {V.}~\bibnamefont {Vaithyanathan}}, \bibinfo {author} {\bibfnamefont {D.~G.}\
+  \bibnamefont {Schlom}}, \bibinfo {author} {\bibfnamefont {U.~V.}\
+  \bibnamefont {Waghmare}}, \bibinfo {author} {\bibfnamefont {N.~A.}\
+  \bibnamefont {Spaldin}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
+  \bibnamefont {Rabe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Wuttig}}, \ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Ramesh}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Epitaxial
+  bifeo<sub>3</sub> multiferroic thin film heterostructures},}\ }\href
+  {\doibase 10.1126/science.1080615} {\bibfield  {journal} {\bibinfo  {journal}
+  {Science}\ }\textbf {\bibinfo {volume} {299}},\ \bibinfo {pages} {1719--1722}
+  (\bibinfo {year} {2003})},\ \Eprint
+  {http://arxiv.org/abs/https://www.science.org/doi/pdf/10.1126/science.1080615}
+  {https://www.science.org/doi/pdf/10.1126/science.1080615} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Dawber}\ \emph {et~al.}(2005)\citenamefont {Dawber},
+  \citenamefont {Rabe},\ and\ \citenamefont {Scott}}]{DawberRMP05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Dawber}}, \bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Rabe}}, \
+  and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Scott}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Physics of thin-film
+  ferroelectric oxides},}\ }\href {\doibase 10.1103/RevModPhys.77.1083}
+  {\bibfield  {journal} {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf
+  {\bibinfo {volume} {77}},\ \bibinfo {pages} {1083--1130} (\bibinfo {year}
+  {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schlom}\ \emph {et~al.}(2007)\citenamefont {Schlom},
+  \citenamefont {Chen}, \citenamefont {Eom}, \citenamefont {Rabe},
+  \citenamefont {Streiffer},\ and\ \citenamefont {Triscone}}]{SchlomARMR07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Darrell~G.}\
+  \bibnamefont {Schlom}}, \bibinfo {author} {\bibfnamefont {Long-Qing}\
+  \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {Chang-Beom}\
+  \bibnamefont {Eom}}, \bibinfo {author} {\bibfnamefont {Karin~M}\ \bibnamefont
+  {Rabe}}, \bibinfo {author} {\bibfnamefont {Stephen~K}\ \bibnamefont
+  {Streiffer}}, \ and\ \bibinfo {author} {\bibfnamefont {Jean-Marc}\
+  \bibnamefont {Triscone}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Strain tuning of ferroelectric thin films},}\ }\href {\doibase
+  10.1146/annurev.matsci.37.061206.113016} {\bibfield  {journal} {\bibinfo
+  {journal} {Annual Review of Materials Research}\ }\textbf {\bibinfo {volume}
+  {37}},\ \bibinfo {pages} {589--626} (\bibinfo {year} {2007})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Koster}\ \emph {et~al.}(2012)\citenamefont {Koster},
+  \citenamefont {Klein}, \citenamefont {Siemons}, \citenamefont {Rijnders},
+  \citenamefont {Dodge}, \citenamefont {Eom}, \citenamefont {Blank},\ and\
+  \citenamefont {Beasley}}]{KosterRMP12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gertjan}\ \bibnamefont
+  {Koster}}, \bibinfo {author} {\bibfnamefont {Lior}\ \bibnamefont {Klein}},
+  \bibinfo {author} {\bibfnamefont {Wolter}\ \bibnamefont {Siemons}}, \bibinfo
+  {author} {\bibfnamefont {Guus}\ \bibnamefont {Rijnders}}, \bibinfo {author}
+  {\bibfnamefont {J.~Steven}\ \bibnamefont {Dodge}}, \bibinfo {author}
+  {\bibfnamefont {Chang-Beom}\ \bibnamefont {Eom}}, \bibinfo {author}
+  {\bibfnamefont {Dave H.~A.}\ \bibnamefont {Blank}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Malcolm~R.}\ \bibnamefont {Beasley}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Structure, physical properties, and applications
+  of ${\mathrm{srruo}}_{3}$ thin films},}\ }\href {\doibase
+  10.1103/RevModPhys.84.253} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
+  Mod. Phys.}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {253--298}
+  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bersuker}(1975)}]{BersukerCCR75}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.B.}\ \bibnamefont
+  {Bersuker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+  {Jahn-Teller} effect in crystal chemistry and spectroscopy},}\ }\href
+  {\doibase https://doi.org/10.1016/S0010-8545(00)80266-0} {\bibfield
+  {journal} {\bibinfo  {journal} {Coordination Chemistry Reviews}\ }\textbf
+  {\bibinfo {volume} {14}},\ \bibinfo {pages} {357--412} (\bibinfo {year}
+  {1975})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kugel}\ and\ \citenamefont {Khomski{\u
+  i}}(1982)}]{KugelSPU82}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kliment~I}\
+  \bibnamefont {Kugel}}\ and\ \bibinfo {author} {\bibfnamefont {D~I}\
+  \bibnamefont {Khomski{\u i}}},\ }\bibfield  {title} {\enquote {\bibinfo
+  {title} {The jahn-teller effect and magnetism: transition metal compounds},}\
+  }\href {\doibase 10.1070/PU1982v025n04ABEH004537} {\bibfield  {journal}
+  {\bibinfo  {journal} {Soviet Physics Uspekhi}\ }\textbf {\bibinfo {volume}
+  {25}},\ \bibinfo {pages} {231} (\bibinfo {year} {1982})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Millis}(1998)}]{MillisN98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
+  {Millis}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Lattice effects
+  in magnetoresistive manganese perovskites},}\ }\href {\doibase 10.1038/32348}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nature}\ }\textbf {\bibinfo
+  {volume} {392}},\ \bibinfo {pages} {147--150} (\bibinfo {year}
+  {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Terakura}(2007)}]{TerakuraPMS07}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Terakura}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Magnetism,
+  orbital ordering and lattice distortion in perovskite transition-metal
+  oxides},}\ }\href {\doibase https://doi.org/10.1016/j.pmatsci.2006.10.007}
+  {\bibfield  {journal} {\bibinfo  {journal} {Progress in Materials Science}\
+  }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {388--400} (\bibinfo
+  {year} {2007})},\ \bibinfo {note} {modelling electrons and atoms for
+  materials science}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Halcrow}(2013)}]{HalcrowRSC13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Malcolm~A.}\
+  \bibnamefont {Halcrow}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Jahn--teller distortions in transition metal compounds, and their importance
+  in functional molecular and inorganic materials},}\ }\href {\doibase
+  10.1039/C2CS35253B} {\bibfield  {journal} {\bibinfo  {journal} {Chemical
+  Society Reviews}\ }\textbf {\bibinfo {volume} {42}},\ \bibinfo {pages}
+  {1784--1795} (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lufaso}\ and\ \citenamefont
+  {Woodward}(2004)}]{LufasoAC04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael~W.}\
+  \bibnamefont {Lufaso}}\ and\ \bibinfo {author} {\bibfnamefont {Patrick~M.}\
+  \bibnamefont {Woodward}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Jahn{--}Teller distortions, cation ordering and octahedral tilting in
+  perovskites}},}\ }\href {\doibase 10.1107/S0108768103026661} {\bibfield
+  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
+  {\bibinfo {volume} {60}},\ \bibinfo {pages} {10--20} (\bibinfo {year}
+  {2004})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Glazer}(1972)}]{GlazerAC72}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Glazer}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Classification
+  of tilted octahedra in perovskites},}\ }\href {\doibase
+  10.1107/S0567740872007976} {\bibfield  {journal} {\bibinfo  {journal} {Acta
+  Crystallogr., Sect. B: Struct. Crystallogr. Cryst. Chem.}\ }\textbf {\bibinfo
+  {volume} {28}},\ \bibinfo {pages} {3384} (\bibinfo {year}
+  {1972})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Thomas}(1996)}]{ThomasAC96}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~W.}\ \bibnamefont
+  {Thomas}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The
+  compositional dependence of octahedral tilting in orthorhombic and tetragonal
+  perovskites}},}\ }\href {\doibase 10.1107/S0108768195006100} {\bibfield
+  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
+  {\bibinfo {volume} {52}},\ \bibinfo {pages} {16--31} (\bibinfo {year}
+  {1996})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Woodward}(1997{\natexlab{a}})}]{WoodwardAC97a}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Woodward}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Octahedral
+  Tilting in Perovskites. I. Geometrical Considerations}},}\ }\href {\doibase
+  10.1107/S0108768196010713} {\bibfield  {journal} {\bibinfo  {journal} {Acta
+  Crystallographica Section B}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo
+  {pages} {32--43} (\bibinfo {year} {1997}{\natexlab{a}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Woodward}(1997{\natexlab{b}})}]{WoodwardAC97b}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
+  {Woodward}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Octahedral
+  Tilting in Perovskites. II. Structure Stabilizing Forces}},}\ }\href
+  {\doibase 10.1107/S0108768196012050} {\bibfield  {journal} {\bibinfo
+  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo {volume}
+  {53}},\ \bibinfo {pages} {44--66} (\bibinfo {year}
+  {1997}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Howard}\ and\ \citenamefont
+  {Stokes}(1998)}]{HowardAC98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
+  {Howard}}\ and\ \bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
+  {Stokes}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Group-Theoretical Analysis of Octahedral Tilting in Perovskites}},}\ }\href
+  {\doibase 10.1107/S0108768198004200} {\bibfield  {journal} {\bibinfo
+  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo {volume}
+  {54}},\ \bibinfo {pages} {782--789} (\bibinfo {year} {1998})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Stokes}\ \emph {et~al.}(2002)\citenamefont {Stokes},
+  \citenamefont {Kisi}, \citenamefont {Hatch},\ and\ \citenamefont
+  {Howard}}]{StokesAC02}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Harold~T.}\
+  \bibnamefont {Stokes}}, \bibinfo {author} {\bibfnamefont {Erich~H.}\
+  \bibnamefont {Kisi}}, \bibinfo {author} {\bibfnamefont {Dorian~M.}\
+  \bibnamefont {Hatch}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {Christopher~J.}\ \bibnamefont {Howard}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Group-theoretical analysis of octahedral tilting in
+  ferroelectric perovskites}},}\ }\href {\doibase 10.1107/S0108768102015756}
+  {\bibfield  {journal} {\bibinfo  {journal} {Acta Crystallographica Section
+  B}\ }\textbf {\bibinfo {volume} {58}},\ \bibinfo {pages} {934--938} (\bibinfo
+  {year} {2002})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Angel}\ \emph {et~al.}(2005)\citenamefont {Angel},
+  \citenamefont {Zhao},\ and\ \citenamefont {Ross}}]{AngelPRL05}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
+  {Angel}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}}, \ and\
+  \bibinfo {author} {\bibfnamefont {N.~L.}\ \bibnamefont {Ross}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {General rules for predicting phase
+  transitions in perovskites due to octahedral tilting},}\ }\href {\doibase
+  10.1103/PhysRevLett.95.025503} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo {pages}
+  {025503} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ghosez}\ and\ \citenamefont
+  {Triscone}(2011)}]{GhosezNM11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Philippe}\
+  \bibnamefont {Ghosez}}\ and\ \bibinfo {author} {\bibfnamefont {Jean-Marc}\
+  \bibnamefont {Triscone}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Coupling of three lattice instabilities},}\ }\href {\doibase
+  10.1038/nmat3003} {\bibfield  {journal} {\bibinfo  {journal} {Nature
+  Materials}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {269--270}
+  (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Rondinelli}\ and\ \citenamefont
+  {Fennie}(2012)}]{RondinelliAM12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {James~M.}\
+  \bibnamefont {Rondinelli}}\ and\ \bibinfo {author} {\bibfnamefont {Craig~J.}\
+  \bibnamefont {Fennie}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Octahedral rotation-induced ferroelectricity in cation ordered
+  perovskites},}\ }\href {\doibase https://doi.org/10.1002/adma.201104674}
+  {\bibfield  {journal} {\bibinfo  {journal} {Advanced Materials}\ }\textbf
+  {\bibinfo {volume} {24}},\ \bibinfo {pages} {1961--1968} (\bibinfo {year}
+  {2012})},\ \Eprint
+  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/adma.201104674}
+  {https://onlinelibrary.wiley.com/doi/pdf/10.1002/adma.201104674} \BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Schick}\ \emph {et~al.}(2014)\citenamefont {Schick},
+  \citenamefont {Jiang}, \citenamefont {Saldana-Greco},\ and\ \citenamefont
+  {Rappe}}]{SchickPRB14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Joseph~T.}\
+  \bibnamefont {Schick}}, \bibinfo {author} {\bibfnamefont {Lai}\ \bibnamefont
+  {Jiang}}, \bibinfo {author} {\bibfnamefont {Diomedes}\ \bibnamefont
+  {Saldana-Greco}}, \ and\ \bibinfo {author} {\bibfnamefont {Andrew~M.}\
+  \bibnamefont {Rappe}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Coupling between octahedral rotations and local polar displacements in
+  $\mathrm{W}{\mathrm{o}}_{3}$/$\mathrm{Re}{\mathrm{o}}_{3}$ superlattices},}\
+  }\href {\doibase 10.1103/PhysRevB.89.195304} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo
+  {pages} {195304} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sim}\ and\ \citenamefont {Kim}(2014)}]{SimPRB14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Hyunsu}\ \bibnamefont
+  {Sim}}\ and\ \bibinfo {author} {\bibfnamefont {Bog~G.}\ \bibnamefont {Kim}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Octahedral tilting and
+  ferroelectricity in rb$a$nb${}_{2}$o${}_{7}$ ($a$ = bi, nd) from first
+  principles},}\ }\href {\doibase 10.1103/PhysRevB.89.144114} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {89}},\ \bibinfo {pages} {144114} (\bibinfo {year} {2014})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Lee}\ \emph {et~al.}(2017)\citenamefont {Lee},
+  \citenamefont {Chang}, \citenamefont {Huang}, \citenamefont {Guo},
+  \citenamefont {Gao}, \citenamefont {Chen}, \citenamefont {Cheong},\ and\
+  \citenamefont {Chu}}]{LeePRL17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont
+  {Lee}}, \bibinfo {author} {\bibfnamefont {C.-P.}\ \bibnamefont {Chang}},
+  \bibinfo {author} {\bibfnamefont {F.-T.}\ \bibnamefont {Huang}}, \bibinfo
+  {author} {\bibfnamefont {G.~Y.}\ \bibnamefont {Guo}}, \bibinfo {author}
+  {\bibfnamefont {B.}~\bibnamefont {Gao}}, \bibinfo {author} {\bibfnamefont
+  {C.~H.}\ \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {S.-W.}\
+  \bibnamefont {Cheong}}, \ and\ \bibinfo {author} {\bibfnamefont {M.-W.}\
+  \bibnamefont {Chu}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Hidden
+  antipolar order parameter and entangled n\'eel-type charged domain walls in
+  hybrid improper ferroelectrics},}\ }\href {\doibase
+  10.1103/PhysRevLett.119.157601} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {119}},\ \bibinfo {pages}
+  {157601} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2022)\citenamefont {Wang},
+  \citenamefont {Tang}, \citenamefont {Stengel}, \citenamefont {Xiang},
+  \citenamefont {An}, \citenamefont {Low},\ and\ \citenamefont
+  {Wu}}]{WangPRL22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Hongwei}\ \bibnamefont
+  {Wang}}, \bibinfo {author} {\bibfnamefont {Fujie}\ \bibnamefont {Tang}},
+  \bibinfo {author} {\bibfnamefont {Massimiliano}\ \bibnamefont {Stengel}},
+  \bibinfo {author} {\bibfnamefont {Hongjun}\ \bibnamefont {Xiang}}, \bibinfo
+  {author} {\bibfnamefont {Qi}~\bibnamefont {An}}, \bibinfo {author}
+  {\bibfnamefont {Tony}\ \bibnamefont {Low}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Xifan}\ \bibnamefont {Wu}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Convert widespread paraelectric perovskite to
+  ferroelectrics},}\ }\href {\doibase 10.1103/PhysRevLett.128.197601}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {128}},\ \bibinfo {pages} {197601} (\bibinfo {year}
+  {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2022)\citenamefont {Zhou},
+  \citenamefont {Dong}, \citenamefont {Shan}, \citenamefont {Ji},\ and\
+  \citenamefont {Zhang}}]{ZhouPRB22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Ying}\ \bibnamefont
+  {Zhou}}, \bibinfo {author} {\bibfnamefont {Shuai}\ \bibnamefont {Dong}},
+  \bibinfo {author} {\bibfnamefont {Changxun}\ \bibnamefont {Shan}}, \bibinfo
+  {author} {\bibfnamefont {Ke}~\bibnamefont {Ji}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Junting}\ \bibnamefont {Zhang}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Two-dimensional ferroelectricity induced by
+  octahedral rotation distortion in perovskite oxides},}\ }\href {\doibase
+  10.1103/PhysRevB.105.075408} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {105}},\ \bibinfo {pages}
+  {075408} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gao}\ \emph {et~al.}(2023)\citenamefont {Gao},
+  \citenamefont {Paillard},\ and\ \citenamefont {Bellaiche}}]{GaoPRB23}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Lingyuan}\
+  \bibnamefont {Gao}}, \bibinfo {author} {\bibfnamefont {Charles}\ \bibnamefont
+  {Paillard}}, \ and\ \bibinfo {author} {\bibfnamefont {Laurent}\ \bibnamefont
+  {Bellaiche}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Photoinduced
+  control of ferroelectricity in hybrid-improper ferroelectric
+  superlattices},}\ }\href {\doibase 10.1103/PhysRevB.107.104109} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
+  {107}},\ \bibinfo {pages} {104109} (\bibinfo {year} {2023})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Khomskii}(2009)}]{KhomskiiPhys09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Daniel}\ \bibnamefont
+  {Khomskii}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Classifying
+  multiferroics: Mechanisms and effects},}\ }\href {\doibase
+  10.1103/Physics.2.20} {\bibfield  {journal} {\bibinfo  {journal} {Physics}\
+  }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {20} (\bibinfo {year}
+  {2009})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Benedek}\ and\ \citenamefont
+  {Fennie}(2011)}]{BenedekPRL11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Nicole~A.}\
+  \bibnamefont {Benedek}}\ and\ \bibinfo {author} {\bibfnamefont {Craig~J.}\
+  \bibnamefont {Fennie}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Hybrid improper ferroelectricity: A mechanism for controllable
+  polarization-magnetization coupling},}\ }\href {\doibase
+  10.1103/PhysRevLett.106.107204} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {106}},\ \bibinfo {pages}
+  {107204} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2014)\citenamefont {Yang},
+  \citenamefont {\'I\~niguez}, \citenamefont {Mao},\ and\ \citenamefont
+  {Bellaiche}}]{YangPRL14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Yurong}\ \bibnamefont
+  {Yang}}, \bibinfo {author} {\bibfnamefont {Jorge}\ \bibnamefont
+  {\'I\~niguez}}, \bibinfo {author} {\bibfnamefont {Ai-Jie}\ \bibnamefont
+  {Mao}}, \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
+  {Bellaiche}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Prediction of
+  a novel magnetoelectric switching mechanism in multiferroics},}\ }\href
+  {\doibase 10.1103/PhysRevLett.112.057202} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo
+  {pages} {057202} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ye}\ \emph {et~al.}(2018)\citenamefont {Ye},
+  \citenamefont {Wang}, \citenamefont {Sheng}, \citenamefont {Hoffmann},
+  \citenamefont {Gu}, \citenamefont {Xiang}, \citenamefont {Tian},
+  \citenamefont {Molaison}, \citenamefont {dos Santos}, \citenamefont
+  {Matsuda}, \citenamefont {Chakoumakos}, \citenamefont {Fernandez-Baca},
+  \citenamefont {Tong}, \citenamefont {Gao}, \citenamefont {Kim},\ and\
+  \citenamefont {Cheong}}]{YePRB18}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Feng}\ \bibnamefont
+  {Ye}}, \bibinfo {author} {\bibfnamefont {Jinchen}\ \bibnamefont {Wang}},
+  \bibinfo {author} {\bibfnamefont {Jieming}\ \bibnamefont {Sheng}}, \bibinfo
+  {author} {\bibfnamefont {C.}~\bibnamefont {Hoffmann}}, \bibinfo {author}
+  {\bibfnamefont {T.}~\bibnamefont {Gu}}, \bibinfo {author} {\bibfnamefont
+  {H.~J.}\ \bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont {Wei}\
+  \bibnamefont {Tian}}, \bibinfo {author} {\bibfnamefont {J.~J.}\ \bibnamefont
+  {Molaison}}, \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont {dos
+  Santos}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Matsuda}},
+  \bibinfo {author} {\bibfnamefont {B.~C.}\ \bibnamefont {Chakoumakos}},
+  \bibinfo {author} {\bibfnamefont {J.~A.}\ \bibnamefont {Fernandez-Baca}},
+  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Tong}}, \bibinfo {author}
+  {\bibfnamefont {Bin}\ \bibnamefont {Gao}}, \bibinfo {author} {\bibfnamefont
+  {Jae~Wook}\ \bibnamefont {Kim}}, \ and\ \bibinfo {author} {\bibfnamefont
+  {S.-W.}\ \bibnamefont {Cheong}},\ }\bibfield  {title} {\enquote {\bibinfo
+  {title} {Soft antiphase tilt of oxygen octahedra in the hybrid improper
+  multiferroic
+  ${\mathrm{ca}}_{3}{\mathrm{mn}}_{1.9}{\mathrm{ti}}_{0.1}{\mathrm{o}}_{7}$},}\
+  }\href {\doibase 10.1103/PhysRevB.97.041112} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
+  {pages} {041112} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph
+  {et~al.}(2020{\natexlab{a}})\citenamefont {Zhang}, \citenamefont {Shen},
+  \citenamefont {Wang}, \citenamefont {Ji}, \citenamefont {Zhou}, \citenamefont
+  {Wang}, \citenamefont {Huang},\ and\ \citenamefont {Lu}}]{ZhangPRL20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Junting}\ \bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {Xiaofan}\ \bibnamefont {Shen}},
+  \bibinfo {author} {\bibfnamefont {Yancheng}\ \bibnamefont {Wang}}, \bibinfo
+  {author} {\bibfnamefont {Chao}\ \bibnamefont {Ji}}, \bibinfo {author}
+  {\bibfnamefont {Ying}\ \bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont
+  {Jianli}\ \bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {Fengzhen}\
+  \bibnamefont {Huang}}, \ and\ \bibinfo {author} {\bibfnamefont {Xiaomei}\
+  \bibnamefont {Lu}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Design
+  of two-dimensional multiferroics with direct polarization-magnetization
+  coupling},}\ }\href {\doibase 10.1103/PhysRevLett.125.017601} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {125}},\ \bibinfo {pages} {017601} (\bibinfo {year}
+  {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph
+  {et~al.}(2020{\natexlab{b}})\citenamefont {Zhang}, \citenamefont {Wang},\
+  and\ \citenamefont {Ghosez}}]{ZhangYajunPRL20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Yajun}\ \bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {Jie}\ \bibnamefont {Wang}}, \
+  and\ \bibinfo {author} {\bibfnamefont {Philippe}\ \bibnamefont {Ghosez}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Unraveling the suppression
+  of oxygen octahedra rotations in ${A}_{3}{B}_{2}{\mathrm{o}}_{7}$
+  ruddlesden-popper compounds: Engineering multiferroicity and beyond},}\
+  }\href {\doibase 10.1103/PhysRevLett.125.157601} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\
+  \bibinfo {pages} {157601} (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2021)\citenamefont {Zhou},
+  \citenamefont {Chen}, \citenamefont {Wu}, \citenamefont {Shen}, \citenamefont
+  {Wang}, \citenamefont {Zhang},\ and\ \citenamefont {Sun}}]{ZhouPRB21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Ying}\ \bibnamefont
+  {Zhou}}, \bibinfo {author} {\bibfnamefont {Zefeng}\ \bibnamefont {Chen}},
+  \bibinfo {author} {\bibfnamefont {Zongshuo}\ \bibnamefont {Wu}}, \bibinfo
+  {author} {\bibfnamefont {Xiaofan}\ \bibnamefont {Shen}}, \bibinfo {author}
+  {\bibfnamefont {Jianli}\ \bibnamefont {Wang}}, \bibinfo {author}
+  {\bibfnamefont {Junting}\ \bibnamefont {Zhang}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Hui}\ \bibnamefont {Sun}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Hybrid improper ferroelectricity and magnetoelectric
+  coupling in a two-dimensional perovskite oxide},}\ }\href {\doibase
+  10.1103/PhysRevB.103.224409} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo {pages}
+  {224409} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2022)\citenamefont {Zhang},
+  \citenamefont {Zhou}, \citenamefont {Wang}, \citenamefont {Shen},
+  \citenamefont {Wang},\ and\ \citenamefont {Lu}}]{ZhangPRL22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Junting}\ \bibnamefont
+  {Zhang}}, \bibinfo {author} {\bibfnamefont {Ying}\ \bibnamefont {Zhou}},
+  \bibinfo {author} {\bibfnamefont {Fan}\ \bibnamefont {Wang}}, \bibinfo
+  {author} {\bibfnamefont {Xiaofan}\ \bibnamefont {Shen}}, \bibinfo {author}
+  {\bibfnamefont {Jianli}\ \bibnamefont {Wang}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Xiaomei}\ \bibnamefont {Lu}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Coexistence and coupling of spin-induced ferroelectricity
+  and ferromagnetism in perovskites},}\ }\href {\doibase
+  10.1103/PhysRevLett.129.117603} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {129}},\ \bibinfo {pages}
+  {117603} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Amat}\ \emph {et~al.}(2014)\citenamefont {Amat},
+  \citenamefont {Mosconi}, \citenamefont {Ronca}, \citenamefont {Quarti},
+  \citenamefont {Umari}, \citenamefont {Nazeeruddin}, \citenamefont {Gratzel},\
+  and\ \citenamefont {De~Angelis}}]{AmatNL14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Anna}\ \bibnamefont
+  {Amat}}, \bibinfo {author} {\bibfnamefont {Edoardo}\ \bibnamefont {Mosconi}},
+  \bibinfo {author} {\bibfnamefont {Enrico}\ \bibnamefont {Ronca}}, \bibinfo
+  {author} {\bibfnamefont {Claudio}\ \bibnamefont {Quarti}}, \bibinfo {author}
+  {\bibfnamefont {Paolo}\ \bibnamefont {Umari}}, \bibinfo {author}
+  {\bibfnamefont {Md.~K.}\ \bibnamefont {Nazeeruddin}}, \bibinfo {author}
+  {\bibfnamefont {Michael}\ \bibnamefont {Gratzel}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Filippo}\ \bibnamefont {De~Angelis}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Cation-induced band-gap tuning in organohalide
+  perovskites: Interplay of spin-orbit coupling and octahedra tilting},}\
+  }\href {\doibase 10.1021/nl5012992} {\bibfield  {journal} {\bibinfo
+  {journal} {Nano Letters}\ }\textbf {\bibinfo {volume} {14}},\ \bibinfo
+  {pages} {3608--3616} (\bibinfo {year} {2014})},\ \bibinfo {note} {pMID:
+  24797342},\ \Eprint {http://arxiv.org/abs/https://doi.org/10.1021/nl5012992}
+  {https://doi.org/10.1021/nl5012992} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Krach}\ \emph {et~al.}(2023)\citenamefont {Krach},
+  \citenamefont {Forero-Correa}, \citenamefont {Biega}, \citenamefont
+  {Reyes-Lillo},\ and\ \citenamefont {Leppert}}]{KrachJPCM23}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Sonja}\ \bibnamefont
+  {Krach}}, \bibinfo {author} {\bibfnamefont {Nicol\'as}\ \bibnamefont
+  {Forero-Correa}}, \bibinfo {author} {\bibfnamefont {Raisa-Ioana}\
+  \bibnamefont {Biega}}, \bibinfo {author} {\bibfnamefont {Sebastian~E}\
+  \bibnamefont {Reyes-Lillo}}, \ and\ \bibinfo {author} {\bibfnamefont {Linn}\
+  \bibnamefont {Leppert}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Emergence of rashba-/dresselhaus effects in ruddlesden popper halide
+  perovskites with octahedral rotations},}\ }\href {\doibase
+  10.1088/1361-648X/acbd0c} {\bibfield  {journal} {\bibinfo  {journal} {Journal
+  of Physics: Condensed Matter}\ }\textbf {\bibinfo {volume} {35}},\ \bibinfo
+  {pages} {174001} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Balachandran}\ and\ \citenamefont
+  {Rondinelli}(2013)}]{BalachandranPRB13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Prasanna~V.}\
+  \bibnamefont {Balachandran}}\ and\ \bibinfo {author} {\bibfnamefont
+  {James~M.}\ \bibnamefont {Rondinelli}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Interplay of octahedral rotations and breathing
+  distortions in charge-ordering perovskite oxides},}\ }\href {\doibase
+  10.1103/PhysRevB.88.054101} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {88}},\ \bibinfo {pages} {054101}
+  (\bibinfo {year} {2013})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Aguado-Puente}\ \emph {et~al.}(2011)\citenamefont
+  {Aguado-Puente}, \citenamefont {Garc\'{\i}a-Fern\'andez},\ and\ \citenamefont
+  {Junquera}}]{Aguado-PuentePRL11}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Pablo}\ \bibnamefont
+  {Aguado-Puente}}, \bibinfo {author} {\bibfnamefont {Pablo}\ \bibnamefont
+  {Garc\'{\i}a-Fern\'andez}}, \ and\ \bibinfo {author} {\bibfnamefont {Javier}\
+  \bibnamefont {Junquera}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Interplay of couplings between antiferrodistortive, ferroelectric, and
+  strain degrees of freedom in monodomain
+  ${\mathrm{pbtio}}_{3}/{\mathrm{srtio}}_{3}$ superlattices},}\ }\href
+  {\doibase 10.1103/PhysRevLett.107.217601} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {107}},\ \bibinfo
+  {pages} {217601} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jia}\ \emph {et~al.}(2022)\citenamefont {Jia},
+  \citenamefont {He}, \citenamefont {Akhtar}, \citenamefont {Herranz},\ and\
+  \citenamefont {Pruneda}}]{JiaPRB22}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jiahui}\ \bibnamefont
+  {Jia}}, \bibinfo {author} {\bibfnamefont {Xu}~\bibnamefont {He}}, \bibinfo
+  {author} {\bibfnamefont {Arsalan}\ \bibnamefont {Akhtar}}, \bibinfo {author}
+  {\bibfnamefont {Gervasi}\ \bibnamefont {Herranz}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Miguel}\ \bibnamefont {Pruneda}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Dynamic control of octahedral rotation in
+  perovskites by defect engineering},}\ }\href {\doibase
+  10.1103/PhysRevB.105.224112} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {105}},\ \bibinfo {pages}
+  {224112} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Xiang}\ \emph {et~al.}(2017)\citenamefont {Xiang},
+  \citenamefont {Guennou}, \citenamefont {\'I\~niguez}, \citenamefont
+  {Kreisel},\ and\ \citenamefont {Bellaiche}}]{XiangPRB17}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont
+  {Xiang}}, \bibinfo {author} {\bibfnamefont {Mael}\ \bibnamefont {Guennou}},
+  \bibinfo {author} {\bibfnamefont {Jorge}\ \bibnamefont {\'I\~niguez}},
+  \bibinfo {author} {\bibfnamefont {Jens}\ \bibnamefont {Kreisel}}, \ and\
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Rules and mechanisms governing
+  octahedral tilts in perovskites under pressure},}\ }\href {\doibase
+  10.1103/PhysRevB.96.054102} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {054102}
+  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Johnson}\ \emph {et~al.}(2020)\citenamefont
+  {Johnson}, \citenamefont {Khalyavin}, \citenamefont {Manuel}, \citenamefont
+  {Zhang}, \citenamefont {Yamaura},\ and\ \citenamefont
+  {Belik}}]{JohnsonPRL20}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont
+  {Johnson}}, \bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
+  {Khalyavin}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Manuel}},
+  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zhang}}, \bibinfo
+  {author} {\bibfnamefont {K.}~\bibnamefont {Yamaura}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Belik}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Emergence of a magnetostructural dipolar glass
+  in the quadruple perovskite
+  ${\mathrm{dy}}_{1\ensuremath{-}\ensuremath{\delta}}{\mathrm{mn}}_{7+\ensuremath{\delta}}{\mathrm{o}}_{12}$},}\
+  }\href {\doibase 10.1103/PhysRevLett.125.097601} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\
+  \bibinfo {pages} {097601} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ogawa}\ \emph {et~al.}(2012)\citenamefont {Ogawa},
+  \citenamefont {Ogimoto}, \citenamefont {Ida}, \citenamefont {Nomura},
+  \citenamefont {Arita},\ and\ \citenamefont {Miyano}}]{OgawaPRL12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Naoki}\ \bibnamefont
+  {Ogawa}}, \bibinfo {author} {\bibfnamefont {Yasushi}\ \bibnamefont
+  {Ogimoto}}, \bibinfo {author} {\bibfnamefont {Yoshiaki}\ \bibnamefont {Ida}},
+  \bibinfo {author} {\bibfnamefont {Yusuke}\ \bibnamefont {Nomura}}, \bibinfo
+  {author} {\bibfnamefont {Ryotaro}\ \bibnamefont {Arita}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {Kenjiro}\ \bibnamefont {Miyano}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Polar antiferromagnets produced with
+  orbital order},}\ }\href {\doibase 10.1103/PhysRevLett.108.157603} {\bibfield
+   {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {108}},\ \bibinfo {pages} {157603} (\bibinfo {year}
+  {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2019)\citenamefont {Chen},
+  \citenamefont {Xu}, \citenamefont {Tian}, \citenamefont {Xiang},
+  \citenamefont {\'I\~niguez}, \citenamefont {Yang},\ and\ \citenamefont
+  {Bellaiche}}]{ChenPRL19}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Lan}\ \bibnamefont
+  {Chen}}, \bibinfo {author} {\bibfnamefont {Changsong}\ \bibnamefont {Xu}},
+  \bibinfo {author} {\bibfnamefont {Hao}\ \bibnamefont {Tian}}, \bibinfo
+  {author} {\bibfnamefont {Hongjun}\ \bibnamefont {Xiang}}, \bibinfo {author}
+  {\bibfnamefont {Jorge}\ \bibnamefont {\'I\~niguez}}, \bibinfo {author}
+  {\bibfnamefont {Yurong}\ \bibnamefont {Yang}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Electric-field control of magnetization, jahn-teller
+  distortion, and orbital ordering in ferroelectric ferromagnets},}\ }\href
+  {\doibase 10.1103/PhysRevLett.122.247701} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo
+  {pages} {247701} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2021)\citenamefont {Huang},
+  \citenamefont {Liu}, \citenamefont {Shao}, \citenamefont {Feng},
+  \citenamefont {Zhang}, \citenamefont {Fu}, \citenamefont {Lee}, \citenamefont
+  {Shen}, \citenamefont {Chuang},\ and\ \citenamefont {Liu}}]{HuangPRB21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Wencheng}\
+  \bibnamefont {Huang}}, \bibinfo {author} {\bibfnamefont {Wanling}\
+  \bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont {Yu-Cheng}\
+  \bibnamefont {Shao}}, \bibinfo {author} {\bibfnamefont {Xuefei}\ \bibnamefont
+  {Feng}}, \bibinfo {author} {\bibfnamefont {Nian}\ \bibnamefont {Zhang}},
+  \bibinfo {author} {\bibfnamefont {Jiamin}\ \bibnamefont {Fu}}, \bibinfo
+  {author} {\bibfnamefont {Jenn-Min}\ \bibnamefont {Lee}}, \bibinfo {author}
+  {\bibfnamefont {Dawei}\ \bibnamefont {Shen}}, \bibinfo {author}
+  {\bibfnamefont {Yi-De}\ \bibnamefont {Chuang}}, \ and\ \bibinfo {author}
+  {\bibfnamefont {Xiaosong}\ \bibnamefont {Liu}},\ }\bibfield  {title}
+  {\enquote {\bibinfo {title} {Enhanced orbital anisotropy through the
+  proximity to a $\mathrm{SrTi}{\mathrm{o}}_{3}$ layer in the perovskite
+  iridate superlattices},}\ }\href {\doibase 10.1103/PhysRevB.104.075156}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+  {volume} {104}},\ \bibinfo {pages} {075156} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Abarca~Morales}\ \emph {et~al.}(2023)\citenamefont
+  {Abarca~Morales}, \citenamefont {Siemann}, \citenamefont {Zivanovic},
+  \citenamefont {Murgatroyd}, \citenamefont {Markovi\ifmmode~\acute{c}\else
+  \'{c}\fi{}}, \citenamefont {Edwards}, \citenamefont {Hooley}, \citenamefont
+  {Sokolov}, \citenamefont {Kikugawa}, \citenamefont {Cacho}, \citenamefont
+  {Watson}, \citenamefont {Kim}, \citenamefont {Hicks}, \citenamefont
+  {Mackenzie},\ and\ \citenamefont {King}}]{MoralesPRL23}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Edgar}\ \bibnamefont
+  {Abarca~Morales}}, \bibinfo {author} {\bibfnamefont {Gesa-R.}\ \bibnamefont
+  {Siemann}}, \bibinfo {author} {\bibfnamefont {Andela}\ \bibnamefont
+  {Zivanovic}}, \bibinfo {author} {\bibfnamefont {Philip A.~E.}\ \bibnamefont
+  {Murgatroyd}}, \bibinfo {author} {\bibfnamefont {Igor}\ \bibnamefont
+  {Markovi\ifmmode~\acute{c}\else \'{c}\fi{}}}, \bibinfo {author}
+  {\bibfnamefont {Brendan}\ \bibnamefont {Edwards}}, \bibinfo {author}
+  {\bibfnamefont {Chris~A.}\ \bibnamefont {Hooley}}, \bibinfo {author}
+  {\bibfnamefont {Dmitry~A.}\ \bibnamefont {Sokolov}}, \bibinfo {author}
+  {\bibfnamefont {Naoki}\ \bibnamefont {Kikugawa}}, \bibinfo {author}
+  {\bibfnamefont {Cephise}\ \bibnamefont {Cacho}}, \bibinfo {author}
+  {\bibfnamefont {Matthew~D.}\ \bibnamefont {Watson}}, \bibinfo {author}
+  {\bibfnamefont {Timur~K.}\ \bibnamefont {Kim}}, \bibinfo {author}
+  {\bibfnamefont {Clifford~W.}\ \bibnamefont {Hicks}}, \bibinfo {author}
+  {\bibfnamefont {Andrew~P.}\ \bibnamefont {Mackenzie}}, \ and\ \bibinfo
+  {author} {\bibfnamefont {Phil D.~C.}\ \bibnamefont {King}},\ }\bibfield
+  {title} {\enquote {\bibinfo {title} {Hierarchy of lifshitz transitions in the
+  surface electronic structure of ${\mathrm{sr}}_{2}{\mathrm{ruo}}_{4}$ under
+  uniaxial compression},}\ }\href {\doibase 10.1103/PhysRevLett.130.096401}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
+  {\bibinfo {volume} {130}},\ \bibinfo {pages} {096401} (\bibinfo {year}
+  {2023})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carpenter}\ and\ \citenamefont
+  {Howard}(2009)}]{CarpenterAC09}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michael~A.}\
+  \bibnamefont {Carpenter}}\ and\ \bibinfo {author} {\bibfnamefont
+  {Christopher~J.}\ \bibnamefont {Howard}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Symmetry rules and strain/order-parameter relationships
+  for coupling between octahedral tilting and cooperative Jahn{--}Teller
+  transitions in {\it ABX}${\sb 3 }$perovskites. I. Theory}},}\ }\href
+  {\doibase 10.1107/S0108768109000974} {\bibfield  {journal} {\bibinfo
+  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo {volume}
+  {65}},\ \bibinfo {pages} {134--146} (\bibinfo {year} {2009})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Jahn}\ \emph {et~al.}(1937)\citenamefont {Jahn},
+  \citenamefont {Teller},\ and\ \citenamefont {Donnan}}]{JahnPRSL37}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.}\ \bibnamefont
+  {Jahn}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Teller}}, \ and\
+  \bibinfo {author} {\bibfnamefont {Frederick~George}\ \bibnamefont {Donnan}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Stability of polyatomic
+  molecules in degenerate electronic states - i?orbital degeneracy},}\ }\href
+  {\doibase 10.1098/rspa.1937.0142} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the Royal Society of London. Series A - Mathematical and
+  Physical Sciences}\ }\textbf {\bibinfo {volume} {161}},\ \bibinfo {pages}
+  {220--235} (\bibinfo {year} {1937})},\ \Eprint
+  {http://arxiv.org/abs/https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1937.0142}
+  {https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1937.0142}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jahn}\ and\ \citenamefont
+  {Bragg}(1938)}]{JahnPRSL38}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.}\ \bibnamefont
+  {Jahn}}\ and\ \bibinfo {author} {\bibfnamefont {William~Henry}\ \bibnamefont
+  {Bragg}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Stability of
+  polyatomic molecules in degenerate electronic states ii-spin degeneracy},}\
+  }\href {\doibase 10.1098/rspa.1938.0008} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the Royal Society of London. Series A -
+  Mathematical and Physical Sciences}\ }\textbf {\bibinfo {volume} {164}},\
+  \bibinfo {pages} {117--131} (\bibinfo {year} {1938})},\ \Eprint
+  {http://arxiv.org/abs/https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1938.0008}
+  {https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1938.0008}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {\"Opik}\ and\ \citenamefont
+  {Pryce}(1957)}]{OpikRS57}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
+  {\"Opik}}\ and\ \bibinfo {author} {\bibfnamefont {M.~H.~L.}\ \bibnamefont
+  {Pryce}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Studies of the
+  jahn-teller effect. i. a survey of the static problem},}\ }\href
+  {http://www.jstor.org/stable/100101} {\bibfield  {journal} {\bibinfo
+  {journal} {Proceedings of the Royal Society of London. Series A, Mathematical
+  and Physical Sciences}\ }\textbf {\bibinfo {volume} {238}},\ \bibinfo {pages}
+  {425--447} (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Sturge}(1968)}]{Sturge68}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.D.}\ \bibnamefont
+  {Sturge}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The jahn-teller
+  effect in solids},}\ \ }(\bibinfo  {publisher} {Academic Press},\ \bibinfo
+  {year} {1968})\ pp.\ \bibinfo {pages} {91--211}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Gehring}\ and\ \citenamefont
+  {Gehring}(1975)}]{GehringRPP75}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G~A}\ \bibnamefont
+  {Gehring}}\ and\ \bibinfo {author} {\bibfnamefont {K~A}\ \bibnamefont
+  {Gehring}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Co-operative
+  jahn-teller effects},}\ }\href {\doibase 10.1088/0034-4885/38/1/001}
+  {\bibfield  {journal} {\bibinfo  {journal} {Reports on Progress in Physics}\
+  }\textbf {\bibinfo {volume} {38}},\ \bibinfo {pages} {1} (\bibinfo {year}
+  {1975})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pavarini}(2016)}]{PavariniChap}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Eva}\ \bibnamefont
+  {Pavarini}},\ }\href {https://juser.fz-juelich.de/record/819465} {\emph
+  {\bibinfo {title} {{Q}uantum {M}aterials: {E}xperiments and {T}heory}}},\
+  edited by\ \bibinfo {editor} {\bibfnamefont {Eva}\ \bibnamefont {Pavarini}},
+  \bibinfo {editor} {\bibfnamefont {Erik}\ \bibnamefont {Koch}}, \bibinfo
+  {editor} {\bibfnamefont {Jeroen}\ \bibnamefont {van~den Brink}}, \ and\
+  \bibinfo {editor} {\bibfnamefont {George}\ \bibnamefont {Sawatzky}},\
+  \bibinfo {series} {Schriften des Forschungszentrums J\"ulich. Reihe modeling
+  and simulation}, Vol.~\bibinfo {volume} {6}\ (\bibinfo  {publisher}
+  {Forschungszentrum J\"ulich GmbH Zentralbibliothek, Verlag},\ \bibinfo
+  {address} {J\"ulich},\ \bibinfo {year} {2016})\ p.\ \bibinfo {pages} {420
+  S.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Khomskii}\ and\ \citenamefont
+  {Streltsov}(2021)}]{KhomskiiCR21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Daniel~I.}\
+  \bibnamefont {Khomskii}}\ and\ \bibinfo {author} {\bibfnamefont {Sergey~V.}\
+  \bibnamefont {Streltsov}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Orbital effects in solids: Basics, recent progress, and opportunities},}\
+  }\href {\doibase 10.1021/acs.chemrev.0c00579} {\bibfield  {journal} {\bibinfo
+   {journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {121}},\ \bibinfo
+  {pages} {2992--3030} (\bibinfo {year} {2021})},\ \bibinfo {note} {pMID:
+  33314912},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/acs.chemrev.0c00579}
+  {https://doi.org/10.1021/acs.chemrev.0c00579} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Goldschmidt}(1926)}]{Goldschmidt1926}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
+  {Goldschmidt}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The laws of
+  crystal chemistry},}\ }\href {\doibase 10.1007/BF01507527} {\bibfield
+  {journal} {\bibinfo  {journal} {Naturwissenschaften}\ }\textbf {\bibinfo
+  {volume} {14}},\ \bibinfo {pages} {477} (\bibinfo {year} {1926})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Kieslich}\ \emph {et~al.}(2015)\citenamefont
+  {Kieslich}, \citenamefont {Sun},\ and\ \citenamefont
+  {Cheetham}}]{KieslichCS15}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Kieslich}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sun}}, \
+  and\ \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Cheetham}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {An extended tolerance factor
+  approach for organic-inorganic perovskites},}\ }\href {\doibase
+  10.1039/C5SC00961H} {\bibfield  {journal} {\bibinfo  {journal} {Chem. Sci.}\
+  }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages} {3430} (\bibinfo {year}
+  {2015})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Garcia-Fernandez}\ \emph {et~al.}(2010)\citenamefont
+  {Garcia-Fernandez}, \citenamefont {Aramburu}, \citenamefont {Barriuso},\ and\
+  \citenamefont {Moreno}}]{garcia-fernandezJPCL10}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Garcia-Fernandez}}, \bibinfo {author} {\bibfnamefont {J.~a.}\ \bibnamefont
+  {Aramburu}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
+  {Barriuso}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Moreno}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Key role of
+  covalent bonding in octahedral tilting in perovskites},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Phys. Chem. Lett.}\ }\textbf
+  {\bibinfo {volume} {1}},\ \bibinfo {pages} {647} (\bibinfo {year}
+  {2010})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cammarata}\ and\ \citenamefont
+  {Rondinelli}(2014)}]{CammarataJCP14}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Antonio}\ \bibnamefont
+  {Cammarata}}\ and\ \bibinfo {author} {\bibfnamefont {James~M.}\ \bibnamefont
+  {Rondinelli}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Covalent
+  dependence of octahedral rotations in orthorhombic perovskite oxides}},}\
+  }\href {\doibase 10.1063/1.4895967} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+  {141}},\ \bibinfo {pages} {114704} (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/https://pubs.aip.org/aip/jcp/article-pdf/doi/10.1063/1.4895967/15484681/114704\_1\_online.pdf}
+  {https://pubs.aip.org/aip/jcp/article-pdf/doi/10.1063/1.4895967/15484681/114704\_1\_online.pdf}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lee}\ \emph {et~al.}(2016)\citenamefont {Lee},
+  \citenamefont {Bristowe}, \citenamefont {Lee}, \citenamefont {Lee},
+  \citenamefont {Bristowe}, \citenamefont {Cheetham},\ and\ \citenamefont
+  {Jang}}]{LeeCM16}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jung-Hoon}\
+  \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont {Nicholas~C.}\
+  \bibnamefont {Bristowe}}, \bibinfo {author} {\bibfnamefont {June~Ho}\
+  \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont {Sung-Hoon}\
+  \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont {Paul~D.}\ \bibnamefont
+  {Bristowe}}, \bibinfo {author} {\bibfnamefont {Anthony~K.}\ \bibnamefont
+  {Cheetham}}, \ and\ \bibinfo {author} {\bibfnamefont {Hyun~Myung}\
+  \bibnamefont {Jang}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Resolving the physical origin of octahedral tilting in halide
+  perovskites},}\ }\href {\doibase 10.1021/acs.chemmater.6b00968} {\bibfield
+  {journal} {\bibinfo  {journal} {Chemistry of Materials}\ }\textbf {\bibinfo
+  {volume} {28}},\ \bibinfo {pages} {4259--4266} (\bibinfo {year} {2016})},\
+  \Eprint {http://arxiv.org/abs/https://doi.org/10.1021/acs.chemmater.6b00968}
+  {https://doi.org/10.1021/acs.chemmater.6b00968} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yoshida}\ \emph {et~al.}(2021)\citenamefont
+  {Yoshida}, \citenamefont {Akamatsu},\ and\ \citenamefont
+  {Hayashi}}]{YoshidaPRL21}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Suguru}\ \bibnamefont
+  {Yoshida}}, \bibinfo {author} {\bibfnamefont {Hirofumi}\ \bibnamefont
+  {Akamatsu}}, \ and\ \bibinfo {author} {\bibfnamefont {Katsuro}\ \bibnamefont
+  {Hayashi}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Electronic
+  origin of non-zone-center phonon condensation: Octahedral rotation as a case
+  study},}\ }\href {\doibase 10.1103/PhysRevLett.127.215701} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {127}},\ \bibinfo {pages} {215701} (\bibinfo {year}
+  {2021})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Herzberg}\ and\ \citenamefont
+  {Teller}(1933)}]{HerzbergZPC33}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Herzberg}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Teller}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Schwingungsstruktur der elektronen\"uberg\"ange bei mehratomigen
+  molek\"ulen},}\ }\href {\doibase doi:10.1515/zpch-1933-2136} {\bibfield
+  {journal} {\bibinfo  {journal} {Zeitschrift f\"ur Physikalische Chemie}\
+  }\textbf {\bibinfo {volume} {21B}},\ \bibinfo {pages} {410--446} (\bibinfo
+  {year} {1933})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bersuker}(1966)}]{BersukerPL66}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.B.}\ \bibnamefont
+  {Bersuker}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {On the origin
+  of ferroelectricity in perovskite-type crystals},}\ }\href {\doibase
+  https://doi.org/10.1016/0031-9163(66)91127-9} {\bibfield  {journal} {\bibinfo
+   {journal} {Physics Letters}\ }\textbf {\bibinfo {volume} {20}},\ \bibinfo
+  {pages} {589--590} (\bibinfo {year} {1966})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kristoffel}\ and\ \citenamefont
+  {Konsin}(1967)}]{KristoffelPSSB67}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
+  {Kristoffel}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
+  {Konsin}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Pseudo-jab-teller effect and second order phase transitions in crystals},}\
+  }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys. Status
+  Solidi B}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {K39}
+  (\bibinfo {year} {1967})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Pearson}(1983)}]{PearsonJMS83}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
+  {Pearson}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The
+  second-order jahn-teller effect},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Mol. Struct.: THEOCHEM}\ }\textbf {\bibinfo {volume}
+  {103}},\ \bibinfo {pages} {25} (\bibinfo {year} {1983})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Fulton}\ and\ \citenamefont
+  {Gouterman}(2004)}]{FultonJCP04}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Robert~L.}\
+  \bibnamefont {Fulton}}\ and\ \bibinfo {author} {\bibfnamefont {Martin}\
+  \bibnamefont {Gouterman}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Vibronic Coupling. I. Mathematical Treatment for Two Electronic States}},}\
+  }\href {\doibase 10.1063/1.1701181} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo {volume}
+  {35}},\ \bibinfo {pages} {1059--1071} (\bibinfo {year} {2004})},\ \Eprint
+  {http://arxiv.org/abs/https://pubs.aip.org/aip/jcp/article-pdf/35/3/1059/8125554/1059\_1\_online.pdf}
+  {https://pubs.aip.org/aip/jcp/article-pdf/35/3/1059/8125554/1059\_1\_online.pdf}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bersuker}(2013)}]{BersukerCR13}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Isaac~B.}\
+  \bibnamefont {Bersuker}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Pseudo-jahn teller effect: A two-state paradigm in formation, deformation,
+  and transformation of molecular systems and solids},}\ }\href {\doibase
+  10.1021/cr300279n} {\bibfield  {journal} {\bibinfo  {journal} {Chemical
+  Reviews}\ }\textbf {\bibinfo {volume} {113}},\ \bibinfo {pages} {1351--1390}
+  (\bibinfo {year} {2013})},\ \bibinfo {note} {pMID: 23301718},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/cr300279n}
+  {https://doi.org/10.1021/cr300279n} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bethe}(1929)}]{BetheAP29}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Bethe}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Termaufspaltung
+  in kristallen},}\ }\href {\doibase https://doi.org/10.1002/andp.19293950202}
+  {\bibfield  {journal} {\bibinfo  {journal} {Annalen der Physik}\ }\textbf
+  {\bibinfo {volume} {395}},\ \bibinfo {pages} {133--208} (\bibinfo {year}
+  {1929})},\ \Eprint
+  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/andp.19293950202}
+  {https://onlinelibrary.wiley.com/doi/pdf/10.1002/andp.19293950202}
+  \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Van~Vleck}(1932)}]{VanVleckPR32}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
+  {Van~Vleck}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Theory of the
+  variations in paramagnetic anisotropy among different salts of the iron
+  group},}\ }\href {\doibase 10.1103/PhysRev.41.208} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {41}},\
+  \bibinfo {pages} {208--215} (\bibinfo {year} {1932})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Paxton}(2009{\natexlab{a}})}]{PaxtonNotes}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Anthony~T.}\
+  \bibnamefont {Paxton}},\ }\href {https://tonypaxton.org/Notes/TB.pdf} {\emph
+  {\bibinfo {title} {Multiscale Simulation Methods in Molecular Sciences}}},\
+  edited by\ \bibinfo {editor} {\bibfnamefont {J.}~\bibnamefont {Grotendorst}},
+  \bibinfo {editor} {\bibfnamefont {N.}~\bibnamefont {Attig}}, \bibinfo
+  {editor} {\bibfnamefont {S.}~\bibnamefont {Bl\"ugel}}, \ and\ \bibinfo
+  {editor} {\bibfnamefont {D.}~\bibnamefont {Marx}},\ Vol.~\bibinfo {volume}
+  {42}\ (\bibinfo  {publisher} {Academic Press, Institute for Advanced
+  Simulation, Forschungszentrum J\"ulich},\ \bibinfo {year} {2009})\ pp.\
+  \bibinfo {pages} {145--176}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Carter}\ \emph {et~al.}(2012)\citenamefont {Carter},
+  \citenamefont {Shankar}, \citenamefont {Zeb},\ and\ \citenamefont
+  {Kee}}]{CarterPRB12}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jean-Michel}\
+  \bibnamefont {Carter}}, \bibinfo {author} {\bibfnamefont {V.~Vijay}\
+  \bibnamefont {Shankar}}, \bibinfo {author} {\bibfnamefont {M.~Ahsan}\
+  \bibnamefont {Zeb}}, \ and\ \bibinfo {author} {\bibfnamefont {Hae-Young}\
+  \bibnamefont {Kee}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Semimetal and topological insulator in perovskite iridates},}\ }\href
+  {\doibase 10.1103/PhysRevB.85.115105} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo
+  {pages} {115105} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ivanic}\ and\ \citenamefont
+  {Ruedenberg}(1996)}]{IvanicJPC96}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Joseph}\ \bibnamefont
+  {Ivanic}}\ and\ \bibinfo {author} {\bibfnamefont {Klaus}\ \bibnamefont
+  {Ruedenberg}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Rotation
+  matrices for real spherical harmonics. direct determination by recursion},}\
+  }\href {\doibase 10.1021/jp953350u} {\bibfield  {journal} {\bibinfo
+  {journal} {The Journal of Physical Chemistry}\ }\textbf {\bibinfo {volume}
+  {100}},\ \bibinfo {pages} {6342--6347} (\bibinfo {year} {1996})},\ \Eprint
+  {http://arxiv.org/abs/https://doi.org/10.1021/jp953350u}
+  {https://doi.org/10.1021/jp953350u} \BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Finnis}\ \emph {et~al.}(1998)\citenamefont {Finnis},
+  \citenamefont {Paxton}, \citenamefont {Methfessel},\ and\ \citenamefont {van
+  Schilfgaarde}}]{FinnisPRL98}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
+  {Finnis}}, \bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont {Paxton}},
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Methfessel}}, \ and\
+  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {van Schilfgaarde}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Crystal structures of
+  zirconia from first principles and self-consistent tight binding},}\ }\href
+  {\doibase 10.1103/PhysRevLett.81.5149} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
+  {pages} {5149--5152} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Paxton}\ and\ \citenamefont
+  {Finnis}(2008)}]{PaxtonPRB08}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Anthony~T.}\
+  \bibnamefont {Paxton}}\ and\ \bibinfo {author} {\bibfnamefont {Michael~W.}\
+  \bibnamefont {Finnis}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Magnetic tight binding and the iron-chromium enthalpy anomaly},}\ }\href
+  {\doibase 10.1103/PhysRevB.77.024428} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
+  {pages} {024428} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ewald}(1921)}]{Ewald1921}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~P.}\ \bibnamefont
+  {Ewald}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Die berechnung
+  optischer und elektrostatischer gitterpotentiale},}\ }\href {\doibase
+  https://doi.org/10.1002/andp.19213690304} {\bibfield  {journal} {\bibinfo
+  {journal} {Annalen der Physik}\ }\textbf {\bibinfo {volume} {369}},\ \bibinfo
+  {pages} {253--287} (\bibinfo {year} {1921})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Paxton}(2009{\natexlab{b}})}]{Questaal}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Tony}\ \bibnamefont
+  {Paxton}},\ }\href {https://www.questaal.org/docs/code/tbe/} {\enquote
+  {\bibinfo {title} {{TBE code}},}\ } (\bibinfo {year}
+  {2009}{\natexlab{b}})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Liechtenstein}\ \emph {et~al.}(1995)\citenamefont
+  {Liechtenstein}, \citenamefont {Anisimov},\ and\ \citenamefont
+  {Zaanen}}]{LiechtensteinPRB95}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont
+  {Liechtenstein}}, \bibinfo {author} {\bibfnamefont {V.~I.}\ \bibnamefont
+  {Anisimov}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Zaanen}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Density-functional theory and strong interactions: Orbital ordering in
+  mott-hubbard insulators},}\ }\href {\doibase 10.1103/PhysRevB.52.R5467}
+  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo
+  {volume} {52}},\ \bibinfo {pages} {R5467--R5470} (\bibinfo {year}
+  {1995})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Slater}\ and\ \citenamefont
+  {Koster}(1954)}]{SlaterPR54}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~C.}\ \bibnamefont
+  {Slater}}\ and\ \bibinfo {author} {\bibfnamefont {G.~F.}\ \bibnamefont
+  {Koster}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Simplified lcao
+  method for the periodic potential problem},}\ }\href {\doibase
+  10.1103/PhysRev.94.1498} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev.}\ }\textbf {\bibinfo {volume} {94}},\ \bibinfo {pages} {1498--1524}
+  (\bibinfo {year} {1954})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Inc.}(2023)}]{Mathematica}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Wolfram~Research{,}}\
+  \bibnamefont {Inc.}},\ }\href {https://www.wolfram.com/mathematica} {\enquote
+  {\bibinfo {title} {Mathematica, {V}ersion 13.3},}\ } (\bibinfo {year}
+  {2023}),\ \bibinfo {note} {champaign, IL, 2023}\BibitemShut {NoStop}%
+\end{thebibliography}%
 

### 2023-12-27 manuscript/prb-submitted/paper.tex
reply added

--- 2023-12-16 manuscript/prb-submitted/paper.tex
@@
 ($D_4=\frac{3a}{160q_o} \Delta$) and 
-we can estimate its value from realistic values of $\Delta$ for a given octahedron of size $a$ and ion charge $q_o$. 
+we can estimate its value from realistic values of $\Delta$ for a given octahedron of size $a$ and ion charge $-q_o$. 
 Assuming $a=7.0$ bohr and $q_o=2e$ ($e$ being the elementary charge),
@@
 depends on their relative charges.
-Using the charge neutrality $q_B=3q_o-q_A$,
+Using the charge neutrality $q_B=3q_o-q_A$ (remember that we take anion charge to be $-q_o$),
 we can write 
@@
 let us briefly describe 
-the kind of behaviour that would indicate a JT instability 
-against the tilting and rotations of the octahedra,
+the kind of behaviour that would indicate a JT instab against the tilting and rotations of the octahedra,
 and how it relates to the standard JT problem.
@@
 than the elastic energy associated with the changes in the unit cell volume.
-In contrast to 
-%hypothetical 
-elongations or 
-compressions---$a\delta_1,a\delta_2$ 
-of an octahedron along two of its axes---where the 
- the unit cell volume changes
-as $\sim a^3\left(\delta_1+\delta_1\right)$
-and thus the elastic energy approximately goes
-as $\sim\left(\delta_1+\delta_1\right)^2$,
-the unit cell volume
-in case of octahedral rotation and tilting
+\rev{Here, the unit cell volume
  depends on the ``distortions'' $\alpha,\beta$ 
@@
 and, at $\alpha,\beta\ll1$,
-it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$
-leading to a \emph{quartic} elastic energy that should roughly behave as
-$\sim\left(\alpha ^2+\beta ^2\right)^2$.
-So, the behaviour we are looking for in the electronic spectrum 
+it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$.
+The elastic energy in the harmonic approximation thus goes
+as $\sim\left(\alpha ^2+\beta ^2\right)^2$,
+which is \emph{quartic} in $\alpha,\beta$.
+So, 
+in contrast to the case of
+elongations or 
+compressions  
+of the octahedra~\cite{KhomskiiCR21},
+the behavior we are looking for in the electronic spectrum 
 is not linear
@@
 matches to the standard JT problem.
+}
+
+\com{In contrast to 
+%hypothetical 
+elongations or 
+compressions---$a\delta_1,a\delta_2$ 
+of an octahedron along two of its axes---where the 
+ the unit cell volume changes
+as $\sim a^3\left(\delta_1+\delta_2\right)$
+and thus
+the elastic energy in the harmonic approximation goes
+as $\sim\left(\delta_1+\delta_2\right)^2$,
+the unit cell volume
+in case of octahedral rotation and tilting
+ depends on the ``distortions'' $\alpha,\beta$ 
+as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
+and, at $\alpha,\beta\ll1$,
+it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$
+leading to a \emph{quartic} elastic energy that should roughly behave as
+$\sim\left(\alpha ^2+\beta ^2\right)^2$.
+So, the behavior we are looking for in the electronic spectrum 
+is not linear
+but quadratic, 
+which would compete with such a quartic elastic energy
+ to produce a finite distortion in the optimum structure.
+Thinking of squared angles 
+$\alpha ^2,\beta ^2$
+as the basic distortion variables,
+the order of the electronic and elastic energy terms
+matches to the standard JT problem.
+}
 
@@
 but keeps the qualitative picture the same.
+(The bold black line is nothing but an overlap of two practically degenerate black lines.)
 }
@@
 we discussed in this manuscript is also an interesting future work.
-However, a few remarks are in order. 
-Unlike the electronic correlations and spin-orbit interaction,
- the hybridization between 
-the orbitals localized on different B sites are not
-rotationally invariant.
+A discussion 
+about the role of 
+electron hopping 
+along with some preliminary results 
+follows.
+
 Assuming the crystal field splitting to be the largest energy scale,
-the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra,
-and
-the hybridization between the orbitals localized on different B sites
-(and the electronic band structure arising from them)
-are modified as the octahedra rotate.
+the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra.
+The electron hopping between these orbitals that are 
+localized on different B sites 
+%(that creates electronic bands)
+depends on the relative orientation of the orbitals.
+As the octahedra rotate (or tilt),
+the hybridization between the
+neighboring sites
+change,
+modifying
+the electronic bands and associated band energy.
+
+\begin{figure}[htbp]
+\begin{center}
+\includegraphics[width=1.0\linewidth]{hybrid}
+\caption{The effect of electron hopping between B sites.
+(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
+as a function of $\beta$ when either the crystal field or the hopping is considered alone.
+In the latter case, the energy changes are scaled with the bandwidth $W$.
+(b) Considering both the crystal field and the hopping simultaneously,
+the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
+as a function of the average bandwidth $W$, 
+for the same two configurations
+$t_{2g}^1$ and $e_g^1$.
+The results of the crystal field model presented in this manuscript 
+hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
+}
+\label{fig:hybrid}
+\end{center}
+\end{figure}
 
@@
 we consider the nearest neighbor hopping between the B sites
-using the Slater-Koster method~\cite{SlaterKoster}
+using the Slater-Koster method~\cite{SlaterPR54}
 and
-calculate the change in the energy of two configurations
-$t_{2g}^1$ and $e_g^1$
-as the octahedra rotate
-in three cases: with either the crystal field or the hopping only and with both of these simultaneously.
+calculate the change in the energy of 
+the system
+as the octahedra rotate.
+We do this for three cases: with either the crystal field or the hopping only,
+ and with both of these simultaneously.
+%
 Figure~\ref{fig:hybrid}(a)
 shows the change in the energy 
+of two (spinless) configurations $t_{2g}^1$ and $e_g^1$
 as a function of $\beta$ for the first two cases
@@
 and for the hopping-only case (red/gray curves, right y-axis).
-We use Slater-Koster hopping parameters
+We
+use Slater-Koster hopping parameters
 $(t_{\sigma},t_{\pi},t_{\delta})=(0.15,-0.1,0.025)$~eV, 
+% W = \{0.0330745,0.0385869,0.0358307\} Hartree
+% W = {0.900005, 1.05, 0.975004} eV
+%$(t_{\sigma},t_{\pi},t_{\delta})/W= {0.153846, -0.102564, 0.0256409}$
 $a=7$~bohr, $q_o=2$~e,
@@
 $t_{2g}$ and $e_g$ manifolds.
+(These parameters produce an average
+bandwidth $W=0.97$~eV for the two manifolds).
 While both $t_{2g}^1$ and $e_g^1$ configurations 
@@
 This is due to a reduced hybridization leading to narrower $e_g$ bands.
-In contrast, the energy of $t_{2g}^1$ decreases due band widening arising from 
+In contrast, the energy of $t_{2g}^1$ decreases due to a band widening arising from 
 an enhanced hybridization.
@@
 The rotation induced splitting of the $t_{2g}$/$e_g$ manifolds
+arising from the crystal field
 suppresses the effectiveness of the hopping in creating 
 the dispersion in the energy states, 
-and thus reduces the bandwidths and
-affects the associated rotation induced energetic changes.
+and thus reduces the bandwidths and the
+the associated rotation induced energetic changes.
 
@@
 From this analysis, we conclude that the results of our crystal field model 
-hold unambiguously only for narrower bands, $W/\Delta_o\ll1$.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{hybrid}
-\caption{The effect of dispersion due to the electron hopping between B sites.
-(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
-as a function of $\beta$ when either the crystal field or the hopping is considered alone.
-In the latter case, the energy changes are scaled with the bandwidth $W$.
-(b) Considering both the crystal field and the hopping simultaneously,
-the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
-as a function of the average bandwidth $W$ 
-for the same two configurations
-$t_{2g}^1$ and $e_g^1$.
-The results of the crystal field model presented in this manuscript 
-hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
-}
-\label{fig:hybrid}
-\end{center}
-\end{figure}
+hold unambiguously only for narrower bands, $W/\Delta_o\ll1$,
+while a detailed further study is required to understand the interplay of the two effects
+at larger bandwidths.
 
@@
 \label{Bibliography}
-\bibliographystyle{apsrev4-1}
-%\bibliography{perovskites}
-
-%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
-%Control: key (0)
-%Control: author (8) initials jnrlst
-%Control: editor formatted (1) identically to author
-%Control: production of article title (-1) disabled
-%Control: page (0) single
-%Control: year (1) truncated
-%Control: production of eprint (0) enabled
-\begin{thebibliography}{83}%
-\makeatletter
-\providecommand \@ifxundefined [1]{%
- \@ifx{#1\undefined}
-}%
-\providecommand \@ifnum [1]{%
- \ifnum #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \@ifx [1]{%
- \ifx #1\expandafter \@firstoftwo
- \else \expandafter \@secondoftwo
- \fi
-}%
-\providecommand \natexlab [1]{#1}%
-\providecommand \enquote  [1]{``#1''}%
-\providecommand \bibnamefont  [1]{#1}%
-\providecommand \bibfnamefont [1]{#1}%
-\providecommand \citenamefont [1]{#1}%
-\providecommand \href@noop [0]{\@secondoftwo}%
-\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
-\providecommand \@href[1]{\@@startlink{#1}\@@href}%
-\providecommand \@@href[1]{\endgroup#1\@@endlink}%
-\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
-  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
-\providecommand \@@startlink[1]{}%
-\providecommand \@@endlink[0]{}%
-\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
-\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
-\providecommand \urlprefix  [0]{URL }%
-\providecommand \Eprint [0]{\href }%
-\providecommand \doibase [0]{http://dx.doi.org/}%
-\providecommand \selectlanguage [0]{\@gobble}%
-\providecommand \bibinfo  [0]{\@secondoftwo}%
-\providecommand \bibfield  [0]{\@secondoftwo}%
-\providecommand \translation [1]{[#1]}%
-\providecommand \BibitemOpen [0]{}%
-\providecommand \bibitemStop [0]{}%
-\providecommand \bibitemNoStop [0]{.\EOS\space}%
-\providecommand \EOS [0]{\spacefactor3000\relax}%
-\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
-\let\auto@bib@innerbib\@empty
-%</preamble>
-\bibitem [{\citenamefont {Zubko}\ \emph {et~al.}(2011)\citenamefont {Zubko},
-  \citenamefont {Gariglio}, \citenamefont {Gabay}, \citenamefont {Ghosez},\
-  and\ \citenamefont {Triscone}}]{ZubkoARCMP11}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Zubko}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Gariglio}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Gabay}}, \bibinfo
-  {author} {\bibfnamefont {P.}~\bibnamefont {Ghosez}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.-M.}\ \bibnamefont {Triscone}},\ }\href {\doibase
-  10.1146/annurev-conmatphys-062910-140445} {\bibfield  {journal} {\bibinfo
-  {journal} {Annual Review of Condensed Matter Physics}\ }\textbf {\bibinfo
-  {volume} {2}},\ \bibinfo {pages} {141} (\bibinfo {year} {2011})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Hwang}\ \emph {et~al.}(2012)\citenamefont {Hwang},
-  \citenamefont {Iwasa}, \citenamefont {Kawasaki}, \citenamefont {Keimer},
-  \citenamefont {Nagaosa},\ and\ \citenamefont {Tokura}}]{HwangNM12}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~Y.}\ \bibnamefont
-  {Hwang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Iwasa}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Kawasaki}}, \bibinfo
-  {author} {\bibfnamefont {B.}~\bibnamefont {Keimer}}, \bibinfo {author}
-  {\bibfnamefont {N.}~\bibnamefont {Nagaosa}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {Y.}~\bibnamefont {Tokura}},\ }\href {\doibase
-  10.1038/nmat3223} {\bibfield  {journal} {\bibinfo  {journal} {Nature
-  Materials}\ }\textbf {\bibinfo {volume} {11}},\ \bibinfo {pages} {103}
-  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bhattacharya}\ and\ \citenamefont
-  {May}(2014)}]{BhattacharyaARMR14}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Bhattacharya}}\ and\ \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont
-  {May}},\ }\href {\doibase 10.1146/annurev-matsci-070813-113447} {\bibfield
-  {journal} {\bibinfo  {journal} {Annual Review of Materials Research}\
-  }\textbf {\bibinfo {volume} {44}},\ \bibinfo {pages} {65} (\bibinfo {year}
-  {2014})},\ \Eprint
-  {http://arxiv.org/abs/https://doi.org/10.1146/annurev-matsci-070813-113447}
-  {https://doi.org/10.1146/annurev-matsci-070813-113447} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Hellman}\ \emph {et~al.}(2017)\citenamefont
-  {Hellman}, \citenamefont {Hoffmann}, \citenamefont {Tserkovnyak},
-  \citenamefont {Beach}, \citenamefont {Fullerton}, \citenamefont {Leighton},
-  \citenamefont {MacDonald}, \citenamefont {Ralph}, \citenamefont {Arena},
-  \citenamefont {D\"urr}, \citenamefont {Fischer}, \citenamefont {Grollier},
-  \citenamefont {Heremans}, \citenamefont {Jungwirth}, \citenamefont {Kimel},
-  \citenamefont {Koopmans}, \citenamefont {Krivorotov}, \citenamefont {May},
-  \citenamefont {Petford-Long}, \citenamefont {Rondinelli}, \citenamefont
-  {Samarth}, \citenamefont {Schuller}, \citenamefont {Slavin}, \citenamefont
-  {Stiles}, \citenamefont {Tchernyshyov}, \citenamefont {Thiaville},\ and\
-  \citenamefont {Zink}}]{HellmanRMP17}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Hellman}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Hoffmann}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Tserkovnyak}}, \bibinfo
-  {author} {\bibfnamefont {G.~S.~D.}\ \bibnamefont {Beach}}, \bibinfo {author}
-  {\bibfnamefont {E.~E.}\ \bibnamefont {Fullerton}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Leighton}}, \bibinfo {author}
-  {\bibfnamefont {A.~H.}\ \bibnamefont {MacDonald}}, \bibinfo {author}
-  {\bibfnamefont {D.~C.}\ \bibnamefont {Ralph}}, \bibinfo {author}
-  {\bibfnamefont {D.~A.}\ \bibnamefont {Arena}}, \bibinfo {author}
-  {\bibfnamefont {H.~A.}\ \bibnamefont {D\"urr}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Fischer}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Grollier}}, \bibinfo {author} {\bibfnamefont {J.~P.}\
-  \bibnamefont {Heremans}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Jungwirth}}, \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
-  {Kimel}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont {Koopmans}},
-  \bibinfo {author} {\bibfnamefont {I.~N.}\ \bibnamefont {Krivorotov}},
-  \bibinfo {author} {\bibfnamefont {S.~J.}\ \bibnamefont {May}}, \bibinfo
-  {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Petford-Long}}, \bibinfo
-  {author} {\bibfnamefont {J.~M.}\ \bibnamefont {Rondinelli}}, \bibinfo
-  {author} {\bibfnamefont {N.}~\bibnamefont {Samarth}}, \bibinfo {author}
-  {\bibfnamefont {I.~K.}\ \bibnamefont {Schuller}}, \bibinfo {author}
-  {\bibfnamefont {A.~N.}\ \bibnamefont {Slavin}}, \bibinfo {author}
-  {\bibfnamefont {M.~D.}\ \bibnamefont {Stiles}}, \bibinfo {author}
-  {\bibfnamefont {O.}~\bibnamefont {Tchernyshyov}}, \bibinfo {author}
-  {\bibfnamefont {A.}~\bibnamefont {Thiaville}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {B.~L.}\ \bibnamefont {Zink}},\ }\href {\doibase
-  10.1103/RevModPhys.89.025006} {\bibfield  {journal} {\bibinfo  {journal}
-  {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo {pages}
-  {025006} (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chen}\ and\ \citenamefont
-  {Millis}(2017)}]{ChenJPCM17}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Chen}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Millis}},\
-  }\href {\doibase 10.1088/1361-648X/aa6efe} {\bibfield  {journal} {\bibinfo
-  {journal} {Journal of Physics: Condensed Matter}\ }\textbf {\bibinfo {volume}
-  {29}},\ \bibinfo {pages} {243001} (\bibinfo {year} {2017})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Dagotto}(2005)}]{DagottoS05}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Dagotto}},\ }\href {\doibase 10.1126/science.1107559} {\bibfield  {journal}
-  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {309}},\ \bibinfo
-  {pages} {257} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Dagotto}\ and\ \citenamefont
-  {Tokura}(2008)}]{DagottoMRSB08}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Dagotto}}\ and\ \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Tokura}},\ }\href {\doibase 10.1557/mrs2008.223} {\bibfield  {journal}
-  {\bibinfo  {journal} {MRS Bulletin}\ }\textbf {\bibinfo {volume} {33}},\
-  \bibinfo {pages} {1037} (\bibinfo {year} {2008})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Salamon}\ and\ \citenamefont
-  {Jaime}(2001)}]{SalamonRMP01}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~B.}\ \bibnamefont
-  {Salamon}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Jaime}},\ }\href {\doibase 10.1103/RevModPhys.73.583} {\bibfield  {journal}
-  {\bibinfo  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {73}},\
-  \bibinfo {pages} {583} (\bibinfo {year} {2001})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2003)\citenamefont {Wang},
-  \citenamefont {Neaton}, \citenamefont {Zheng}, \citenamefont {Nagarajan},
-  \citenamefont {Ogale}, \citenamefont {Liu}, \citenamefont {Viehland},
-  \citenamefont {Vaithyanathan}, \citenamefont {Schlom}, \citenamefont
-  {Waghmare}, \citenamefont {Spaldin}, \citenamefont {Rabe}, \citenamefont
-  {Wuttig},\ and\ \citenamefont {Ramesh}}]{WangS03}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {J.~B.}\ \bibnamefont {Neaton}},
-  \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Zheng}}, \bibinfo
-  {author} {\bibfnamefont {V.}~\bibnamefont {Nagarajan}}, \bibinfo {author}
-  {\bibfnamefont {S.~B.}\ \bibnamefont {Ogale}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Liu}}, \bibinfo {author} {\bibfnamefont
-  {D.}~\bibnamefont {Viehland}}, \bibinfo {author} {\bibfnamefont
-  {V.}~\bibnamefont {Vaithyanathan}}, \bibinfo {author} {\bibfnamefont {D.~G.}\
-  \bibnamefont {Schlom}}, \bibinfo {author} {\bibfnamefont {U.~V.}\
-  \bibnamefont {Waghmare}}, \bibinfo {author} {\bibfnamefont {N.~A.}\
-  \bibnamefont {Spaldin}}, \bibinfo {author} {\bibfnamefont {K.~M.}\
-  \bibnamefont {Rabe}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Wuttig}}, \ and\ \bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
-  {Ramesh}},\ }\href {\doibase 10.1126/science.1080615} {\bibfield  {journal}
-  {\bibinfo  {journal} {Science}\ }\textbf {\bibinfo {volume} {299}},\ \bibinfo
-  {pages} {1719} (\bibinfo {year} {2003})},\ \Eprint
-  {http://arxiv.org/abs/https://www.science.org/doi/pdf/10.1126/science.1080615}
-  {https://www.science.org/doi/pdf/10.1126/science.1080615} \BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Dawber}\ \emph {et~al.}(2005)\citenamefont {Dawber},
-  \citenamefont {Rabe},\ and\ \citenamefont {Scott}}]{DawberRMP05}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Dawber}}, \bibinfo {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Rabe}}, \
-  and\ \bibinfo {author} {\bibfnamefont {J.~F.}\ \bibnamefont {Scott}},\ }\href
-  {\doibase 10.1103/RevModPhys.77.1083} {\bibfield  {journal} {\bibinfo
-  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {77}},\ \bibinfo
-  {pages} {1083} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Schlom}\ \emph {et~al.}(2007)\citenamefont {Schlom},
-  \citenamefont {Chen}, \citenamefont {Eom}, \citenamefont {Rabe},
-  \citenamefont {Streiffer},\ and\ \citenamefont {Triscone}}]{SchlomARMR07}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~G.}\ \bibnamefont
-  {Schlom}}, \bibinfo {author} {\bibfnamefont {L.-Q.}\ \bibnamefont {Chen}},
-  \bibinfo {author} {\bibfnamefont {C.-B.}\ \bibnamefont {Eom}}, \bibinfo
-  {author} {\bibfnamefont {K.~M.}\ \bibnamefont {Rabe}}, \bibinfo {author}
-  {\bibfnamefont {S.~K.}\ \bibnamefont {Streiffer}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.-M.}\ \bibnamefont {Triscone}},\ }\href {\doibase
-  10.1146/annurev.matsci.37.061206.113016} {\bibfield  {journal} {\bibinfo
-  {journal} {Annual Review of Materials Research}\ }\textbf {\bibinfo {volume}
-  {37}},\ \bibinfo {pages} {589} (\bibinfo {year} {2007})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Koster}\ \emph {et~al.}(2012)\citenamefont {Koster},
-  \citenamefont {Klein}, \citenamefont {Siemons}, \citenamefont {Rijnders},
-  \citenamefont {Dodge}, \citenamefont {Eom}, \citenamefont {Blank},\ and\
-  \citenamefont {Beasley}}]{KosterRMP12}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Koster}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Klein}},
-  \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Siemons}}, \bibinfo
-  {author} {\bibfnamefont {G.}~\bibnamefont {Rijnders}}, \bibinfo {author}
-  {\bibfnamefont {J.~S.}\ \bibnamefont {Dodge}}, \bibinfo {author}
-  {\bibfnamefont {C.-B.}\ \bibnamefont {Eom}}, \bibinfo {author} {\bibfnamefont
-  {D.~H.~A.}\ \bibnamefont {Blank}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {M.~R.}\ \bibnamefont {Beasley}},\ }\href {\doibase
-  10.1103/RevModPhys.84.253} {\bibfield  {journal} {\bibinfo  {journal} {Rev.
-  Mod. Phys.}\ }\textbf {\bibinfo {volume} {84}},\ \bibinfo {pages} {253}
-  (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bersuker}(1975)}]{BersukerCCR75}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Bersuker}},\ }\href {\doibase https://doi.org/10.1016/S0010-8545(00)80266-0}
-  {\bibfield  {journal} {\bibinfo  {journal} {Coordination Chemistry Reviews}\
-  }\textbf {\bibinfo {volume} {14}},\ \bibinfo {pages} {357} (\bibinfo {year}
-  {1975})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kugel}\ and\ \citenamefont {Khomski{\u
-  i}}(1982)}]{KugelSPU82}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.~I.}\ \bibnamefont
-  {Kugel}}\ and\ \bibinfo {author} {\bibfnamefont {D.~I.}\ \bibnamefont
-  {Khomski{\u i}}},\ }\href {\doibase 10.1070/PU1982v025n04ABEH004537}
-  {\bibfield  {journal} {\bibinfo  {journal} {Soviet Physics Uspekhi}\ }\textbf
-  {\bibinfo {volume} {25}},\ \bibinfo {pages} {231} (\bibinfo {year}
-  {1982})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Millis}(1998)}]{MillisN98}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~J.}\ \bibnamefont
-  {Millis}},\ }\href {\doibase 10.1038/32348} {\bibfield  {journal} {\bibinfo
-  {journal} {Nature}\ }\textbf {\bibinfo {volume} {392}},\ \bibinfo {pages}
-  {147} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Terakura}(2007)}]{TerakuraPMS07}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Terakura}},\ }\href {\doibase https://doi.org/10.1016/j.pmatsci.2006.10.007}
-  {\bibfield  {journal} {\bibinfo  {journal} {Progress in Materials Science}\
-  }\textbf {\bibinfo {volume} {52}},\ \bibinfo {pages} {388} (\bibinfo {year}
-  {2007})},\ \bibinfo {note} {modelling electrons and atoms for materials
-  science}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Halcrow}(2013)}]{HalcrowRSC13}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Halcrow}},\ }\href {\doibase 10.1039/C2CS35253B} {\bibfield  {journal}
-  {\bibinfo  {journal} {Chemical Society Reviews}\ }\textbf {\bibinfo {volume}
-  {42}},\ \bibinfo {pages} {1784} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Lufaso}\ and\ \citenamefont
-  {Woodward}(2004)}]{LufasoAC04}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
-  {Lufaso}}\ and\ \bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
-  {Woodward}},\ }\href {\doibase 10.1107/S0108768103026661} {\bibfield
-  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
-  {\bibinfo {volume} {60}},\ \bibinfo {pages} {10} (\bibinfo {year}
-  {2004})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Glazer}(1972)}]{GlazerAC72}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Glazer}},\ }\href {\doibase 10.1107/S0567740872007976} {\bibfield  {journal}
-  {\bibinfo  {journal} {Acta Crystallogr., Sect. B: Struct. Crystallogr. Cryst.
-  Chem.}\ }\textbf {\bibinfo {volume} {28}},\ \bibinfo {pages} {3384} (\bibinfo
-  {year} {1972})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Thomas}(1996)}]{ThomasAC96}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~W.}\ \bibnamefont
-  {Thomas}},\ }\href {\doibase 10.1107/S0108768195006100} {\bibfield  {journal}
-  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo
-  {volume} {52}},\ \bibinfo {pages} {16} (\bibinfo {year} {1996})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Woodward}(1997{\natexlab{a}})}]{WoodwardAC97a}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
-  {Woodward}},\ }\href {\doibase 10.1107/S0108768196010713} {\bibfield
-  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
-  {\bibinfo {volume} {53}},\ \bibinfo {pages} {32} (\bibinfo {year}
-  {1997}{\natexlab{a}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Woodward}(1997{\natexlab{b}})}]{WoodwardAC97b}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~M.}\ \bibnamefont
-  {Woodward}},\ }\href {\doibase 10.1107/S0108768196012050} {\bibfield
-  {journal} {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf
-  {\bibinfo {volume} {53}},\ \bibinfo {pages} {44} (\bibinfo {year}
-  {1997}{\natexlab{b}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Howard}\ and\ \citenamefont
-  {Stokes}(1998)}]{HowardAC98}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
-  {Howard}}\ and\ \bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
-  {Stokes}},\ }\href {\doibase 10.1107/S0108768198004200} {\bibfield  {journal}
-  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo
-  {volume} {54}},\ \bibinfo {pages} {782} (\bibinfo {year} {1998})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Stokes}\ \emph {et~al.}(2002)\citenamefont {Stokes},
-  \citenamefont {Kisi}, \citenamefont {Hatch},\ and\ \citenamefont
-  {Howard}}]{StokesAC02}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~T.}\ \bibnamefont
-  {Stokes}}, \bibinfo {author} {\bibfnamefont {E.~H.}\ \bibnamefont {Kisi}},
-  \bibinfo {author} {\bibfnamefont {D.~M.}\ \bibnamefont {Hatch}}, \ and\
-  \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont {Howard}},\ }\href
-  {\doibase 10.1107/S0108768102015756} {\bibfield  {journal} {\bibinfo
-  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo {volume}
-  {58}},\ \bibinfo {pages} {934} (\bibinfo {year} {2002})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Angel}\ \emph {et~al.}(2005)\citenamefont {Angel},
-  \citenamefont {Zhao},\ and\ \citenamefont {Ross}}]{AngelPRL05}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~J.}\ \bibnamefont
-  {Angel}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Zhao}}, \ and\
-  \bibinfo {author} {\bibfnamefont {N.~L.}\ \bibnamefont {Ross}},\ }\href
-  {\doibase 10.1103/PhysRevLett.95.025503} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {95}},\ \bibinfo
-  {pages} {025503} (\bibinfo {year} {2005})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ghosez}\ and\ \citenamefont
-  {Triscone}(2011)}]{GhosezNM11}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Ghosez}}\ and\ \bibinfo {author} {\bibfnamefont {J.-M.}\ \bibnamefont
-  {Triscone}},\ }\href {\doibase 10.1038/nmat3003} {\bibfield  {journal}
-  {\bibinfo  {journal} {Nature Materials}\ }\textbf {\bibinfo {volume} {10}},\
-  \bibinfo {pages} {269} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Rondinelli}\ and\ \citenamefont
-  {Fennie}(2012)}]{RondinelliAM12}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Rondinelli}}\ and\ \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
-  {Fennie}},\ }\href {\doibase https://doi.org/10.1002/adma.201104674}
-  {\bibfield  {journal} {\bibinfo  {journal} {Advanced Materials}\ }\textbf
-  {\bibinfo {volume} {24}},\ \bibinfo {pages} {1961} (\bibinfo {year}
-  {2012})},\ \Eprint
-  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/adma.201104674}
-  {https://onlinelibrary.wiley.com/doi/pdf/10.1002/adma.201104674} \BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Schick}\ \emph {et~al.}(2014)\citenamefont {Schick},
-  \citenamefont {Jiang}, \citenamefont {Saldana-Greco},\ and\ \citenamefont
-  {Rappe}}]{SchickPRB14}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~T.}\ \bibnamefont
-  {Schick}}, \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Jiang}},
-  \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Saldana-Greco}}, \ and\
-  \bibinfo {author} {\bibfnamefont {A.~M.}\ \bibnamefont {Rappe}},\ }\href
-  {\doibase 10.1103/PhysRevB.89.195304} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo
-  {pages} {195304} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sim}\ and\ \citenamefont {Kim}(2014)}]{SimPRB14}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Sim}}\ and\ \bibinfo {author} {\bibfnamefont {B.~G.}\ \bibnamefont {Kim}},\
-  }\href {\doibase 10.1103/PhysRevB.89.144114} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {89}},\ \bibinfo
-  {pages} {144114} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lee}\ \emph {et~al.}(2017)\citenamefont {Lee},
-  \citenamefont {Chang}, \citenamefont {Huang}, \citenamefont {Guo},
-  \citenamefont {Gao}, \citenamefont {Chen}, \citenamefont {Cheong},\ and\
-  \citenamefont {Chu}}]{LeePRL17}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~H.}\ \bibnamefont
-  {Lee}}, \bibinfo {author} {\bibfnamefont {C.-P.}\ \bibnamefont {Chang}},
-  \bibinfo {author} {\bibfnamefont {F.-T.}\ \bibnamefont {Huang}}, \bibinfo
-  {author} {\bibfnamefont {G.~Y.}\ \bibnamefont {Guo}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Gao}}, \bibinfo {author} {\bibfnamefont
-  {C.~H.}\ \bibnamefont {Chen}}, \bibinfo {author} {\bibfnamefont {S.-W.}\
-  \bibnamefont {Cheong}}, \ and\ \bibinfo {author} {\bibfnamefont {M.-W.}\
-  \bibnamefont {Chu}},\ }\href {\doibase 10.1103/PhysRevLett.119.157601}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {119}},\ \bibinfo {pages} {157601} (\bibinfo {year}
-  {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Wang}\ \emph {et~al.}(2022)\citenamefont {Wang},
-  \citenamefont {Tang}, \citenamefont {Stengel}, \citenamefont {Xiang},
-  \citenamefont {An}, \citenamefont {Low},\ and\ \citenamefont
-  {Wu}}]{WangPRL22}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Tang}}, \bibinfo
-  {author} {\bibfnamefont {M.}~\bibnamefont {Stengel}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont
-  {Q.}~\bibnamefont {An}}, \bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Low}}, \ and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Wu}},\
-  }\href {\doibase 10.1103/PhysRevLett.128.197601} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {128}},\
-  \bibinfo {pages} {197601} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2022)\citenamefont {Zhou},
-  \citenamefont {Dong}, \citenamefont {Shan}, \citenamefont {Ji},\ and\
-  \citenamefont {Zhang}}]{ZhouPRB22}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhou}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Dong}}, \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {Shan}}, \bibinfo {author}
-  {\bibfnamefont {K.}~\bibnamefont {Ji}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {J.}~\bibnamefont {Zhang}},\ }\href {\doibase
-  10.1103/PhysRevB.105.075408} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {105}},\ \bibinfo {pages}
-  {075408} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gao}\ \emph {et~al.}(2023)\citenamefont {Gao},
-  \citenamefont {Paillard},\ and\ \citenamefont {Bellaiche}}]{GaoPRB23}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Gao}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Paillard}}, \
-  and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\href
-  {\doibase 10.1103/PhysRevB.107.104109} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {107}},\ \bibinfo
-  {pages} {104109} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Khomskii}(2009)}]{KhomskiiPhys09}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Khomskii}},\ }\href {\doibase 10.1103/Physics.2.20} {\bibfield  {journal}
-  {\bibinfo  {journal} {Physics}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo
-  {pages} {20} (\bibinfo {year} {2009})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Benedek}\ and\ \citenamefont
-  {Fennie}(2011)}]{BenedekPRL11}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.~A.}\ \bibnamefont
-  {Benedek}}\ and\ \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
-  {Fennie}},\ }\href {\doibase 10.1103/PhysRevLett.106.107204} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
-  {volume} {106}},\ \bibinfo {pages} {107204} (\bibinfo {year}
-  {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Yang}\ \emph {et~al.}(2014)\citenamefont {Yang},
-  \citenamefont {\'I\~niguez}, \citenamefont {Mao},\ and\ \citenamefont
-  {Bellaiche}}]{YangPRL14}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Yang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {\'I\~niguez}},
-  \bibinfo {author} {\bibfnamefont {A.-J.}\ \bibnamefont {Mao}}, \ and\
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\href
-  {\doibase 10.1103/PhysRevLett.112.057202} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {112}},\ \bibinfo
-  {pages} {057202} (\bibinfo {year} {2014})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ye}\ \emph {et~al.}(2018)\citenamefont {Ye},
-  \citenamefont {Wang}, \citenamefont {Sheng}, \citenamefont {Hoffmann},
-  \citenamefont {Gu}, \citenamefont {Xiang}, \citenamefont {Tian},
-  \citenamefont {Molaison}, \citenamefont {dos Santos}, \citenamefont
-  {Matsuda}, \citenamefont {Chakoumakos}, \citenamefont {Fernandez-Baca},
-  \citenamefont {Tong}, \citenamefont {Gao}, \citenamefont {Kim},\ and\
-  \citenamefont {Cheong}}]{YePRB18}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {F.}~\bibnamefont
-  {Ye}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wang}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Sheng}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Hoffmann}}, \bibinfo {author}
-  {\bibfnamefont {T.}~\bibnamefont {Gu}}, \bibinfo {author} {\bibfnamefont
-  {H.~J.}\ \bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont
-  {W.}~\bibnamefont {Tian}}, \bibinfo {author} {\bibfnamefont {J.~J.}\
-  \bibnamefont {Molaison}}, \bibinfo {author} {\bibfnamefont {A.~M.}\
-  \bibnamefont {dos Santos}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Matsuda}}, \bibinfo {author} {\bibfnamefont {B.~C.}\
-  \bibnamefont {Chakoumakos}}, \bibinfo {author} {\bibfnamefont {J.~A.}\
-  \bibnamefont {Fernandez-Baca}}, \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Tong}}, \bibinfo {author} {\bibfnamefont {B.}~\bibnamefont
-  {Gao}}, \bibinfo {author} {\bibfnamefont {J.~W.}\ \bibnamefont {Kim}}, \ and\
-  \bibinfo {author} {\bibfnamefont {S.-W.}\ \bibnamefont {Cheong}},\ }\href
-  {\doibase 10.1103/PhysRevB.97.041112} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {97}},\ \bibinfo
-  {pages} {041112} (\bibinfo {year} {2018})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph
-  {et~al.}(2020{\natexlab{a}})\citenamefont {Zhang}, \citenamefont {Shen},
-  \citenamefont {Wang}, \citenamefont {Ji}, \citenamefont {Zhou}, \citenamefont
-  {Wang}, \citenamefont {Huang},\ and\ \citenamefont {Lu}}]{ZhangPRL20}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Shen}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {C.}~\bibnamefont {Ji}}, \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Zhou}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Wang}}, \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Huang}}, \ and\
-  \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Lu}},\ }\href {\doibase
-  10.1103/PhysRevLett.125.017601} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\ \bibinfo {pages}
-  {017601} (\bibinfo {year} {2020}{\natexlab{a}})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph
-  {et~al.}(2020{\natexlab{b}})\citenamefont {Zhang}, \citenamefont {Wang},\
-  and\ \citenamefont {Ghosez}}]{ZhangYajunPRL20}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {Wang}}, \ and\
-  \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Ghosez}},\ }\href
-  {\doibase 10.1103/PhysRevLett.125.157601} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\ \bibinfo
-  {pages} {157601} (\bibinfo {year} {2020}{\natexlab{b}})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Zhou}\ \emph {et~al.}(2021)\citenamefont {Zhou},
-  \citenamefont {Chen}, \citenamefont {Wu}, \citenamefont {Shen}, \citenamefont
-  {Wang}, \citenamefont {Zhang},\ and\ \citenamefont {Sun}}]{ZhouPRB21}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont
-  {Zhou}}, \bibinfo {author} {\bibfnamefont {Z.}~\bibnamefont {Chen}}, \bibinfo
-  {author} {\bibfnamefont {Z.}~\bibnamefont {Wu}}, \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wang}}, \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zhang}}, \ and\ \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Sun}},\
-  }\href {\doibase 10.1103/PhysRevB.103.224409} {\bibfield  {journal} {\bibinfo
-   {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo
-  {pages} {224409} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Zhang}\ \emph {et~al.}(2022)\citenamefont {Zhang},
-  \citenamefont {Zhou}, \citenamefont {Wang}, \citenamefont {Shen},
-  \citenamefont {Wang},\ and\ \citenamefont {Lu}}]{ZhangPRL22}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zhang}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Zhou}},
-  \bibinfo {author} {\bibfnamefont {F.}~\bibnamefont {Wang}}, \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Shen}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Wang}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {X.}~\bibnamefont {Lu}},\ }\href {\doibase 10.1103/PhysRevLett.129.117603}
-  {\bibfield  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf
-  {\bibinfo {volume} {129}},\ \bibinfo {pages} {117603} (\bibinfo {year}
-  {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Amat}\ \emph {et~al.}(2014)\citenamefont {Amat},
-  \citenamefont {Mosconi}, \citenamefont {Ronca}, \citenamefont {Quarti},
-  \citenamefont {Umari}, \citenamefont {Nazeeruddin}, \citenamefont {Gratzel},\
-  and\ \citenamefont {De~Angelis}}]{AmatNL14}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Amat}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Mosconi}},
-  \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Ronca}}, \bibinfo
-  {author} {\bibfnamefont {C.}~\bibnamefont {Quarti}}, \bibinfo {author}
-  {\bibfnamefont {P.}~\bibnamefont {Umari}}, \bibinfo {author} {\bibfnamefont
-  {M.~K.}\ \bibnamefont {Nazeeruddin}}, \bibinfo {author} {\bibfnamefont
-  {M.}~\bibnamefont {Gratzel}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {F.}~\bibnamefont {De~Angelis}},\ }\href {\doibase 10.1021/nl5012992}
-  {\bibfield  {journal} {\bibinfo  {journal} {Nano Letters}\ }\textbf {\bibinfo
-  {volume} {14}},\ \bibinfo {pages} {3608} (\bibinfo {year} {2014})},\ \bibinfo
-  {note} {pMID: 24797342},\ \Eprint
-  {http://arxiv.org/abs/https://doi.org/10.1021/nl5012992}
-  {https://doi.org/10.1021/nl5012992} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Krach}\ \emph {et~al.}(2023)\citenamefont {Krach},
-  \citenamefont {Forero-Correa}, \citenamefont {Biega}, \citenamefont
-  {Reyes-Lillo},\ and\ \citenamefont {Leppert}}]{KrachJPCM23}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Krach}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Forero-Correa}}, \bibinfo {author} {\bibfnamefont {R.-I.}\ \bibnamefont
-  {Biega}}, \bibinfo {author} {\bibfnamefont {S.~E.}\ \bibnamefont
-  {Reyes-Lillo}}, \ and\ \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Leppert}},\ }\href {\doibase 10.1088/1361-648X/acbd0c} {\bibfield  {journal}
-  {\bibinfo  {journal} {Journal of Physics: Condensed Matter}\ }\textbf
-  {\bibinfo {volume} {35}},\ \bibinfo {pages} {174001} (\bibinfo {year}
-  {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Balachandran}\ and\ \citenamefont
-  {Rondinelli}(2013)}]{BalachandranPRB13}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~V.}\ \bibnamefont
-  {Balachandran}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Rondinelli}},\ }\href {\doibase 10.1103/PhysRevB.88.054101} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {88}},\ \bibinfo {pages} {054101} (\bibinfo {year} {2013})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Aguado-Puente}\ \emph {et~al.}(2011)\citenamefont
-  {Aguado-Puente}, \citenamefont {Garc\'{\i}a-Fern\'andez},\ and\ \citenamefont
-  {Junquera}}]{Aguado-PuentePRL11}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Aguado-Puente}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Garc\'{\i}a-Fern\'andez}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Junquera}},\ }\href {\doibase
-  10.1103/PhysRevLett.107.217601} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {107}},\ \bibinfo {pages}
-  {217601} (\bibinfo {year} {2011})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Jia}\ \emph {et~al.}(2022)\citenamefont {Jia},
-  \citenamefont {He}, \citenamefont {Akhtar}, \citenamefont {Herranz},\ and\
-  \citenamefont {Pruneda}}]{JiaPRB22}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Jia}}, \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {He}}, \bibinfo
-  {author} {\bibfnamefont {A.}~\bibnamefont {Akhtar}}, \bibinfo {author}
-  {\bibfnamefont {G.}~\bibnamefont {Herranz}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {M.}~\bibnamefont {Pruneda}},\ }\href {\doibase
-  10.1103/PhysRevB.105.224112} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {105}},\ \bibinfo {pages}
-  {224112} (\bibinfo {year} {2022})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Xiang}\ \emph {et~al.}(2017)\citenamefont {Xiang},
-  \citenamefont {Guennou}, \citenamefont {\'I\~niguez}, \citenamefont
-  {Kreisel},\ and\ \citenamefont {Bellaiche}}]{XiangPRB17}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~J.}\ \bibnamefont
-  {Xiang}}, \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Guennou}},
-  \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont {\'I\~niguez}}, \bibinfo
-  {author} {\bibfnamefont {J.}~\bibnamefont {Kreisel}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {L.}~\bibnamefont {Bellaiche}},\ }\href {\doibase
-  10.1103/PhysRevB.96.054102} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Rev. B}\ }\textbf {\bibinfo {volume} {96}},\ \bibinfo {pages} {054102}
-  (\bibinfo {year} {2017})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Johnson}\ \emph {et~al.}(2020)\citenamefont
-  {Johnson}, \citenamefont {Khalyavin}, \citenamefont {Manuel}, \citenamefont
-  {Zhang}, \citenamefont {Yamaura},\ and\ \citenamefont
-  {Belik}}]{JohnsonPRL20}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~D.}\ \bibnamefont
-  {Johnson}}, \bibinfo {author} {\bibfnamefont {D.~D.}\ \bibnamefont
-  {Khalyavin}}, \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {Manuel}},
-  \bibinfo {author} {\bibfnamefont {L.}~\bibnamefont {Zhang}}, \bibinfo
-  {author} {\bibfnamefont {K.}~\bibnamefont {Yamaura}}, \ and\ \bibinfo
-  {author} {\bibfnamefont {A.~A.}\ \bibnamefont {Belik}},\ }\href {\doibase
-  10.1103/PhysRevLett.125.097601} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {125}},\ \bibinfo {pages}
-  {097601} (\bibinfo {year} {2020})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ogawa}\ \emph {et~al.}(2012)\citenamefont {Ogawa},
-  \citenamefont {Ogimoto}, \citenamefont {Ida}, \citenamefont {Nomura},
-  \citenamefont {Arita},\ and\ \citenamefont {Miyano}}]{OgawaPRL12}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Ogawa}}, \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Ogimoto}},
-  \bibinfo {author} {\bibfnamefont {Y.}~\bibnamefont {Ida}}, \bibinfo {author}
-  {\bibfnamefont {Y.}~\bibnamefont {Nomura}}, \bibinfo {author} {\bibfnamefont
-  {R.}~\bibnamefont {Arita}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {K.}~\bibnamefont {Miyano}},\ }\href {\doibase
-  10.1103/PhysRevLett.108.157603} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {108}},\ \bibinfo {pages}
-  {157603} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2019)\citenamefont {Chen},
-  \citenamefont {Xu}, \citenamefont {Tian}, \citenamefont {Xiang},
-  \citenamefont {\'I\~niguez}, \citenamefont {Yang},\ and\ \citenamefont
-  {Bellaiche}}]{ChenPRL19}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {L.}~\bibnamefont
-  {Chen}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Xu}}, \bibinfo
-  {author} {\bibfnamefont {H.}~\bibnamefont {Tian}}, \bibinfo {author}
-  {\bibfnamefont {H.}~\bibnamefont {Xiang}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {\'I\~niguez}}, \bibinfo {author} {\bibfnamefont
-  {Y.}~\bibnamefont {Yang}}, \ and\ \bibinfo {author} {\bibfnamefont
-  {L.}~\bibnamefont {Bellaiche}},\ }\href {\doibase
-  10.1103/PhysRevLett.122.247701} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {122}},\ \bibinfo {pages}
-  {247701} (\bibinfo {year} {2019})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Huang}\ \emph {et~al.}(2021)\citenamefont {Huang},
-  \citenamefont {Liu}, \citenamefont {Shao}, \citenamefont {Feng},
-  \citenamefont {Zhang}, \citenamefont {Fu}, \citenamefont {Lee}, \citenamefont
-  {Shen}, \citenamefont {Chuang},\ and\ \citenamefont {Liu}}]{HuangPRB21}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
-  {Huang}}, \bibinfo {author} {\bibfnamefont {W.}~\bibnamefont {Liu}}, \bibinfo
-  {author} {\bibfnamefont {Y.-C.}\ \bibnamefont {Shao}}, \bibinfo {author}
-  {\bibfnamefont {X.}~\bibnamefont {Feng}}, \bibinfo {author} {\bibfnamefont
-  {N.}~\bibnamefont {Zhang}}, \bibinfo {author} {\bibfnamefont
-  {J.}~\bibnamefont {Fu}}, \bibinfo {author} {\bibfnamefont {J.-M.}\
-  \bibnamefont {Lee}}, \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
-  {Shen}}, \bibinfo {author} {\bibfnamefont {Y.-D.}\ \bibnamefont {Chuang}}, \
-  and\ \bibinfo {author} {\bibfnamefont {X.}~\bibnamefont {Liu}},\ }\href
-  {\doibase 10.1103/PhysRevB.104.075156} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {104}},\ \bibinfo
-  {pages} {075156} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Abarca~Morales}\ \emph {et~al.}(2023)\citenamefont
-  {Abarca~Morales}, \citenamefont {Siemann}, \citenamefont {Zivanovic},
-  \citenamefont {Murgatroyd}, \citenamefont {Markovi\ifmmode~\acute{c}\else
-  \'{c}\fi{}}, \citenamefont {Edwards}, \citenamefont {Hooley}, \citenamefont
-  {Sokolov}, \citenamefont {Kikugawa}, \citenamefont {Cacho}, \citenamefont
-  {Watson}, \citenamefont {Kim}, \citenamefont {Hicks}, \citenamefont
-  {Mackenzie},\ and\ \citenamefont {King}}]{MoralesPRL23}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Abarca~Morales}}, \bibinfo {author} {\bibfnamefont {G.-R.}\ \bibnamefont
-  {Siemann}}, \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont {Zivanovic}},
-  \bibinfo {author} {\bibfnamefont {P.~A.~E.}\ \bibnamefont {Murgatroyd}},
-  \bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Markovi\ifmmode~\acute{c}\else \'{c}\fi{}}}, \bibinfo {author}
-  {\bibfnamefont {B.}~\bibnamefont {Edwards}}, \bibinfo {author} {\bibfnamefont
-  {C.~A.}\ \bibnamefont {Hooley}}, \bibinfo {author} {\bibfnamefont {D.~A.}\
-  \bibnamefont {Sokolov}}, \bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Kikugawa}}, \bibinfo {author} {\bibfnamefont {C.}~\bibnamefont {Cacho}},
-  \bibinfo {author} {\bibfnamefont {M.~D.}\ \bibnamefont {Watson}}, \bibinfo
-  {author} {\bibfnamefont {T.~K.}\ \bibnamefont {Kim}}, \bibinfo {author}
-  {\bibfnamefont {C.~W.}\ \bibnamefont {Hicks}}, \bibinfo {author}
-  {\bibfnamefont {A.~P.}\ \bibnamefont {Mackenzie}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {P.~D.~C.}\ \bibnamefont {King}},\ }\href {\doibase
-  10.1103/PhysRevLett.130.096401} {\bibfield  {journal} {\bibinfo  {journal}
-  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {130}},\ \bibinfo {pages}
-  {096401} (\bibinfo {year} {2023})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carpenter}\ and\ \citenamefont
-  {Howard}(2009)}]{CarpenterAC09}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont
-  {Carpenter}}\ and\ \bibinfo {author} {\bibfnamefont {C.~J.}\ \bibnamefont
-  {Howard}},\ }\href {\doibase 10.1107/S0108768109000974} {\bibfield  {journal}
-  {\bibinfo  {journal} {Acta Crystallographica Section B}\ }\textbf {\bibinfo
-  {volume} {65}},\ \bibinfo {pages} {134} (\bibinfo {year} {2009})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Jahn}\ \emph {et~al.}(1937)\citenamefont {Jahn},
-  \citenamefont {Teller},\ and\ \citenamefont {Donnan}}]{JahnPRSL37}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.}\ \bibnamefont
-  {Jahn}}, \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont {Teller}}, \ and\
-  \bibinfo {author} {\bibfnamefont {F.~G.}\ \bibnamefont {Donnan}},\ }\href
-  {\doibase 10.1098/rspa.1937.0142} {\bibfield  {journal} {\bibinfo  {journal}
-  {Proceedings of the Royal Society of London. Series A - Mathematical and
-  Physical Sciences}\ }\textbf {\bibinfo {volume} {161}},\ \bibinfo {pages}
-  {220} (\bibinfo {year} {1937})},\ \Eprint
-  {http://arxiv.org/abs/https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1937.0142}
-  {https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1937.0142}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Jahn}\ and\ \citenamefont
-  {Bragg}(1938)}]{JahnPRSL38}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.~A.}\ \bibnamefont
-  {Jahn}}\ and\ \bibinfo {author} {\bibfnamefont {W.~H.}\ \bibnamefont
-  {Bragg}},\ }\href {\doibase 10.1098/rspa.1938.0008} {\bibfield  {journal}
-  {\bibinfo  {journal} {Proceedings of the Royal Society of London. Series A -
-  Mathematical and Physical Sciences}\ }\textbf {\bibinfo {volume} {164}},\
-  \bibinfo {pages} {117} (\bibinfo {year} {1938})},\ \Eprint
-  {http://arxiv.org/abs/https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1938.0008}
-  {https://royalsocietypublishing.org/doi/pdf/10.1098/rspa.1938.0008}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {\"Opik}\ and\ \citenamefont
-  {Pryce}(1957)}]{OpikRS57}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {U.}~\bibnamefont
-  {\"Opik}}\ and\ \bibinfo {author} {\bibfnamefont {M.~H.~L.}\ \bibnamefont
-  {Pryce}},\ }\href {http://www.jstor.org/stable/100101} {\bibfield  {journal}
-  {\bibinfo  {journal} {Proceedings of the Royal Society of London. Series A,
-  Mathematical and Physical Sciences}\ }\textbf {\bibinfo {volume} {238}},\
-  \bibinfo {pages} {425} (\bibinfo {year} {1957})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Sturge}(1968)}]{Sturge68}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Sturge}}\ }(\bibinfo  {publisher} {Academic Press},\ \bibinfo {year}
-  {1968})\ pp.\ \bibinfo {pages} {91--211}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Gehring}\ and\ \citenamefont
-  {Gehring}(1975)}]{GehringRPP75}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.~A.}\ \bibnamefont
-  {Gehring}}\ and\ \bibinfo {author} {\bibfnamefont {K.~A.}\ \bibnamefont
-  {Gehring}},\ }\href {\doibase 10.1088/0034-4885/38/1/001} {\bibfield
-  {journal} {\bibinfo  {journal} {Reports on Progress in Physics}\ }\textbf
-  {\bibinfo {volume} {38}},\ \bibinfo {pages} {1} (\bibinfo {year}
-  {1975})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pavarini}(2016)}]{PavariniChap}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Pavarini}},\ }\href {https://juser.fz-juelich.de/record/819465} {\emph
-  {\bibinfo {title} {{Q}uantum {M}aterials: {E}xperiments and {T}heory}}},\
-  edited by\ \bibinfo {editor} {\bibfnamefont {E.}~\bibnamefont {Pavarini}},
-  \bibinfo {editor} {\bibfnamefont {E.}~\bibnamefont {Koch}}, \bibinfo {editor}
-  {\bibfnamefont {J.}~\bibnamefont {van~den Brink}}, \ and\ \bibinfo {editor}
-  {\bibfnamefont {G.}~\bibnamefont {Sawatzky}},\ \bibinfo {series} {Schriften
-  des Forschungszentrums J\"ulich. Reihe modeling and simulation},
-  Vol.~\bibinfo {volume} {6}\ (\bibinfo  {publisher} {Forschungszentrum
-  J\"ulich GmbH Zentralbibliothek, Verlag},\ \bibinfo {address} {J\"ulich},\
-  \bibinfo {year} {2016})\ p.\ \bibinfo {pages} {420 S.}\BibitemShut {Stop}%
-\bibitem [{\citenamefont {Khomskii}\ and\ \citenamefont
-  {Streltsov}(2021)}]{KhomskiiCR21}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.~I.}\ \bibnamefont
-  {Khomskii}}\ and\ \bibinfo {author} {\bibfnamefont {S.~V.}\ \bibnamefont
-  {Streltsov}},\ }\href {\doibase 10.1021/acs.chemrev.0c00579} {\bibfield
-  {journal} {\bibinfo  {journal} {Chemical Reviews}\ }\textbf {\bibinfo
-  {volume} {121}},\ \bibinfo {pages} {2992} (\bibinfo {year} {2021})},\
-  \bibinfo {note} {pMID: 33314912},\ \Eprint
-  {http://arxiv.org/abs/https://doi.org/10.1021/acs.chemrev.0c00579}
-  {https://doi.org/10.1021/acs.chemrev.0c00579} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Goldschmidt}(1926)}]{Goldschmidt1926}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {V.}~\bibnamefont
-  {Goldschmidt}},\ }\href {\doibase 10.1007/BF01507527} {\bibfield  {journal}
-  {\bibinfo  {journal} {Naturwissenschaften}\ }\textbf {\bibinfo {volume}
-  {14}},\ \bibinfo {pages} {477} (\bibinfo {year} {1926})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Kieslich}\ \emph {et~al.}(2015)\citenamefont
-  {Kieslich}, \citenamefont {Sun},\ and\ \citenamefont
-  {Cheetham}}]{KieslichCS15}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Kieslich}}, \bibinfo {author} {\bibfnamefont {S.}~\bibnamefont {Sun}}, \
-  and\ \bibinfo {author} {\bibfnamefont {A.~K.}\ \bibnamefont {Cheetham}},\
-  }\href {\doibase 10.1039/C5SC00961H} {\bibfield  {journal} {\bibinfo
-  {journal} {Chem. Sci.}\ }\textbf {\bibinfo {volume} {6}},\ \bibinfo {pages}
-  {3430} (\bibinfo {year} {2015})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Garcia-Fernandez}\ \emph {et~al.}(2010)\citenamefont
-  {Garcia-Fernandez}, \citenamefont {Aramburu}, \citenamefont {Barriuso},\ and\
-  \citenamefont {Moreno}}]{garcia-fernandezJPCL10}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Garcia-Fernandez}}, \bibinfo {author} {\bibfnamefont {J.~a.}\ \bibnamefont
-  {Aramburu}}, \bibinfo {author} {\bibfnamefont {M.~T.}\ \bibnamefont
-  {Barriuso}}, \ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Moreno}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
-  Phys. Chem. Lett.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {647}
-  (\bibinfo {year} {2010})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Cammarata}\ and\ \citenamefont
-  {Rondinelli}(2014)}]{CammarataJCP14}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
-  {Cammarata}}\ and\ \bibinfo {author} {\bibfnamefont {J.~M.}\ \bibnamefont
-  {Rondinelli}},\ }\href {\doibase 10.1063/1.4895967} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {141}},\ \bibinfo {pages} {114704} (\bibinfo {year} {2014})},\
-  \Eprint
-  {http://arxiv.org/abs/https://pubs.aip.org/aip/jcp/article-pdf/doi/10.1063/1.4895967/15484681/114704\_1\_online.pdf}
-  {https://pubs.aip.org/aip/jcp/article-pdf/doi/10.1063/1.4895967/15484681/114704\_1\_online.pdf}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Lee}\ \emph {et~al.}(2016)\citenamefont {Lee},
-  \citenamefont {Bristowe}, \citenamefont {Lee}, \citenamefont {Lee},
-  \citenamefont {Bristowe}, \citenamefont {Cheetham},\ and\ \citenamefont
-  {Jang}}]{LeeCM16}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-H.}\ \bibnamefont
-  {Lee}}, \bibinfo {author} {\bibfnamefont {N.~C.}\ \bibnamefont {Bristowe}},
-  \bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont {Lee}}, \bibinfo
-  {author} {\bibfnamefont {S.-H.}\ \bibnamefont {Lee}}, \bibinfo {author}
-  {\bibfnamefont {P.~D.}\ \bibnamefont {Bristowe}}, \bibinfo {author}
-  {\bibfnamefont {A.~K.}\ \bibnamefont {Cheetham}}, \ and\ \bibinfo {author}
-  {\bibfnamefont {H.~M.}\ \bibnamefont {Jang}},\ }\href {\doibase
-  10.1021/acs.chemmater.6b00968} {\bibfield  {journal} {\bibinfo  {journal}
-  {Chemistry of Materials}\ }\textbf {\bibinfo {volume} {28}},\ \bibinfo
-  {pages} {4259} (\bibinfo {year} {2016})},\ \Eprint
-  {http://arxiv.org/abs/https://doi.org/10.1021/acs.chemmater.6b00968}
-  {https://doi.org/10.1021/acs.chemmater.6b00968} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Yoshida}\ \emph {et~al.}(2021)\citenamefont
-  {Yoshida}, \citenamefont {Akamatsu},\ and\ \citenamefont
-  {Hayashi}}]{YoshidaPRL21}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {S.}~\bibnamefont
-  {Yoshida}}, \bibinfo {author} {\bibfnamefont {H.}~\bibnamefont {Akamatsu}}, \
-  and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont {Hayashi}},\ }\href
-  {\doibase 10.1103/PhysRevLett.127.215701} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {127}},\ \bibinfo
-  {pages} {215701} (\bibinfo {year} {2021})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Herzberg}\ and\ \citenamefont
-  {Teller}(1933)}]{HerzbergZPC33}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
-  {Herzberg}}\ and\ \bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
-  {Teller}},\ }\href {\doibase doi:10.1515/zpch-1933-2136} {\bibfield
-  {journal} {\bibinfo  {journal} {Zeitschrift f\"ur Physikalische Chemie}\
-  }\textbf {\bibinfo {volume} {21B}},\ \bibinfo {pages} {410} (\bibinfo {year}
-  {1933})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bersuker}(1966)}]{BersukerPL66}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.}~\bibnamefont
-  {Bersuker}},\ }\href {\doibase https://doi.org/10.1016/0031-9163(66)91127-9}
-  {\bibfield  {journal} {\bibinfo  {journal} {Physics Letters}\ }\textbf
-  {\bibinfo {volume} {20}},\ \bibinfo {pages} {589} (\bibinfo {year}
-  {1966})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Kristoffel}\ and\ \citenamefont
-  {Konsin}(1967)}]{KristoffelPSSB67}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {N.}~\bibnamefont
-  {Kristoffel}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont
-  {Konsin}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
-  Status Solidi B}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {K39}
-  (\bibinfo {year} {1967})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Pearson}(1983)}]{PearsonJMS83}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~G.}\ \bibnamefont
-  {Pearson}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal} {J.
-  Mol. Struct.: THEOCHEM}\ }\textbf {\bibinfo {volume} {103}},\ \bibinfo
-  {pages} {25} (\bibinfo {year} {1983})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Fulton}\ and\ \citenamefont
-  {Gouterman}(2004)}]{FultonJCP04}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~L.}\ \bibnamefont
-  {Fulton}}\ and\ \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
-  {Gouterman}},\ }\href {\doibase 10.1063/1.1701181} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Chemical Physics}\ }\textbf {\bibinfo
-  {volume} {35}},\ \bibinfo {pages} {1059} (\bibinfo {year} {2004})},\ \Eprint
-  {http://arxiv.org/abs/https://pubs.aip.org/aip/jcp/article-pdf/35/3/1059/8125554/1059\_1\_online.pdf}
-  {https://pubs.aip.org/aip/jcp/article-pdf/35/3/1059/8125554/1059\_1\_online.pdf}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bersuker}(2013)}]{BersukerCR13}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~B.}\ \bibnamefont
-  {Bersuker}},\ }\href {\doibase 10.1021/cr300279n} {\bibfield  {journal}
-  {\bibinfo  {journal} {Chemical Reviews}\ }\textbf {\bibinfo {volume} {113}},\
-  \bibinfo {pages} {1351} (\bibinfo {year} {2013})},\ \bibinfo {note} {pMID:
-  23301718},\ \Eprint {http://arxiv.org/abs/https://doi.org/10.1021/cr300279n}
-  {https://doi.org/10.1021/cr300279n} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Bethe}(1929)}]{BetheAP29}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
-  {Bethe}},\ }\href {\doibase https://doi.org/10.1002/andp.19293950202}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annalen der Physik}\ }\textbf
-  {\bibinfo {volume} {395}},\ \bibinfo {pages} {133} (\bibinfo {year}
-  {1929})},\ \Eprint
-  {http://arxiv.org/abs/https://onlinelibrary.wiley.com/doi/pdf/10.1002/andp.19293950202}
-  {https://onlinelibrary.wiley.com/doi/pdf/10.1002/andp.19293950202}
-  \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Van~Vleck}(1932)}]{VanVleckPR32}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.~H.}\ \bibnamefont
-  {Van~Vleck}},\ }\href {\doibase 10.1103/PhysRev.41.208} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {41}},\
-  \bibinfo {pages} {208} (\bibinfo {year} {1932})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Paxton}(2009{\natexlab{a}})}]{PaxtonNotes}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont
-  {Paxton}},\ }\href {https://tonypaxton.org/Notes/TB.pdf} {\emph {\bibinfo
-  {title} {Multiscale Simulation Methods in Molecular Sciences}}},\ edited by\
-  \bibinfo {editor} {\bibfnamefont {J.}~\bibnamefont {Grotendorst}}, \bibinfo
-  {editor} {\bibfnamefont {N.}~\bibnamefont {Attig}}, \bibinfo {editor}
-  {\bibfnamefont {S.}~\bibnamefont {Bl\"ugel}}, \ and\ \bibinfo {editor}
-  {\bibfnamefont {D.}~\bibnamefont {Marx}},\ Vol.~\bibinfo {volume} {42}\
-  (\bibinfo  {publisher} {Academic Press, Institute for Advanced Simulation,
-  Forschungszentrum J\"ulich},\ \bibinfo {year} {2009})\ pp.\ \bibinfo {pages}
-  {145--176}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Carter}\ \emph {et~al.}(2012)\citenamefont {Carter},
-  \citenamefont {Shankar}, \citenamefont {Zeb},\ and\ \citenamefont
-  {Kee}}]{CarterPRB12}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.-M.}\ \bibnamefont
-  {Carter}}, \bibinfo {author} {\bibfnamefont {V.~V.}\ \bibnamefont {Shankar}},
-  \bibinfo {author} {\bibfnamefont {M.~A.}\ \bibnamefont {Zeb}}, \ and\
-  \bibinfo {author} {\bibfnamefont {H.-Y.}\ \bibnamefont {Kee}},\ }\href
-  {\doibase 10.1103/PhysRevB.85.115105} {\bibfield  {journal} {\bibinfo
-  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {85}},\ \bibinfo
-  {pages} {115105} (\bibinfo {year} {2012})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Ivanic}\ and\ \citenamefont
-  {Ruedenberg}(1996)}]{IvanicJPC96}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Ivanic}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
-  {Ruedenberg}},\ }\href {\doibase 10.1021/jp953350u} {\bibfield  {journal}
-  {\bibinfo  {journal} {The Journal of Physical Chemistry}\ }\textbf {\bibinfo
-  {volume} {100}},\ \bibinfo {pages} {6342} (\bibinfo {year} {1996})},\ \Eprint
-  {http://arxiv.org/abs/https://doi.org/10.1021/jp953350u}
-  {https://doi.org/10.1021/jp953350u} \BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Finnis}\ \emph {et~al.}(1998)\citenamefont {Finnis},
-  \citenamefont {Paxton}, \citenamefont {Methfessel},\ and\ \citenamefont {van
-  Schilfgaarde}}]{FinnisPRL98}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
-  {Finnis}}, \bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont {Paxton}},
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {Methfessel}}, \ and\
-  \bibinfo {author} {\bibfnamefont {M.}~\bibnamefont {van Schilfgaarde}},\
-  }\href {\doibase 10.1103/PhysRevLett.81.5149} {\bibfield  {journal} {\bibinfo
-   {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {81}},\ \bibinfo
-  {pages} {5149} (\bibinfo {year} {1998})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Paxton}\ and\ \citenamefont
-  {Finnis}(2008)}]{PaxtonPRB08}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~T.}\ \bibnamefont
-  {Paxton}}\ and\ \bibinfo {author} {\bibfnamefont {M.~W.}\ \bibnamefont
-  {Finnis}},\ }\href {\doibase 10.1103/PhysRevB.77.024428} {\bibfield
-  {journal} {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume}
-  {77}},\ \bibinfo {pages} {024428} (\bibinfo {year} {2008})}\BibitemShut
-  {NoStop}%
-\bibitem [{\citenamefont {Ewald}(1921)}]{Ewald1921}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~P.}\ \bibnamefont
-  {Ewald}},\ }\href {\doibase https://doi.org/10.1002/andp.19213690304}
-  {\bibfield  {journal} {\bibinfo  {journal} {Annalen der Physik}\ }\textbf
-  {\bibinfo {volume} {369}},\ \bibinfo {pages} {253} (\bibinfo {year}
-  {1921})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Paxton}(2009{\natexlab{b}})}]{Questaal}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.}~\bibnamefont
-  {Paxton}},\ }\href {https://www.questaal.org/docs/code/tbe/} {\enquote
-  {\bibinfo {title} {{TBE code}},}\ } (\bibinfo {year}
-  {2009}{\natexlab{b}})\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Liechtenstein}\ \emph {et~al.}(1995)\citenamefont
-  {Liechtenstein}, \citenamefont {Anisimov},\ and\ \citenamefont
-  {Zaanen}}]{LiechtensteinPRB95}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~I.}\ \bibnamefont
-  {Liechtenstein}}, \bibinfo {author} {\bibfnamefont {V.~I.}\ \bibnamefont
-  {Anisimov}}, \ and\ \bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
-  {Zaanen}},\ }\href {\doibase 10.1103/PhysRevB.52.R5467} {\bibfield  {journal}
-  {\bibinfo  {journal} {Phys. Rev. B}\ }\textbf {\bibinfo {volume} {52}},\
-  \bibinfo {pages} {R5467} (\bibinfo {year} {1995})}\BibitemShut {NoStop}%
-\bibitem [{\citenamefont {Inc.}()}]{Mathematica}%
-  \BibitemOpen
-  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.~R.}\ \bibnamefont
-  {Inc.}},\ }\href {https://www.wolfram.com/mathematica} {\enquote {\bibinfo
-  {title} {Mathematica, {V}ersion 13.3},}\ }\bibinfo {note} {Champaign, IL,
-  2023}\BibitemShut {NoStop}%
-\end{thebibliography}%
+%\bibliographystyle{apsrev4-1}
+\bibliography{perovskites}
 

### 2023-12-27 manuscript/referee/reply.tex
reply added

--- 2023-12-27 manuscript/prb-submitted/paper.tex
@@
-\documentclass[a4paper,prb,twocolumn,longbibliography]{revtex4-1}  %a4paper,prb,twocolumn
+\documentclass[a4paper,prb]{revtex4-1}  %a4paper,prb,twocolumn
 %\documentclass[preprint]{revtex4-1}
@@
 
-\title{Jahn-Teller effect with rigid octahedral rotations in perovskites} %Cooperative
+\textbf{BK14571/Naheed: Jahn-Teller effect with rigid octahedral rotations in perovskites}
 
-%\title{Orbital ordering in perovskites transition metal oxides with rigid octahedral rotations}
+\rev{
+The paper "Jahn-Teller effect with rigid octahedral rotations in
+perovskites" by R. Naheed and co-authors represents in my opinion a
+very nice piece of work, where the authors thoroughly study a rather
+complicated subject of influence of rotation and tilting on lifting
+orbital degeneracy. However, it has to be mentioned that there is one
+rather general point, which must be cleared out before the decision
+can be made.
 
-\author{Rukhshanda Naheed}
-\affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}
+The present treatment follows a general route often taken in the JT
+physics: to consider the effect of Madelung field, but there is also
+another extremely important contribution to the crystal field coming
+from the hybridization, i.e. the overlap between orbitals centered on
+different sites. Typically it acts in the same direction, but this
+effect should be taken into account for the quantitative results, on
+which the authors aimed. The angle dependence of the hopping
+integrals, can be considered via the Slater-Koster approximation.
 
-\author{M. Ahsan Zeb}
-\affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}
-\email{ahsan.zeb@hotmail.com}
-%\orcidlink{https://orcid.org/0000-0002-3448-2357}
-
-\author{Kashif Sabeeh}
-\affiliation{Department of Physics, Quaid-i-Azam University, Islamabad 45320, Pakistan}
-
-\date{\today}
-\begin{abstract}
-
-We consider
-rigid rotation and tilting of the 
-%BO$_{6/2}$ 
-anion octahedra around the transition metal ions
- in ABO$_3$ perovskites
- from the viewpoint of Jahn-Teller problem
- and study the
-effect of the crystal field of the nearest A and B ion cages 
-on the single electron spectrum of the 
-central 
-transition metal B ions.
-While the crystal field of the octahedra,
-which
-% quenches the orbital angular momentum of the central B ion and 
-creates degenerate manifolds $e_g$ and $t_{2g}$,
-do not change with such rigid rotations, 
-the field of 
-%A and B ionic cages %that immediately surround the octahedra
-A and B cages
-deforms significantly %with the octahedral rotations 
-from the ideal octahedral field
-in a way that
-leads to sizeable splittings in 
-%the $e_g$ and $t_{2g}$ manifolds of the central B ion.
-these manifolds.
-%Similar to the Jahn-Teller problem,
-The lowering of the ground state energy
-of a given many-electron configuration
-due to these splittings
-can thus be an important driving force behind the octahedral rotations 
-and associated structural transformations.
-We find that the size of the splitting and the 
-%local orbital ordering 
-order of the orbitals
-are
-determined by a competition between the A and B cages, 
-as well as a competition between the tilt and rotation angles.
-
-\end{abstract}
-\maketitle
-
-Perovskites  
-exhibit a rich variety of intriguing 
-electronic,
-magnetic
- and optical
-properties~\cite{ZubkoARCMP11,
-HwangNM12, 
-BhattacharyaARMR14,
-HellmanRMP17,
-ChenJPCM17,DagottoS05,DagottoMRSB08}
-due to the interplay between
-spin, orbital, and structural degrees of 
-freedom
-and widely varying electronic 
-correlations.
-These materials 
-are important
-both for practical applications in all sorts of modern devices 
-and 
-fundamental understanding of various physical 
-phenomena~\cite{SalamonRMP01,
-WangS03,
-DawberRMP05,
-SchlomARMR07,
-KosterRMP12}.
-
-%Their crystal structures 
-The perovskite structures
-have a common formula unit ABX$_3$,
-where 
-%positive ions A and negative ions X form a cube and an octahedron around positive ion B.
-A and B are positive ions while X are negative ions 
-%whose six-fold coordination forms octahedra around B.
-that form octahedra around  B.
-In a cubic perovskite,
-the octahedra are symmetric, 
-but they can 
-distort~\cite{
-BersukerCCR75,
-KugelSPU82,
-MillisN98,
-TerakuraPMS07,
-HalcrowRSC13,
-LufasoAC04}
-or simply 
-rotate~\cite{
-GlazerAC72, ThomasAC96,
-WoodwardAC97a,WoodwardAC97b,
-HowardAC98,StokesAC02,AngelPRL05}
- to lower the symmetry
-and produce, e.g., a rhombohedral, tetragonal or orthorhombic structure.
-% cubic perovskite [spacegroup 221] can transform to:
-% crystal system: spacegroups
-% triclinic: 2
-% monoclinic: 11,12,15
-% orthorhombic: 59,62,63,71,74
-% tetragonal 127,139,140
-% rhombohedral/trigonal: 167
-% cubic: 204, 221 
-Octahedral rotations also occur in other perovskite related structures
-and
-have been extensively 
-studied
-due to their crucial role in determining various physical properties,
-e.g., in 
-ferroelectric~\cite{GhosezNM11,
-RondinelliAM12,
-SchickPRB14,
-SimPRB14,
-LeePRL17,
-WangPRL22,
-ZhouPRB22,
-GaoPRB23} and 
-multiferroic~\cite{KhomskiiPhys09,
-BenedekPRL11,
-YangPRL14,
-YePRB18,
-ZhangPRL20,
-ZhangYajunPRL20, 
-ZhouPRB21,
-ZhangPRL22}
-systems.
-The interplay of octahedral rotations
-and 
-spin-orbit coupling~\cite{AmatNL14,KrachJPCM23},
-breathing distortions~\cite{BalachandranPRB13},
-strain~\cite{Aguado-PuentePRL11},
-defects~\cite{JiaPRB22}, and
-pressure~\cite{XiangPRB17},
-and 
-their role in
-magnetostructural phase transitions~\cite{JohnsonPRL20},
-orbital order~\cite{OgawaPRL12,ChenPRL19}, orbital anisotropy~\cite{HuangPRB21}, 
-and
-%surface electronic structure under in-plane uniaxial compression~\cite{MoralesPRL23}
-surface electronic structure~\cite{MoralesPRL23},
-have also been investigated.
-% JT interacting with octa tilting:
-Since, usually, the octahedra are not just %(Jahn-Teller) 
-distorted or rotated but a combination of both,
-the influence of these two 
-structural mutations %instabilities 
-on each other has recently been explored by many authors~\cite{LufasoAC04,CarpenterAC09,ChenPRL19}
-as well.
-
-While the tetragonal distortion of the octahedra is associated with
-a (cooperative) Jahn-Teller 
-effect~\cite{JahnPRSL37,JahnPRSL38,
-OpikRS57,
-Sturge68,
-GehringRPP75,
-BersukerCCR75,
-KugelSPU82,
-MillisN98,
-LufasoAC04,
-TerakuraPMS07,
-HalcrowRSC13,
-PavariniChap,
-KhomskiiCR21}
-(i.e., the orbital degeneracy of the metal ion coordinated by the anionic octahedron
-is lifted, which stabilises the distortion),
-%[as it distorts the octahedral field at the central site that split its electronic states],
-the rotation and tilting of the octahedra are almost always 
-explained empirically in terms of 
-the relative sizes of the three ions
-with the
-Goldschmidt tolerance factor~\cite{Goldschmidt1926,KieslichCS15}. 
-%[probably because rigid rotation of the octahedra do not change its potential at the central site]
-%We only find two exceptions.
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/struc/structures-combined-bonds-labelled-2}
-\includegraphics[width=1\linewidth]{structures-combined-bonds-labelled-2}
-\caption{
-Crystal structures and coordination cages.
-Crystal structures of cubic (a) and orthorhombic (b) perovskites.
-The anions (red) form the shown octahedra around 
-the B cations (gold), while the A cations (green) sit in the voids between the octahedra.
-In the orthorhombic structure shown here (b),
- the octahedra are rotated and tilted by $15^\circ$.
-(c-d)
-The coordination cages of A %(green) 
-and B 
-%(golden) 
-cations just next to the anion 
-%(red) 
-octahedron
-around a B ion in cubic %(c)
- and orthorhombic %(d)
-  perovskites.
-In the anion octahedron's frame,
-the cages are symmetric and aligned to the octahedron in the cubic perovskites (c),
-while they are rotated and slightly distorted in the orthorhombic perovskites (d).
-}
-\label{fig:struc}
-\end{center}
-\end{figure}
-
-Based on density functional theory (DFT) calculations,
-a few recent works
-~\cite{garcia-fernandezJPCL10,CammarataJCP14,LeeCM16,YoshidaPRL21}, 
-however, 
-suggest that the octahedral rotation and tilting is 
-a second order Jahn-Teller effect
-~\cite{HerzbergZPC33,BersukerPL66,KristoffelPSSB67,PearsonJMS83,FultonJCP04,BersukerCR13}
-%\az{describe SOJT in a sentence: coupling to the low lying unoccupied states on the JT ion, or orbital hybridisation with other ions, coupling between bands...}
-(i.e., the distortion is stabilised by a coupling between the ground and excited adiabatic potential energy surfaces).
-% garcia-fernandezJPCL2010
-Garcia-Fernandez~et~al.
-study
-potassium fluoride perovskite family KMF$_3$ (M$=$Ca$^{2+}$ or a $3$d transition metal)
-and found that the tilting angle
-depends on the covalent bonding through the mixing of occupied and 
-low-lying unoccupied orbitals of the transition metal~\cite{garcia-fernandezJPCL10}.
-% CammarataJCP2014
-Cammarata and Rondinelli
-find a negative correlation between metal-oxygen bond covalency 
-and octahedral rotation in orthorhombic perovskite oxides~\cite{CammarataJCP14}.
-% Lee, nick2016
-Lee~et~al. find 
-similar results for metal-iodine bonding in
-lead iodide perovskites,
-where the role of 
-the hydrogen bonding 
-in a hybrid perovskite with
-organic ammonium ions at A sites
-is also found to be crucial~\cite{LeeCM16}.
-Yoshida~et~al.
-use DFT along with 
-representation theory analysis 
-and 
-indicate that 
-the rotations are induced by bonding interaction 
-between the valence and conduction band Bloch states at different wavevectors
-that are mapped onto each other on Brillouin zone folding
- for the associated lattice distortion~\cite{YoshidaPRL21}.
-
-We take a completely different approach to this problem.
-We go back to the basics
-and see 
-what is it that lifts 
- the orbital degeneracy in the classical JT effect?
-It is a specific 
-deformation of the crystal field 
-%(${\sim z^2}$)
-at the transition metal (JT ion) site.
-Does the same happen in the case of octahedral tilting and rotations?
-While the potential of an octahedral anion cage 
-in its own frame
-does not change 
-%in case of 
-with
-rigid rotations for obvious reason,
-the total crystal field 
-does deform %indeed
-because
- the rest of the lattice is not only rotated
-  in a given octahedron's frame (that turns its non-spherical potential)
- but also distorted owing to the accompanying structural transformation.
-%So, in principle, there should be a (first order) JT effect at play.
-Using this insight
-and elements of crystal field theory~\cite{BetheAP29,VanVleckPR32,PavariniChap},
-%here in this manuscript,
-we 
-consider next two coordination cages around an octahedron
-% explore this problem in detail
-and find that,
-just like a first order JT effect,
- the deformed crystal field 
-in this case also lifts the orbital degeneracy,
-by a significant amount for typical system parameters,
-signalling the instability against the rotations.
-
-% cooperative: pairs of alpha beta....
-% terminnology: rotation vs tilt
-% coop/consistent rotations/tilting then makes Pbnm etc...
-
-Since the octahedra are connected to each other 
-(making a 3-dimensional network in the perovskite structure),
-rotating one octahedron rotates all other in the crystal in a consistent fashion~\cite{GlazerAC72};
- see Figs.~\ref{fig:struc}(a,b).
-We consider an octahedral \emph{rotation} $\beta$ around $001$ direction
-(that transforms the structure from cubic Pm$\bar 3$m to tetragonal P4/mbm)
-%({No.~$127$})
-followed by a \emph{tilting} $\alpha$ around the new $110$ direction
-(transforming to orthorhombic Pbnm, 
-%({No.~$62$})
-or Imma 
-%({No.~$74$})
- at ${\beta=0}$).
-We use the rotation and tilt terminology for these 
-two angles throughout the rest of the manuscript.
-
-Beyond the anion octahedron,
-each transition metal ion B in a cubic perovskite
-is coordinated by two cation cages,
-a cube of A and an octahedron of B, as shown in Figs.~\ref{fig:struc}(c,d).
-Including the 
-%electrostatic 
-potential of these two ion cages
-into the 
-crystal field Hamiltonian of 
-the central ion B,
-we explore the effect 
-of the rotation and tilting on 
-%the splittings in 
-its $t_{2g}$ and $e_g$ manifolds
-that are
-created primarily by the anion's octahedral potential.
-We find that the degeneracy of $t_{2g}$ and $e_g$
-is lifted. 
-The size of the splitting 
-and 
-%local orbital ordering
-the order of the orbitals
-depend
-on the relative charges on the two types of cations
-and a competition between rotation and tilting.
-At typical parameter values,
-the splitting is large enough 
-to play a major role in 
-the corresponding structural instability. 
-The qualitative picture developed by our calculations 
-holds even when the potential of the full lattice is considered.
-
-% 3 dim hilbert space of t2g, 2 dim hipbert space of eg
-% the mixing of t2g states due to rot and tilting is equiv to an artifact in cubic phase
-% so it's not similar to SOCJT states at diff energy mix due to distortion.
-% exlain it in the results/discussion section.....???
-
-\com{
-$\alpha=0, \beta \neq 0$\\
-Tetragonal:
-127. P 4 / m b m
-$\alpha \neq 0,\beta=0$\\
-Orthorhombic:
-74. I m m a
-$\alpha,\beta \neq 0$\\
-Orthorhombic:
-62. Pbnm
+Other, more technical comments:
 }
 
-The paper is organised as follows.
-Section~\ref{sec:formalistm}
-presents the formalism and 
-Sec.~\ref{sec:JT} reviews the Jahn-Teller effect to
-introduce the notation and concepts involved
-by considering tetragonal distortion of an octahedron.
-%\az{[.... multiple subsections?]}
-The model and calculations are presented
-in Sec.~\ref{sec:calc},
-where
-we first discuss the relative contributions of the three closest ion cages
-in the cubic structure
- to
-the crystal field at the central transition metal site 
-and crystal field splitting between its $e_g$ and $t_{2g}$ manifolds
-(Sec.~\ref{sec:relativeVoctABO}),
-and then 
-describe the deformation effects of 
-rigid octahedral rotations %(Sec.~\ref{sec:rotation})
-on
-the structure (Sec.~\ref{sec:structure}) 
-and crystal field (Sec.~\ref{sec:deformCF}).
-The results are in Sec.~\ref{sec:results},
-where we %seperately
-present the splitting in the single particle spectrum
-belonging to the $t_{2g}$ (Sec.~\ref{sec:t2g})
-and $e_g$ (Sec.~\ref{sec:eg-gen}) manifolds,
-and finally describe the effect of the full lattice (Sec.~\ref{sec:FL}).
-%\az{appendix?}
-
-\section{Formalism: Crystal field Hamiltonian using multipole expansion of the crystal field potential}
-\label{sec:formalistm}
-
-Let us introduce the basic formalism we use throughout this manuscript.
-The spectrum of an atom or ion
-changes in the presence of nearby charged species.
-This is described by the crystal field Hamiltonian of the atom
-that contains the coupling between its atomic orbitals and/or their energy shifts
-induced by the electrostatic potential of those charges.
-Since the angular part of atomic orbitals are described by 
-the spherical harmonics,
-an expansion of the potential at the atom's site 
-in the same bases simplifies the analysis.
-This is because
-the effect of various multipole components of the potential
-is governed by certain selection rules 
-(enforced by the symmetries of the spherical harmonics
-through Gaunt coefficients, see below).
-
-If we have an arrangement of ions with charge $q$ around a given site,
-we can express their %(crystal field) 
-potential in terms of spherical harmonics~\cite{PavariniChap}, 
-\begin{align}
-V(\vec r) &= \frac{q}{a}\sum_{lm}V_{lm}~\left(\frac{r}{a}\right)^l \ylm{lm},
-\end{align}
-where $a$ sets the length scale, $\hat r=\vec r/r$ is the direction of $\vec r$,
-and $V_{l,m}$ are multipole components of the potential
- (for the given site as origin and a chosen orientation).
-%and calculate the crystal field hamiltonian of the central ion/atom.
-Assuming we have a transition metal atom/ion
-at the central site
-with
-only $d$-orbitals ($l=2$),
-the matrix elements of its crystal field Hamiltonian
-are then given by,
-\begin{align}
-H_{m' m''} &= -\frac{q}{a}\sum_{l,m} V_{lm} C_{l}^{m'm''m} D_{l} ,
-\end{align}
-where 
-$C_{l}^{m'm''m}=\braket{Y_{2m'}| Y_{lm}| Y_{2m''}}$ are Gaunt coefficients for the given (real or complex) spherical harmonics,
-and $D_{l}=\braket{(r/a)^l}$
-is the expectation of $(r/a)^l$ evaluated in the $d$-orbitals bases
-assuming the same radial dependence for all orbitals~\cite{PaxtonNotes}.
-The sum is restricted to even values of $l\leq 4$ as 
-$C_{l}^{m'm''m}=0$ otherwise,
-with $-l \leq m \leq l$.
-
-We consider transition metal oxides as an example perovskite system throughout the rest of the manuscript,
-but our calculations and results are general and also apply to perovskite transition metal compounds with other anions, e.g., halides and chalcogenides.
-
-\subsection{Atom/ion in an octahedral field: $t_{2g}$  and $e_g$ manifolds}
-\label{sec:egt2g}
-Consider six oxygen (O) ions each with a charge $-q_o$ making an octahedron of size $a$ (where these anions are placed at the face centres of a cube of edge length $a$).
-The non-spherical part of the potential they
- produce at the centre of the octahedron
- %that is 
- relevant for the $d$-orbitals contains 
- only two $l=4$ components, 
-  in a specific ratio (${V_{4,0}:V_{4,4}=1:\sqrt{5/7}}$),
- and is called octahedral field. 
-It is given by~\cite{PavariniChap},
-\begin{align}
-\label{eq:voct}
-V_{oct}(\vec r) = -\frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right].
-\end{align}
-%where the monopole and $l>4$ components have been dropped
-The crystal field Hamiltonian of a transition metal ion B 
-%at the centre 
-in the field $V_{oct}(\vec r)$
-turns out to be diagonal,
-with its states split into two manifolds: 
-% $\Delta$ apart:
-$H_{mm} = -\Delta/3$ for $m\in\{-2,-1,1\}$ ($xy,yz,zx$ orbitals)
-called $t_{2g}$,
-and 
-$H_{mm} = +2\Delta/3$ for $m\in\{2,0\}$ ($x^2-y^2,z^2$ orbitals)
-called $e_g$.
-The crystal field splitting between the two manifolds is
-${\Delta=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
-
-\com{
-$V_{oct}(\vec r)$ causes the d-orbitals to split into two manifolds,
-$t_{2g}$  and $e_g$, where $t_{2g}$ contains three degenerate states ($xy,yz,zx$) while $e_g$ has two degenerate states ($x^2-y^2,z^2$).
-The crystal field splitting between the two manifolds is
-${\Delta=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
-\az{We will see how these degeneracies are lifted as we elongate (or compress)
-the octahedron along a ....??}
+\begin{enumerate}
+\item
+\rev{It is not clearly explained how exactly the authors define sign of
+q0, qA,qB. E.g. the charge neutrality relation mentioned above (16) is
+$qB = 3q0 - qA$. For oxides q0 is -2 and $qA>0$ and does not typically
+exceed +4, but then $qB<0$. Obviously the authors used some other
+conventions, but do not really explain this.
 }
 
-\section{Jahn-Teller Effect}
-\label{sec:JT}
+Thanks for pointing it out.
+We take the charge on the anion/oxygen to be $-q_o$ (so $q_B=3q_o-q_A$ is not incorrect).
+This is stated at the start of  
+Sec.~I-A: Atom/ion in an octahedral field: $t_{2g}$  and $e_g$ manifolds (page 3, first column).
+For oxides, $-q_o=-2$ (so $q_o=2$), and the charge netrality correctly gives $q_B=6-q_A$;
+$q_A, q_B >0$.
 
-The Jahn--Teller 
-effect~\cite{JahnPRSL37,JahnPRSL38,
-OpikRS57,
-Sturge68,
-GehringRPP75,
-BersukerCCR75,
-KugelSPU82,
-MillisN98,
-LufasoAC04,
-TerakuraPMS07,
-HalcrowRSC13,
-PavariniChap,
-KhomskiiCR21}
- describes the 
-geometric and electronic instability of a %non-linear 
-molecule, cluster or crystal with
-a symmetric structure and orbitally degenerate ground state
-%(i.e., except Kramers degeneracy)
-against structural distortions.
-The distortions  
-reduce the symmetry of the structure
-and lift the electronic degeneracy.
-This lowers the energy of the system proportional to
-the distortion.
-The elastic energy of the structure that increases as the square of the distortion
-competes with this linear term and the optimum structure 
-is obtained at a finite distortion, as described below.
+In the revised version,
+for clarity,
+we have added a comment ``(remember that we take anion charge to be $-q_o$)''
+just after the charge neutrality relation above Eq.~(16).
 
-%\subsection{Dependence of electronic and elastic energies on the distortion}
-
-The dependence of the elastic energy on the distortion can be roughly explained
-as follows.
-Consider an 
-elongation or a compression of an octahedron along one of its axes by $a\delta$,
-where $a$ is the size of the octahedron and lattice constant of the cubic perovskite structure.
-The corresponding change in the unit cell volume would be linear in $\delta$
-as $\sim a^3 \delta$
-so the elastic energy
-would change as $\sim\delta^2$.
-Assuming a linear change 
- in the electronic spectrum,
-  the total energy has a form
-$E=-\rho\delta + K \delta^2$, where $\rho$ and $K$ are positive constants 
-describing the changes in the electronic and elastic energies,
-and would be optimum at $\delta=\rho/2K$.
-In general, as long as the two competing terms 
-are not the same degree monomial in the distortion,
-the ground state can have a finite distortion.
-We use this argument to focus only on the changes
- in the electronic energy throughout this paper.
-
-\com{
-The dependence of the elastic energy on the distortion can be roughly explained
-as follows.
-Consider a 
-hypothetical 
-distortion of an octahedron 
-along two of its axes, say, by $a\delta_1,a\delta_2$,
-where $a$ is the lattice constant of the cubic structure.
-The corresponding change in the unit cell volume would be linear in $\delta_{1,2}$
-as $\sim a^3\left(\delta_1+\delta_1\right)$
-so the elastic energy %(for an isotropic system) 
-changes as $\sim\left(\delta_1+\delta_1\right)^2$.
-A linear change ($\propto \delta_{1/2}$) in the electronic spectrum is required to produce
- a finite distortion in the optimum structure (or the ground state of full electron-lattice/nuclear problem).
+\item
+\rev{
+I'm not sure that it is clear for a general reader why from volume
+dependence $V = a^3 (\delta_1 + \delta_2)$ follows that the elastic energy
+must be proportional to $(\delta_1 + \delta_2)^2$ [BTW one of the
+subscripts is wrong]. OK, they know from the high-school courses that
+the elastic term must quadratic and could agree, but why the same
+logic applies to $(\alpha^2 + \beta^2)^2$ can be not clear. Moreover,
+it's not clear a priori why there is no cubic terms. Please explain
+this part in more detail.
 }
 
-It is worth reminding that, in the Jahn-Teller problem,
-we usually consider single particle spectrum, i.e.,
-single electron energy states,
-to analyse the ground state of a many electron system,
-which is the lowest energy ``electronic configuration'' 
-(a combination of occupied single particle states 
-out of all available single particle states, 
-or a slater determinant of that combination to be more precise!).
-So a degenerate set of states that are completely occupied
-makes a non-degenerate many electron state because 
-only a single configuration/combination is possible.
-For a given number of electrons in the d-shell of the transition metal ion,
-we can determine the (most likely) configuration(s) or ground state(s)
-using Hund's rule and see if it is degenerate or otherwise.
+Thanks. 
+The the main point we
+tried to make here is that 
+the electronic and elastic energies have different dependence on the distortion (so the optimum structure is distorted).
+For our purpose, it is not important to know the exact form of the elastic energy and whether anharmonic effects would be important or not.
 
-\com{
-Instability:\\
- Low/high spin configurations, rules/arguments using single particle spectrum and a given low/high spin state with a given number of electrons:\\
-elastic energy vs electronic... number of electrons... multi-electron configurations.... degenerate vs non-degenerate cases...
+To avoid any distraction and confusion,
+we have rewritten the whole paragraph. 
+We now focus
+on conveying the key point without
+unnecessary details.
+
+\item
+\rev{
+Fig. 7. Should not be there explained what a bold line means? And
+why there is no a bold line for dashed curves?
 }
 
-In the following, we 
-consider an octahedral environment around a transition metal ion 
-and 
-illustrate how the changes in the electronic energy 
-can be calculated
- when the octahedron is elongated.
+Thanks for noticing. 
+What appears to be a bold line are actually two nearly degenerate lines of the same thickness as the other lines in the plot.
+In comparison to the dashed lines (nearest AB cages only), 
+the Ewald sum
+in case of infinite lattice considers
+a large number of \emph{unit cells}
+that include some \emph{incomplete}
+coordination cages at the boundary, 
+ which breaks some symmetries present in the 
+ case of complete coordination cages.
 
-\subsection{Tetragonal distortion of an octahedron}
-\label{sec:JTtertagonal}
+ To avoid any confusion,
+we have included in the caption:
+ ``(The bold black line is nothing but an overlap of two practically degenerate black lines.)''.
 
-Let us consider elongation of an octahedron % in Sec.~\ref{sec:egt2g} 
-along one of its O-B-O bonds. 
-Align the cartesian axes along O-B-O bonds and stretch the two bonds along $z$-axis equally by an amount $a\delta$.
-%where $a$ is the size of the octahedron (the distance between the O-O along any cartesian axes).
-The potential $V^{JT}(\vec r)$ at the central B site (JT ion) of this deformed octahedron 
-still contains only a few non-zero components (see appendix for a method to calculate $V_{lm}^{JT}$).
-Not only the ratio 
-$V_{4,0}^{JT}:V_{4,4}^{JT}$ now deviates from
- ideal 
-octahedral field in \eref{eq:voct},
-there is an $l=2$ component induced due to the deformation,
-\begin{align}
-%V_{0,0}^{JT}=& \frac{8 \sqrt{\pi } (2 \delta +3)}{\delta +1},\\
-V_{2,0}^{JT}=& -\frac{32 \sqrt{\frac{\pi }{5}} \delta  \left(\delta ^2+3 \delta +3\right)}{(\delta +1)^3},\\
-V_{4,0}^{JT}=& \frac{32}{3} \sqrt{\pi } \left(\frac{4}{(\delta +1)^5}+3\right),\\
-V_{4,4}^{JT}=& \frac{32 \sqrt{35 \pi }}{3}.
-\end{align}
-
-\com{
-At $\delta=0$, keeping only the non-spherical components, 
-we obtain the
- octahedral potential for a symmetric octahedron~\cite{PavariniChap},
-\begin{align}
-\label{eq:voct}
-\lim_{\delta\to0}V^{JT}(\vec r) \to V_{oct}(\vec r) = -\frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right],
-\end{align}
+\item
+\rev{
+I would also suggest to put labels of the A and B cages to Fig. 1.
 }
 
-The crystal field Hamiltonian of the JT ion,
-${H_{m' m''}^{JT} = (q_o/a)\sum_{l,m} V_{lm}^{JT} C_{l}^{m'm''m} D_{l}}$,
-still turns out to be diagonal 
-(i.e., the deformation $\delta$
-will not couple these orbitals to each other),
-but the degeneracies of the two manifolds is lifted
-and their respective average energies also shifted.
-Defining 
-$F_n(\delta) = 1-1/(1+\delta)^n$,
-we see that
-the $t_{2g}$ now splits into two levels,
-with energies
-\begin{align}
-E_{xy} =&
-\frac{32}{7}\frac{q_o}{a} \left(
- D_2F_3 - \frac{20}{9}D_4F_5 
-\right),\\
-E_{yz} =& E_{zx} = -\frac{1}{2} E_{xy},
-\end{align}
-as measured from their average 
-$E_0^{t_{2g}} = -64q_oD_4 \left(3-F_5\right)/9a$.
-Similarly, $e_g$ splits up as
-\begin{align}
-E_{x^2-y^2}=&
-\frac{32}{7}\frac{q_o}{a} \left(D_2F_3+\frac{5}{3} D_4F_5\right),\\
-E_{z^2}=&-E_{x^2-y^2},\\
-\end{align}
-as measured from their average 
-$E_0^{e_{g}} = 32 q_oD_4 \left(3-F_5\right)/3a$.
-The crystal field splitting becomes
-$\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=
-160q_oD_4\left(3-F_5\right)/9a$.
-At small $\delta$, 
-expanding 
-$F_3,F_5$
- up to first order in $\delta$,
-we obtain
-\begin{align}
-\label{eq:JTt2g}
-(E_{xy},E_{yz},E_{zx})&= (2, -1, -1)
-%\left[\frac{16}{63} (27 \text{D2}-100 \text{D4})\right]
-\left[D_2-\frac{100}{27}  D_4\right]\frac{48}{7}\frac{q_o}{a}\delta,\\
-\label{eq:JTeg}
-(E_{x^2-y^2},E_{z^2})&=(1,-1)
-\left[D_2+\frac{25}{9} D_4\right]\frac{96}{7}\frac{q_o}{a}\delta,
-\end{align}
-whereas
-%${\Delta_{\delta}= \frac{48}{7}\frac{q_o}{a}\frac{\delta}{a}}$.
-$E_0^{t_{2g}}$, $E_0^{e_{g}}$ and $\Delta$ all are rescaled by a factor of ${1-5\delta/3}$.
+Thanks. We have done it in the revised version.
 
-\com{
-The crystal field splitting becomes
-\begin{align}
-E_0^{t_{2g}},E_0^{e_{g}},\Delta \to (1-\frac{5}{3}\delta)E_0^{t_{2g}}
-E_0^{e_{g}} \to (1-\frac{5}{3}\delta) E_0^{e_{g}}
-\Delta \to (1-\frac{5}{3}\delta)\Delta
-\end{align}
-}
-
-%\subsection{Parameters $D_2$ and $D_4$ of the JT ion/atom}
-The terms in square brackets on the right of Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}
-contain $D_2$ and $D_4$. 
-$D_4$ is proportional to the crystal field splitting $\Delta$ 
-($D_4=\frac{3a}{160q_o} \Delta$) and 
-we can estimate its value from realistic values of $\Delta$ for a given octahedron of size $a$ and ion charge $-q_o$. 
-Assuming $a=7.0$ bohr and $q_o=2e$ ($e$ being the elementary charge),
-$D_4$ ranges from $1 \times 10^{-3}$ to  $7 \times 10^{-3}$
-for $\Delta \simeq 0.5-3$~eV.
-Typically, ${D_{2}\approx \sqrt{D_{4}}}$,
-so $D_{2}/D_{4} \approx 1/\sqrt{D_{4}}$
-and it roughly ranges between $29$ and $12$ for $D_4$ in the above range.
-This means that, for realistic systems, 
-we should always have $D_{2}/D_{4} > 100/27, 25/9 \approx 4$
-so 
-$D_{2}$ terms in 
-Eqs.~\ref{eq:JTt2g},\ref{eq:JTeg}
-dominate and determine the sign and size of the splittings.
-
-So far, we have calculated the changes in the single particle energy levels of the B ion. 
-Whether the deformation would be energetically favourable 
-or not will depend on the number of electrons occupying these levels,
-as illustrated below.
-
-%\subsection{Examples}
-Let us consider %the following two cases.
-%\begin{enumerate}
-%\item
-a JT/B ion with two electrons.
-In the symmetric octahedron case, 
-we will have a degenerate (many electron) ground state 
-with both electron in the same spin state (Hund's rule) in the $t_{2g}$ manifold.
-Distorting the structure $\delta>0$, we lower the ground state energy because 
-we can now choose $yz,zx$ orbitals that have lower energy than the original $t_{2g}$ energy of the undistorted structure.
-%\item
-In case of a JT/B ion with three electrons, the situation is very different.
-Assuming Hund's coupling is enough to still produce complete spin polarisation,
-there is only one possible orbital configuration, one electron in each of $xy,yz,zx$ orbitals.
-This non-degenerate (many electron) ground state
-does not lower its energy if the structure is distorted 
-because the gain due to $yz,zx$ is already balanced by the loss due to picking the higher energy $xy$ state.
-%\end{enumerate}
-
-%\subsection{cooperative JT and orbital order}
-%\az{just a brief description... cooperative JT and orbital order}
-To complete the discussion of the JT instability,
-it is worth mentioning that
-JT effect occurs in all kinds of systems---molecules, clusters and crystals.
-In crystals, e.g., perovskites, it becomes a cooperative effect where the
-elongation of one octahedron is accompanied by a compression of adjacent octahedron,
-which minimizes the changes in the unit cell volume and hence the elastic energy cost of the transformation.
-Such alternate elongations and compressions also lead to 
-an interesting long range orbital ordering where alternate orbitals
-are populated on the adjacent JT sites.
-
-\com{
-\begin{align}
-E_{xy} =&
-\frac{32}{7} \left[
-\left(1-\frac{1}{(\delta +1)^3}\right) D_2
--
-\left(1-\frac{1}{(\delta +1)^5}\right) \frac{20}{9}D_4
-\right]\frac{q_o}{a},\\
-E_{yz} =& E_{zx} = -3/2 E_{xy},
-\end{align}
-as measured from their average 
-%\begin{align}
-$E_0^{t_{2g}} = -64q_oD_4 \left(2+(\delta +1)^{-5}\right)/9a$.
-%\frac{64}{9} \left(-\frac{1}{(\delta +1)^5}-2\right) \text{D4}
-%\end{align}
-Similarly, $e_g$ splits up as
-\begin{align}
-E_{x^2-y^2}=&\frac{32}{7} \left[\left(1-\frac{1}{(\delta +1)^3}\right) \text{D2}+\frac{5}{3}\left(1-\frac{1}{(\delta +1)^5}\right) \text{D4}\right]\frac{q_o}{a},\\
-E_{z^2}=&-E_{x^2-y^2},
-\end{align}
-measured from their average 
-%\begin{align}
-$E_0^{e_{g}} = 32 q_oD_4 \left(2+(\delta +1)^{-5}\right)/3a$.
-%\frac{32}{3} \left(\frac{1}{(\delta +1)^5}+2\right) \text{D4}
-%\end{align}
-The crystal field splitting becomes
-\begin{align}
-\Delta \equiv E_0^{e_{g}}-E_0^{t_{2g}}=\frac{160}{9} \left(\frac{1}{(\delta +1)^5}+2\right) D_4.
-\end{align}
-}
-
-\section{Model and calculations of ABO$_3$ Perovskites}%}
-\label{sec:calc}
-
-We now turn to our model and calculations of the splittings in the 
-$t_{2g}$ and $e_{g}$ manifolds due to the deformations 
-in the crystal field that are produced as the octahedra rotate or tilt.
-First, let us consider the cubic perovskite and see 
-how much A and B cages contribute to the octahedral crystal field and associated splitting $\Delta$ between $t_{2g}$ and $e_{g}$ manifolds.
-
-\subsection{Contribution of different coordination cages in a cubic perovskite}
-\label{sec:relativeVoctABO}
-
-In a cubic perovskite ABO$_3$,
-each transition metal atom/ion B
-is surrounded by six O$^{2-}$, each at a distance $a/2$,
- making an octahedron of size $a$ around it.
-The potential of these ions $V_{O}(\vec r)= V_{oct}(\vec r)$
-splits the degenerate d-orbitals
-by an amount ${\Delta_o=160q_oD_{4}/3a}$
- into $t_{2g}$ and $e_g$.
-However, this is not the only crystal field potential at the B site.
-The coordination cages of next nearest neighbours, 
-eight A atoms/cations all at the same distance $\sqrt{3}a/2$
-make a cube around the B ion,
-which also produces an octahedral field, given by 
-\begin{align}
-V_{A}(\vec r) = \frac{8}{81 \sqrt{3}}\frac{q_A}{q_o} V_{O}(\vec r).
-\end{align}
-Furthermore,
-the nearest neighbouring B ions, six of them each at a distance $a$,
-make an octahedron, with a potential 
-\begin{align}
-V_{B}(\vec r) = -\frac{1}{32}\frac{q_B}{q_o}V_{O}(\vec r).
-\end{align}
-It is interesting to note that 
-$V_{A}(\vec r)$ and $V_{B}(\vec r)$ have opposite signs
-and 
-their combined effect 
-$V_{AB}(\vec r) = V_{A}(\vec r)+ V_{B}(\vec r)$
-depends on their relative charges.
-Using the charge neutrality $q_B=3q_o-q_A$ (remember that we take anion charge to be $-q_o$),
-we can write 
-\begin{align}
-V_{AB}(\vec r) &= f_{q_A}V_{O}(\vec r),\\
-f_{q_A} &= \left(\frac{1}{32}+\frac{8}{81 \sqrt{3}}\right)\frac{q_A}{q_o} -\frac{3}{32},
-\end{align}
-which shows that ${V_{AB}(\vec r)}$ vanishes
-at
-$q_A/q_o=729/({256 \sqrt{3}+243}) {\simeq 1.062}$.
-%where they cancel each other exactly.
-
-\com{
-\begin{align}
-%V_{oct}(\vec r) &= \frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right],\\
-V(\vec r) &= V_{O}(\vec r) + V_{A}(\vec r) + V_{B}(\vec r),\\
-V_{O}(\vec r) &= V_{oct}(\vec r),\\
-V_{A}(\vec r) &= \left(\frac{4}{81 \sqrt{3}}q_A \right)V_{oct}(\vec r),\\
-V_{B}(\vec r) &= -\left(\frac{q_B}{64}\right)V_{oct}(\vec r).
-\end{align}
-It is interesting to note that 
-$V_{A}(\vec r)$ and $V_{B}(\vec r)$ have opposite signs
-and 
-their combined effect
-depends on their relative charges and vanishes
-as
-${q_A\to 1458/({256 \sqrt{3}+243})\simeq 2.124}$
-where they cancel each other exactly.
-
-\begin{align}
-%V_{oct}(\vec r) &= \frac{224\sqrt{\pi}}{3}\frac{q_o}{a} \left(\frac{r}{a}\right)^4\left[\ylm{4,0}+\sqrt{\frac{5}{7}}\ylm{4,4} \right],\\
-V(\vec r) &= V_{O}(\vec r) + V_{AB}(\vec r),\\
-V_{O}(\vec r) &= V_{oct}(\vec r),\\
-V_{AB}(\vec r) &= f_{q_A}V_{oct}(\vec r),\\
-f_{q_A} &= \left(\frac{1}{32}+\frac{8}{81 \sqrt{3}}\right)\frac{q_A}{q_o} -\frac{3}{32},
-\end{align}
-where we have use the charge neutrality $q_B=3q_o-q_A$ in the last equation.
-It is interesting to note that 
-$V_{A}(\vec r)$ and $V_{B}(\vec r)$ have opposite signs
-and 
-their combined effect
-depends on their relative charges and vanishes
-as
-${q_A\to 1458/({256 \sqrt{3}+243})\simeq 2.124}$
-where they cancel each other exactly.
-
-}
-
-Including the contribution of these AB cages to the crystal field,
-we obtain
-\begin{align}
-%V(\vec r) &= V_{O}(\vec r) + V_{AB}(\vec r),\\
-V(\vec r)  &= (1+f_{q_A}) V_{O}(\vec r),
-\end{align}
-whereas the 
- splitting becomes
-%\begin{align}
-$\Delta = (1+f_{q_A})\Delta_o$.
-%\end{align}
-%where ${\Delta_O=\frac{160}{3}\frac{q_o}{a} D_{4}}$.
-We see that, relative to the O octahedron,
- the contribution of the
- two cation cages towards the total field splitting
- is relatively small at any $q_A$ but
- %still large enough to be ignored.
- still too large to be ignored.
-It can be measured by $(\Delta-\Delta_o)/\Delta_o=f_{q_A}$,
-which linearly changes from 
-$-3/32\simeq -10\%$ at $q_A=0$
-to $8/{27 \sqrt{3}}\simeq 17\%$ at $q_A=3q_o$. 
-Typical values of $q_A$ relevant for real transition metal oxides
-can be safely assumed to range between $0$ and $4$;  
-$q_A=0$ for systems like tungsten oxide $WO_3$ that do not have any cations at the A sites,
-and $q_A=4$ still contributing just above $8\%$.
-We will see that,
-as the anion octahedra rotate or tilt,
-$V_{AB}(\vec r)$ rotate in its frame and deform as well.
-The deformation also induces $l=2$ components, which couple to the 
-$d$-orbitals of the B ion much more strongly. 
-%due to a much larger $D_{l=2}$.
-
-%\subsection{Rigid octahedral rotations}
-%\label{sec:rotation}
-
-\subsection{Rigid octahedral rotations: Transformation of the crystal structure}
-\label{sec:structure}
-
-\com{
-Coordinates of the Oxygen atoms transform according to 
-the rotation matrix $R$.
-While the d-orbitals basis states attached to the octahedron transform according to
-$\mathcal{R}$.
-}
-
-We consider a
-$\sqrt{2}\times\sqrt{2}\times 2$ unit cell of the cubic structure that transforms
-to the unit cell of the orthorhombic structure under octahedral rotation and tilting,
-as shown in Fig.~\ref{fig:struc}.
-Assuming 
-%$\vec a_1,\vec a_2,\vec a_3$
-$\textbf{a},\textbf{b},\textbf{c}$
- to be the lattice vectors,
-two B atoms in a layer are situated at
-%$(0,0,0)$, 
-$\textbf{a}/2$, $\textbf{b}/2$,
-%$(\textbf{a}  + \textbf{b} )/2$, 
-while two A atoms in the same layer are at
-% all coor shifted by a/2 to match to those in Fig.1 [vesta: unit cell transformation]:
-%$(\textbf{a} + \textbf{c}/2)/2$, $(\textbf{b}+ \textbf{c}/2)/2$,
-$\textbf{c}/4$, $(\textbf{a}+\textbf{b})/2 + \textbf{c}/4$.
-Similar atoms in the second layer are simply shifted by 
-$\textbf{c} /2$.
-While the lattice vectors change under the rotation and tilting of the octahedra, 
-these relations do not change.
-%The B atom at the origin will be considered as the central JT atom.
-The O atoms in the cubic structure lie half way between the B atoms and make octahedral cages around them.
-Their positions in the deformed structure %(see appendix) 
-are not directly required for our calculations and discussion.
-
-We rotate the octahedra by an angle $\beta$ about $\hat z \equiv 001$
-and then tilt it about the new $110$ by an angle $\alpha$~\cite{CarterPRB12}.
-The four octahedra in the cell 
-have to be rotated and tilted clockwise or counter clockwise
-consistently. For example, %$\alpha  \{1,-1,-1,1\}$, $\beta  \{1,-1,1,-1\}$.
-$(\alpha,\beta)$,
-$(-\alpha,-\beta)$,
-$(-\alpha,\beta)$,
-$(\alpha,-\beta)$
-for the octaherda labelled $1$ through $4$ in Fig.~\ref{fig:struc}(b).
-The structure transforms from cubic to orthorhombic under these rotation and tilting of the octahedra.
-%The rotation matrix $R$ for $(\alpha,\beta)$ case is given in the appendix~\ref{sec:appendix}. 
-The lattice vectors of the deformed structure and the positions of A and B atoms can be calculated easily by calculating the coordinates of all six oxygen atoms that make the octahedra (by rotating and tilting the octahedra) for all four octahedra in the unit cell and
-comparing the coordinates of their shared oxygen atoms.
-We obtain,
-%\az{just rescaled, not rotated. write as cos * (1,1), etc?}
-% lattice vectors:
-\begin{align}
-\left(
-\begin{array}{c}
-%\vec a_1 \\
-%\vec a_2\\
-%\vec a_3\\
-\textbf{a}\\
-\textbf{b}\\
-\textbf{c}
-\end{array}
-\right)
-= a
-\left(
-\begin{array}{ccc}
- \cos \beta  & \cos \beta  & 0 \\
- -\cos \alpha  \cos \beta  & \cos \alpha  \cos \beta  & 0 \\
- 0 & 0 & 2 \cos \alpha  \\
-\end{array}
-\right)
-\end{align}
-
-\com{
-\begin{align}
-\vec a_1 & =  \cos\beta ( 1,1,0 ) ,\\
-\vec a_2 & =  \cos\alpha  \cos\beta(-1,1,0 ),\\
-\vec a_3 & =  \cos\alpha ( 0,0,2 ).
-\end{align}
-}
-
-\subsection{Deformation of the crystal field}
-\label{sec:deformCF}
-
-%\subsubsection{Deformation of the crystal field due to AB cages}
-
-\com{Before we present calculations and results, let's briefly
-summarise the contribution of the AB cages towards the crystal field Hamiltonian
-....}
-
-There are two different ways the crystal field $V(\vec r)$
- is deformed from the ideal case $V(\vec r) \propto V_{oct}(\vec r)$
- when the octahedra are rigidly rotated. 
-% to make an orthorhombic structure. 
-\begin{enumerate}[(i)]
-\item
-%(i) 
-The relative rotations of the AB and O frames due to
-the rigid rotation and tilting of the oxygen octahedra removes the
-choice of a set of d-orbitals where the effect of 
-AB and O cages is the same. 
-We no longer just get $e_g, t_{2g}$ manifolds in any frame but with splittings induced by the rotation,
-which generates non-octahedral but still only $l=4$ field components. 
-\item
-%(ii) 
-The rigid rotation and tilting of the octahedra keeps the octahedra symmetric but deforms the unit cell and AB ionic cages with it.
-This not only changes the $l=4$ components but also induces 
-$l=2$ field components
-that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below \eref{eq:JTeg} in Sec.~\ref{sec:JTtertagonal}).
-So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see Sec.~\ref{sec:relativeVoctABO}).
 \end{enumerate}
 
-\com{
-There are two different ways the crystal field $V(\vec r)$
- is deformed from the ideal case, $V_{voct}(\vec r)$.
-\begin{enumerate}
-\item The relative rotations of the AB and O frames due to
-the rigid rotation and tilting of the oxygen octahedra removes the
-choice of a set of d-orbitals where the effect of 
-AB and O cages is the same. 
-We no longer just get eg-t2g in any frame but with splittings induced by the rotation.
-This can generate non-octahedral but still $l=4$ field components. 
-\item
-The rigid rotation and tilting of the octahedra keeps the octahedra symmetric but deforms the unit cell and AB ionic cages with it.
-This not only changes the $l=4$ components but also induces 
-$l=2$ field components
-that can couple to the JT ion much more strongly (see discussion on $D_2$ vs $D_4$ below).
-So, the magnitude of the net effect of the octahedral rotations is not limited by the relative sizes of the octahedral fields of AB and O in the cubic case (see Sec.~\ref{sec:relativeVoctABO}).
-\end{enumerate}
-
-}
-
-Since $V_{O}(\vec r)$ is relatively stronger, 
-we can take the octahedra's local frames (that are rotated with them)
-to first describe the effect of $V_{O}(\vec r)$, i.e.,
-splitting of degenerate d-orbitals into $e_g, t_{2g}$ manifolds with 
-a gap $\Delta_o$,
-and then
-consider the effect of $V_{AB}(\vec r)$ on these manifolds.
-$V_{AB}(\vec r)$ will couple and mix the orbitals in the two manifolds.
-Since %$\Delta_AB << \Delta_O$,
-$f_{q_A} \ll 1$,
-we can even ignore the coupling between the states belonging to
-different manifolds that are $\Delta_o$ apart.
-This also makes it possible to analytically solve the problem in two limiting cases discussed later.
-
-\com{
-The total crystal field potential at the central B atom that we consider
- is given by
-\begin{align}
-V(\vec r) &= V_O(\vec r) + V_{AB}(\vec r),
-\end{align}
-where
-$V_{AB}(\vec r)=V_{A}(\vec r)+V_{B}(\vec r)$
-is due to A and B ion cages.
-\az{repetition.... cubic case has similar expressions.... }
-}
-
-It is worth reminding that
-$V(\vec r) $ a scalar quantity in the position space but a vector 
-%$V$ is as a vector %of length $(l_{max}+1)^2=25$ for $l_{max}=4$.
-in the spherical harmonics bases, so
-we can calculate it in one bases as per our convenience and then transform it to another.
-%Its components in the new basis.
-\begin{align}
-V(\vec r) &= \sum_{l,m} V_{lm} r^l Y_{lm}(\hat r)
-= \sum_{l,m} \tilde V_{lm} r^l \tilde Y_{lm}(\hat r),\\
-%\tilde V_{lm} &= \sum_{l',m'}\mathcal{R}_{lm,l'm'}V_{l'm'},
-\tilde V_{lm} &= \sum_{m'=-l}^{l}\mathcal{R}^{l}_{m,m'}V_{lm'},
-\end{align}
-where 
-$\mathcal{R}^{l}=\mathcal{R}^{l}(\alpha,\beta)$ is the rotation matrix for real spherical harmonics 
-of degree $l$. % (see appendix~\ref{sec:appendix}).
-It can be calculated using the method 
-devised by Ivanic and Ruedenberg~\cite{IvanicJPC96}.
-The multipole components of $V_O(\vec r)$ in the rotated frame do not change with the rigid octahedral rotations because, by definition, the octahedron itself rotates with its frame.
-These can be directly read off \eref{eq:voct}.
-Similarly, it is easier to obtain the components of $V_{AB}(\vec r)$
-in the unrotated frame so we do that first and later transforms them to obtain the rotated frame components.
-That is,
-\begin{gather}
-\tilde V_{lm} = \tilde V_{lm}^O + \sum_{m'=-l}^{l}\mathcal{R}^{l}_{m m'} V_{lm'}^{AB},\\
-V_{lm}^{AB} = \left(\frac{q_A}{a} \right)V_{lm}^{A}   
-+ \left(\frac{q_B}{a}\right)V_{lm}^{B},
-\end{gather}
-%where $q_A + q_B = 3q_o$ ensures charge neutrality.
-where the quantities bearing a tilde on top belong to the rotated (octahedron's) frame.
-As described above, 
-$\tilde V_{lm}^O$ are simply octahedral field components 
-with $l=4,m=0,4$ (see \eref{eq:voct}).
-However, $V_{lm}^{AB}$ contain the effect of the deformation of the crystal structure 
-%on AB ion cages due to the octahedral rotations
-so it now has not only other $l=4$ components but also $l=2$ components; see below.
-A procedure to obtain these multipole components, without
-actually calculating the projection of the potential $V_{AB}(\vec r)$ 
-onto the spherical harmonics, is described in the appendix. %~\ref{append:multipoles}.
-
-We find that the splittings due to octahedral rotation and tilting are practically the same for all B ions
-(but their eigenstates differ considerably, which creates interesting orbital ordering as discussed later in the discussion in Sec.~\ref{sec:discussion}),
-so we consider the octahedron $1$ with central B ion at $\textbf{a}/2$
-in the calculations that follow.
-We obtain the following exact expressions for $V_{lm}^{A}$,
-\begin{widetext}
-%\rev{$V(r)=q\sum_{i}(\sqrt{ ..... r\cos... })^{-1}$}
-%\az{full potential of the charges in deformed cage: manually refined}:
-\begin{align}
-V^A_{2,-2}&= 64 \sqrt{\frac{3 \pi }{5}} \cos ^2\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}-\frac{\sec ^3\alpha }{(\cos 2 \beta +2)^{5/2}}\right),\\
-V^A_{2,0}&= 32 \sqrt{\frac{\pi }{5}} \left(\frac{2 \sec ^3\alpha  \sin ^2\beta }{(\cos 2 \beta +2)^{5/2}}-\frac{32 \sqrt{\frac{\pi }{5}} (\cos 2 \beta -\cos 2 \alpha )}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{5/2}}\right),\\
-V^A_{4,-2}&= \frac{128\sqrt{5 \pi } }{3} \cos ^2\beta  \left(\frac{3 \cos 2 \alpha -\cos 2 \beta +2}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha  (\cos 2 \beta -5)}{(\cos 2 \beta +2)^{9/2}}\right),\\ \nonumber
-V^A_{4,0}&= \frac{16\sqrt{\pi } }{3} \left(
-\frac{\sec ^5\alpha  (36 \cos 2 \beta -3 \cos 4 \beta +23)}{(\cos 2 \beta +2)^{9/2}}
--
-\frac{8 \cos 2 \alpha  (3 \cos 2 \beta +2)-2 \cos 4 \alpha+12 \cos 2 \beta -3 \cos 4 \beta +9}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}
-\right),\\
-V^A_{4,4}&=-\frac{128\sqrt{35 \pi } }{3} \cos ^4\beta  \left(\frac{1}{\left(\cos ^2\alpha +2 \cos ^2\beta \right)^{9/2}}+\frac{\sec ^5\alpha }{(\cos 2 \beta +2)^{9/2}}\right),
-\end{align}
-\end{widetext}
-whereas $V_{lm}^{B}$ are given by,
-%\az{full potential of the charges in deformed cage: }:
-\begin{align}
-V^{B}_{2,-2}&= 64 \sqrt{\frac{3 \pi }{5}}  \frac{\sin ^2\alpha  \sec ^3\beta }{(\cos 2 \alpha +3)^{5/2}},
- \\ V^{B}_{2,0}&=  4 \sqrt{\frac{\pi }{5}} \left(\sec ^3\alpha -\frac{8 \sec ^3\beta }{(\cos 2 \alpha +3)^{3/2}}\right),\\
- V^{B}_{4,-2}&=  - \frac{128 \sqrt{5 \pi } }{3} \frac{\sin ^2\alpha  \sec ^5\beta }{ (\cos 2 \alpha +3)^{7/2}},\\ 
-V^{B}_{4,0}&= \frac{4\sqrt{\pi } }{3} \left(\frac{24 \sec ^5\beta }{(\cos 2 \alpha +3)^{5/2}}+\sec ^5\alpha \right),\\
- V^{B}_{4,4}&=  \frac{16 \sqrt{35 \pi } }{3} \frac{(20 \cos 2 \alpha -\cos 4 \alpha +13) 
- \sec ^5\beta }
- {(\cos 2 \alpha +3)^{9/2}}.
- \end{align}
-
-% expansion of V^{AB} at small alpha,beta is not useful because
-% we still have to Rotate them that brings in more alpa beta dependance
-\com{
-%A
-\begin{align}
-\text{Vlm}(2,-2)&=  \frac{64}{81} \sqrt{\frac{\pi }{5}} \alpha ^2 \left(\beta ^2-6\right),\\
-\text{Vlm}(2,0)&=  \frac{64}{27} \sqrt{\frac{\pi }{15}} \left(2 \left(\alpha ^2+3\right) \beta ^2-3 \alpha ^2\right),\\
-\text{Vlm}(4,-2)&=  \frac{1}{243} (-256) \sqrt{\frac{5 \pi }{3}} \alpha ^2 \left(9 \beta ^2+5\right),\\\text{Vlm}(4,0)&=  \frac{1}{243} (-128) \sqrt{\frac{\pi }{3}} \left(5 \alpha ^2 \left(11 \beta ^2+4\right)+30 \beta ^2+14\right),\\
-\text{Vlm}(4,4)&=  \frac{1}{243} (-128) \sqrt{\frac{35 \pi }{3}} \left(\alpha ^2 \left(5 \beta ^2+4\right)+2 \left(\beta ^2+1\right)\right)
- \end{align}
-% B
-\begin{align}
-\text{Vlm}(2,-2)&=  \sqrt{\frac{3 \pi }{5}} \alpha ^2 \left(3 \beta ^2+2\right),\\
-\text{Vlm}(2,0)&=  \frac{1}{2} (-3) \sqrt{\frac{\pi }{5}} \left(\alpha ^2 \left(3 \beta ^2-2\right)+4 \beta ^2\right),\\
-\text{Vlm}(4,-2)&=  -\frac{1}{6} \sqrt{5 \pi } \alpha ^2 \left(5 \beta ^2+2\right),\\
-\text{Vlm}(4,0)&=  \frac{1}{24} \sqrt{\pi } \left(5 \alpha ^2 \left(15 \beta ^2+22\right)+60 \beta ^2+56\right),\\
-\text{Vlm}(4,4)&=  \frac{1}{24} \sqrt{35 \pi } \left(5 \alpha ^2+4\right) \left(5 \beta ^2+2\right)
- \end{align}
-}
-
-%\subsection{Crystal Field Hamiltonian}
-
-\com{ Considering an octahedron,.... which one?
- why only one but not all four?
- spectra of all octahedra are similar...???
-}
-
-\com{V20, JT:\\
-V2-2, V4-2, couple yz and zx.
-But... rotation.... produce all m components in general, ....
-}
-
-The Hamiltonian of the central ion (JT ion) including 
-the crystal field of the AB cages 
-in the octahedron's frame %(rotated frame)
-are given by,
-\begin{align}
-\tilde H_{m' m''} &= \sum_{l,m} \tilde V_{l m} \tilde C_{l}^{m'm''m} D_{l} ,
-%C_{l}^{m'm''m} &= \braket{\tilde Y_{2,m'}|\tilde Y_{l,m}|\tilde Y_{2,m''}},
-\end{align}
-where %$C_{l}^{m'm''m}$ 
-$\tilde C_{l}^{m'm''m}=\braket{\tilde Y_{2m'}|\tilde Y_{lm}|\tilde Y_{2m''}}= C_{l}^{m'm''m}$. 
-% are again the Gaunt coefficients for the real spherical harmonics.
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-0-width-row}
-\includegraphics[width=1.0\linewidth]{energy-vs-beta-alpha-0-width-row}
-\caption{
-Splitting in $t_{2g}$ manifold induced by the
-octahedral rotations.
-%The changes in the energies of $t_{2g}$ states 
-$E_{xy},E_{yz},E_{zx}$ 
-%and the average of $t_{2g}$ energy
-and $E_0^{t_{2g}}$
-as a function of the rotation angel $\beta$
-at $\alpha=0$ (no tilting),
-$\Delta_o=4q_o/15a$ ($D_4=1/200$), $D_2=\sqrt{D_4}$,
-and three values of $q_A/q_o$.
-(a)
-The B cage dominates at $q_A/q_o=1/2$;
-it lowers $xy$ state and raises $yz,zx$ states
-with increasing $\beta$.
-As $q_A/q_o$ increases to $1$, 
-(b)
-A cage almost cancels the effect of B cage reducing the splitting,
-while it dominates at $q_A/q_o=2$ (c) where it switches the order of the states. 
-}
-\label{fig:t2g-alpha0}
-\end{center}
-\end{figure}
-
-\section{Results: Single particle spectrum and JT instability}
-\label{sec:results}
-
-Before we present our results,
-let us briefly describe 
-the kind of behaviour that would indicate a JT instab against the tilting and rotations of the octahedra,
-and how it relates to the standard JT problem.
-As describe in Sec.~\ref{sec:JT},
-the optimum structure can have a finite distortion
-as long as 
-the splitting in the single particle spectrum has a different dependence on the distortion
-than the elastic energy associated with the changes in the unit cell volume.
-\rev{Here, the unit cell volume
- depends on the ``distortions'' $\alpha,\beta$ 
-as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
-and, at $\alpha,\beta\ll1$,
-it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$.
-The elastic energy in the harmonic approximation thus goes
-as $\sim\left(\alpha ^2+\beta ^2\right)^2$,
-which is \emph{quartic} in $\alpha,\beta$.
-So, 
-in contrast to the case of
-elongations or 
-compressions  
-of the octahedra~\cite{KhomskiiCR21},
-the behavior we are looking for in the electronic spectrum 
-is not linear
-but quadratic, 
-which would compete with such a quartic elastic energy
- to produce a finite distortion in the optimum structure.
-Thinking of squared angles 
-$\alpha ^2,\beta ^2$
-as the basic distortion variables,
-the order of the electronic and elastic energy terms
-matches to the standard JT problem.
-}
-
-\com{In contrast to 
-%hypothetical 
-elongations or 
-compressions---$a\delta_1,a\delta_2$ 
-of an octahedron along two of its axes---where the 
- the unit cell volume changes
-as $\sim a^3\left(\delta_1+\delta_2\right)$
-and thus
-the elastic energy in the harmonic approximation goes
-as $\sim\left(\delta_1+\delta_2\right)^2$,
-the unit cell volume
-in case of octahedral rotation and tilting
- depends on the ``distortions'' $\alpha,\beta$ 
-as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
-and, at $\alpha,\beta\ll1$,
-it changes as $\sim a^3\left(\alpha ^2+\beta ^2\right)$
-leading to a \emph{quartic} elastic energy that should roughly behave as
-$\sim\left(\alpha ^2+\beta ^2\right)^2$.
-So, the behavior we are looking for in the electronic spectrum 
-is not linear
-but quadratic, 
-which would compete with such a quartic elastic energy
- to produce a finite distortion in the optimum structure.
-Thinking of squared angles 
-$\alpha ^2,\beta ^2$
-as the basic distortion variables,
-the order of the electronic and elastic energy terms
-matches to the standard JT problem.
-}
-
-\com{
-Before we present our results,
-let's briefly describe 
-the kind of behaviour that would indicate a JT instability 
-against the tilting and rotations of the octahedra,
-and how it relates to the standard JT problem.
-As describe in Sec.~\ref{sec:JT},
-the optimum structure can have a finite distortion
-as long as 
-the splitting in the single particle spectrum has a different dependence on the distortion
-than the elastic energy associated with the changes in the unit cell volume.
-
-%\subsection{Dependence of electronic spectrum on the ``distortion'' angles}
-In case of \az{names? Tetragonal distortion, or quadrupolar distortion, }
-elongation or compression of a cube of size $a$ along two of its edges, say, by $a\delta_1,a\delta_2$,
-the change in the unit cell volume would be linear in $\delta_{1,2}$
-as $\sim a^3\left(\delta_1+\delta_1\right)$.
-So the elastic energy %(for an isotropic system) 
-changes as $\sim\left(\delta_1+\delta_1\right)^2$.
-A linear change ($\propto \delta_{1/2}$) in the electronic spectrum is required to produce
- a finite distortion in the optimum structure (or the ground state of full electron-lattice/nuclear problem).
-For example, in the case of tetragonal distortion of an octahedron,
- the total energy has a form
-$E=-\rho\delta + K \delta^2$, where $\rho$ and $K$ are constants 
-describing the changes in the electronic and elastic energies,
-and would be optimum at $\delta=\rho/2K$.
-In our case, however,
-the unit cell volume depends on the ``distortions'' $\alpha,\beta$ as ${v=4a^3 \cos ^2\alpha \cos ^2\beta}$,
-and, at $\alpha,\beta\ll1$,
-it changes as $-4a^3\left(\alpha ^2+\beta ^2\right)$.
-So, the behaviour we are looking for in the electronic spectrum does not have to be linear 
-but quadratic, which would compete with a quartic elastic energy $\left[ \sim\left(\alpha ^2+\beta ^2\right)^2 \right]$
- to produce a finite distortion in the optimum structure.
-}
-
-%\az{Focus on t2g first:}\\
-
-We will first focus on the $t_{2g}$ manifold
-and see how the potential of the AB cages split it when 
-the octahedra tilt and rotate.
-
-\subsection{$t_{2g}$ manifold} %states and energies}
-\label{sec:t2g}
-
-Let's consider three cases separately, only rotation, only tilting, and both rotation and tilting.
-
-\subsubsection{Only rotation: $\alpha=0,\beta\neq 0$}
-\label{sec:alpha0}
-
-%We find that $xy$ is coupled to $x^2-y^2$
-%$t_{2g}$ and $e_{g}$ manifolds are coupled.
-
-Ignoring the coupling between the $e_{g}$ and $t_{2g}$ manifolds (between $xy$ and $x^2-y^2$ at $\alpha=0$),
-their Hamiltonians turn out to be diagonal.
-We can write the single particle energies of $t_{2g}$ states
-as
-\begin{align}
-\label{eq:theta0-Es}
-(E_{xy},&E_{yz},E_{zx})= (2, -1, -1)
-\left[\frac{}{} \Delta_{2}  D_2 + \Delta_4 D_4\right],
- \end{align}
- where $E_{yz}$ and $E_{zx}$ are degenerate and 
-\begin{align}
-\Delta_{l} =&  \left(q_A \Delta_{l}^A + q_B\Delta_{l}^B\right)/a,~(l=2,4),\\
-\Delta_{2}^A =& 
-%from A
-\frac{64 \sin ^2\beta }{7 (\cos 2 \beta +2)^{5/2}} % simplifies.... from:
- %\frac{16 (3 \sin \beta+\sin 3\beta)^2}{7 (\cos 2\beta+2)^{9/2}},\\
- \simeq \frac{64}{63 \sqrt{3}}\beta ^2,\\
- \nonumber
-\Delta_4^A =&
- \frac{160 \sin ^2\beta}{63 (\cos 2\beta+2)^{9/2}} \times \\
-&  (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82)\\
-\simeq& \frac{40960}{5103 \sqrt{3}}\beta ^2,\\
-% \Delta_4^A =&
-% \frac{160 \sin ^2\beta (125 \cos 2\beta+42 \cos 4\beta+7 \cos 6\beta+82)}{63 (\cos 2\beta+2)^{9/2}},\\
- %from B
- \label{eq:theta0-delB2}
-\Delta_{2}^B =& \frac{2}{7} \left(1-\sec ^3\beta\right)
-\simeq -\frac{3}{7}\beta ^2,\\
-\label{eq:theta0-delB4}
-  \Delta_4^B =&\frac{5}{126} \left((7 \cos 4\beta-3) \sec ^5\beta-4\right)
-  \simeq -\frac{115}{63}\beta ^2.
- %\left( \Delta_{2}  D_2 + \Delta_4 D_4\right),\\
- \end{align}
- We see that $\Delta_{2/4}^A>0$ while $\Delta_{2/4}^B<0$,
- revealing a competition between the two terms 
- that would determine the sign and size of the term
-  in the square bracket in \eref{eq:theta0-Es} 
-%  (hence the ground state and splitting) 
-  as $q_A$ (and hence $q_B$)
-  is varied.
-The average $t_{2g}$ energy
- also shifts from
-$-2/5\Delta$ by an amount
-%\rev{E0t2g or change in it? how to define the expressions... plotted is always change in it...}
-\begin{align}
-\label{eq:theta0-E0}
-E_{0}^{t_{2g}} = \left(q_A E_{0}^A + q_BE_{0}^B\right)D_4/a
--(2/5)f_{q_A}\Delta_{o},
- \end{align}
- where
-\begin{align}
-\nonumber
-E_{0}^A =&
- \frac{8 (92 \cos 2\beta+24 \cos 4\beta+20 \cos 6\beta+5 \cos 8\beta+51)}{9 (\cos 2\beta+2)^{9/2}}\\
- \simeq& \frac{512}{243 \sqrt{3}}-\frac{2560 \beta ^2}{729 \sqrt{3}},\\
- \nonumber
-E_{0}^B=&
- -\frac{1}{18} \left((5 \cos 4\beta+3) \sec ^5\beta+4\right)\\
- \simeq& -\frac{2}{3}+\frac{10 \beta ^2}{9}.
- \end{align}
-
-The results in Eqs.~\ref{eq:theta0-Es},\ref{eq:theta0-E0}
-are summarised in Fig.~\ref{fig:t2g-alpha0},
-where $E_{xy}$, $E_{yz/zx}$ and $E_0^{t_{2g}}$ are shown
-as a function of $\beta$
-at three values of $q_A/q_o=1/2,1,2$.
-We have 
-assumed $D_2=\sqrt{D_4}$ and
-taken $\Delta_o=4q_o/15a$ throughout this paper,
-which fixes the value of $D_4=1/200$, 
-and corresponds to $\Delta_o= 2.073$ eV at 
-$q_o=2$ e and $a=7.0$ bohr.
-We present the energies as a percentage of $\Delta_o$
-by calculating all quantities at the above values of $q_o,a$.
-Fig.~\ref{fig:t2g-alpha0} shows that
-the competition between A and B cages
-determines the ground state and the size of the splitting between the 
-$t_{2g}$ states
-$E_{xy}$ and $E_{yz/zx}$.
-In Fig.~\ref{fig:t2g-alpha0}(a),
-where $q_A/q_o=1/2$ ($q_B/q_o=5/2$),
-the effect of B cage dominates.
-Since it's negative (see Eqs.~\ref{eq:theta0-delB2},\ref{eq:theta0-delB4}),
-it reverses the order in \eref{eq:theta0-Es}
-and $E_{xy}$ becomes lower than $E_{yz/zx}$, by about $6\%$ of $\Delta_o$ at $\beta=15^\circ$.
-When A cage dominates at large $q_A/q_o$,
-as shown in Fig.~\ref{fig:t2g-alpha0}(c) for $q_A/q_o=2$,
-$E_{yz/zx}$ are the single particle ground states
- (with a splitting of the same order), %$\sim6\%$ of $\Delta_o$ at $15^\circ$),
-whereas the net effect of both cages
-is reduced in Fig.~\ref{fig:t2g-alpha0}(b)
-that corresponds to $q_A/q_o=1$
-and we only obtain a splitting of $\sim2\%$ of $\Delta_o$ at $\beta=15^\circ$.
-%between $E_{xy}$ and $E_{yz/zx}$ levels.
-Obviously, there will also be a point near 
-$q_A/q_o=1$ where A and B completely 
-cancel the effect of each other (not shown in Fig.~\ref{fig:t2g-alpha0}).
-We also see that $E_0^{t_{2g}}$ changes from a small negative to a small positive value
-with an increase in $q_A/q_o$ as we
-go from Fig.~\ref{fig:t2g-alpha0}(a)
-to Fig.~\ref{fig:t2g-alpha0}(c).
-This is because the rotation suppresses the
-effect of AB cages on the
-gap $\Delta$ between $e_{g}$ and $t_{2g}$.
-Since A supports O while B opposes it,
-$\Delta$ slightly widens at small $q_A$ and shrinks at large $q_A$,
-shifting the $t_{2g}$ manifold slightly down or up with $\beta$.
-
-These results also indicate that in case of a superlattice with $q_A$ alternating
-between the two regimes shown in Figs.~\ref{fig:t2g-alpha0}(a,c),
-we should obtain an alternating orbital order if the octahedra are rotated.
-
-\com{
-$\eta=\left(\frac{a\Delta_{O}}{q_o}\right)=\frac{4}{15}$
-at $D_4=1/200$\\
-$a=7$ bohr, and $\braket{r^4}=11.5809$ gives $2eV$ crystal field gap: $D_4=11.5809/a^4=0.004823365264473\simeq0.005=1/200=5\times10^{-3}$,
-$D_2=\sqrt{D4}=0.0694503$,
-$D_2/D_4\simeq 14$.
-}
-\com{$D_2/D_4$ ranges between $15$-$20$ for typical gaps of $2$-$1$ eV and $a\simeq 7$ bohr (and $q_o=2e$). 
-It decreases with increasing gap as $1/\sqrt(gap)$, but is still $10$ at $gap=3.5$eV.
-}
-
-\subsubsection{Only tilting: $\alpha\neq 0,\beta = 0$}
-\label{sec:t2g-beta0}
-
-In this case, the situation gets slightly complicated as
-the couplings between the three states become finite. 
-However, 
-the Hamiltonian still has a simple structure, 
-\begin{align} 
-\tilde H = 
-\left(
-\begin{array}{ccc}
- E_{xy} & g & -g \\
- g & E_{yz} & \lambda  \\
- -g & \lambda  & E_{yz} \\
-\end{array}
-\right),
-\end{align}
-where the matrix elements have relatively long expressions and 
-only an approximation at small $\alpha,\beta$ is given later in this section.
-%\com{are not given here \az{[?? can be found in the appendix.]} An approximation at small $\alpha,\beta$ is given later in this section.}
-$\tilde H$ can be simplified by rotating the bases in $\{\ket{yz},\ket{zx}\}$ space
-to obtain bright and dark states
-as follows.
-\begin{align}
-\ket{B} &= \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
-\ket{D} &=  (\ket{yz} + \ket{zx})/\sqrt{2}.
-\end{align}
-The state $\ket{D}$ at energy ${E_D= E_{yz}+\lambda}$ decouples 
-from the rest (so is already an eigenstate of $\tilde H$) 
-and the state $\ket{B}$ at energy ${E_{yz}-\lambda}$ obtains the enhanced collective coupling $\sqrt{2} g$. 
-\com{
-\begin{align}
-\tilde H_{Bright} = 
-\left(
-\begin{array}{cc}
-E_{xy} & \sqrt{2} g \\
-\sqrt{2} g & E_{yz}-\lambda
-\end{array}
-\right).
-\end{align}
-The Hamiltonian can be solved analytically.
-}
-The Hamiltonian can thus be solved analytically to
-obtain the remaining two
-eigenstates
-\begin{gather}
-%\ket{+} = \cos\gamma \ket{xy} + \sin\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
-%\ket{-} = \sin\gamma \ket{xy} - \cos\gamma \left(\ket{yz} - \ket{zx}\right)/\sqrt{2},\\
-\ket{+} = \cos\gamma \ket{xy} + \sin\gamma \ket{B},\\
-\ket{-} = \sin\gamma \ket{xy} - \cos\gamma \ket{B},\\
-\tan2\gamma = \sqrt{8}g/(E_{xy}-E_{yz}+\lambda),
-\end{gather}
-at 
-energies
-\begin{gather}
-E_{\pm} = \frac{E_{xy}+E_{yz}-\lambda}{2}  \pm \frac{1}{2}\sqrt{(E_{xy}-E_{yz}+\lambda)^2 + 8g^2 }.
-%\delta = E_{xy}-e_z+\lambda.
-\end{gather}
-
-Since we are only interested in small tilt and rotation,
-an expansion of the matrix elements of the Hamiltonian about 
-%${\alpha=0=\beta}$
-${\alpha,\beta=0}$
-%${(\alpha,\beta)=(0,0)}$
-to the leading order turns out to be quite good an approximation.
-The matrix elements in this case simplify a lot.
-Defining a vector ${Q = \left( q_A D_2, q_A D_4, q_B D_2,q_B D_4  \right)}$,
- we can write them as
-\begin{align}
-E_{xy}=& Q.
-\left(-\frac{64 \alpha ^2}{63 \sqrt{3}},-\frac{512 \left(15 \alpha ^2+7\right)}{1701 \sqrt{3}},\frac{3\alpha ^2}{7} ,\frac{5 \alpha ^2}{7}+\frac{2}{3}\right),\\
-E_{yz}=& Q.
-\left(\frac{32 \alpha ^2}{63 \sqrt{3}},\frac{512 \left(25 \alpha ^2-7\right)}{1701 \sqrt{3}},-\frac{3 \alpha ^2}{14},-\frac{85 \alpha ^2}{42}+\frac{2}{3}\right),\\
-g=& Q.
-\left(-\frac{80}{63} \sqrt{\frac{2}{3}} \alpha ^3,0,\frac{15 \alpha ^3}{14 \sqrt{2}},\frac{5 \alpha ^3}{2 \sqrt{2}}\right),\\
-\lambda=& Q.
-\left(\frac{64 \alpha ^2}{63 \sqrt{3}},-\frac{2560 \alpha ^2}{1701 \sqrt{3}},-\frac{3 \alpha ^2}{7},\frac{40 \alpha ^2}{21}\right).
-%E_0=& Q.\left(-\frac{16 \alpha ^2}{21 \sqrt{3}},\frac{256 \left(15 \alpha ^2-14\right)}{1701 \sqrt{3}},\frac{9 \alpha ^2}{28},\frac{2}{3}-\frac{45 \alpha ^2}{28}\right),
-%Q =& \left( q_A D_2, q_A D_4, q_B D_2,q_B D_4     \right).
-%E_0(0,0)=& Q.
-%\frac{1}{2} \left(\frac{4 \text{D4} \text{qB}}{3}-\frac{1024 \text{D4} \text{qA}}{243 \sqrt{3}}\right)
-\end{align}
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-alpha-beta-0-width-row-character}
-\includegraphics[width=1.0\linewidth]{energy-vs-alpha-beta-0-width-row-character}
-\caption{
-Splitting and mixing in $t_{2g}$ manifold induced by octahedral tilting.
-(a-c) 
-$E_D, E_{\pm}$ and $E_0^{t_{2g}}$
-as a function of $\alpha$
-at 
-$\beta=0$;
-other parameters are the same as in Fig.~\ref{fig:t2g-alpha0}.
-(d-f) Weight $W_{xy}$ of $xy$ orbital in 
-$\ket{E_{\pm}}$ states 
-shown in (a-c).
-The $xy$ orbital predominantly
-contributes to 
-$\ket{E_{+}}$
-at $q_A/q_o=1/2,1$ (a,b,d,e), 
-but to   
-$\ket{E_{-}}$
-at $q_A/q_o=2$ (c,f).
-}
-\label{fig:t2g-beta0}
-\end{center}
-\end{figure}
-
-$E_D, E_{\pm}$ relative to their average
-and the weight of $xy$ state $W_{xy}$ in $E_{\pm}$,
-as a function of $\alpha$ at $q_A/q_o=1/2,1,2$ (and $\Delta_o=4q_o/15a$)
-are shown in Fig.~\ref{fig:t2g-beta0}.
-The average shifts slightly with $\alpha,q_A$ by 
-$E_0^{t_{2g}}= \left(E_{xy} + 2 E_{yz}\right)/3-(2/5)f_{q_A}\Delta_{o}$,
-again reflecting 
-a change in the gap $\Delta$,
-and is also included in Fig.~\ref{fig:t2g-beta0}.
-Apart from the mixing between the three states $xy,yz,zx$ in $\ket{\pm}$ at finite $\alpha$, 
-Fig.~\ref{fig:t2g-beta0} shows a similar trend as in Fig.~\ref{fig:t2g-alpha0}
-but with an interesting twist.
-%Fig.~\ref{fig:evals-alpha} reveals another interesting point.
-In contrast to $\alpha=0$ case discussed in the previous section,
-$W_{xy}$ is the largest in the highest (lowest) energy state at small (large) $q_A/q_o$,
-as shown in Fig.~\ref{fig:t2g-beta0}(a,c).
-$\alpha$ and $\beta$ would thus tend to produce different ordering
-(details in the next section).
-The splittings are also about the same magnitude, between $4$-$6\%$ at $\alpha=15^\circ$
-at $q_A/q_o=1/2,2$ [Fig.~\ref{fig:t2g-beta0}(a,c)] and about $2\%$ at $q_A/q_o=1$ [Fig.~\ref{fig:t2g-beta0}(b)].
-The mixing is sizeable but still far from perfect ($50/50\%$) even at the largest $\alpha$ shown ($W_{xy}=0.25$-$0.35$ at $\alpha=20^\circ$).
-% At unrealistically large $\alpha\sim30-40^\circ$, 
-Overall, at finite $\alpha$,
-the lowest energy state is either purely $xy/yz$,
-or contains at least some fraction of these,
-but it is never pure $xy$.
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-vs-beta-alpha-10-width-row-beta-0-15}
-\includegraphics[width=1.0\linewidth]{energy-vs-beta-alpha-10-width-row-beta-0-15}
-\caption{
-Splitting in $t_{2g}$ manifold due to octahedral rotation and tilting.
-$t_{2g}$ energies as a function of $\beta$ at $\alpha=10^\circ$
-at the same values of other parameters as in Figs.~\ref{fig:t2g-alpha0},\ref{fig:t2g-beta0}.
-There are two anticrossings between the three states around $\beta\sim\alpha$.
-The character of the states depends on 
-the competition between the two angles and 
-the two ion cages.
-}
-\label{fig:t2g-ge-Es}
-\end{center}
-\end{figure}
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
-\includegraphics[width=1.0\linewidth]{wts-energy-vs-beta-alpha-10-width-row-beta-0-15}
-\caption{
-The dependence of the character of the $t_{2g}$ states
-on the competitions between
-$\alpha,\beta$ and 
-A,B ion cages.
-Weights of the three $t_{2g}$ orbitals in the three 
-$t_{2g}$ eigenstates 
-shown in
-Fig.~\ref{fig:t2g-ge-Es}.
-%(at the same parameters).
-At $q_A=q_o/2$, B cage dominates and
-$\ket{E_1}$ is predominantly $yz,zx$ at $\beta\sim 0\ll\alpha=10^\circ$, but 
-becomes $\sim xy$ at $\beta\gtrsim10^\circ$ (a).
-The situation flips when A cage dominates at $q_A=2q_o$ (d).
-Similarly, the character of $\ket{E_3}$ at 
-$q_A=q_o/2$
-resembles 
-that of $\ket{E_1}$ at $q_A=2q_o$  [compare (c) with (d)], and vice versa [compare (f) with (a)].
-The character of the middle state $\ket{E_2}$ (b,e)
-becomes $\sim xy$ only around the ``resonance'' region
-$\beta\sim \alpha$.
-}
-\label{fig:t2g-ge-wts}
-\end{center}
-\end{figure}
-
-\subsubsection{Rotation and tilting: $\alpha,\beta\neq 0$}
-\label{sec:t2g-gen}
-
-The $t_{2g}$ Hamiltonian in the general case $\alpha,\beta\neq 0$ cannot be solved analytically
- so there is no longer any advantage of ignoring the coupling between 
- the $e_{g}$ and $t_{2g}$ manifolds.
-Even though their effect should be negligible due to a large gap $\Delta$ between the two manifolds,
-here we keep these couplings 
-and numerically solve
-the full Hamiltonian.
-Figure~\ref{fig:t2g-ge-Es}
-shows the energies at $\alpha=10^\circ$
-as a function of $\beta$
-at $q_A/q_o=1/2,2$ and $\Delta_o=4q_o/15a$ again.
-All states in the $t_{2g}$ mix up to make the eigenstates $\{\ket{E_i}\}$
-at energies $\{E_i\}, i=1,2,3$.
-%\az{E0, can we show E0 only in the first fig and not all of them?}
-At $\beta=0$, these results correspond to $\alpha=10^\circ$ 
-in Figs.~\ref{fig:t2g-beta0}(a,c),
-so the lowest state at $\beta=0$
-here is $\ket{D}$ in Fig.~\ref{fig:t2g-ge-Es}(a)
-while it is the highest in Fig.~\ref{fig:t2g-ge-Es}(b).
-We see two anticrossings or level repulsion in either of Figs.~\ref{fig:t2g-ge-Es}(a,b)
-in different orders.
-In Fig.~\ref{fig:t2g-ge-Es}(a), 
-the anticorssing between the highest two states occurs at smaller $\beta$,
-while the situation is the opposite in Fig.~\ref{fig:t2g-ge-Es}(b) where 
-it occurs between the lowest pair at smaller $\beta$.
-From the results in the previous two sections,
-we know that not only A and B but also $\alpha$ and $\beta$ tend to establish different orders.
-To get more insight, the weights of these three $t_{2g}$ states in the three eigenstates 
-% in Fig.~\ref{fig:t2g-ge-Es}
-are shown in Fig.~\ref{fig:t2g-ge-wts}.
-Let us first focus on the left column ($q_A/q_o=1/2$). 
-Fig.~\ref{fig:t2g-ge-wts}(a)
-shows that, while $\ket{E_1}\to \ket{D}$ as $\beta\to 0$,
-$\ket{E_1}$ practically stays in $yz,xz$ subspace
-for $\beta<7^\circ$ and it quickly becomes $xy$
-as $\beta\to\alpha=10^\circ$.
-Figs.~\ref{fig:t2g-ge-wts}(b,c)
-show a complimentary behaviour 
-between $xy$ and $yz,xz$,
-where $\ket{E_3}$
-transforms from almost pure $xy$ at $\beta=0$
-to almost complete $yz,xz$ at $\beta\gtrsim\alpha=10^\circ$.
-The right column
-in Fig.~\ref{fig:t2g-ge-wts} ($q_A/q_o=2$),
-shows the opposite behaviour 
-about the ``resonance'' $\beta\sim\alpha$.
-Figs.~\ref{fig:t2g-ge-wts}(b,e)
-show an interesting aspect,
-the $W_{xy}$ peaking in the middle state $\ket{E_2}$
-before it is transferred between $\ket{E_1}$ and $\ket{E_2}$
-around $\beta\sim\alpha$,
-i.e., at $\beta$
-between the two anticrossings in 
-Fig.~\ref{fig:t2g-ge-Es},
-which makes sense if we imagine the continuation of various energy surfaces/curves
-in 
-the spectra in Fig.~\ref{fig:t2g-ge-Es}
-ignoring their anticorssings:
-$xy$ starts from the top and goes down in 
-Fig.~\ref{fig:t2g-ge-Es}(a),
-while it starts from the bottom and goes up
-in Fig.~\ref{fig:t2g-ge-Es}(b).
-
-\com{
-Summarise t2g results here.\\
-copy from summary section...??
-tilt vs rotation, preference:\\
- }
-
-In a given material,
-assuming
-the charges on A and B are fixed
-and either A or B dominates,
-one type of distortion 
-would be energetically preferred
-over the other
-for certain
-numbers of electrons in 
-the $d$-orbitals of the Jahn-Teller ion B.
-For example,
-if B cage dominates,
-a $d^2$ configuration
-should prefer tilting over rotation
-because it stabilises two occupied orbitals 
-while rotation stabilises one and destabilises the other occupied orbital.
-
-\subsection{$e_{g}$ manifold}
-\label{sec:eg-gen}
-
-\com{
-So we consider the general case of
-
-both theta phi couples the two states..... expressions relatively longer, but, can be approximated by simpler expressions obtained by an expansion about zero angles....
-
-simpler expressions of eigenstates and eigenvalues.... in terms of D2 and D4 terms of A and B.
-
-presentation and discussion of eg splitting...
-combined plots for the three cases w.r.t  angles... as three  rows
-and two q values on the opposite side of the crossover...
-so 2x3 panel figure.
-}
-
-Since $e_{g}$ has only two states,
-we can always analytically diagonalise it
-if we
-ignore its coupling to the $t_{2g}$ states.
-The expressions for the
-matrix elements of the Hamiltonian are long however,
-so we present the expansion at small angles in the following.
-The diagonal terms with reference to the average $e_g$ energy are given by
-\begin{align}
-\label{eq:eg-hiix}
-(H_{x^2-y^2},&H_{z^2}) = (1,-1)
-\left[\frac{}{} \Omega_{2}  D_2 + \Omega_4 D_4\right],\\
-\Omega_{l} =&  \left(q_A \Omega_{l}^A + q_B\Omega_{l}^B\right)/a,~(l=2,4),\\
-\Omega_{2}^A =&  -\frac{64 \left(\alpha ^2 \left(7 \beta ^2+3\right)-6 \beta ^2\right)}{189 \sqrt{3}},\\
-\Omega_{4}^A =& \frac{640 \left(\alpha ^2 \left(\beta ^2+16\right)-32 \beta ^2\right)}{1701 \sqrt{3}},\\
-\Omega_{2}^B =&  \frac{3}{14} \left(\alpha ^2 \left(3 \beta ^2+2\right)-4 \beta ^2\right),\\
-\Omega_{4}^B =& -\frac{5}{168}\left(\alpha ^2 \left(37 \beta ^2+46\right)-92 \beta ^2\right),
-\end{align}
-whereas the coupling between the two states is,
-\begin{align}
-\nonumber
-H_{x^2-y^2,z^2}=
-\frac{2\alpha ^2 \beta}{567} 
-&\left(\frac{}{}128 q_A (3 D_2-20 D_4) \right. \\ \label{eq:eg-hijx}
-&~~\left. - 81 \sqrt{3} q_B (2 D_2 -5 D_4)\right),
-%&=\frac{2\alpha ^2 \beta}{567} \left(384 ( D_2-\frac{20}{3} D_4)q_A  - 162 \sqrt{3} (D_2 -\frac{5}{2} D_4)q_B \right)
-\end{align}
-which vanishes if 
-either of $\alpha,\beta$ is zero.
-
-%Similar to the $t_{2g}$ case, 
-The average energy slightly shifts at nonzero $\alpha,\beta$
-from $3/5\Delta$ by an amount
-\begin{align}
-\label{eq:eg-E0}
-E_0^{e_{g}} &= \left(q_A E_0^A +q_B E_0^B\right)D_4/a - (3/5)f_{q_A}\Delta_o,\\
-E_0^A &=
-\frac{256 \left(5 \left(4 \beta ^2+1\right) \alpha ^2+5 \beta ^2-3\right)}{243 \sqrt{3}},\\
-E_0^B &=
--\frac{1}{12} 5 \left(7 \beta ^2+4\right) \alpha ^2-\frac{5 \beta ^2}{3}+1.
-\end{align}
-
-% important, dont delete: H_{x^2-y^2,z^2} in terms of \Lambda_{l}^A/B
-% where \Lambda_{l}^A/B are approximated upto second order in alpha beta.  
-\com{
-\begin{align}
-H_{x^2-y^2,z^2}&=
-\left[\frac{}{} \Lambda_{2}  D_2 + \Lambda_4 D_4\right],\\
-\Lambda_{l} =&  \left(q_A \Lambda_{l}^A + q_B\Lambda_{l}^B\right)/a,~(l=2,4),\\
-\Lambda_{2}^A =&
-\frac{256 \alpha ^2 \beta }{189},\\
-\Lambda_{4}^A =&
--\frac{1}{567} \left(5120 \alpha ^2 \beta \right),\\
-\Lambda_{2}^B =&\frac{1}{7} (-4) \sqrt{3} \alpha ^2 \beta ,\\
-\Lambda_{4}^B =&\frac{10}{7} \sqrt{3} \alpha ^2 \beta
-\end{align}
-}
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/fig-data/energy-wts-eg}
-\includegraphics[width=1.0\linewidth]{energy-wts-eg}
-\caption{
-Energies and characters of $e_g$ states.
-$E_{\pm}$ and $E_0^{e_g}$
-as a function of $\beta$ at $\alpha=10^\circ$, 
-and the same parameters as in Fig.~\ref{fig:t2g-ge-Es}.
-At $q_A=q_o/2$ (a,c) where B cage dominates,
-$\alpha$ tends to make $\ket{E_{+}}$
-more $x^2-y^2$ (see small $\beta$ region),
-while $\beta$ tends to do the opposite 
-(see large $\beta$ region).
-The roles of $\alpha,\beta$ switch
-at $q_A=2q_o$ (b,d), where A cage dominates.
-We see that the splitting is relatively small as compared to $t_{2g}$ manifold.
-Approximate results obtained by a second order expansion of the Hamiltonian given in Eqs.\ref{eq:eg-hiix}-\ref{eq:eg-E0}
-are also shown for comparison.
-}
-\label{fig:e-wts-eg}
-\end{center}
-\end{figure}
-
-Diagonalising the Hamiltonian,
-we obtain two eigenstates $\ket{\pm}$
-at energies $E_{\pm}$.
-We present the results obtained using 
- the exact expressions instead 
-of the expansions in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx}.
-Figure~\ref{fig:e-wts-eg}
-shows $E_{\pm}$ and weights $W_{x^2-y^2}$ of $x^2-y^2$ orbital
-in the two states
-as a function of $\beta$
-at $\alpha=10^\circ$, $\Delta_o=4q_o/15a$,
-and 
-$q_A/q_o=1/2,2$.
-We get the same ordering of orbitals ``with and without $z$''
- as in $t_{2g}$ case,
-i.e.,
-at $q_A/q_o=1/2$,
-$\beta$ tends to lower
-$x^2-y^2$ while $\alpha$ tend to lower $z^2$ orbital,
-as indicated by the behaviour of $W_{x^2-y^2}$,
-which is almost zero in $\ket{E_{-}}$ at $\beta\lesssim 5^\circ$
- ($\ll \alpha=10^\circ$),
-while it approaches unity
-at $\beta\gtrsim \alpha$.
-Similarly, at $q_A/q_o=2$,
-$W_{x^2-y^2}$ shows this behaviour for $\ket{E_{+}}$.
-This is also evident from the signs of the $\Omega_l$
-in \eref{eq:eg-hiix}.
-We see that $l=2$ terms have the same signs as $t_{2g}$ case but 
-$l=4$ terms have switched the signs. 
-Since $D_4$ is much smaller than $D_2$,
-we will still get the same ordering as in $t_{2g}$ case.
-The splitting is much smaller in this case though, only $\sim 0.5\%$ of $\Delta_o$
-at $\beta=10^\circ$ in either case shown.
-To see how well
-the expansions in Eqs.~\ref{eq:eg-hiix},\ref{eq:eg-hijx}
-can approximate the exact results,
-Fig.~\ref{fig:e-wts-eg} includes
-them as thin dotted lines that are collectively labelled Approx.,
- which are almost indistinguishable from the exact results
-at $q_A/q_o=1/2$, but deviate at $q_A/q_o=2$ as their
-``resonance point'' is shifted towards larger $\beta$.
-
-\subsection{Effect of the full lattice}
-\label{sec:FL}
-
-In a crystal, obviously, not only the nearest coordination cages of A,B ions but also
- the other ions (including O) at longer distances
-all have finite contributions to the crystal field and hence the JT effect.
-To see how much our results change when 
-%the potential of 
- the full lattice (FL) is considered instead of just the nearest AB cages,
-we numerically calculate the multipole components of the potential
- of the full lattice by following the recipe in Ref.~\cite{FinnisPRL98,PaxtonPRB08,PaxtonNotes}
-and Ewald summation method~\cite{Ewald1921}.
-To do this, 
-we borrow relevant routines from the tight binding package in Questaal suite~\cite{Questaal} that implements these methods.
-
-\com{First,
-FL does not preserve the cubic symmetry of the potential and the degeneracy of the t2g manifold 
-is slightly lifted at zero rotations, i.e., for a cubic structure.
-However, it is insignificant and we will not discuss it further.
-What's more important is that the
-potential of the full lattice does not change the qualitative picture we resented
-but merely shifts the balance between A and B cages towards smaller $q_A$.
-}
-
-We find that the
-potential of the FL does not change the qualitative picture we presented
-but merely shifts the balance between A and B cages towards smaller $q_A$.
-This can be seen in Fig.~\ref{fig:t2g-lattice}
-where the energies of the $t_{2g}$ states as a function of $q_A/q_o$
-are compared for the two cases
-at $\alpha=0$, $\beta=20^\circ$ (and $\Delta_o=4q_o/15a$).
-In case of AB cages, the crossing of the 
-($xy$ and $yz/zx$)
-energy levels occurs 
-at $q_A/q_o\simeq1.1$,
-whereas the FL moves it to $q_A/q_o\simeq0.3$.
-The slopes of the lines are almost the same in both cases,
-meaning that the splitting due to octahedral rotations 
-would be the same in both cases if $q_A$ is measured 
-from their crossing points.
-The shift towards smaller $q_A$ in case of FL
-can be explained by noting that
-the next coordination cage beyond the first AB cages
-has O ions
-($24$ of them at a distance of $\sqrt{5}a/2$ at $\alpha,\beta=0$) %and $\sqrt{5/2}a$ at $\alpha,\beta=0$),....
-%\az{both of which supports the A cage potential.??? plot and see... }
-that supports A cage
-against the B cage, lowering the value of $q_A$ that balances it
-at the crossing in Fig.~\ref{fig:t2g-lattice}.
-It significantly increases the agreement between the two cases presented
-by moving the crossing point 
-to $q_A/q_o\simeq0.8$ (not shown in Fig.~\ref{fig:t2g-lattice}).
-
-From the above results, we also see that
-a comparison between the rotation induced splittings
- in the two
-cases (FL vs AB cages)
-at a fixed value of $q_A$
-would show an underestimation or an overestimation 
-depending on whether $q_A$ lies to the right or the left side of the 
-middle point of the two crossings.
-Besides, the characters of the eigenstates
-would be in a disagreement at $q_A$
-between the two crossings.
-
-\com{
-Since the qualitative picture stays the same
-in FL case,
-we can 
-think of the effect of the rest of the ions in the lattice
-still in terms of the AB cages by renormalising $q_A$.
-}
-
-\begin{figure}[htbp]
-\begin{center}
-%\includegraphics[width=1.0\linewidth]{/Users/maz/repos/perovskite/calc/analytical-structure-param/full-lattice-potential-tests/full-lattice-vs-AB}
-\includegraphics[width=1.0\linewidth]{full-lattice-vs-AB}
-\caption{
-The effect of the potential of full ionic lattice.
-$t_{2g}$ spectrum computed using the potential of full lattice 
-and that obtained from only nearest AB cages (and the anion octahedron itself)
-are
-shown as a function of $q_A/q_o$ at 
-$\alpha=0,\beta=20^\circ$, $\Delta_o=4q_o/15a$.
-Full lattice only shifts the balance between the two cation cages towards A 
-(i.e, the crossing point, where the two cages balance each other, moves to smaller $q_A$)
-but keeps the qualitative picture the same.
-(The bold black line is nothing but an overlap of two practically degenerate black lines.)
-}
-\label{fig:t2g-lattice}
-\end{center}
-\end{figure}
-
-\section{Summary and Conclusion}
-
-We consider the effects of octahedral rotations and tilting in perovskites
-on the $t_{2g}$ and $e_g$ manifolds of the central transition metal ions.
-We find significant splitting in these levels
-caused by the distortions in the crystal field of nearest A and B ion cages,
-which
-essentially amounts to a 
-Jahn-Teller instability.
-The sign and strength of this effect is 
-determined by
-a competition between the two ion cages.
-%depending on the proportion of charges $q_A,q_B$ on A and B ions.
-The tilt 
-%$\alpha$ 
-and rotation 
-%$\beta$
-also tend to establish different ground states
-%that depends 
-depending
-on which ion cage dominates.
-While the tilting alone can mix $t_{2g}$ states,
-$e_g$ states
-do not mix unless both rotation and tilting are non-zero.
-Despite such mixing, we can see which orbitals are stabilized or destabilized.
-If A cage dominates (i.e., $q_A$ is larger than a critical value),
-%$\alpha$
-tilting lowers
-$xy,x^2-y^2$ orbitals
-and raises $yz,zx,z^2$,
-while 
-%$\beta$
-rotation tends to do the opposite;
-the whole situation reverses if B cage dominates.
-Considering the crystal field of the full lattice 
-only shifts the balance towards A cage
-but does not qualitatively change the results.
-
-\section{Discussion and Outlook}
-\label{sec:discussion}
-
-\com{
-% beside the hardness, the Madelung energy will increase due to an increased repulsion between the two ions that take part in the charge transfer.
-Consider that q1^2+q2^2 with constant that q1+q2=2q=fixed is min when q1=q2=q.
-% so the electronic energy gain will have to fight against both the chem hardness and the Madelung energy.
-Based on our analysis of A and B cages,
-we expect that,
-in case of atomic scale perovskite superlattices
-with cations having different charges in alternating layers,
-the crystal field at B sites will bear the exact same deformation as in case of 
-a tetragonal distortion of the octahedra,
-and should lead to 
-a JT like splitting even 
-in the symmetric structure, i.e., with no structural distortion.
-Considering the charge as a dynamic variable,
-it should then also be possible that in 
-simple perovskites structure,
-the system might encounter charge instabilities similar to the structural ones,
-where the system is stabilised by a charge transfer from one site to another
-that lowers the electronic energy and costs 
-the ``elastic'' energy proportional to the chemical hardness of the ions involved.
-Such considerations might be useful in studying polaron formation and dynamics.
-}
-
-% orbital ordering
-We have only focused on the spectrum of 
-the B ion at 
-%position ${(0,0,0)}$
-$\textbf{a}/2$
- in the cell 
-described in Sec.~\ref{sec:structure}
-but 
-there are three more \emph{distinct} B ions in the unit cell 
-at finite octahedral rotations that also 
-need to be considered simultaneously.
-We find that the splittings in the spectra
-of all B ions are
-practically identical.
-However, their eigenstates 
-are different in a way that can
-create interesting orbital ordering
-that depends on the tilt and rotation angles,
-unlike what happens in 
-tetragonal Jahn-Teller distortions (elongation and compression) 
-such as seen in KCuF$_3$~\cite{LiechtensteinPRB95}, 
-where the orbital ordering does not depend on the size of the distortion.
-The eigenstates' components in the local bases attached to the octahedra's frame
-also vary between different B sites 
-so the dependence on the rotation and tilt angle is not trivial,
-which is understandable because different B sites in the unit cell have different environments. 
-A detailed study of orbital ordering in this case is out of scope of this manuscript and is left for future work.
-
-Of course, beside the crystal field we consider in our simplistic model,
-in real materials,
- there would be other local effects like
-electronic correlations (Hubbard and Hund's interaction)
-and spin-orbit interaction, 
-as well as band structure effects arising from
-the electron hopping between the B ions.
-The interplay between these and the crystal field (or JT) effect 
-we discussed in this manuscript is also an interesting future work.
-A discussion 
-about the role of 
-electron hopping 
-along with some preliminary results 
-follows.
-
-Assuming the crystal field splitting to be the largest energy scale,
-the orbitals in the $e_g$ and $t_{2g}$ manifolds of B sites are aligned with their respective octahedra.
-The electron hopping between these orbitals that are 
-localized on different B sites 
-%(that creates electronic bands)
-depends on the relative orientation of the orbitals.
-As the octahedra rotate (or tilt),
-the hybridization between the
-neighboring sites
-change,
-modifying
-the electronic bands and associated band energy.
-
-\begin{figure}[htbp]
-\begin{center}
-\includegraphics[width=1.0\linewidth]{hybrid}
-\caption{The effect of electron hopping between B sites.
-(a) Energy of two configurations $t_{2g}^1$ and $e_g^1$
-as a function of $\beta$ when either the crystal field or the hopping is considered alone.
-In the latter case, the energy changes are scaled with the bandwidth $W$.
-(b) Considering both the crystal field and the hopping simultaneously,
-the ratio of the change in energy with rotation $\beta$ at a finite hopping to that in the absence of hopping $E(W)/E(0)$
-as a function of the average bandwidth $W$, 
-for the same two configurations
-$t_{2g}^1$ and $e_g^1$.
-The results of the crystal field model presented in this manuscript 
-hold in the small bandwidth limit where $E(W)/E(0)\sim 1$.
-}
-\label{fig:hybrid}
-\end{center}
-\end{figure}
-
-To shed some light on the 
-role of these band structure effects,
-we consider the nearest neighbor hopping between the B sites
-using the Slater-Koster method~\cite{SlaterPR54}
-and
-calculate the change in the energy of 
-the system
-as the octahedra rotate.
-We do this for three cases: with either the crystal field or the hopping only,
- and with both of these simultaneously.
-%
-Figure~\ref{fig:hybrid}(a)
-shows the change in the energy 
-of two (spinless) configurations $t_{2g}^1$ and $e_g^1$
-as a function of $\beta$ for the first two cases
-for the crystal-field-only (black curves, left y-axis;
-$\alpha=0$, $q=2q_o$, $\Delta_o=4q_o/15a$)
-and for the hopping-only case (red/gray curves, right y-axis).
-We
-use Slater-Koster hopping parameters
-$(t_{\sigma},t_{\pi},t_{\delta})=(0.15,-0.1,0.025)$~eV, 
-% W = \{0.0330745,0.0385869,0.0358307\} Hartree
-% W = {0.900005, 1.05, 0.975004} eV
-%$(t_{\sigma},t_{\pi},t_{\delta})/W= {0.153846, -0.102564, 0.0256409}$
-$a=7$~bohr, $q_o=2$~e,
-and consider only the crystal field of O octahedra that creates
-$t_{2g}$ and $e_g$ manifolds.
-(These parameters produce an average
-bandwidth $W=0.97$~eV for the two manifolds).
-While both $t_{2g}^1$ and $e_g^1$ configurations 
-show a lowering of energy 
-due to
-the crystal field 
-as $\beta$ 
-increases---consistent with the results presented 
-before---the energy of $e_g^1$ increases when only hopping is considered 
-(the effect scales with the hopping parameters or the bandwidth).
-This is due to a reduced hybridization leading to narrower $e_g$ bands.
-In contrast, the energy of $t_{2g}^1$ decreases due to a band widening arising from 
-an enhanced hybridization.
-The crystal field and these band structure effects are not additive however.
-The rotation induced splitting of the $t_{2g}$/$e_g$ manifolds
-arising from the crystal field
-suppresses the effectiveness of the hopping in creating 
-the dispersion in the energy states, 
-and thus reduces the bandwidths and the
-the associated rotation induced energetic changes.
-
-To show the validity regime of our crystal field model 
-presented in this manuscript,
-Fig.~\ref{fig:hybrid}(b)
-presents  
-the ratio of the
- change in the energy 
-at $\beta=20^\circ$ (i.e., the energy difference from the cubic case)
-at finite hopping $E(W)$ to that of our simplistic crystal field model $E(0)$
-as a function of the average bandwidth $W$ of $t_{2g}$ and $e_g$ bands.
-Here we scale the Slater-Koster parameters used for Fig.~\ref{fig:hybrid}(a)
-to tune the bandwidth $W$.
-We see that $E(W)/E(0)$ decreases from unity at $W=0$
-to half its value for $t_{2g}^1$ configuration at $W/\Delta_o\gtrsim0.3$,
-and even becomes negative for $e_g^1$ configuration around 
-$W/\Delta_o\gtrsim0.15$ (showing the dominance of the band structure effects).
-From this analysis, we conclude that the results of our crystal field model 
-hold unambiguously only for narrower bands, $W/\Delta_o\ll1$,
-while a detailed further study is required to understand the interplay of the two effects
-at larger bandwidths.
-
-%\begin{acknowledgements}
-%\end{acknowledgements}
-
-\appendix*
-\section{Computing $V_{lm}$}
-\label{append:multipoles}
-
-Here we describe a method to obtain the multipole components 
-$V_{lm}$ of a potentials $V(\vec r)$ %of $A/B$ ion cages 
-at a position $\vec r$ around a JT ion.
-It is worth noting that this can be done without 
-evaluating the 
-inner products between the spherical harmonics and
-$V(\vec r)$.
-
-Let's consider $V^{A}(\vec r)$ to illustrate the idea. 
-$V^{B}(\vec r)$ and $V^{JT}(\vec r)$ can also be dealt in the same way.
-We like to expand the potentials $V^{A}(\vec r)$
-in spherical harmonics as
-\begin{align}
-\label{eq:ylm_compA}
-V^{A}(\vec r) =& \frac{q_A}{a}\sum_{l,m} V_{lm}^{A} \left(\frac{r}{a}\right)^l Y_{lm}(\hat r),
-\end{align}
-where we have assumed $a$ as a length scale and 
-taken out the factor $q_A/a$ for clarity.
-
-First we calculate
-$V^{A}(\vec r)$
-using the simple textbook formula.
-$V^{A}(\vec r;\alpha,\beta)=q_A\sum_{i}1/|\vec r^A_i-\vec r |$, 
-where $\vec r^A_i$ is the position of $i$-th A ion
-and 
-$\vec r$ is the position of the observation point 
-measured from the JT ion.
-Writing cartesian components of $\vec r$ as
-$\vec r=r(\cos\phi\sin\theta,\sin\theta\sin\phi,\cos\theta)$,
-where $(r,\theta,\phi)$ 
-are the spherical coordinates in the frame of JT ion,
-and expanding 
-${V^{A}(\vec r;\alpha,\beta)}$
-in powers of $r$, 
-we can separate 
-coefficient of $r^l$
-that give degree $l$ components.
-We can then consider each degree $l$ term individually,
-and resolve it in its $(2l+1)$ $m$-components.
-This can be done by 
-expanding such a coefficient of $r^l$
-in powers of $\cos\theta, \cos\phi$ 
-(or $\sin\theta, \sin\phi$) 
-and comparing the terms with a similar expansion of 
-the formal expression on the right side 
-of \eref{eq:ylm_compA}.
-This gives a set of
-linear equations in $\{V_{lm}^{A}\}$ (for a fixed value of $l$)
- that can be easily solved.
-The whole calculation can be performed
- on Mathematica~\cite{Mathematica}
-or a similar software.
-
-\label{Bibliography}
-%\bibliographystyle{apsrev4-1}
-\bibliography{perovskites}
-
 \end{document}

### 2023-12-27 manuscript/referee/reply.tex
revised version, referee reply

@@
 
+\begin{center}
 \textbf{BK14571/Naheed: Jahn-Teller effect with rigid octahedral rotations in perovskites}
+\end{center}
+
+Dear Editor,
+\\
+
+We thank you and the referee for their invaluable insight and comments.
+\\
+
+We have revised our manuscript in response to the referee's comments. 
+We feel that the revised version has been improved significantly, especially due to a discussion of the hopping effects and associated results in newly added Fig.~8.
+\\
+
+A point by point response 
+to the the referee's comments
+along with a description of the changes made is given below at the end.
+\\
+
+We hope that the referee would be satisfied with the revised version and the manuscript would kindly be granted acceptance. 
+\\
+
+Thank you!
+\\
+
+Yours Sincerely,
+\\
+
+The Authors
+\\
+
+\rule[1ex]{\textwidth}{.5pt}
+
+\textbf{Major changes:}
+\begin{itemize}
+\item
+Included a discussion on the hybridization effects at the end of Sec.~VI along with a new figure, Fig.~8. (page 11 in the revised version)
+\end{itemize}
+
+\textbf{Minor changes:}
+\begin{itemize}
+\item 
+Added a comment ``(remember that we take anion charge to be $-q_o$)''
+just above Eq.~(16) on page 4.
+\item
+Rewritten the second half of the first paragraph 
+of Sec.~IV on page 6. Typos corrected.
+\item
+Added to the caption of Fig.~7:
+ ``(The bold black line is nothing but an overlap of two practically degenerate black lines.)''.
+ \item
+ Added labels of A,B cages in Fig.~1(c,d).
+
+ \item 
+References style changed: titles of the journal articles are included.
+\end{itemize}
+\rule[1ex]{\textwidth}{.5pt}
+\\
+
+\textbf{Referee's comments (blue) and our response (black):}
+\\
 
@@
 integrals, can be considered via the Slater-Koster approximation.
-
 Other, more technical comments:
 }
+
+Thanks for your kind and positive opinion,
+and mentioning your concern about the hybridization effects.
+We have done some preliminary calculations 
+including the hopping between the B sites
+and find that they can significantly affect our results when
+the bandwidth of the $t_{2g}$ and $e_g$ bands cannot be ignored in comparison to the crystal field splitting between the two manifolds. 
+This limits the validity of our crystal field model to small bandwidths.
+
+We find that the crystal field and the hopping do not produce additive effects.
+We have included the main idea
+in the discussion section in the revised version
+(Fig.~8 and last three paragraphs of sec.~VI). A brief description of it follows.
+When considered separately, 
+the crystal field (Madelung) effects are scaled with the crystal field splitting
+whereas the hybridization effects are scaled
+with the bandwidth [Fig.~8(a)].
+However,
+when considered simultaneously,
+lifting of the degeneracy due to the crystal field 
+suppresses the energetic changes due to the hybridization effects [Fig.~8(b)].
+A detailed study of the interplay between the two types of effects is left for future work.
 
@@
 tried to make here is that 
-the electronic and elastic energies have different dependence on the distortion (so the optimum structure is distorted).
-For our purpose, it is not important to know the exact form of the elastic energy and whether anharmonic effects would be important or not.
+the electronic and elastic energies have different 
+polynomial dependence on the distortion (so the optimum structure is guaranteed to be distorted).
+For our purpose, it is not important to know the exact form of the elastic energy, and whether the anharmonic effects would be important or not.
 
 To avoid any distraction and confusion,
-we have rewritten the whole paragraph. 
+we have rewritten the paragraph. 
 We now focus
@@
  case of complete coordination cages.
+ Since the two lines are practically degenerate,
+ we did not check if there are other reasons apart from the above symmetry breaking (e.g., some noise from O ions that belong to other octahedra nearby).
 
- To avoid any confusion,
-we have included in the caption:
+We think that, in the manuscript,
+it suffices to simply clearly state that these are two lines
+and leave the 
+above technical details. 
+So, we have included in the caption:
  ``(The bold black line is nothing but an overlap of two practically degenerate black lines.)''.
